---
title: '`r paste0(maxyr, " ", SURVEY, " Bottom Trawl Survey: What Did They Find?") `'
subtitle: '`r paste0("Strait Science:\n", format(min(haul_cruises_vess_maxyr$start_date_cruise), format = "%B %d"), " to ", format(max(haul_cruises_vess_maxyr$end_date_cruise), format = "%B %d, %Y") )  `'
author: 
- affiliation: Resource Assessment & Conservation Engineering Division
  description: Groundfish Assessment Program
  email: Duane.Stevenson@noaa.gov
  name: Duane Stevenson, Emily Markowitz, Liz Dawson, Chris Anderson, Sean Rohan, Nicole Charriere, Jon Richar
csl: "https://raw.githubusercontent.com/citation-style-language/styles/master/apa-no-ampersand.csl"
bibliography: "https://raw.githubusercontent.com/afsc-gap-products/citations/main/cite/bibliography.bib"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
  powerpoint_presentation:
    reference_doc: styles_reference.pptx
    slide_level : 2
---

```{r setup, include=FALSE}
# "`r maxyr` Fisheries Survey: What did they find?"
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  message = FALSE,
  #   dev = "svg",
  fig.width = 12,
  fig.height = 12, 
  fig.cap = FALSE
  # fig.retina = 3
)
```

## Outline

 - Survey overview and area
 - Charter vessels
 - Survey gear
 - Results
   - Bering Sea temperatures/Cold pool
   - Distribution, abundance, and sizes (select species)
   - Special projects
     - Cod tagging
     - Fish condition
     - Harmful algal blooms
     

## Bering Sea Bottom Trawl Surveys

How Often?
 - EBS Annually since 1982; Late May - late July
 - NBS `r text_list(nbsyr) `; August - early September

Goals 
 - Ecosystem monitoring
   - Movement of fishes, crabs, and other seafloor invertebrates
   - Changes in food web
 - Stock assessment
   - Population size, age structure, genetics, etc., of important species
 - Environmental monitoring
   - Water temp, salinity, light, etc.
   - Changes associated with loss of seasonal sea ice

## `r paste0(maxyr, " ", text_list(SRVY1), " bottom trawl survey")`
 
```{r}
str0 <- text_list(paste0("*", stringr::str_to_title(haul_cruises_maxyr$SRVY_long), " bottom trawl survey (", haul_cruises_maxyr$SRVY, "):* \n\n - ", 
haul_cruises_maxyr$yrofsurvey, haul_cruises_maxyr$stndth, " year of survey\n\n - ", 
haul_cruises_maxyr$stations_completed, " of ", haul_cruises_maxyr$stations_avail, " were completed\n - ", 
format(min(haul_cruises_vess_maxyr$start_date_cruise), format = "%B %d"), " to ", format(max(haul_cruises_vess_maxyr$end_date_cruise), format = "%B %d, %Y"), 
sep_last = "\n\n", sep_last2 = "\n\n", sep = "\n\n"))
```
 
`r str0`

## Survey Charter Vessels

```{r, 'fig-vessels'} 
nickname <- 'fig-vessels'
no_cap <- TRUE

temp <- haul_cruises_vess %>%
  dplyr::select(vessel_id, vessel_ital, year) %>% 
  dplyr::distinct()
temp <- temp %>% 
  dplyr::filter(vessel_id %in% temp$vessel_id[temp$year == maxyr]) %>% 
  dplyr::arrange(desc(year)) %>% 
  dplyr::group_by(vessel_id) %>% 
  dplyr::summarise(n_year = n(), 
                   max_year = max(year, na.rm = TRUE), 
                   min_year = min(year, na.rm = TRUE)) %>% 
  dplyr::mutate(nth = stndth(n_year))
```


```{r fig-vessels-child, child = paste0(dir_code, \"_child_report_figtab.Rmd\")}
```


```{r figtab, echo=FALSE, results='asis'}
list_fig <- list.files(path = dir_out_figtab, pattern = "-pres.png", full.names = FALSE, recursive = FALSE)
list_fig <- gsub(pattern = ".png", replacement = "", x = list_fig)
# list_fig <- list_fig[!grepl(x = list_fig, pattern = "temperature")]

nickname1 <- c("fig-survey-points", 
               "fig-survey-sample-stations", 
               "fig-vessels",
               "fig-trawl-gear-alt",
               "fig-cold-pool-area",
               "fig-mean-temperature",
               "fig-ptpres-temperature-bt",
               "fig-ptpres-temperature-st",
               "tab-ptpres-length-samples",
               "tab-ptpres-age-samples",
               sort(list_fig),
               "tab-biomass-pchange-ptpres",
               "tab-ptpres-special-projects"
               )

# for (i in 1:length(nickname1)) {
#   print(paste0(i, ": ", length(list.files(path = dir_out_figtab, pattern = nickname1))>0))
# }

nickname_text <- nickname1
str0 <- c("fig-", 
          "tab-", 
          "-ptpres", 
          "ptpres-", 
          # " distribution" = "-dist", 
          # "distribution " = "dist-", 
          "length measurements" = "length", 
          "age structures" = "age",
          "sizecomp " = "sizecomp-", 
          "estimates " = "est-", 
          "fish-", 
          "invert-",
          "-data", 
          "-comm", 
          "Environmental summary " = "env-", 
          "Biomass summary " = "bio-", 
          " (CPUE kg/km^2^)" = "-wt", 
          " (CPUE no./km^2^)" = "-num",
          " " = "-", 
          "Alaska" = "alaska", 
          "Bering" = "bering", 
          "Arctic" = "arctic", 
          "Pacific" = "pacific", 
          "major taxa" = "majortaxa", 
          "percent change" = "pchange", 
          "otolith" = "oto", 
          "surface temperature" = "temperature st", 
          "bottom temperature" = "temperature bt", 
          " " = " alt", 
          "Bottom Temperature" = "temperature bt", 
          "Surface Temperature" = "temperature st")

for (i in 1:length(str0)){
  nickname_text <- gsub(pattern = str0[i], replacement = names(str0)[i], x = nickname_text)
}

nickname_text <- paste0(toupper(substr(x = nickname_text, start = 1, stop = 1)), 
                        (substr(x = nickname_text, start = 2, stop = nchar(nickname_text))) )
nickname_text <- gsub(pattern = "[0-9]+", replacement = "", x = nickname_text)
nickname_text <- trimws(nickname_text)

src <- c()
for (ii in 1:length(nickname1)) {
  # print(ii)
  src[[ii]] <- paste0("
## ", nickname_text[ii], "
\n```{r, '", nickname1[ii],"'} 
nickname <- '", nickname1[ii],"'
no_cap <- TRUE
\n```

\n```{r ", nickname1[ii],"-child, child = paste0(dir_code, \"_child_report_figtab.Rmd\")}\n```
")
}
res = knitr::knit_child(text = unlist(src), quiet = TRUE)
cat(res, sep = '\n')
```

## Data documentation

[Documentation of our production data, data prepared for AKFIN and FOSS and other data products is avaialble on the GAP_PRODUCTS GitHub repository: https://afsc-gap-products.github.io/gap_products/

*Please consider this resource to be a Living Document. The code in this repository is regularly being updated and improved. Please refer to releases for finalized products and project milestones.*

## Access our data

These data will soon be available to the public!

 - *Learn about our data products:* https://afsc-gap-products.github.io/gap_products/
 - *Historical survey catch data (FOSS):* https://www.fisheries.noaa.gov/foss/f?p=215:28
 - *Mapping of survey catch data (DisMAP):* https://apps-st.fisheries.noaa.gov/dismap/
 - *Request data from us:* https://github.com/afsc-gap-products/data-requests; afsc.gap.metadata@noaa.gov

## Thank you!

*Duane Stevenson (afsc.gap.metadata@noaa.gov and Duane.Stevenson@noaa.gov)*

Alaska Fisheries Science Center (AFSC)

National Oceanic and Atmospheric Administration (NOAA)

Resource Assessment and Conservation Engineering Division (RACE)

Groundfish Assessment Program (GAP)

7600 Sand Point Way, N.E. bldg. 4

Seattle, WA 98115 USA

https://www.fisheries.noaa.gov/alaska/science-data/groundfish-assessment-program-bottom-trawl-surveys

