
# Introduction{#introduction}

```{r intro-dates-surveyed}
str00 <- ""
if (sum(haul_cruises_maxyr$srvy %in% "EBS")>0) {
  str00 <- paste0(str00, 
                  'The eastern Bering Sea shelf survey has occurred annually ', 
                  ifelse(maxyr>2020, '(except in 2020 due to the COVID-19 pandemic) ', ''),
                  'since 1982 and is the longest-running, standardized time series of fish and invertebrate data in the region [@RN976]. ')
}

if (sum(haul_cruises_maxyr$srvy %in% "NBS")>0) {
  temp2 <- cruises %>% 
    dplyr::filter(srvy == "NBS" & year >= 2010 & 
                    year != maxyr) %>% 
    dplyr::select(year, srvy) %>% 
    unique() %>% 
    dplyr::select(year) %>% 
    dplyr::arrange(year) %>%
    unlist()
  str00 <- paste0(str00,
                  'The standardized northern Bering Sea shelf survey [@RN909] has only been conducted in ',text_list(temp2),'. ')
}

temp <- haul_cruises_maxyr %>% 
  dplyr::mutate(survey_name = tolower(survey_name), 
                survey_name = 
                  gsub(pattern = "eastern bering sea crab/groundfish", 
                       replacement = paste0("eastern Bering Sea groundfish and shellfish"), 
                       x = survey_name), 
                survey_name = 
                  gsub(pattern = "northern bering sea ", 
                       replacement = paste0("northern Bering Sea "), 
                       x = survey_name))

str0 <- gsub(pattern = " ,", replacement = ",", 
             x = text_list(paste0(temp$yrofsurvey, 
                                  temp$stndth, " ", temp$survey_name, " from ", 
                                  temp$start_mo_long, " to ", temp$end_mo_long, " ", maxyr), 
                           sep_last = ", as well as the "))
```

In `r maxyr`, the Resource Assessment and Conservation Engineering (RACE) Division of the National Marine Fisheries Service's (NMFS') Alaska Fisheries Science Center (AFSC) conducted the `r str0`. The survey`r plural_surveys` collect`r ifelse(length(srvy1)>1, "", "s")` information about fish and invertebrate populations and environmental conditions to support fisheries stock assessment and management. `r str00``r paste0(readLines(con = paste0(dir_out_rawdata, "/0-introduction.Rmd")), collapse = "") ` 

The data collected during the survey`r plural_surveys` are vital for managing fisheries resources and ecosystem monitoring. Fishery-independent abundance estimates, in addition to other biological and oceanographic information collected, are used by the AFSC, the North Pacific Fishery Management Council (NPFMC), and the Alaska Department of Fish and Game (ADF&G). These organizations use the survey data products to manage groundfish and crab stocks and conduct ecosystem forecast modeling, which are requirements of the Bering Sea and Aleutian Island (BSAI) Fishery Management Plan (FMP) established under the Magnuson-Stevens Fishery Conservation and Management Act^[https://www.fisheries.noaa.gov/topic/laws-policies].

The most recent modeling results on the status of these commercial groundfish^[https://www.fisheries.noaa.gov/alaska/population-assessments/north-pacific-groundfish-stock-assessments-and-fishery-evaluation] and crab^[https://www.npfmc.org/about-the-council/plan-teams/bsai-crab-planning-team/ and https://www.npfmc.org/library/safe-reports/] stocks are reported in the annual Stock Assessment and Fishery Evaluation report prepared by the NPFMC. Detailed information on bottom trawl survey results for commercial crab species, including Tanner crab (*Chionoecetes bairdi*), snow crab (*Chionoecetes opilio*), red king crab (*Paralithodes camtschaticus*), blue king crab (*Paralithodes platypus*), and hair crab (*Erimacrus isenbeckii*) are discussed and analyzed separately in the AFSC Shellfish Assessment Program's annual data report [@SAPcrab`r maxyr`]. Commercial crab stocks are managed by the ADF&G with federal oversight by NMFS. 

This technical memorandum compares results from the `r maxyr` survey with results from the prior year's survey`r plural_surveys` in the same region`r plural_surveys` [`r ref_compareyr`]. `r ifelse(plural_surveys == "s", paste0("Specifically, ", text_list(paste0("the ", maxyr, " ", srvy11, " survey results are compared with those from the ", compareyr, " ", srvy11, " bottom trawl survey."))), "")`Technical memoranda reporting past survey data can be found on the NOAA^[https://repository.library.noaa.gov/] and AFSC websites^[https://www.fisheries.noaa.gov/resource/publication-database/alaska-fisheries-science-center-technical-memorandums and https://www.fisheries.noaa.gov/alaska/science-data/groundfish-assessment-program-bottom-trawl-surveys].

## History of Bering Sea Shelf Bottom Trawl Surveys{#history}

```{r intro-history-text, child=paste0(dir_out_rawdata, "/0-history.Rmd")}
```

```{r fig-survey-sample-stations0}
nickname <- "fig-survey-sample-stations" # Fig. \@ref(fig:fig-survey-sample-stations)
```

```{r fig-survey-sample-stations0-child, child = paste0(dir_code, "_child_report_figtab.Rmd")}
```

```{r fig-survey-grid0}
nickname <- "fig-survey-grid" # Fig. \@ref(fig:fig-survey-grid)
```

```{r fig-survey-grid0-child, child = paste0(dir_code, "_child_report_figtab.Rmd")}
```

