---
output:
  officedown::rdocx_document: 
    pandoc_args: ["--metadata-file=header.yaml"]
    reference_docx: styles_reference.docx
    fig_caption: yes
    df_print: kable
bibliography: "../cite/bibliography.bib"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, error = FALSE, message = FALSE)
```

# Introduction

```{r}
insert2 <- ""
if (sum(haul_cruises_maxyr$SRVY %in% "EBS")>0) {
  insert2 <- paste0(insert2, 
                         'The EBS survey has occurred annually ', 
                    ifelse(maxyr>2020, '(except in 2020 due to the COVID-19 pandemic) ', ''),
                    'since 1982 and is the longest-running timeseries of fish and invertebrate data in the region [@RN976]. ')
}

if (sum(haul_cruises_maxyr$SRVY %in% "NBS")>0) {
  temp2 <- cruises %>% 
    dplyr::filter(SRVY == "NBS" & year >= 2010 & 
                    year != maxyr) %>% 
    dplyr::select(year, SRVY) %>% 
    unique() %>% 
    dplyr::select(year) %>% 
    unlist()
  insert2 <- paste0(insert2,
                         'The NBS survey has only been conducted previously in ',NMFSReports::text_list(temp2),' [@RN909]. ')
}

# insert <- readtext(file = paste0(dir_out_rawdata, "/doc_abstract_conclusion.docx"))
insert <- readtext2(file = paste0(dir_out_rawdata, "/0_introduction.docx"), 
                    refcontent = refcontent)
```

 
In `r maxyr`, the RACE Division of NMFS' AFSC conducted `r text_list(paste0('the ', haul_cruises_maxyr$yrofsurvey, haul_cruises_maxyr$stndth, " " , haul_cruises_maxyr$SRVY," shelf bottom trawl survey"))`. `r insert2` `r insert`

In this document, we will compare the 
`r NMFSReports::text_list(x = paste0(maxyr, " ", haul_cruises_maxyr$SRVY, " survey results with those from the ", haul_cruises_maxyr$compareyr, " ", haul_cruises_maxyr$SRVY, " survey"))`. 
`r ifelse(SRVY == "NEBS", paste0("To simplify the results and discussion from here forward, the terms “EBS” and “NBS” will be used to refer to the eastern or northern Bering Sea bottom trawl survey areas, respectively."), "")` For survey results referenced from previous surveys herein, the reader should refer to the AFSC Technical Memoranda cited here.

These mission-critical bottom trawl surveys are vital to managing fisheries resources, monitoring the ecosystem, and providing a valuable data time series for basic fisheries research. Fishery-independent abundance estimates, in addition to other biological and oceanographic information from Bering Sea bottom trawl surveys, are used by the AFSC, North Pacific Fishery Management Council (NPFMC), and the Alaska Department of Fish and Game (ADF&G). These organizations utilize those survey data products to manage groundfish and crab stocks, as well as conduct ecosystem forecast modeling, which are requirements of the Bering Sea and Aleutian Island (BSAI) Fishery Management Plan (FMP) established under the Magnuson-Stevens Fishery Conservation and Management Act. 

Effective management of fisheries resources and a healthy ecosystem are especially important to the Alaska Native communities as a way of life and to the tens of thousands of people who are employed by the Alaska fishing industry, which generates billions of dollars for the U.S. economy.

`r list_figures$fig_sample_grid$res `

`r list_figures$fig_sampled_survey_stations$res `

`r list_figures$fig_vessels$res `

## History of Bering Sea Bottom Trawl Surveys


```{r}
insert <- readtext2(file = paste0(dir_out_rawdata, "/0_history.docx"), 
                    refcontent = refcontent)
```

`r insert`

In this document, we will compare the `r maxyr` `r NMFSReports::text_list(SRVY1)` survey results with those from the `r compareyr` `r NMFSReports::text_list(SRVY1)` survey [`r ref_compareyr`]. For survey results referenced from previous surveys herein, the reader should refer to the AFSC Technical Memoranda cited above.
