
# Introduction{#introduction}

```{r intro-dates-surveyed}
str00 <- ""
if (sum(haul_cruises_maxyr$srvy %in% "EBS")>0) {
  str00 <- paste0(str00, 
                  'The eastern Bering Sea survey has occurred annually since 1982 ', 
                  ifelse(maxyr>2020, '(except in 2020 due to the COVID-19 pandemic) ', ''),
                  'and is the longest-running, standardized time series of fish and invertebrate data in the region [@EBS2016]. ')
}

if (sum(haul_cruises_maxyr$srvy %in% "NBS")>0) {
  temp2 <- cruises|> 
    dplyr::filter(srvy == "NBS" & year >= 2010 & 
                    year != maxyr)|> 
    dplyr::select(year, srvy)|> 
    unique()|> 
    dplyr::select(year)|> 
    dplyr::arrange(year)|>
    unlist()
  str00 <- paste0(str00,
                  'The standardized northern Bering Sea survey [@RN909] has been conducted in ',text_list(temp2),'. ')
}

temp <-  haul_cruises_maxyr |> 
  dplyr::mutate(survey_name = tolower(survey_name), 
                survey_name = gsub(x = survey_name, pattern = "bering sea", replacement = "Bering Sea"), 
                survey_name = gsub(x = survey_name, pattern = "shelf", replacement = "Shelf"), 
                survey_name = gsub(x = survey_name, pattern = "crab/groundfish", replacement = "groundfish and shellfish"))
                # survey_name = 
                #   gsub(pattern = "eastern bering sea crab/groundfish", 
                #        replacement = paste0("eastern Bering Sea groundfish and shellfish"), 
                #        x = survey_name), 
                #   gsub(pattern = "northern bering sea crab/groundfish", 
                #        replacement = paste0("northern Bering Sea groundfish and shellfish"), 
                #        x = survey_name))

str0 <- gsub(pattern = " ,", replacement = ",", 
             x = text_list(paste0(temp$yrofsurvey, 
                                  temp$stndth, " ", temp$survey_name, " from ", 
                                  temp$start_mo_long, " to ", temp$end_mo_long, " ", maxyr), 
                           sep_last = ", as well as the "))
```

In `r maxyr`, the Resource Assessment and Conservation Engineering (RACE) Division of the National Marine Fisheries Service's (NMFS') Alaska Fisheries Science Center (AFSC) conducted the `r str0`. The survey`r plural_surveys` collect`r ifelse(length(srvy1)>1, "", "s")` information about fish and invertebrate populations and environmental conditions to support fisheries stock assessment and management. `r str00``r paste0(readLines(con = paste0(dir_out_rawdata, "/0-introduction.Rmd")), collapse = "") ` 

Data collected during these survey`r plural_surveys` are vital for managing fisheries resources and ecosystem monitoring. Fishery-independent abundance estimates, in addition to other biological and oceanographic information collected, are used by the AFSC, the North Pacific Fishery Management Council (NPFMC), and the Alaska Department of Fish and Game (ADF&G). These organizations use the survey data products to manage groundfish and crab stocks and conduct ecosystem forecast modeling, which are requirements of the Bering Sea and Aleutian Island (BSAI) Fishery Management Plan (FMP) established under the Magnuson-Stevens Fishery Conservation and Management Act^[https://www.fisheries.noaa.gov/topic/laws-policies].

The most recent modeling results on the status of these commercial groundfish^[https://www.fisheries.noaa.gov/alaska/population-assessments/north-pacific-groundfish-stock-assessments-and-fishery-evaluation] and crab^[https://www.npfmc.org/about-the-council/plan-teams/bsai-crab-planning-team/ and https://www.npfmc.org/library/safe-reports/] stocks are reported in the annual Stock Assessment and Fishery Evaluation report prepared by the NPFMC. Detailed information on bottom trawl survey results for commercial crab species, including Tanner crab (*Chionoecetes bairdi*), snow crab (*Chionoecetes opilio*), red king crab (*Paralithodes camtschaticus*), blue king crab (*Paralithodes platypus*), and hair crab (*Erimacrus isenbeckii*) are discussed and analyzed separately in the AFSC Shellfish Assessment Program's annual data report [@SAPcrab`r maxyr`]. Commercial crab stocks are managed by the ADF&G with federal oversight by NMFS. 

This Technical Memorandum compares results from the `r maxyr` survey with results from the prior year's survey`r plural_surveys` in the same region`r plural_surveys` [`r ref_compareyr`]. `r ifelse(plural_surveys == "s", paste0("Specifically, ", text_list(paste0("the ", maxyr, " ", srvy11, " survey results are compared with those from the ", compareyr, " ", srvy11, " bottom trawl survey")), collapse = " and "), "")`. Technical Memoranda reporting past survey data can be found on the NOAA^[https://repository.library.noaa.gov/] and AFSC websites^[https://www.fisheries.noaa.gov/resource/publication-database/alaska-fisheries-science-center-technical-memorandums and https://www.fisheries.noaa.gov/alaska/science-data/groundfish-assessment-program-bottom-trawl-surveys].

## History of Bering Sea Bottom Trawl Surveys{#history}

Federal government agencies have conducted bottom trawl surveys of the eastern Bering Sea continental shelf since the 1940s. These early surveys were often exploratory efforts to locate commercial fisheries resources [@RN945] and led to the development of a red king crab fishery. Bottom trawl surveys by the United States continued into the 1970s, with private industry involvement, to study the biology, distribution, abundance, and best fishing practices for red king crab [@RN945]. The first large-scale survey of the Bering Sea shelf was conducted in 1975 under contract from the U.S. Bureau of Land Management. The purpose was to collect baseline data for assessing the potential impact of growth in the offshore oil industry on Bering Sea groundfish and crab fishery resources [@RN920]. During the 1975 baseline survey, sampling was conducted across the shelf between the 20 m and 200 m isobaths from the Alaska Peninsula north to approximately 62°N.

In subsequent years, the areal coverage of the annual survey`r plural_surveys` was reduced. However, in 1979, a comprehensive survey of the Bering Sea shelf was undertaken in cooperation with the Japan Fisheries Agency [@RN978]. That survey encompassed the entire region sampled in the 1975 baseline study and included the upper continental slope waters between St. Matthew and St. Lawrence islands.

Following the 1979 survey, annual bottom trawl surveys have resampled the areas and stations established during the 1975 survey, with slight modifications in sampling design in some years. Beginning in 1979 and continuing triennially until 1991, the survey was extended to include the continental slope and the area between St. Matthew and St. Lawrence islands. After a hiatus from 1992 to 1999, due to lack of funding, the Bering Sea slope survey resumed in 2002 as an independent, standardized bottom trawl survey series that was conducted on a quasi-biennial and funding-dependant basis until 2016 [@RN933; @RN898; @RN979].

The current eastern Bering Sea shelf survey design has been used since 1982. This design standardized survey gear [@RN933], collection methods, and timing, in addition to implementing a systematic survey grid design that includes 330 regularly spaced (37.04 square kilometers, km; 20 square nautical miles, nmi) stations (Figs. @ref(fig:fig-survey-sample-stations) and @ref(fig:fig-survey-grid); @RN890). A total of 26 additional “corner stations” were established near both the Pribilof Islands in 1981 and St. Matthew Island in 1983. These stations were placed at the corners of four standard station grids to better sample blue king crab populations in the area.

Two major changes to the total station count have occurred since the survey design was established in 1982. First, beginning in 1987, 20 regularly spaced stations that comprise Strata 82 and 90 (Fig.  @ref(fig:fig-survey-sample-stations)) were added to monitor more northerly distributions of snow crab and walleye pollock, bringing the total eastern Bering Sea station count to from 356 to 376. Annual sampling of the northwestern strata has continued since 1987 because the region encompasses major portions of the commercially exploited Bering Sea groundfish and crab populations that require management actions under the Bering Sea-Aleutian Islands Fisheries Management Plan (BSAI FMP). Second, in the interest of maximizing the efficient use of survey resources, the 26 corner stations established near the Pribilof Islands and St. Matthew Island were discontinued after 2023 following an analysis by @defilippo2023evaluating. The analysis indicated that the removal of these corner stations in high-density sampling areas would lead to negligible impacts on the precision and accuracy of groundfish and crab biomass estimates. The eastern Bering Sea shelf survey area now consists of 350 total stations and no additional high-density sampling areas.

The northern Bering Sea shelf survey was initiated by the AFSC as part of the Loss of Sea Ice (LOSI) Research Plan to monitor long-term climate trends in the transition zone between the temperate waters of the eastern Bering Sea and the Arctic waters of the Chukchi Sea, where climate change can have a significant effect on physical and biological ecosystem processes [@RN900; @RN901; @RN936; @RN932; @RN977]. Although LOSI funding for the northern Bering Sea extension was discontinued after the 2010 northern Bering Sea shelf survey, the survey resumed biennially in 2017 to monitor the effects of changing ocean conditions on fish and crab distributions [@RN923]. The northern Bering Sea shelf survey consists of 144 bottom trawl stations extending the eastern Bering Sea shelf survey grid northward to the Bering Strait and the U.S.-Russia Maritime Boundary, and includes all of Norton Sound and the Chirikov Basin (Fig. @ref(fig:fig-survey-grid)). The standard northern Bering Sea shelf survey was conducted in `r text_list(nbsyr)` [@RN909; @Lauth2019; @2018EBS2022; @2019NEBS2022; @2021NEBS2022; @2022NEBS2023; @2023NEBS]. In 2018, a rapid-response survey was conducted in the northern Bering Sea using a different sampling design than the standard northern Bering Sea shelf survey. Therefore, the survey results from the 2018 northern Bering Sea rapid-response survey are not directly comparable to the results from other standard northern Bering Sea shelf surveys. In 2020, no Bering Sea shelf surveys were conducted due to the COVID-19 pandemic. 



```{r intro-history-text, child=paste0(dir_out_rawdata, "/0-history.Rmd"), eval  = FALSE}
```

```{r fig-survey-sample-stations0}
nickname <- "fig-survey-sample-stations" # Fig. \@ref(fig:fig-survey-sample-stations)
```

```{r fig-survey-sample-stations0-child, child = paste0(dir_code, "_child_report_figtab.Rmd")}
```

```{r fig-survey-grid0}
nickname <- "fig-survey-grid" # Fig. \@ref(fig:fig-survey-grid)
```

```{r fig-survey-grid0-child, child = paste0(dir_code, "_child_report_figtab.Rmd")}
```

