
# Introduction

```{r intro_dates_surveyed}
insert2 <- ""
if (sum(haul_cruises_maxyr$SRVY %in% "EBS")>0) {
  insert2 <- paste0(insert2, 
                         'The EBS survey has occurred annually ', 
                    ifelse(maxyr>2020, '(except in 2020 due to the COVID-19 pandemic) ', ''),
                    'since 1982 and is the longest-running, standardized time series of fish and invertebrate data in the region [@RN976]. ')
}

if (sum(haul_cruises_maxyr$SRVY %in% "NBS")>0) {
  temp2 <- cruises %>% 
    dplyr::filter(SRVY == "NBS" & year >= 2010 & 
                    year != maxyr) %>% 
    dplyr::select(year, SRVY) %>% 
    unique() %>% 
    dplyr::select(year) %>% 
    dplyr::arrange(year) %>%
    unlist()
  insert2 <- paste0(insert2,
                         'The standardized NBS survey [@RN909] has only been conducted previously in ',text_list(temp2),'. ')
}

# insert <- readtext(file = paste0(dir_out_rawdata, "/doc_abstract_conclusion.docx"))
# insert <- readtext2(file = paste0(dir_out_rawdata, "/0_introduction.docx"), 
#                     refcontent = refcontent)
# `r insert`

temp <- haul_cruises_maxyr 
str1 <- gsub(pattern = " ,", replacement = ",", 
             x = text_list(paste0(temp$yrofsurvey, 
                                               temp$stndth, " ", temp$survey_name, " (", temp$SRVY, ") from ", 
                                               temp$start_mo_long, " to ", temp$end_mo_long, " ", maxyr), 
                                        sep_last = ", as well as the "))
```

The purpose of the `r text_list(SRVY1)` shelf bottom trawl survey`r ifelse(SRVY=="NEBS", "s", "")` is to collect information about the fish and invertebrate populations and environmental conditions in the Bering Sea. In `r maxyr`, the Resource Assessment and Conservation Engineering (RACE) Division of National Marine Fisheries Service's (NMFS') Alaska Fisheries Science Center (AFSC) conducted the `r str1`. `r insert2` 

```{r intro_insert_text, child=paste0(dir_out_rawdata, "/0_introduction.Rmd")}
```

The data collected during `r text_list(SRVY1)` bottom trawl surveys are vital for managing fisheries resources and for ecosystem monitoring. Fishery-independent abundance estimates, in addition to other biological and oceanographic information from Bering Sea shelf bottom trawl surveys, are used by the AFSC, North Pacific Fishery Management Council (NPFMC), and the Alaska Department of Fish and Game (ADF&G). These organizations utilize the survey data products to manage groundfish and crab stocks, as well as conduct ecosystem forecast modeling, which are requirements of the Bering Sea and Aleutian Island (BSAI) Fishery Management Plan (FMP) established under the Magnuson-Stevens Fishery Conservation and Management Act (https://www.fisheries.noaa.gov/topic/laws-policies). 


This document compares the `r maxyr` survey with the most similar, recent surveys of the same regions. Specifically, `r text_list(paste0("the ", maxyr, " ", SRVY1, " survey results are compared with those from the ", compareyr, " ", SRVY1, " shelf bottom trawl survey"))` [`r ref_compareyr`]. For data referenced from previous surveys, refer to the AFSC Technical Memoranda cited at the end of the report and listed on the AFSC website ([https://www.fisheries.noaa.gov/resource/publication-database/alaska-fisheries-science-center-technical-memorandums](https://www.fisheries.noaa.gov/resource/publication-database/alaska-fisheries-science-center-technical-memorandums)).

## History of Bering Sea Bottom Trawl Surveys

The Bering Sea continental shelf supports several of the most productive groundfish and crab fisheries in the world [@Fissel2021]. Although many species of groundfish are caught commercially in the Bering Sea, groundfish such as walleye pollock (*Gadus chalcogrammus*), Pacific cod (*Gadus macrocephalus*) and yellowfin sole (*Limanda aspera*) have been the primary targets of commercial fisheries. Walleye pollock is the most abundant of the Bering Sea's commerically harvested species. Catches ranged from 0.8 million metric tons (t) in 2009 to 1.5 million t from 2003-2006 per year over the history of the EBS survey, and the marketed products represented 40% of the global whitefish market [@RN971]. Commercial crab stocks on the Bering Sea shelf include Tanner crab (*Chionoecetes bairdi*), snow crab (*Chionoecetes opilio*), red king crab (*Paralithodes camtschaticus*), blue king crab (*Paralithodes platypus*), and hair crab (*Erimacrus isenbeckii*; @RN956).

The federal government has conducted bottom trawl surveys of the eastern Bering Sea continental shelf since the 1940s. These early surveys were often exploratory efforts to locate commercial fisheries resources [@RN945] and led to the development of a valuable red king crab fishery. Bottom trawl surveys by the U.S. continued into the 1970s with private industry involvement to study the biology, distribution, abundance, and best fishing practices for red king crab [@RN945]. The first large-scale survey of the Bering Sea shelf was conducted in 1975 under contract from the U.S. Bureau of Land Management. The purpose was to collect baseline data for assessing the potential impact of the growth in the offshore oil industry on the development of Bering Sea groundfish and crab fishery resources [@RN920]. During the 1975 baseline survey, sampling was conducted over the shelf between the 20 m and 200 m isobaths from the Alaska Peninsula north to approximately 62°N.

In subsequent years, the areal coverage of the annual survey`r ifelse(SRVY=="NEBS", "s", "")` was reduced. However, in 1979, a comprehensive survey of the Bering Sea shelf was undertaken in cooperation with the Japan Fisheries Agency [@RN978]. That survey encompassed the entire region sampled in the 1975 baseline study and included the upper continental slope waters between St. Matthew and St. Lawrence islands.

Following the 1979 survey, annual bottom trawl surveys have re-sampled the same areas and stations established during the 1975 survey with slight modifications in sampling design in some years. Beginning in 1979 and continuing triennially until 1991, the survey was extended to include bottom trawl sampling of the continental slope and in the region between St. Matthew and St. Lawrence islands. After a hiatus from 1992 to 1999 due to lack of funding, the Bering Sea slope survey was resumed in 2002 as an independent, standardized bottom trawl survey series that has been conducted on a quasi-biennial basis dependent on funding [@RN933; @RN898; @RN979]. The most recent slope survey was conducted in 2016 [@RN979].

```{r intro_history_text, child=paste0(dir_out_rawdata, "/0_history.Rmd")}
```

```{r fig-sampled-survey-stations}
nickname <- "fig-sampled-survey-stations" # Fig. \@ref(fig:fig-sampled-survey-stations)
```

```{r fig-sampled-survey-stations-child, child = paste0(dir_code, "_child_report_figtab.Rmd")}
```

```{r fig-sample-grid}
nickname <- "fig-sample-grid" # Fig. \@ref(fig:fig-sample-grid)
```

```{r fig-sample-grid-child, child = paste0(dir_code, "_child_report_figtab.Rmd")}
```

