---
output:
  word_document:
    pandoc_args: ["--metadata-file=header.yaml"]
    reference_docx: styles_reference.docx
    df_print: kable
csl: "../cite/citestyle.csl"
bibliography: "../cite/bibliography.bib"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, error = FALSE, message = FALSE)
```

# History of Bering Sea Bottom Trawl Surveys

> the figure 2 noted in this paragraph seems more relevant to the intro or results, not history or methods. Moved to intro

```{r}

# a<-dat_cpue %>%
#   dplyr::filter(
#     species_code %in% report_species$fish1$`Walleye pollock` & 
#       survey ==  "EBS") %>% 
#   dplyr::select(cpue_kgha, year) %>% 
#   dplyr::group_by(year) %>% 
#   dplyr::summarise(cpue = sum(cpue_kgha, na.rm = T))

a<-dat_biomass %>%
  dplyr::filter(
    species_code %in% report_species$fish1$`Walleye pollock` & 
      survey ==  "EBS"
  ) %>% 
  dplyr::select(biomass, year) %>% 
  dplyr::group_by(year) %>% 
  dplyr::summarise(biomass = sum(biomass, na.rm = T)) # Already in metric tons

```

> **Can't get these values:** "Although many species of groundfish are caught commercially, walleye pollock is the most abundant with catches ranging from 0.8 million to 1.5 million metric tons (t) per year for the past 30 years"

The Bering Sea continental shelf supports one of the most productive groundfish and crab fisheries in the world [@RN891]. Groundfish such as walleye pollock (*Gadus chalcogrammus*), Pacific cod (*G. macrocephalus*) and yellowfin sole (*Limanda aspera*) have been the primary target species among commercial catches. Although many species of groundfish are caught commercially, walleye pollock is the most abundant with catches ranging from `r  NMFSReports::xunits(min(a$biomass))` to `r NMFSReports::xunits(max(a$biomass))` metric tons (t) per year over the course of the EBS survey, the marketed products of which represent 40% of the global whitefish market [@RN971]. Commercial crab stocks include Tanner crab (*Chionoecetes bairdi*), snow crab (*C. opilio*), red king crab (*Paralithodes camtschaticus*), blue king crab (*P. platypus*), and hair crab (*Erimacrus isenbeckii*) [@RN956].

The involvement of the U.S. government in Bering Sea bottom trawl surveys dates back to the 1940s when the work was exploratory prospecting for commercial fisheries resources [@RN945]. Early efforts led to the development of a valuable single-species fishery in Alaska for red king crab. Bottom trawl surveys by the U.S. continued into the 1970s with private industry involvement to study the biology, distribution, abundance, and best fishing practices for red king crab [@RN945]. The first large-scale systematic survey of the Bering Sea shelf was conducted in 1975 under contract from the U.S. Bureau of Land Management to collect baseline data for assessing the potential impact of the growth in the offshore oil industry on the development of Bering Sea groundfish and crab fishery resources [@RN920]. During the 1975 baseline survey, sampling was conducted over the shelf between the 20-m and 200-m isobaths from the Alaska Peninsula north to approximately 62° N.

In subsequent years, the area coverage of the annual surveys was reduced until 1979 when a comprehensive survey of the Bering Sea shelf was undertaken in cooperation with the Japan Fisheries Agency [@RN978]. That survey encompassed the entire region sampled in the 1975 baseline study and included the upper continental slope waters between St. Matthew and St. Lawrence islands.

Following the 1979 survey, annual bottom trawl surveys have essentially re-sampled the same areas and stations established during the 1975 survey, with slight modifications in sampling design each year. Beginning in 1979 and continuing triennially until 1991, the survey was extended to include bottom trawl sampling of the continental slope and in the region between St. Matthew and St. Lawrence islands. After a hiatus in the Bering Sea slope survey from 1992 to 1999, it was resumed in 2002 as an independent bottom trawl survey series that is now conducted on a quasi-biennial basis dependent on funding [@RN979].

The ongoing annual EBS shelf survey time series officially began in 1982 marked by the standardization of bottom trawl gear [@RN933], survey methods and a systematic design that included 356 stations [@RN891]. Beginning in 1987, 20 new stations comprising Strata 82 and 90 (Figure `r crossref(list_obj = list_figures, nickname = "sampled_survey_stations", sublist = "number") `) were added to monitor more northerly distributions of snow crab and walleye pollock. The reason the BS shelf region continues to be surveyed annually is because it encompasses major portions of the commercially exploited Bering Sea groundfish and crab populations that require management actions under the BSAI FMP.

Following the expansive 1979 effort, annual BT surveys continued in the `r SRVY ` shelf, and a triennial survey was initiated combining the upper continental slope and different parts of the NBS shelf. The spatio-temporal scale, trawl gear and sampling methods of the `r SRVY ` shelf survey lacked consistency until 1982 when they were all standardized to include 356 stations [@RN891]. Beginning in 1987, survey coverage of the `r SRVY ` shelf was expanded northwest to include 20 more stations along the U.S.-Russian Maritime Boundary (Strata 82 and 90; Figure `r crossref(list_obj = list_figures, nickname = "sampled_survey_stations", sublist = "number") `). 

> 2017 or 2010? "In this document, we will compare the 2017 EBS survey results with those from the 2016 EBS survey (Conner and Lauth 2017) as well as with those from the NEBS survey conducted in 2010 (Lauth 2011)."

> Also whwere did this below paragraph come form? it mentions 2018?

The triennial surveys of the NBS and `r SRVY ` slope were discontinued after 1991 due to lack of funding; however, starting in 2000, the slope BT survey resumed on a biennial basis as a new time series using standard AFSC gear and methods [@RN933; @RN898]. In 2010 and 2017, the `r SRVY ` shelf survey grid was extended into the NBS [@RN909]. The 2018 survey extension into the NBS did not employ the same sampling design as 2010 and 2017, and therefore the survey results from the 2018 rapid response NBS survey cannot be compared to the results from the 2010 and 2017 NBS surveys.

> is citing figure 1 dependant on anything in the paragraph below? e.g., in yeras without an NBS survey?

> text had 144 nbs station, but code counts 143. Is that ok?

> need to think about how to automate the first sentance "The most comprehensive bottom trawl survey coverage of the Bering Sea in a single year was in 2010"

The most comprehensive bottom trawl survey coverage of the Bering Sea in a single year was in 2010 when there were three surveys: 1) the continental slope [@RN898], 2) the `r SRVY ` shelf, and 3) the NBS (@RN909; Figure `r crossref(list_obj = list_figures, nickname = "sample_grid", sublist = "number")`). The NBS survey consisted of `r length(akgfmaps::get_survey_stations(select.region = "nbs"))` additional bottom trawl stations extending the `r SRVY ` survey grid northward to the Bering Strait and the U.S.-Russia Maritime Boundary and also included all of Norton Sound and the Chirikov Basin (Figure `r crossref(list_obj = list_figures, nickname = "sample_grid", sublist = "number")`). The NBS survey was initiated by the AFSC as part of the Loss of Sea Ice (LOSI) Research Plan to study the impacts of diminished sea ice on the marine ecosystem [@RN900]. The objective of the LOSI Research Plan was to monitor long-term climate trends in the transition zone between the temperate waters of the eastern Bering Sea and the Arctic waters of the Chukchi Sea where climate change can have a profound effect on physical and biological ecosystem processes [@RN901; @RN936; @RN932; @RN977].

> is the following paragraph dependant on NBS also being surveyed in the report year?

> note to self: hyperlink ocean conditions section?

> "NBS (hereafter, the combined areas will be referred to as the “NEBS”)" should be introduced earlier? Move it. 

LOSI funding of the NBS bottom trawl survey was discontinued the following year but was re-implemented 5 years later with a new budget plan for repeating the survey in 2017 and continuing it on a biennial basis [@RN923]. With the changing environmental conditions in the EBS (see Ocean Conditions section below), it was becoming more critical to obtain an extended time series of snapshots that included both the EBS and NBS (NEBS) for longer-term monitoring of the demersal marine fauna in response to diminishing ice in both the Bering Sea and the Arctic Ocean.



