
# Methods{#methods}

## Survey Area and Sampling Design 

```{r, nbs_area}
nbs_str0 <- ifelse(srvy == "NEBS", 
                   # NBS sampled
                   paste0(" The standardized northern Bering Sea shelf survey consists of a systematic design with 144 fixed sations."), 
                   # EBS only
                   paste0(" The northern Bering Sea shelf survey was not conducted in ", maxyr, "."))
```

The standardized eastern Bering Sea shelf survey consists of a systematic design with 350 fixed sampling stations arranged on a regularly spaced 37.04 × 37.04 km grid (20 × 20 nmi; Fig. \@ref(fig:fig-survey-grid)). In 2024, following analysis by @defilippo2023evaluating, the 26 previously sampled 'corner stations' were removed from the survey grid (see [History of Bering Sea Shelf Bottom Trawl Surveys](#history) section). `r nbs_str0`

## Survey Vessels and Sampling Gear

```{r, vessel_method}
vessels0 <- vessels %>% 
  dplyr::filter(vess_shape != "X")
```

The `r maxyr` `r SURVEY` survey`r plural_surveys` `r ifelse(plural_surveys == "s", "were", "was")` conducted aboard the chartered, commercial stern-trawlers `r text_list(vessels0$vessel_ital)` (Fig. \@ref(fig:fig-vessels)). `r ifelse(nrow(vessels0) == 1, "The vessel", "Both vessels") ` are house-forward trawlers with stern ramps. The overall length of `r text_list(paste0("the ", vessels0$vessel_ital, " is ", vessels0$length_m, " m (", vessels0$length_ft, " ft)") ) `. All fishing operations were conducted in compliance with national and regional protocols detailed in @RN933. Trawl sampling was conducted using 83-112 eastern otter trawls, each with a 25.3 m (83 ft) headrope and 34.1 m (112 ft) footrope (Fig. \@ref(fig:fig-trawl-gear-diagram)). The net was attached to tail chains with 54.9 m (180 ft or 30 fm) paired dandylines. Each lower dandyline had a 0.61 m (2 ft) chain extension connected to the lower wing edge to improve bottom tending. Steel "V" doors measuring 1.8 × 2.7 m (6 × 9 ft) and weighing 816 kg each were used for spreading the net opening while the trawl was fishing on the seafloor.

```{r fig-vessels0}
nickname <- "fig-vessels" # Fig. \@ref(fig:fig-vessels)
```

```{r fig-vessels-child, child = paste0(dir_code, "_child_report_figtab.Rmd")}
```

```{r fig-trawl-gear-diagram0}
nickname <- "fig-trawl-gear-diagram" # Fig. \@ref(fig:fig-trawl-gear)
```

```{r fig-trawl-gear-diagram-child, child = paste0(dir_code, "_child_report_figtab.Rmd")}
```

The Marport Deep Sea Technologies Inc. net mensuration system was used to record net spread and net height. Net spread was measured as the horizontal distance between two sensors attached at wing tips immediately forward of the junction of the upper breastline and the dandyline. Net height was measured from the headrope to the seafloor. Mean net spread values for estimating area swept per tow were calculated according to methods described by @RN910. A customized Onset HOBO Pendant G Data Logger (accelerometer) in custom housing was attached to the center of the footrope and used as a bottom contact sensor in order to determine tow duration based on footrope contact with the seafloor.

Temperature and depth profiles were recorded using a Sea-Bird SBE-39 temperature-depth recorder (Sea-Bird Electronics Inc., Bellevue, WA) attached to the headrope of the trawl. Observations were made at 3-second intervals at each station. Average bottom depth was calculated by adding the average net height to the average depth of the headrope while the net was in contact with the seafloor. 

```{r methods-net-width}
temp <- 
  dplyr::left_join(
    x = vessels %>% 
      dplyr::select(vessel_id, vessel_ital), 
    y = haul_maxyr %>%
      dplyr::select(srvy, haul, vessel_id, net_measured) %>% 
      dplyr::distinct() %>% 
      dplyr::group_by(srvy, vessel_id, net_measured) %>% 
      dplyr::summarize(n = n()) %>% 
      tidyr::pivot_wider(id_cols = c("vessel_id", "srvy"),
                         names_from = "net_measured", 
                         values_from = "n"), 
    by = c("vessel_id")) %>% 
  dplyr::arrange(vessel_ital) %>% 
  dplyr::rename("N" = `0`, "Y" = `1`) %>% 
  dplyr::left_join(y = data.frame(srvy = srvy1, srvy_long = srvy11)) %>% 
  dplyr::filter(!is.na(vessel_id))

str0 <- c()
if (sum(temp$N, na.rm = TRUE)>0) {
  # if (sum(!is.na(temp$vessel_id)) == nrow(temp)) { # if equations were estimated
  for (i in 1:length(unique(temp$srvy))){
    temp0 <- temp %>% 
      dplyr::filter(!is.na(N) & 
                      srvy == unique(temp$srvy)[i])
    str0 <- paste0(str0, 
                   ifelse(plural_surveys == "", "T", paste0("In the ",unique(temp$srvy_long)[i], ", t")),
                   "he net mensuration system failed to record data for ", 
                   text_list(paste0(xunits(temp0$N), " tow", ifelse(temp0$N>1, "s", "")," on the ", temp0$vessel_ital)), ". ")
  }
  
  str0 <- paste0(str0, "To estimate missing net width values, the *mgcv* R package [@RN997] was used to relate mean net width with the inverse scope (m) and mean net height (m) from valid tows following the relationship investigated by @RN921, where $w$ is the net width (m), $h$ is the net height (m), $s$ is the scope, and $\\epsilon$ represents the modeled error

$$ w \\sim {s}^{-1} + h + \\frac{h}{s} + \\epsilon $$

$$ \\epsilon \\sim N(0,\\sigma^{2})  . $$
") 
}
```

`r str0 `

## `r ifelse(plural_surveys == "", "", "Eastern Bering Sea ")`Sampling Logistics and Stratification Scheme

```{r methods-ebs-survey-plan}
str0 <- c()

for (i in 1:length(unique(haul_cruises_maxyr$srvy_long))){
  
  srvy <- unique(haul_cruises_vess_maxyr$srvy)[i]
  cruises_maxyr0  <- haul_cruises_vess_maxyr %>% 
    dplyr::filter(srvy %in% srvy &
                    year %in% maxyr) %>% 
    dplyr::select("year", "survey_name", "vessel_id", "vessel_name", 
                  "vessel_ital", "srvy", "srvy_long", 
                  "start_date_cruise", "end_date_cruise", 
                  "start_date_haul", "end_date_haul") %>% 
    unique() %>% 
    group_by(year, survey_name, vessel_id, vessel_name, 
             vessel_ital, srvy, srvy_long) %>% 
    dplyr::summarise(start_date_cruise = as.Date(min(start_date_cruise)), 
                     end_date_cruise = as.Date(max(end_date_cruise)), 
                     start_date_haul = as.Date(min(start_date_haul), 
                                               format = "%m/%d/%Y"), 
                     end_date_haul = as.Date(max(end_date_haul), 
                                             format = "%m/%d/%Y")) 
  
  temp <- "" 
  
  if (length(unique(cruises_maxyr0$start_date_haul)) != 1 &
      length(unique(cruises_maxyr0$end_date_haul)) != 1) { 
    # 1. vessels started and ended on different dates
    temp <- paste0(temp, 
                   text_list(paste0("the ", cruises_maxyr0$vessel_ital, 
                                    " started sampling on ", 
                                    date_formatter(cruises_maxyr0$start_date_haul), 
                                    ", and ended on ", 
                                    date_formatter(cruises_maxyr0$end_date_haul)
                   )) )
    
  } else if (length(unique(cruises_maxyr0$start_date_haul)) == 1 &
             length(unique(cruises_maxyr0$end_date_haul)) == 1) { 
    # 2. vessels started and ended on the same dates
    temp <- paste0(temp, 
                   text_list(cruises_maxyr0$vessel_ital), 
                   " started sampling on ",
                   date_formatter(unique(cruises_maxyr0$start_date_haul)), 
                   ". Sampling ended on ", 
                   date_formatter(unique(cruises_maxyr0$end_date_haul)) )
    
  } else if (length(unique(cruises_maxyr0$start_date_haul)) == 1 &
             length(unique(cruises_maxyr0$end_date_haul)) != 1) {
    # 3. vessels started on the same dates and ended on different dates
    temp <- paste0(temp, "", 
                   ifelse(length(unique(cruises_maxyr0$vessel_ital)) == 1, 
                          "The vessel", "Both vessels"), 
                   " started sampling on ",
                   date_formatter(unique(cruises_maxyr0$start_date_haul)), 
                   ". Sampling ended ",
                   text_list(paste0("on ", 
                                    date_formatter(unique(cruises_maxyr0$end_date_haul)), 
                                    " for the ", cruises_maxyr0$vessel_ital) ))
    
  } else if (length(unique(cruises_maxyr0$start_date_haul)) != 1 &
             length(unique(cruises_maxyr0$end_date_haul)) == 1) {
    # 4. vessels started on different dates and ended on the same dates
    temp <- paste0(temp, "the sampling started ", 
                   text_list(paste0("on ", 
                                    date_formatter(unique(cruises_maxyr0$start_date_haul)), 
                                    " for the ", cruises_maxyr0$vessel_ital) ), 
                   ". Sampling ended for ", 
                   ifelse(length(unique(cruises_maxyr0$vessel_ital)) == 1, 
                          "the vessel", "both vessels"), 
                   " on ",
                   date_formatter(unique(cruises_maxyr0$end_date_haul))
    )
  }
  str0 = c(str0, temp)
}

str0 <- data.frame(str = str0, 
                   srvy = unique(cruises_maxyr$srvy))
```

Scientists boarded the chartered vessels in Dutch Harbor, Alaska, and transited to eastern Bristol Bay to begin sampling. From Bristol Bay, the survey proceeded westward, completing north-south columns of grid cells to the shelf edge (Fig. \@ref(fig:fig-survey-sample-stations)). The east-to-west survey progression is based on an understanding of historical trends in fish movement and is intended to ensure the survey moves in the opposite direction of the seasonal on-shelf (eastward) migration patterns typical of yellowfin sole and other species. This strategy reduces the likelihood of encountering a portion of these populations multiple times [@RN928; @RN913]. `r str0$str[str0$srvy == "EBS"]`.

```{r methods-ebs-survey-area}
load(file = paste0(dir_out_figtab, "tab-stratum-areas.Rdata"))
temp0 <- obj$raw %>% 
  dplyr::mutate(Region = paste0(srvy, " ", area_name))

temp <- temp0 %>% 
  dplyr::filter(!grepl(pattern = "Total", x = Region) & 
                  grepl(pattern = "EBS", x = Region))

temp1 <- ifelse(srvy == "NEBS", "EBS Total", "Total")

temp_tot <- temp0 %>% 
  dplyr::filter(grepl(pattern = temp1, x = Region) & 
                  grepl(pattern = "EBS", x = Region)) %>% 
  dplyr::select(density)
```

The survey footprint covered bathymetric depths ranging from 20 m to 200 m. For design-based index catch analysis, this footprint was separated into 12 strata by the 50 m and 100 m isobaths and a biogeographic boundary line running from the southwest to the northeast (Fig. \@ref(fig:fig-survey-sample-stations); @1986EBSReport). The stratum boundaries correspond with different oceanographic domains and biological communities [@Coachman1986]. This stratification scheme reflects some differences observed in Bering Sea groundfish distributions across the oceanographic domains and was designed to reduce the variances of population and biomass estimates [@RN891]. Overall sampling density across the eastern Bering Sea shelf was one station per `r xunits(temp_tot$density)` km^2^, and within-stratum sampling density ranged from one station per `r xunits(min(temp$density))` km^2^ (stratum `r temp$stratum[temp$density == min(temp$density)]`) to one per `r xunits(max(temp$density))` km^2^ (stratum `r temp$stratum[temp$density == max(temp$density)]`; Table \@ref(tab:tab-stratum-areas)). For some analyses (e.g., abundance-at-length), strata were combined by depth-region, resulting in eight subareas: 10, 20, 30 (31+32), 40 (41+42+43), 50, 60 (61+62), 82, and 90 (Fig. \@ref(fig:fig-survey-sample-stations); Table \@ref(tab:tab-stratum-areas)).

```{r methods-nbs-survey-plan}
str00 <- ""

if ("NBS" %in% haul_cruises_maxyr$srvy) {
  
  load(file = paste0(dir_out_figtab, "tab-stratum-areas.Rdata"))
  
  temp0 <- obj$raw %>% 
    dplyr::mutate(Region = paste0(srvy, " ", area_name))
  
  temp <- temp0 %>% 
    dplyr::filter(!grepl(pattern = "Total", x = Region) & 
                    grepl(pattern = "NBS", x = Region))
  
  temp_tot <- temp0 %>% 
    dplyr::filter(grepl(pattern = "NBS Total", x = Region) & 
                    !grepl(pattern = " NBS Total", x = Region) & 
                    grepl(pattern = "NBS", x = Region))
  
  str00 <- paste0(
    "After the completion of the eastern Bering Sea shelf survey, both vessels began sampling survey stations in the northern Bering Sea shelf survey region. In the northern Bering Sea, ", 
    str0$str[str0$srvy == "NBS"], # from 2 chunks above! 
    ". After the northern Bering Sea shelf survey was completed, both vessels returned to Dutch Harbor. The northern Bering Sea is divided into three strata: one including the area north of St. Lawrence Island and Norton Sound, and two others south of St. Lawrence Island separated by the 50 m isobath (Fig. \\@ref(fig:fig-survey-sample-stations)). Sampling density was ", 
    # Sampling density was 1,367 km2 /station for Stratum 70, 1,475 km2 /station for Stratum 71, 1,370 km2 /station for Stratum 81, 
    text_list(paste0(xunits(temp$density), " km^2^/station for stratum ", temp$stratum)), 
    ". Overall sampling density for the northern Bering Sea shelf survey area was ", xunits(temp_tot$density), " km^2^/station (Table \\@ref(tab:tab-stratum-areas)).")
}
```

`r ifelse(srvy == "NEBS", "## Northern Bering Sea Sampling Logistics and Stratification Scheme", "") `

`r str00 `

```{r tab-stratum-areas0}
nickname <- "tab-stratum-areas"
```

```{r tab-stratum-areas-child, child = paste0(dir_code, "_child_report_figtab.Rmd")}
```

## Catch Sampling Procedures

Standard catch sampling procedures used in these Bering Sea shelf surveys are described in detail by @RN939 and @RN933. In summary, samples were collected by trawling near the center of each grid square for a target fishing time of 30 minutes at a speed of 1.54 m/sec (3 knots). If the center of the grid cell was not considered trawlable due to obstructions visible on the depth sounder or a known history of obstructions, the nearest trawlable site within the same grid square was used. Hauls that resulted in significant gear damage contained debris (e.g., derelict crab pots) or had visible changes in net mensuration data during the haul were redeployed to obtain a successful sample.

Catches estimated to be less than approximately 1,000 kg were fully sorted and enumerated, while larger catches were weighed in aggregate or volumetrically measured and subsampled before sorting. The goal of subsampling is to obtain a representative sample, which requires some variation in catch processing methods among hauls. After sorting subsampled catches, individual species present in low numbers were weighed and counted in aggregate, while species present in high numbers were weighed in aggregate, and further subsampled to obtain counts. These secondary subsample counts were extrapolated to the subsample weight for the species. All subsample weights and numbers were then expanded proportionally to the total catch. Fish and invertebrate species were sorted and identified to the lowest reliable taxonomic level. 

All commercial crab species were typically sorted from the entire catch and weighed. Other select species, including Pacific halibut (*Hippoglossus stenolepis*), Greenland turbot (*Reinhardtius hippoglossoides*), rockfish (*Sebastes* spp.), Atka mackerel (*Pleurogrammus monopterygius*), prowfish (*Zaprora silenus*), Bering wolffish (*Anarhichas orientalis*), Pacific cod (*Gadus macrocephalus*), large skates, some sculpins, sharks, and any other large, rare species that were not represented in the subsample, were often completely sorted from the catch and weighed.

```{r tab-oto-collection-scheme-data}
load(file = paste0(dir_out_figtab, "tab-oto-collection-scheme.Rdata"))
obj$raw <- obj$raw %>% # creates object called 'obj'
  dplyr::filter(srvy == "EBS")
```

For all hauls, subsampling for length measurements was based on the fish species size range, targeting 100 specimens collected per species. For each fish in a length subsample, sex was determined and then the length (generally fork or total, depending on the species) was measured to the nearest 1.0 cm. For Pacific halibut on the FV *Northwest Explorer*, the first 10 fish were retained for biological sampling and all others were measured to fork length upon capture`r ifelse(maxyr > 2020, "", " and 50% were randomly selected to receive a preopercle tag")`, then immediately released in an effort to reduce mortality. Pacific halibut weights were estimated using an International Pacific Halibut Commission (IPHC) length-weight regression [@IPHC2023].

```{r methods-collection-scheme}
load(file = paste0(dir_out_figtab, "tab-oto-collection-scheme.Rdata"))
temp <- obj$raw %>% 
  dplyr::select(srvy, srvy_long, print_name) %>% 
  dplyr::distinct() %>%
  dplyr::group_by(srvy, srvy_long) %>% 
  dplyr::summarise(n = length((srvy))) %>% 
  dplyr::mutate(srvy_long = paste(tolower(substr(srvy_long, 1, 1)), substr(srvy_long, 2, nchar(srvy_long)), sep=""))

temp$n <- xunits(temp$n)

str0 <- text_list(paste0(temp$n, " fish species", 
                         ifelse(plural_surveys == "", "", paste0(" in the ", temp$srvy_long)) ))
if (srvy == "NEBS") {
  if (temp$n[1]==temp$n[2]) {
    str0 <- paste0(temp$n[1], " fish species in the ", 
                   text_list(paste0(temp$srvy_long)))
  } 
}

# describing types of oto samples  
temp <- obj$raw %>% 
  dplyr::select(oto_samp_type, srvy, srvy_long) %>% 
  dplyr::distinct()  %>% 
  dplyr::mutate(srvy_long = paste(tolower(substr(srvy_long, 1, 1)), substr(srvy_long, 2, nchar(srvy_long)), sep="")) 

str2 <- c()
for (i in 1:length(unique(temp$srvy))) {
  srvy <- (unique(temp$srvy))[i]
  str2 <- c(str2, 
            paste0(text_list(sort(temp$oto_samp_type[temp$srvy == srvy]))))
}

if (length(str2)>1 & # if there is more than one region
    length(unique(str2))==1) { # and the regions have the same samp types
  str2 <- paste0(str2[1], " sampling method", plural_surveys, 
                 " in both the ", text_list(unique(temp$srvy_long)))
} else {
  temp0 <- temp %>% 
    dplyr::group_by(srvy, srvy_long) %>% 
    dplyr::summarise(freq = n())
  str2 <- text_list(paste0("a ", str2, " sampling method", ifelse(temp0$freq>1,"s", ""),
                         ifelse(plural_surveys == "", "", paste0(" in the ", temp0$srvy_long))))
}
```

Sagittal otoliths were collected from `r str0` (Table \@ref(tab:tab-oto-collection-scheme)). Otolith samples were collected following `r str2 `. Otoliths were preserved in a glycerol-thymol solution for age determination by the Age and Growth Program of the AFSC’s Resource Ecology and Fisheries Management (REFM) Division^[https://www.fisheries.noaa.gov/alaska/science-data/age-and-growth-research-alaska]. Weight and length were collected for each fish from which otoliths were taken. For walleye pollock, age structure sampling effort was further divided into low-density and high-density regions based on historical population densities and an isobath of approximately 70 m.  

```{r methods-stomach-collection}
load(file = paste0(dir_out_figtab, "tab-stomach-collection-scheme.Rdata")) # creates object called 'obj'
```

Stomachs were collected from `r xunits(nrow(obj$raw))` fish species and preserved in 10% formalin for later analysis by the Food Habits Lab of the AFSC's REFM Division^[https://www.fisheries.noaa.gov/alaska/science-data/resource-ecology-and-ecosystem-modeling] (Table \@ref(tab:tab-stomach-collection-scheme)). Arrowtooth flounder and Kamchatka flounder (*Atheresthes* spp.) stomachs were collected together because they occupy a similar trophic niche in the Bering Sea [@YangandLivingston1986]. 

```{r tab-oto-collection-scheme0}
nickname <- "tab-oto-collection-scheme"
```

```{r tab-oto-collection-scheme0-child, child = paste0(dir_code, "_child_report_figtab.Rmd")}
```

```{r tab-stomach-collection-scheme0}
nickname <- "tab-stomach-collection-scheme"
```

```{r tab-stomach-collection-scheme0-child, child = paste0(dir_code, "_child_report_figtab.Rmd")}
```

## Catch Data Analysis

The standard sampling procedures are described in detail by @RN939 and @RN933. Some species were grouped by family for catch data analysis because of their limited commercial value or an inability to identify to lower taxonomic level while in the field. 

Mean catch per unit effort (CPUE) for each species was calculated in kilograms per square kilometer (kg/km^2^) and number of fish per square kilometer (no/km^2^) for each stratum  [@RN889; @RN910]. Area swept (km^2^) was computed as the linear distance towed, multiplied by the mean net width (m; @RN889; @RN910). Mean CPUE was calculated for individual strata and summed proportionally for the overall survey area. Design-based biomass (t) and population (count) estimates were calculated for each stratum by multiplying the stratum mean CPUE by the stratum area. Stratum estimates were then summed for total survey area estimates. 

For size composition estimates, the proportion of fish at each centimeter length interval (from subsamples at each station), weighted by CPUE (no/km^2^), was expanded to the stratum population. Stratum abundance-at-length estimates were summed for the total estimated size composition for the survey area.

Age estimates were obtained from otolith samples by the AFSC's Age and Growth Program for all fish except for Pacific halibut, which were processed by the IPHC. The most current information about age, growth, and population analyses are presented in the `r maxyr` NPFMC Stock Assessment and Fishery Evaluation Report for the Groundfish Resources of the Bering Sea/Aleutian Islands Region^[https://www.fisheries.noaa.gov/alaska/population-assessments/north-pacific-groundfish-stock-assessments-and-fishery-evaluation].

## Scientific Collections and Research Projects

```{r methods-additional-research}
load(file = paste0(dir_out_figtab, "tab-special-projects.Rdata"))
temp <- obj$raw %>% 
  dplyr::group_by(srvy, srvy_long) %>% 
  dplyr::summarise(n = length((srvy))) %>% 
  dplyr::mutate(srvy = dplyr::case_when(
    srvy == "EBS and NBS" ~ "both the EBS and NBS", 
    srvy == "EBS" ~ "only the EBS",
    srvy == "NBS" ~ "only the NBS" ), 
    srvy_long = dplyr::case_when(
      srvy_long == "Eastern and northern Bering Sea" ~ "eastern and northern Bering Sea", 
      srvy_long == "Northern Bering Sea" ~ "the northern Bering Sea",
      srvy_long == "Eastern Bering Sea" ~ "the eastern Bering Sea" ), 
    frag = paste0("project", ifelse(n>1, "s", ""))) %>% 
  dplyr::arrange(-n)

temp$frag[1] <- paste0("scientific collection", ifelse(temp$n[1]>1, "s", "")," and research project", 
                       ifelse(temp$n[1]>1, "s", ""))

# temp1 no longer needed in text?
# temp1 <- readxl::read_excel(path = paste0(dir_out_rawdata, "/special-projects.xlsx"), 
#                             sheet = "solicitation_date", 
#                             skip = 1) %>% 
#   dplyr::filter(year == maxyr) %>% 
#   dplyr::select(solicitation_date) %>% 
#   dplyr::mutate(solicitation_date = date_formatter(solicitation_date)) %>% 
#   unlist()
# 
# str0 ammendment also no longer needed?
# str0 <- paste0(gsub(x = 
#                       text_list(paste0(xunits(temp$n), " ", 
#                                        temp$frag, 
#                                        ifelse(temp$n>1, " were", " was"), 
#                                        " conducted", 
#                                        ifelse(plural_surveys == "", "", paste0(" in ", temp$srvy_long)))), 
#                     pattern = " ,", replacement = ","))
```


`r stringr::str_to_sentence(numbers2words(sum(temp$n)))` scientific and research projects were conducted on the `r maxyr` `r SURVEY` survey`r plural_surveys`. Projects were selected through an annual request for proposals in January `r maxyr` (Table  \@ref(tab:tab-special-projects)). Data for these projects were collected at sea and disseminated to the requesting principal investigator(s). For details about a project or collection, please contact the principal investigator(s) identified in Table \@ref(tab:tab-special-projects).

```{r tab-special-projects0}
nickname <- "tab-special-projects"
```

```{r tab-special-projects-child, child = paste0(dir_code, "_child_report_figtab.Rmd")}
```

## Survey Modernization

```{r intro-survey-modernization-text, child=paste0(dir_out_rawdata, "/0-modernization.Rmd")}
```

