---
output:
  word_document:
    pandoc_args: ["--metadata-file=header.yaml"]
    reference_docx: styles_reference.docx
    df_print: kable
bibliography: "../cite/bibliography.bib"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, error = FALSE, message = FALSE)
```

# Methods

## Survey Area and Sampling Design 

> also true for NBS, right? "37.04 × 37.04 km (20 × 20 nautical mile)"

> edited this down a bit and put the following in the introduction "To simplify the results and discussion from here forward, the terms “EBS” and “NBS” will be used to refer specifically to either the eastern or northern Bering Sea bottom trawl survey area, respectively, and “NEBS” will be used when referring to the combined EBS and NBS survey areas." 

The standardized annual bottom trawl survey of the EBS `r ifelse(SRVY == "NEBS", "and NBS are", " is")` based on a systematic design with `r NMFSReports::text_list(paste0(haul_cruises_maxyr$stations_avail, " in the ", haul_cruises_maxyr$SRVY))` fixed sampling stations at the center of 37.04 × 37.04 km (20 × 20 nautical mile) grid squares (Figure `r crossref(list_obj = list_figures, nickname = "fig_sample_grid", sublist = "number") `). In waters surrounding St. Matthew Island and the Pribilof Islands, high-density “corner stations” are sampled to better assess local blue king crab concentrations (Figure `r crossref(list_obj = list_figures, nickname = "fig_sample_grid", sublist = "number") `). `r ifelse(SRVY == "NEBS", paste0("The ", maxyr, " NBS survey was a northward extension of the EBS systematic design consisting of stations bounded by the U.S.-Russian Maritime Boundary, the Bering Strait, and Norton Sound.") , "")` The results reported herein include data analyses for both the `r NMFSReports::text_list(paste0(haul_cruises_maxyr$SRVY))`. 


## Survey Vessels and Sampling Gear

The `r ifelse(nrow(vessel_info) == 1, "the vessel", "both vessels") ` used for the surveys are house-forward trawlers with stern ramps. The `r text_list(paste0(vessel_info$vessel_name, " has an LOA of ", vessel_info$length_m, " m (", vessel_info$length_ft, " ft)") ) `. All fishing operations were conducted in rigorous compliance with national and regional protocols detailed in @RN933. The AFSC equipped each of the vessels with standard 83-112 Eastern otter trawls, which have 25.3 m (83 ft) headropes and 34.1 m (112 ft) footropes (Figure `r crossref(list_obj = list_figures, nickname = "fig_trawl_gear", sublist = "number") `). These nets were attached to tail chains with 54.9 m (30 fm) paired dandylines. Each lower dandyline had a 0.61 m chain extension connected to the lower wing edge to improve bottom tending. Steel "V" doors measuring 1.8 × 2.7 m (6 × 9 ft) and weighing 816 kg (1,800 lbs) each were used for spreading the net opening while the trawl was fishing on the seafloor.

The Marport Deep Sea Technologies Inc. net mensuration system was used during the deployment of each tow to record net spread and net height. Net spread was measured as the horizontal distance between two sensors attached immediately forward of the junction of the upper breastline and the dandyline, and net height was measured from the headrope to the seafloor. Mean net spread values for estimating area swept per tow were calculated according to methods described by @RN910.

Temperature and depth profiles were recorded using a Sea-Bird SBE-39 datalogger (Sea-Bird Electronics Inc., Bellevue, WA) attached to the headrope of the trawl. Observations were made at 3-second intervals at each station. Average bottom depth was calculated by adding the average net height to the average depth of the headrope. 

`r list_figures$fig_trawl_gear$res `

> How do I calculate "net mensuration system failed to record data for six tows"?

```{r}
str_ebs <- "the net mensuration system failed to record data for six tows on the FV Vesteraalen and nine tows on the FV Alaska Knight"

str_nbs <- "it failed for two tows on each vessel"
```

During the EBS survey, `r str_ebs `, and for the NBS survey `r str_nbs `. To estimate these missing net width values, the mgcv package in R [@RN997] was used to relate mean net width with the inverse scope (m) and mean net height (m) from valid tows based on the relationship investigated by @RN921:

```{r eq_mean_net_width}
equation = "Net width ∼ Inverse scope + Height + Inverse scope * Height"
nickname = "eq_mean_net_width"
header = "Equation to relate mean net width with the inverse scope (m) and mean net height (m)."
alttext = "To estimate these missing net width values, the mgcv package in R (Wood 2004) was used to relate mean net width with the inverse scope (m) and mean net height (m) from valid tows based on the relationship investigated by @RN921."

res <- knitr::knit_child(
  text = knitr::knit_expand(
    file = system.file("rmd/_child_save_eq.Rmd", package = "NMFSReports") ), 
  quiet = TRUE
)

assign(value = res, x = nickname)

```

`r eq_mean_net_width `

> are these calculated each year, and if so, where do I get these values from? Also, would they be shared if there were no estimates? is n = number of successful hauls? (that doesnt seems right?)

For the FV Alaska Knight, both predictor variables and their interaction were significant (P < 0.001). The resulting regression equations by survey were as follows:

EBS (n = 160):

  Net width (m) = 27.372 – 1424.464 * Inverse scope – 3.659 * Net height + 451.441 * Inverse scope * Height

NBS (n = 86): 

  Net width (m) = 25.421 – 853.054 * Inverse scope – 2.617 * Net height + 144.714 * Inverse scope * Height

For the FV Vesteraalen, inverse scope and net height were significant (P < 0.001) but not their interaction term. The resulting regression equations by survey were as follows:

EBS (n = 224): 

  Net width (m) = 22.642 – 355.689 * Inverse scope – 1.619 * Net height

NBS (n = 54):

  Net width (m) = 21.023 – 320.270 * Inverse scope – 1.312 * Net height.

These equations were subsequently used to estimate the respective net spread values for the 19 tows with missing net width values.

Temperature and depth profiles were recorded using a Sea-Bird SBE-39 datalogger (Sea-Bird Electronics Inc., Bellevue, WA) attached to the headrope of the trawl. Observations were made at 3-second intervals at each station and averaged for the tow duration. Average bottom depth was calculated by adding the average net height to the average depth of the headrope.

> How to incorporate: "In 2018, the net mensuration system failed to record data for only one tow on the FV Alaska Knight during the `r SRVY ` shelf survey. Net mensuration data was successfully collected for all tows during the NBS survey. Area swept calculations for the one tow that was missing net mensuration data was estimated using other tows in similar depths."

> note: typo in haul data:   dplyr::mutate(depth = gsub(pattern = "> 1", replacement = ">1", x = description)) %>% 

## EBS Sampling Logistics and Stratification Scheme

```{r}
date_format<- "%B %d, %Y"
str <- c()

for (i in 1:length(unique(haul_cruises_maxyr$SRVY))){
  
  srvy <- unique(haul_cruises_vess_maxyr$SRVY)[i]
  cruises_maxyr0  <- haul_cruises_vess_maxyr %>% 
    dplyr::filter(SRVY == srvy) %>% 
    dplyr::select("year", "survey_name", "vessel", "vessel_name", 
                  "vessel_ital", "SRVY", "SRVY_long", 
                  "start_date_cruise", "end_date_cruise", 
                  "start_date_haul", "end_date_haul") %>% 
    unique() %>% 
    group_by(year, survey_name, vessel, vessel_name, 
             vessel_ital, SRVY, SRVY_long) %>% 
    dplyr::summarise(start_date_cruise = min(start_date_cruise), 
                     end_date_cruise = max(end_date_cruise), 
                     start_date_haul = min(start_date_haul), 
                     end_date_haul = max(end_date_haul))
  
  temp <- "" # paste0("of the ", srvy, ", which ")
  
  if (length(unique(cruises_maxyr0$start_date_haul)) != 1 &
      length(unique(cruises_maxyr0$end_date_haul)) != 1) { 
    # 1. vessels started and ended on different dates
    temp <- paste0(temp, 
                   text_list(paste0("the ", cruises_maxyr0$vessel_ital, 
                                    " started surveying on ", 
                                    format((cruises_maxyr0$start_date_haul), format = date_format), 
                                    " and ended on ", 
                                    format((cruises_maxyr0$end_date_haul), format = date_format) )) )
    # temp<-gsub(pattern = "and ,", replacement = "and,", x = temp)
    
  } else if (length(unique(cruises_maxyr0$start_date_haul)) == 1 &
             length(unique(cruises_maxyr0$end_date_haul)) == 1) { 
    # 2. vessels started and ended on the same dates
    temp <- paste0(temp, 
                   NMFSReports::text_list(cruises_maxyr0$vessel_ital), 
                   # ifelse(length(unique(vessel_info0$vessel)) == 1, 
                   #        "the vessel", "both vessels"), 
                   " started surveying the on ",
                   format(unique(cruises_maxyr0$start_date_haul), format = date_format), 
                   " and ended surveying on ", 
                   format(unique(cruises_maxyr0$end_date_haul), format = date_format))
    
  } else if (length(unique(cruises_maxyr0$start_date_haul)) == 1 &
             length(unique(cruises_maxyr0$end_date_haul)) != 1) {
    # 3. vessels started on the same dates and ended on different dates
    temp <- paste0(temp, "in the survey started for ", 
                   ifelse(length(unique(cruises_maxyr0$vessel_ital)) == 1, 
                          "the vessel", "both vessels"), 
                   " on ",
                   format(unique(cruises_maxyr0$start_date_haul), format = date_format), 
                   " and ended ", 
                   NMFSReports::text_list(paste0("on ", 
                                                 format(cruises_maxyr0$end_date_haul, 
                                                        format = date_format) , 
                                                 " for the ", cruises_maxyr0$vessel_ital) ))
    
  } else if (length(unique(cruises_maxyr0$start_date_haul)) != 1 &
             length(unique(cruises_maxyr0$end_date_haul)) == 1) {
    # 4. vessels started on different dates and ended on the same dates
    temp <- paste0(temp, "the survey started ", 
                   
                   NMFSReports::text_list(paste0("on ", 
                                                 format(cruises_maxyr0$start_date_haul, 
                                                        format = date_format) , 
                                                 " for the ", cruises_maxyr0$vessel_ital) ), 
                   " and ended for ", 
                   
                   ifelse(length(unique(cruises_maxyr0$vessel_ital)) == 1, 
                          "the vessel", "both vessels"), 
                   " on ",
                   format(unique(cruises_maxyr0$end_date_haul), 
                          format = date_format) )
  }
  str = c(str, temp)
  
}

str <- data.frame(str = str, 
                  SRVY = unique(cruises_maxyr$SRVY))

```


The `r text_list(vessel_info$vessel_ital)` conducted the standard EBS shelf survey charters beginning in Dutch Harbor, Alaska, beginning in eastern Bristol Bay and proceeding westward to the shelf edge (Figure `r crossref(list_obj = list_figures, nickname = "fig_sampled_survey_stations", sublist = "number") `). The progression from east to west was established in response to movements of yellowfin sole and perhaps other species, which may be migrating eastward during the course of the survey [@RN928]. In the EBS, the `r str$str[str$SRVY == "EBS"]` (Figure `r crossref(list_obj = list_figures, nickname = "fig_sampled_survey_stations", sublist = "number") `).

`r list_figures$fig_sampled_survey_stations$res `

> OLD TEXT OF THE ABOVE PARAGRAPH: The `r text_list(vessel_info$vessel_ital)` conducted the standard `r SRVY ` shelf survey charters beginning in Dutch Harbor, Alaska, on `r format((min(vessel_info$start_date[vessel_info$SRVY == "EBS"])), format = date_format) `. Survey trawl sampling of the EBS shelf began in eastern Bristol Bay and proceeded westward to the shelf edge (Figure `r crossref(list_obj = list_figures, nickname = "fig_sampled_survey_stations", sublist = "number") `). The progression from east to west was established in response to movements of yellowfin sole and perhaps other species, which may be migrating eastward during the course of the survey [@RN928]. The `r text_list(vessel_info$vessel_name)` completed the standard EBS survey on `r format((max(vessel_info$end_date[vessel_info$SRVY == "EBS"])), format = date_format) ` (Figure `r crossref(list_obj = list_figures, nickname = "fig_sampled_survey_stations", sublist = "number") `).


```{r}
  temp0 <- crossref(list_obj = list_tables, nickname = "tab_stratum_areas", sublist = "raw")[[1]]


temp <- temp0 %>% 
  dplyr::filter(!grepl(pattern = "Total", x = Region) & 
                  grepl(pattern = "EBS", x = Region))


temp_tot <- temp0 %>% 
  dplyr::filter(grepl(pattern = ifelse(SRVY == "NEBS", "EBS Total", "Total"), x = Region) & 
                  grepl(pattern = "EBS", x = Region)) %>% 
  dplyr::select(density)
```

For catch analysis, the EBS shelf was divided into 12 strata bounded by the 50-m, 100-m, and 200-m isobaths, a geographic stratum line separating the northwest and southeast shelf, and localized high-density strata in the regions around St. Matthew and Pribilof Islands (Figure `r crossref(list_obj = list_figures, nickname = "fig_sample_grid", sublist = "number") `). This stratification scheme reflects the differences observed in Bering Sea groundfish distribution across the oceanographic domains, and the intention of the design was to reduce the variances of population and biomass estimates [@RN891]. The purpose of high-density sampling in Strata 32, 42, 43, and 62 was to reduce variance estimates for blue king crab. Sampling density ranged from one station per `r xunits(min(temp$density))` km^2^ (Stratum `r temp$stratum[temp$density == min(temp$density)]`) to one per `r xunits(max(temp$density))` km^2^ (Stratum `r temp$stratum[temp$density == max(temp$density)]`) and the sampling density for the entire EBS shelf was one station per `r xunits(temp_tot$density)` km^2^ (Table `r crossref(list_obj = list_tables, nickname = "tab_stratum_areas", sublist = "number")`). For purposes of some analyses (i.e., abundance at length), the high-density strata were grouped, resulting in eight subareas: 10, 20, 30 (31+32), 40 (41+42+43), 50, 60 (61+62), 82, and 90 (Figure `r crossref(list_obj = list_figures, nickname = "fig_sample_grid", sublist = "number")`; Table `r crossref(list_obj = list_tables, nickname = "tab_stratum_areas", sublist = "number")`).

```{r}

nbs_insert <- ""

if (SRVY == "NEBS") {
  
  
  temp0 <- crossref(list_obj = list_tables, nickname = "tab_stratum_areas", sublist = "raw")[[1]]
  
  temp <- temp0 %>% 
    dplyr::filter(!grepl(pattern = "Total", x = Region) & 
                    grepl(pattern = "NBS", x = Region))
  
  temp_tot <- temp0 %>% 
    dplyr::filter(grepl(pattern = "NBS Total", x = Region) & 
                    !grepl(pattern = " NBS Total", x = Region) & 
                    grepl(pattern = "NBS", x = Region))
  
  nbs_insert <- paste0(
    "After the completion of the EBS shelf survey, both vessels transitioned into sampling survey stations in the southwest corner of the NBS survey region. In the NBS shelf survey, ", 
    str$str[str$SRVY == "NBS"], 
    ". After the NBS suvey was completed, both vessels returned to Dutch Harbor for offloading. The NBS shelf was divided into three strata: one including the area north of St. Lawrence Island and Norton Sound and two others south of St. Lawrence Island separated by the 50-m isobath (Figure ", crossref(list_obj = list_figures, nickname = "fig_sampled_survey_stations", sublist = "number"),
    "). Sampling density was ", 
    # Sampling density was 1,367 km2 /station for Stratum 70, 1,475 km2 /station for Stratum 71, 1,370 km2 /station for Stratum 81, 
    NMFSReports::text_list(paste0(xunits(temp$density), " km^2^/station for Stratum ", temp$stratum)), 
    "and ", xunits(temp_tot$density), " km^2^/station for the total NBS (Table ", crossref(list_obj = list_tables, nickname = "tab_stratum_areas", sublist = "number"),").")
  
}

```

`r ifelse(SRVY == "NEBS", "## NBS Sampling Logistics and Stratification Scheme", "") `

`r nbs_insert `

`r list_tables$tab_stratum_areas$res `

###### 

## Catch Sampling Procedures

Standard sampling procedures used in RACE Bering Sea assessment surveys are described in detail by @RN939 and @RN933. A brief summary of these procedures is described below.

Samples were collected by trawling near the center of each grid square (or grid circle, in the case of high-density strata) for a target fishing time of 30 minutes at a speed of 1.54 m/sec (3 knots). If a station was not considered trawlable due to obstructions visible on the depth sounder, the nearest trawlable site within the same grid square was used. Hauls that resulted in significant gear damage or contained debris such as discarded crab pots which caused visible changes in net mensuration were redeployed to obtain a successful sample.

Catches estimated to be less than approximately 1,200 kg (2,650 lbs) were entirely sorted and enumerated, while larger catches were weighed in aggregate and subsampled before sorting. After sorting subsampled catches, individual species were weighed and counted in aggregate, and these weights and numbers were then expanded arithmetically to the total catch. Fishes and invertebrates were identified and sorted to the lowest taxonomic level practicable. 

Catch weights and numbers by species or species group were either estimated directly when subsampled, or estimated by extrapolating the proportion in the subsample to that of the entire catch weight. All Pacific halibut (*Hippoglossus stenolepis*) and commercial crab species were weighed and enumerated from each catch. Other selected species including Greenland turbot, large skates, Pacific cod, sculpins, sharks, and octopus were also completely sorted from the catch in most cases.

Random samples of selected fish species (Table`r ifelse(SRVY == "NEBS", "s", "")` `r crossref(list_obj = list_tables, nickname = "tab_specimen_samples_EBS", sublist = "number")``r ifelse(SRVY == "NEBS", paste0(" and ", crossref(list_obj = list_tables, nickname = "tab_specimen_samples_NBS", sublist = "number")), "")`) were further processed to obtain length measurements. The number of fish in a random length sample for a species was dependent on the size range of that species in the haul, up to a maximum of about 300 specimens. For each fish in a length sample, sex was determined and then the fork or total length was measured to the nearest 1.0 cm. Unless retained for biological sampling by the International Pacific Halibut Commission (IPHC), Pacific halibut were measured to fork length upon capture, `r ifelse(maxyr > 2020, "in all years other than 2021,", "")` 50% were randomly selected to receive a preopercule tag, after which the halibut were immediately returned to the sea in an effort to reduce mortality; weights of all Pacific halibut were estimated using an IPHC length-weight regression [@RN895].

`r list_tables$tab_specimen_samples_EBS$res `

`r ifelse(SRVY == "NEBS", list_tables$tab_specimen_samples_NBS$res, "") `


```{r}
temp <- specimen_maxyr %>% 
  # dplyr::filter(!is.na(age_determination_method)) %>% # TOLEDO - is this how I get otolith samples?
  dplyr::group_by(SRVY = all_of(SRVY)) %>% 
  dplyr::summarise(species_code_n = unique(species_code)) %>% 
  dplyr::summarise(n = length(all_of(SRVY)))   

```

Sagittal otoliths were collected in the field from `r NMFSReports::text_list(paste0(temp$n, " fish species in the ", temp$SRVY))` (Tables 
`r crossref(list_obj = list_tables, nickname = "tab_specimen_samples_EBS", sublist = "number")`
`r ifelse(SRVY == "NEBS", paste0(", ", crossref(list_obj = list_tables, nickname = "tab_specimen_samples_NBS", sublist = "number")), "")`
`r ifelse(SRVY == "NEBS", ", "," and")` `r crossref(list_obj = list_tables, nickname = "tab_oto_collection_scheme_EBS", sublist = "number")`
`r ifelse(SRVY == "NEBS", paste0(", and ", crossref(list_obj = list_tables, nickname = "tab_oto_collection_scheme_NBS", sublist = "number")), "")`) and brought to the AFSC to be processed for age determination. Depending on fish species, a length-stratified or a random sampling method was used for collecting otolith pairs in `r ifelse(SRVY == "NEBS", "the NBS and ", "")`two different EBS regions (southeast and northwest; Table `r crossref(list_obj = list_tables, nickname = "tab_oto_collection_scheme_EBS", sublist = "number")`
`r ifelse(SRVY == "NEBS", paste0(" and ", crossref(list_obj = list_tables, nickname = "tab_oto_collection_scheme_NBS", sublist = "number")), "")`). Otoliths were preserved in 50% glycerol-thymol solution. Individual fish weights and lengths were collected for each fish from which age structures were taken. For walleye pollock, the survey area was also divided into low- and high-density strata based on historical density and an isobath of approximately 70 m.  

`r list_tables$tab_oto_collection_scheme_EBS$res `

`r ifelse(SRVY == "NEBS", list_tables$tab_oto_collection_scheme_NBS$res, "") `

> # TOLEDO - Liz fill out the rest of this paragraph!  

```{r}
temp <- NMFSReports::crossref(list_obj = list_tables, nickname = "tab_stomach_collection_scheme", sublist = "raw")  
```

Stomachs were collected in the field from `r nrow(temp)` fish species (Table `r NMFSReports::crossref(list_obj = list_tables, nickname = "tab_stomach_collection_scheme", sublist = "number") `). Stomachs were preserved in the field in 10% formalin. Arrowtooth flounder and Kamchatka flounder (*[insert spp name]*) stomachs were collected together as one genus because they represent the same ecological niche. 

`r list_tables$tab_stomach_collection_scheme$res `

## Catch Data Analysis

Trawl survey catch data were used to derive design-based estimates of biomass, population, and size structure of fish and invertebrate species. A brief description of the procedures used in the analysis of RACE Bering Sea survey data follows (for a detailed description see @RN939). Some species were grouped by family for catch data analysis because of their limited commercial value or uncertain identification. 

Mean catch per unit effort (CPUE) values for each species were calculated in kilograms per hectare (1 ha = 10,000 m^2^) and number of fish per hectare for each stratum; area swept (hectares) was computed as the distance towed multiplied by the mean net width [@RN889; @RN910]. Mean CPUE values were calculated for individual strata and for the overall survey area. Design-based biomass and population estimates were derived for each stratum by multiplying the stratum mean CPUE by the stratum area. Stratum totals were then summed to produce estimates for each of the strata and for the total survey area in the `r SRVY `. 

For size composition estimates, the proportion of fish at each centimeter length interval (from subsamples at each station), weighted by CPUE (number of fish/ha), was expanded to the stratum population. Stratum abundance-at-length estimates were summed for the total estimated size composition for the overall survey area in the `r NMFSReports::text_list(paste0(SRVY1))`.

Except for Pacific halibut, otolith samples collected during the survey were read for age estimates by staff of the Age and Growth Program of the AFSC's Resource Ecology and Fisheries Management (REFM) Division. The most current information about age, growth, and population analyses are presented in the 2018 NPFMC Stock Assessment and Fishery Evaluation Report for the Groundfish Resources of the Bering Sea/Aleutian Islands Region [`r paste(ref_maxyr_npfmc)`].

## Additional Research Projects


```{r}
temp <- crossref(list_obj = list_tables, 
                 nickname = "tab_special_projects", 
                 sublist = "raw")[[1]] %>% 
  dplyr::group_by(SRVY) %>% 
  dplyr::summarise(n = length(all_of(SRVY))) %>% 
  dplyr::mutate(SRVY = dplyr::case_when(
    SRVY == "Both" ~ "EBS and NBS", 
    TRUE ~ SRVY
  ))


temp1 <- readxl::read_excel(path = paste0(dir_out_rawdata, "/0_special_projects.xlsx"), 
                         sheet = "solicitation_date", 
                         skip = 1) %>% 
  dplyr::filter(year == maxyr) %>% 
  dplyr::select(solicitation_date) %>% 
  dplyr::mutate(solicitation_date = 
                  format(x = as.POSIXlt(x = solicitation_date), 
                         format="%d %B %Y")) %>% 
  unlist()
```

In addition to standard survey operations, `r NMFSReports::text_list(paste0(temp$n, " research project",ifelse(temp$n>1, "s were", " was")," undertaken in the ", temp$SRVY))` during the `r maxyr` survey season (Table `r crossref(list_obj = list_tables, nickname = "tab_special_projects", sublist = "number")`). A solicitation for research proposals was issued on `r paste(temp1)`. Project requests were prioritized and modified based on their potential support of AFSC goals and their expected impact on survey resources and available time. Some of the approved projects were new for `r maxyr`, while many continued multi-year observations of supplementary data. Data for additional research projects were collected at sea and disseminated to the requesting principal investigator(s). To acquire the details about a special project or collection, please contact the investigator(s) designated in Table `r crossref(list_obj = list_tables, nickname = "tab_special_projects", sublist = "number")`.

`r list_tables$tab_special_projects$res `


