---
output:
  word_document:
    pandoc_args: ["--metadata-file=header.yaml"]
    reference_docx: styles_reference.docx
    df_print: kable
bibliography: "../cite/bibliography.bib"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, error = FALSE, message = FALSE, comment = FALSE)
```

# Results and Discussion

A total of `r NMFSReports::text_list(paste0(haul_cruises_maxyr$stations_completed, " ", haul_cruises_maxyr$SRVY, " stations")) ` were successfully sampled in `r maxyr` (Figure `r crossref(list_obj = list_figures, nickname = "fig_sampled_survey_stations", sublist = "number") `)). Summarized haul and raw catch sample data for successfully trawled stations used in the analyses are listed in Appendix A by vessel along with date, time, start and end positions, mean bottom depth, tow duration, distance fished over ground, mean net width, and trawl performance.

## Ocean Conditions

```{r}
temp <- dplyr::left_join(
  x = temps_avg_yr %>% 
    dplyr::filter(year %in% c(maxyr)), 
  y = temps_avg_yr %>% 
    dplyr::filter(year %in% c(lastyr)) %>% 
    dplyr::select(SRVY, bt, st) %>% 
    dplyr::rename(bt_1 = bt,
                  st_1 = st),
  by = "SRVY") %>% 
  dplyr::mutate(bt_diff = (bt_1 - bt)) %>% 
  dplyr::mutate(st_diff = (st_1 - st)) %>% 
  dplyr::mutate(bt_mean_diff = (bt_mean - bt)) %>% 
  dplyr::mutate(st_mean_diff = (st_mean - st)) 

temp2 <- dplyr::left_join(
  x = haul_maxyr, 
  y = station_info, 
  by = c("stratum", "stationid", "SRVY")) %>% 
  dplyr::filter(reg == "Norton Sound")

a <- summary(lm(haul_maxyr$surface_temperature ~ haul_maxyr$start_longitude))
temp3 <- ifelse(a$coefficients[2]<0 & a$coefficients[8] <= 0.05, "surface temperatures increased from east to west across the shelf, and ", "")
```

Sea surface temperatures recorded during the `r maxyr` `r SRVY` survey ranged from `r round(x = min(haul_maxyr$surface_temperature, na.rm = TRUE), digits = 1)`° to `r round(x = max(haul_maxyr$surface_temperature, na.rm = TRUE), digits = 1)`°C and bottom temperatures ranged from `r round(x = min(haul_maxyr$gear_temperature, na.rm = TRUE), digits = 1)`° to `r round(x = max(haul_maxyr$gear_temperature, na.rm = TRUE), digits = 1)`°C. The mean sea surface temperature for the EBS in `r maxyr` was `r round(x = temp$st, digits = 1)`°C, which was `r round(x = temp$st_diff, digits = 1)`°C `r ifelse((temp$st_diff > 0), "lower", "higher")` than `r lastyr` (`r round(x = temp$st_1, digits = 1)`°C) and `r round(x = temp$st_mean_diff, digits = 1)`°C `r ifelse((temp$st_mean_diff > 0), "lower", "higher")` than the time-series mean (`r round(x = temp$st_mean, digits = 1)`°C) (Figure `r crossref(list_obj = list_figures, nickname = 'fig_mean_temperature', sublist = 'number')`, `r crossref(list_obj = list_figures, nickname = 'fig_cold_pool_area', sublist = 'number')`, and `r crossref(list_obj = list_figures, nickname = 'fig_st_maxyr', sublist = 'number')`). `r ifelse(SRVY == "NEBS", paste0("In the EBS south of 60° N, ", temp3,"an average of ", round(x = mean(temp2$surface_temperature), digits = 1),"°C was observed in the NBS's Norton Sound (Figure ", crossref(list_obj = list_figures, nickname = 'fig_st_maxyr', sublist = 'number'), ")."), "")`

`r list_figures$fig_mean_temperature$res `

`r list_figures$fig_cold_pool_area$res `

`r list_figures$fig_st_maxyr$res `

During the `r haul_cruises_maxyr$yrofsurvey[haul_cruises_maxyr$SRVY == "EBS"]`-year time series (`r haul_cruises_maxyr$SRVY_start[haul_cruises_maxyr$SRVY == "EBS"] `–`r maxyr`) of the annual EBS shelf bottom trawl survey, mean summer bottom temperatures were highly variable, ranging from a low of `r round(x = min(temps_avg_yr$bt), digits = 1)`°C to a high of `r round(x = max(temps_avg_yr$bt), digits = 1)`°C, with a grand mean for all years of `r round(x = min(temps_avg_yr$bt_mean[1]), digits = 1)`°C (Figure `r crossref(list_obj = list_figures, nickname = 'fig_mean_temperature', sublist = 'number')`). The mean survey bottom temperature for the EBS in `r maxyr` was `r round(x = (temps_avg_yr_maxyr$bt), digits = 1)`°C (Figure `r crossref(list_obj = list_figures, nickname = 'fig_mean_temperature', sublist = 'number')`), which was `r round(x = abs(temp$bt_mean_diff), digits = 1) `°C `r ifelse(temps_avg_yr_maxyr$bt_above_mean, "warmer", "colder")` than than the time-series mean.

The size of the cold pool each summer depends on sea ice coverage from the previous winter, the timing of its retreat during the spring and early summer as well as other oceanographic and meteorological conditions [@RN941]. During the coldest years, sea ice extended farther south and lasted later into spring resulting in cold pools that extended farther south down the middle domain into Bristol Bay and near the Alaska Peninsula (Figure `r crossref(list_obj = list_figures, nickname = 'fig_bt_timeseries_below', sublist = 'number')` and `r crossref(list_obj = list_figures, nickname = 'fig_bt_timeseries_above', sublist = 'number')`). Interannual variability in the dynamics of seasonal ice is a major environmental driver on the Bering Sea shelf [@RN930; @RN931; @RN932] that can change recruitment and migration patterns and cause major distributional shifts in groundfishes and crabs [@RN905; @RN913; @RN977]. 

> Automate ranges for warm and cold stanzas #TOLEDO 

```{r}
temp <- cold_pool_area %>% 
  dplyr::group_by(year) %>% 
  dplyr::summarise(perc = sum(perc, na.rm = T), 
                   freq = sum(freq, na.rm = T)) %>% 
  dplyr::mutate(area_km2 = (perc/100) * 
                  sum(stratum_info %>% 
                        dplyr::filter(SRVY == "EBS") %>% 
                        dplyr::select(area_km2), na.rm = TRUE)) %>%
  dplyr::arrange((perc)) %>% 
  dplyr::mutate(rank = 1:nrow(.)) %>% 
  dplyr::arrange(desc(year))
```

During the last 16 years, `2006 – 2013` were colder than average ("cold stanza"; Figure `r crossref(list_obj = list_figures, nickname = 'fig_bt_timeseries_below', sublist = 'number')`), and `2002 – 2005` and `2014 – 2017` were warmer than average ("warm stanza"; Figure `r crossref(list_obj = list_figures, nickname = 'fig_bt_timeseries_above', sublist = 'number')`). The highly variable survey bottom temperatures in the EBS shelf are related to the area occupied by the summer cold pool (Figure `r crossref(list_obj = list_figures, nickname = 'fig_cold_pool_area', sublist = 'number')`), defined by the extent of bottom temperatures below 2°C. Over the period of the `r haul_cruises_maxyr$yrofsurvey[haul_cruises_maxyr$SRVY == "EBS"] `-year time series, the areal coverage of the summer survey cold pool in the EBS varied in size from `r NMFSReports::xunits(min(temp$area_km2, na.rm = TRUE)) ` km^2^ in `r temp$year[temp$area_km2 == min(temp$area_km2, na.rm = TRUE)] ` to `r NMFSReports::xunits(max(temp$area_km2, na.rm = TRUE)) ` km^2^ in `r temp$year[temp$area_km2 == max(temp$area_km2, na.rm = TRUE)] `, respectively comprising `r round(temp$perc[temp$area_km2 == min(temp$area_km2, na.rm = TRUE)], digits = 1)`% to `r round(temp$perc[temp$area_km2 == max(temp$area_km2, na.rm = TRUE)], digits = 1)`% of EBS shelf area (Figure `r crossref(list_obj = list_figures, nickname = 'fig_cold_pool_area', sublist = 'number')`). In `r maxyr`, the cold pool covered `r round(temp$perc[temp$year == maxyr], digits = 1) `% of the EBS shelf survey area `r formatC(temp$area_km2[temp$year == maxyr], digits = 0, big.mark = ",", format = "f") ` km^2^, which was the `r NMFSReports::numbers2words_th(temp$rank[temp$year == maxyr])` lowest areal coverage in the `r haul_cruises_maxyr$yrofsurvey[haul_cruises_maxyr$SRVY == "EBS"] `-year EBS shelf time series.

`r list_figures$fig_bt_timeseries_below$res `

`r list_figures$fig_bt_timeseries_above$res `


```{r}
# insert <- readtext(file = paste0(dir_out_rawdata, "/doc_abstract_conclusion.docx"))
insert <- readtext2(file = paste0(dir_out_rawdata, "/0_cold_pool_description.docx"), 
                    refcontent = refcontent)
```

`r insert`

## Survey Data and Specimen Collections 

```{r}
temp <- function(cols, SRVY){
  nspec <- c()
  ntaxa <- c()
  ctaxa <- c()
  a <- report_spp1
  a$taxon[a$taxon == "invert" & 
            grepl(pattern = "crab", x = a$print_name)] <- "crab"
  
  for (i in 1:length(cols)){
    
    col <- cols[i]
    if (SRVY == "NEBS") {
      temp <- dplyr::bind_rows(
        crossref(list_obj = list_tables, 
                 nickname = "tab_specimen_samples_EBS", sublist = "raw")[[1]], 
        crossref(list_obj = list_tables, 
                 nickname = "tab_specimen_samples_NBS", sublist = "raw")[[1]])      
    } else {
    temp <- crossref(list_obj = list_tables, 
                 nickname = "tab_specimen_samples_EBS", sublist = "raw")[[1]]      
    }

    temp <- temp[temp[,col]!=0,]
    
    nspec <- c(nspec, 
               xunits(sum(temp[temp$common_name == "Total", 
                               names(temp) %in% col]))) # how many specimen
    ntaxa <- c(ntaxa, 
               xunits(length(unique(temp$common_name)[unique(temp$common_name) != "Total"]))) # number of taxa
    
    ctaxa <- c(ctaxa,
               NMFSReports::text_list(unique(a$taxon[a$print_name %in% 
                                                       unique(temp$common_name)])) )
  }
  
  return(list("col" = tolower(cols), 
              "nspec" = nspec, 
              "ctaxa" = ctaxa, # kinds of taxa
              "ntaxa" = ntaxa))
}

cols <- names(crossref(list_obj = list_tables, 
                       nickname = "tab_specimen_samples_EBS", sublist = "raw")[[1]])
cols <- cols[!(cols %in% c("common_name", "SRVY"))]

# "", "stomachs collected"	count_pathobiology_samples	count_fecundity_and_maturity_(ovaries)_samples

temp <- temp(cols, SRVY)

str <- paste0("A total of ", NMFSReports::text_list(paste0(temp$nspec, " ", temp$col, " were collected from ", temp$ntaxa, " ", temp$ctaxa, ifelse(temp$ntaxa==1, " taxon", " taxa"))), ". ")

```

During the `r SRVY` (Table`r ifelse(SRVY == "NEBS", "s", "")` `r crossref(list_obj = list_tables, nickname = "tab_specimen_samples_EBS", sublist = "number") ``r ifelse(SRVY == "NEBS", paste0(" and ", crossref(list_obj = list_tables, nickname = "tab_specimen_samples_NBS", sublist = "number")), "")`) trawl survey`r ifelse(SRVY == "NEBS", "s", "")` many samples were collected. `r str` Other special collections are listed in table `r crossref(list_obj = list_tables, nickname = "tab_special_projects", sublist = "number")`. 

## Species Composition

```{r}
insert <- ""

# No. fish spp
temp <- spp_info_maxyr %>% 
  dplyr::filter(used_in_counts == TRUE) 

fish_sp <- xunits(length(unique(temp$report_name_scientific[temp$taxon == "fish" & 
                                                              !(grepl(pattern = " sp.", x = temp$report_name_scientific, fixed = T)) & 
                                                              !(grepl(pattern = " unid.", x = temp$report_name_scientific, fixed = T))])))


if (SRVY == "NEBS") {

  temp0 <- list_tables$tab_species_composition$raw %>% 
  dplyr::left_join(x = ., 
                   y = spp_info %>% 
                     dplyr::select(species_code, order_taxon, species_name), 
                   by = c("species_code"))


insert <- paste0("The EBS had a total of ",
                     xunits(nrow(temp0[!is.na(temp0$EBS),])),
                     " fish species, ", 
                     xunits(nrow(temp0[temp0$where == 
                                         "Present in EBS but absent in NBS",])), 
                     " of which did not occur in the NBS (Table ",
                     crossref(list_obj = list_tables, 
                              nickname = "tab_species_composition", 
                              sublist = "number"),
                     "). In comparison, the NBS had ",
                     xunits(nrow(temp0[!is.na(temp0$NBS),])),
                     " total fish species, ", 
                     xunits(nrow(temp0[temp0$where == 
                                         "Present in NBS but absent in EBS",])), 
                     " of which did not occur in the EBS (Table ", 
                     crossref(list_obj = list_tables, 
                              nickname = "tab_species_composition", 
                              sublist = "number"), "). ",
                   xunits(nrow(temp0[temp0$where == 
                                       "Present in NBS but absent in EBS" & 
                                       temp0$NBS == TRUE,])),
                   " of the ", 
                   xunits(nrow(temp0[temp0$where == 
                                       "Present in NBS but absent in EBS",])), 
                   " species observed in the NBS during ",maxyr," (Table ", 
                   crossref(list_obj = list_tables, 
                            nickname = "tab_species_composition", 
                            sublist = "number"), ") are only documented north of 60° N, which are generally corroborated in @RN912. ")

# flatfish
temp1 <- temp0[temp0$order_taxon %in% c("Pleuronectiformes"), ]
temp2 <- temp1 %>% 
  dplyr::filter(where != "Present in EBS and NBS") %>% 
  dplyr::group_by(where) %>% 
  dplyr::summarise(n = n()) %>% 
  dplyr::mutate(where = paste0(tolower(substr(x = where, start = 1, stop = 1)), 
                               substr(x = where, start = 2, stop = nchar(where))), 
                including = NA)
for (i in 1:nrow(temp2)) {
  temp2$including[i] <- 
    NMFSReports::text_list(
      paste0(
        temp1$common_name[grepl(pattern = temp2$where[i], 
                                x = temp1$where, 
                                ignore.case = TRUE)], 
        " (*", 
        temp1$species_name[grepl(pattern = temp2$where[i], 
                                 x = temp1$where, 
                                 ignore.case = TRUE)],
        "*)"))
}

insert <- paste0(insert, "In ", maxyr, " ", 
                     
                     NMFSReports::text_list(
                       paste0(xunits(temp2$n), 
                              " flatfish species that were ", 
                              temp2$where, " including ",
                              temp2$including )),
                     " (Table ", 
                     crossref(list_obj = list_tables, 
                              nickname = "tab_species_composition", 
                              sublist = "number"), ").")
}
```

In the `r SRVY`, a total of `r fish_sp ` species of fishes were identified, representing `r xunits(length(unique(temp$family_taxon[temp$taxon == "fish"])))` families and `r xunits(length(unique(temp$genus_taxon[temp$taxon == "fish"])))` genera were identified from catch samples taken in the combined EBS (Appendix B1) and NBS (Appendix B2) survey areas. `r insert`

```{r}
# No. fish spp
temp <- spp_info_maxyr %>% 
  dplyr::filter(used_in_counts == TRUE) 

invert_sp <- xunits(length(unique(temp$report_name_scientific[temp$taxon == "invert" & 
                                                              !(grepl(pattern = " sp.", x = temp$report_name_scientific, fixed = T)) & 
                                                              !(grepl(pattern = " unid.", x = temp$report_name_scientific, fixed = T))])))
```

`r list_tables$tab_species_composition$res `

> deal with appendicies # TOLEDO

```{r}
temp <- dplyr::left_join(x = catch_haul_cruises, 
                         y = spp_info, 
                         by = "species_code") %>% 
  dplyr::filter(taxon == "invert") %>% 
  dplyr::select(species_code, species_taxon, phylum_taxon, taxon, SRVY) %>% 
  dplyr::distinct()

temp0 <- dplyr::full_join(
  x = temp %>% 
                      dplyr::filter(!is.na(species_taxon)) %>% 
                      dplyr::group_by(SRVY) %>% 
                      dplyr::summarise(species_taxon = n()),
  y = temp %>% 
                      dplyr::filter(!is.na(species_code)) %>% 
                      dplyr::group_by(SRVY) %>% 
                      dplyr::summarise(species_code = n()), 
  by = "SRVY") %>% 
  dplyr::mutate(perc = round(((species_code - species_taxon)/species_code)*100, digits = 2))

```

A total of `r invert_sp ` different invertebrate taxa representing `r xunits(length(unique(temp$phylum_taxon[temp$taxon == "invert"])))` phyla were identified in the combined catch samples taken from the EBS (Appendix B3)`r ifelse(SRVY == "NEBS", " and NBS (Appendix B4)", "")`. In `r maxyr`, `r NMFSReports::text_list(paste0("the ", temp0$SRVY, " had a total of ", xunits(temp0$species_code), " taxa of which ", xunits(temp0$species_taxon), " were identified to the species level"))`. The remaining of invertebrate taxa in each survey area were identified to the genus level or higher. The lack of species level identifications among invertebrates was due to a variety of factors that are outlined in @RN934.

`r list_tables$tab_biomass_est_fish_EBS$res `

`r ifelse(SRVY == "NEBS", list_tables$tab_biomass_est_fish_NBS$res, "") `

`r list_tables$tab_biomass_est_invert_EBS$res `

`r ifelse(SRVY == "NEBS", list_tables$tab_biomass_est_invert_NBS$res, "") `

> All species are idenfitied using and logged in AFSC's databases as *Eschmeyer's Ctaglog of Fishes* (CITATION Eschmeyer) and *An Annotated Checklist of the Marine Macroinvertebrates of Alaska* (CITATION: Drumm). 

## Relative Abundance

> why 12?

> missing data from invert EBS?

> waiting for new data from rebecca

```{r}
temp <- data.frame()

for (i in 1:nrow(haul_cruises_maxyr)) {
  
  temp1 <- cpue_maxyr %>% 
    dplyr::filter(SRVY == haul_cruises_maxyr$SRVY[i]) %>% 
    dplyr::select(cpue_kgha, species_code, taxon) %>%
    dplyr::group_by(species_code, taxon) %>% 
    dplyr::summarise(cpue_kgha = sum(cpue_kgha)) %>%
    dplyr::arrange(-cpue_kgha) %>% 
    dplyr::ungroup()
  
  temp <- rbind.data.frame(
    temp, 
    data.frame(
      SRVY = haul_cruises_maxyr$SRVY[i], 
      fish = temp1 %>% 
        dplyr::filter(taxon == "fish") %>%
        dplyr::summarise(cpue_kgha = sum(cpue_kgha)) %>% 
        as.numeric(), 
      invert = temp1 %>% 
        dplyr::filter(taxon == "invert") %>%
        dplyr::summarise(cpue_kgha = sum(cpue_kgha)) %>% 
        as.numeric(), 
      all = temp1 %>% 
        dplyr::summarise(cpue_kgha = sum(cpue_kgha)) %>% 
        as.numeric(), 
      topfish = temp1 %>% 
        dplyr::filter(taxon == "fish") %>%
        head(12) %>%
        dplyr::summarise(cpue_kgha = sum(cpue_kgha)) %>% 
        as.numeric()))
}  

temp$top_fish <- paste0(round(x = temp$topfish/temp$fish, digits = 0), "%")
temp$top_all <- paste0(round(x = temp$topfish/temp$all, digits = 0), "%")

# temp[,1:4]<-NMFSReports::mod_number(x = temp[,1:4], comma_seperator = T, digits = 0)

temp[,2:5] <- format(temp[,2:5], digits = 0, trim = F, big.mark = ",", scientific = F)

# The top 12 fish taxa in the EBS accounted for 73% (243 kg/ha) of total catch CPUE (335 kg/ha) and 97% of total fish CPUE (252 kg/ha), compared with the NBS where the top 12 fish taxa accounted for only 61% (140 kg/ha) of the total catch CPUE (228 kg/ha) and 98% of total fish CPUE (143 kg/ha). 

```

`r NMFSReports::text_list(paste0("Of the top 12 fish taxa in the ",temp$SRVY," accounted for ",temp$top_all," (",temp$topfish," kg/ha) of total catch CPUE (",temp$all," kg/ha) and ",temp$top_fish," of total fish CPUE (",temp$fish," kg/ha)")) `

> Not sure how to automate this...?

`The lower fish biomass in the NBS is consistent with results of a broader analysis of all survey years showing decreasing fish biomass with increasing latitude on the Bering Sea continental shelf [@RN936]. The relative abundance of flatfishes and gadids were high in the` `r NMFSReports::text_list(SRVY) `, but the species comprising each taxonomic group and their proportion of the total biomass were different between the two areas. In the `r SRVY `, there were 15 different flatfish species that together comprised almost half of the total fish biomass (48%) with yellowfin sole (22%) and northern rock sole (11%) having the greatest proportions. This contrasted with the NBS where there were twelve flatfish species with yellowfin sole (15%) and Alaska plaice (12%) making up a majority of the total fish biomass. 

Walleye pollock and Pacific cod together comprised 44% of the total fish biomass in the `r SRVY ` compared to only 57% in the NBS. The abundance of walleye pollock was relatively high in the `r SRVY ` middle and outer shelf compared to the inner shelf and in the NBS where bottom depths are generally less than 50 m (Figure `r ifelse(SRVY == "NEBS", crossref(list_obj = list_tables, nickname = "tab_majortaxa_pchange_NBS", sublist = "number"), "") `). Unlike the `r SRVY `, saffron cod (*Eleginus gracilis*), was among the 12 most abundant fish species in the NBS, and Arctic cod (*Boreogadus saida*) was the 18th most abundant. For a descending rank of all organisms caught in each area, see Appendix B1 ( `r SRVY `) and Appendix B2 (NBS).

`r list_tables$tab_majortaxa_pchange_EBS$res `

`r ifelse(SRVY == "NEBS", list_tables$tab_majortaxa_pchange_NBS$res, "") `

## Biomass, Abundance, Distribution, CPUE, and Size Composition of Principal Species and Species Groups

Total demersal animal biomass for the `r SRVY ` was estimated at 16.5 million metric tons (t) and for the NBS at 4.6 million t. In the EBS, the proportion of fishes (75%; Table `r crossref(list_obj = list_tables, nickname = "tab_biomass_est_fish_EBS", sublist = "number")`) was three times higher than invertebrates (25%; Table `r crossref(list_obj = list_tables, nickname = "tab_biomass_est_invert_EBS", sublist = "number")`). 

```{r}
# This trend was similarly true in the NBS where the proportion of fishes (63%; Table `r crossref(list_obj = list_tables, nickname = "tab_biomass_est_fish_NBS", sublist = "number")`) was greater than invertebrates (37%; Table `r crossref(list_obj = list_tables, nickname = "tab_biomass_est_invert_NBS", sublist = "number")`). Pleuronectids dominated the fish biomass in both the EBS (6.0 million t) and NBS (0.9 million t), and gadids were the second most abundant fish group in both areas. Walleye pollock were the most abundant gadid in both the `r SRVY ` and NBS (Table `r crossref(list_obj = list_tables, nickname = "tab_biomass_est_fish_EBS", sublist = "number")` and 6a). Echinoderms and crustaceans were the major invertebrate taxa comprising 16% of the total animal biomass in the `r SRVY ` (Table `r crossref(list_obj = list_tables, nickname = "tab_biomass_est_invert_EBS", sublist = "number")`) and 25% in the NBS (Table `r crossref(list_obj = list_tables, nickname = "tab_biomass_est_invert_NBS", sublist = "number")`).
```


Survey results for major fish fauna are presented in maps of geographic distribution and abundance, plots of total abundance-at-size, and tables with estimates of biomass and population number (Table `r crossref(list_obj = list_tables, nickname = "tab_estimates_maxyr_spp_EBS", sublist = "number")``r ifelse(SRVY == "NEBS", paste0(" and ", crossref(list_obj = list_tables, nickname = "tab_estimates_maxyr_spp_NBS", sublist = "number")), "")`). Major species presented include walleye pollock (Figures 7-8 and Table 7a, b), Pacific cod (Figures 9-10 and Table 8a, b), yellowfin sole (Figures 11-12 and Table 9a, b), northern rock sole (Figures 13-14 and Table 10a, b), flathead sole (Figures 15-16 and Table 11a, b), Bering flounder (Figures 17-18 and Table 12a, b), Alaska plaice (Figures 19-20 and Table 13a, b), Greenland turbot (Figures 21-22 and Table 14a, b), arrowtooth flounder (Figures 23-24 and Table 15a, b), Kamchatka flounder (Figures 25-26 and Table 16a, b), and Pacific halibut (Figures 27-28 and Table 17a, b). Mean CPUE by weight and number and maps of geographic distribution for many other species are also included (Tables 18-19, Figures 29-61). Appendix D contains population estimates by sex and size class for all 11 of these fish species. 

`r list_tables$tab_estimates_maxyr_spp_EBS$res `

`r ifelse(SRVY == "NEBS", list_tables$tab_estimates_maxyr_spp_NBS$res, "") `


Total biomass and population size were estimated for an additional 24 fish species that were common in either the `r SRVY ` and NBS or both (Tables 18 to 19). For each of the 24 species, there is a corresponding map showing the geographic distribution and relative abundance (Figures 29 to 53). 

#### Spatial Distribution of Selected Invertebrates

> from 2018

Plots of the broad spatial distribution patterns for eight major invertebrates on the combined `r SRVY ` and NBS continental shelf are presented in Figures 54 to 61. The purple sea star, (Asterias amurensis), is common in the Bering and Chukchi Seas (Hamizaki et al. 2005, Feder et al. 2005) and it was the invertebrate taxon with the highest ranked catch rate by weight in both the `r SRVY ` and NBS. Catch rates for the purple sea star were highest in the middle shelf between the Pribilof Islands and Nunivak Island and along the inner shelf from Bristol Bay to the Bering Strait (Figure 61). 

Figures 54 to 57 show the shelf-wide distributions of the four major commercial crab species: blue king crab, red king crab, snow crab (Chionoecetes opilio), and Tanner crab (Chionoecetes bairdi). Commercial crab stocks are managed by the ADF&G with federal oversight by NMFS. For more detailed information on BT survey results for commercial crab refer to Chilton et al. (2011), and for the most recent modeling data on the status of these commercial crab stocks, refer to the annual Stock Assessment and Fishery Evaluation report prepared by the NPFMC. 

> from 2017

Plots of distribution for seven major invertebrate taxa are presented in Figures 55 to 61 including the purple sea star (Asterias amurensis), northern neptune snail (Neptunea heros), jellyfishes (Scyphozoa), red king crab (Paralithodes camtschaticus), blue king crab (P. platypus), snow crab (Chionoecetes opilio), and Tanner crab (C. bairdi). These last four plots are the major commercial crab species in Alaska. Commercial crab stocks are managed by the ADF&G with federal oversight by NMFS. For more detailed information on bottom trawl survey results for commercial crab refer to Lang et al. (2018), and for the most recent modeling data on the status of these commercial crab stocks, refer to the annual Stock Assessment and Fishery Evaluation report prepared by the NPFMC. 

An interactive map of CPUE by species overlaid with temperature data for the 2017 EBS and NBS surveys, as well as all for other AFSC bottom trawls surveys, can be found at https://www.afsc.noaa.gov/RACE/groundfish/survey_data/default.htm. The CPUE data with associated station information that includes position, surface and bottom temperatures, and bottom depth can be downloaded from https://www.fisheries.noaa.gov/alaska/commercial-fishing/alaska-groundfish-bottom-trawl-survey-data.

## Summary of Results for Selected `r NMFSReports::text_list(haul_cruises_maxyr$SRVY_long)` Fish and Invertebrate Fauna




