
# Results and Discussion{#results}

## Ocean Temperatures and the Cold Pool

```{r results-cold-pool-insert, child=paste0(dir_out_rawdata, "/0-cold-pool.Rmd")}
```

<!-- \newpage -->

```{r fig-temperature-10}
nickname <- "fig-temperature-bt-1-data"
```

```{r temperature-1-child, child = paste0(dir_code, "_child_report_figtab.Rmd")}
```

```{r fig-temperature-20}
nickname <- "fig-temperature-bt-2-data"
```

```{r temperature-2-child, child = paste0(dir_code, "_child_report_figtab.Rmd")}
```

```{r fig-temperature-30}
nickname <- "fig-temperature-st-1-data"
```

```{r temperature-3-child, child = paste0(dir_code, "_child_report_figtab.Rmd")}
```

```{r fig-temperature-40}
nickname <- "fig-temperature-st-2-data"
```

```{r temperature-4-child, child = paste0(dir_code, "_child_report_figtab.Rmd")}
```

```{r fig-mean-temperature0}
nickname <- "fig-mean-temperature"
```

```{r fig-mean-temperature-child, child = paste0(dir_code, "_child_report_figtab.Rmd")}
```

```{r fig-cold-pool-area0}
nickname <- "fig-cold-pool-area"
```

```{r fig-cold-pool-area-child, child = paste0(dir_code, "_child_report_figtab.Rmd")}
```

## Survey Data and Specimen Collections

```{r tab-specimen-samples-howmany}
  load(file = paste0(dir_out_figtab, "tab-specimen-samples-EBS.rdata"))
  temp <- obj$raw
  if (plural_surveys == "s") {
  load(file = paste0(dir_out_figtab, "tab-specimen-samples-NBS.rdata"))
    temp <- temp %>% 
      dplyr::bind_rows(obj$raw)
  }
  names(temp) <- gsub(x = names(temp), pattern = "\n", replacement = " ")
  temp <- temp %>%
    dplyr::filter(common_name == "Total")  %>% 
    dplyr::select(-common_name) %>% 
    dplyr::left_join(cruises_maxyr %>% 
                       dplyr::select(SRVY, SRVY_long) %>% 
                       dplyr::distinct()) %>% 
    dplyr::mutate(across(where(is.numeric), xunits))
  
  # str00 <- grepl(x = names(temp %>% 
  #     dplyr::select(-dplyr::starts_with("SRVY"))), pattern = " deployed")
  # str00 <- ifelse(str00, "deployed ", "")
  names(temp) <- gsub(x = names(temp), pattern = "Satellite tags deployed", replacement = "fish for satellite tagging")
    
  str0 <- c()
  for (i in 1:nrow(temp)) {
    temp0 <- t(temp[i, ] %>% 
      dplyr::select(-dplyr::starts_with("SRVY")))
  str0 <- paste0(str0, text_list(paste0(temp0, " ", tolower(rownames(temp0)) )), 
                                 " during the ", 
                 ifelse(i == 1, paste0(maxyr, " "), ""), 
                 temp[i, "SRVY_long"])
}
```

Survey teams collected `r str0 ` shelf trawl survey`r plural_surveys` (Table`r plural_surveys` \@ref(fig:tab-specimen-samples-ebs)`r ifelse(SRVY == "NEBS", " and \\@ref(fig:tab-specimen-samples-nbs)", "")`). Other special collections are listed in Table \@ref(tab:tab-special-projects).

```{r tab-specimen-samples-0}
nickname <- "tab-specimen-samples-"
```

```{r tab-specimen-samples--child, child = paste0(dir_code, "_child_report_figtab.Rmd")}
```

## Species Composition

```{r results-species-composition}
str0 <- ""

# count taxon
temp <- dplyr::left_join(
  x = catch_haul_cruises_maxyr %>% 
    dplyr::select(SRVY, species_code) %>% 
    dplyr::distinct(), 
  y = spp_info %>% 
    dplyr::filter(used_in_counts) %>%
    dplyr::select(species_code, phylum, family, genus, species, taxon) %>%
    dplyr::distinct(), 
  by = "species_code") %>% 
  # dplyr::filter(taxon == "fish") %>%
  dplyr::select(species_code, phylum, family, genus, species, taxon, SRVY) %>% 
  dplyr::distinct() %>% 
  dplyr::filter(!is.na(taxon))

temp1 <- temp %>% 
    dplyr::group_by(SRVY, taxon) %>% 
    dplyr::summarise_all(dplyr::n_distinct, na.rm = TRUE) %>% 
    dplyr::left_join(
      data.frame(SRVY = SRVY1, 
                 SRVY_long = SRVY11)) %>% 
      dplyr::mutate(dplyr::across(where(is.numeric), xunits)) 

for (i in 1:length(unique(temp1$SRVY))) {
  temp0 <- temp1 %>% 
    dplyr::filter(SRVY == unique(temp1$SRVY)[i])
  
str0 <- paste0(
  "A total of ",temp0$species_code[temp0$taxon == "fish"],
  " fish taxa representing ",temp0$family[temp0$taxon == "fish"],
  " families and ",temp0$genus[temp0$taxon == "fish"],
  " genera were identified during the ",
  maxyr," ",SURVEY," survey",plural_surveys," (Appendix Table", plural_surveys,
  " A \\@ref(tab:tab-app-taxa-found-EBS-fish)", 
  ifelse(plural_surveys == "s", " and B \\@ref(tab:tab-app-taxa-found-NBS-fish)", ""),
  "). Of these ",
  temp0$species_code[temp0$taxon == "fish"]," taxa, ",
  temp0$species[temp0$taxon == "fish"]," were identified to species level, while the remaining taxa were identified to the genus level or higher. ",
               
  "Similarly, there were ",
  temp0$species_code[temp0$taxon == "invert"],
  " different invertebrate taxa representing ",
               temp0$phylum[temp0$taxon == "invert"],
  " phyla, of which ",
  temp0$species[temp0$taxon == "invert"],
  " taxa were identified to species level (Appendix Table", plural_surveys,
  " A \\@ref(tab:tab-app-taxa-found-EBS-invertebrate)", 
  ifelse(plural_surveys == "s", " and B \\@ref(tab:tab-app-taxa-found-NBS-invertebrate)", ""),
  "). ")
}
```

`r str0`The lack of species level identifications among invertebrates was due to a variety of factors that are outlined in @RN934 and @Stevensonetal2016. 

```{r results-species-composition-encountered-in-one-survey}
str0 <- ""
if (SRVY == "NEBS" & "NBS" %in% temp0$SRVY) {
  # how many species encountered in one survey area but not in the other?
  load(file = paste0(dir_out_figtab, "tab-species-composition.rdata"))
  temp3 <- obj$raw %>%
    dplyr::left_join(x = .,
                     y = spp_info %>%
                       dplyr::select(species_code, order, species_name),
                     by = c("species_code"))
  
  str0 <- paste0( 
    "Of the ", 
    xunits(nrow(temp[temp$SRVY == "EBS",])),
    " fish species found in the eastern Bering Sea, ",
    xunits(nrow(temp3[temp3$where == "ebs",])), 
    " did not occur in the northern Bering Sea (Table \\@ref(tab:tab-species-composition)). In comparison, ",
    xunits(nrow(temp3[temp3$where == "nbs",])), 
    " of the ",
    xunits(nrow(temp[temp$SRVY == "NBS",])),
    " fish species encountered in the northern Bering Sea were not encountered in the eastern Bering Sea (Table \\@ref(tab:tab-species-composition)). ")
  
  # flatfish
  temp4 <- temp3[temp3$order %in% c("Pleuronectiformes"), ]
  temp5 <- temp4 %>% 
    dplyr::filter(where != "both") %>% 
    dplyr::group_by(where) %>% 
    dplyr::summarise(n = n()) %>% 
    dplyr::mutate(
                  including = NA, 
                  where0 = dplyr::case_when(
                    where == "nbs" ~ "encountered in the northern Bering Sea but not in the eastern Bering Sea",
                    where == "ebs" ~ "encountered in the eastern Bering Sea but not in the northern Bering Sea"
                  ))
  for (i in 1:nrow(temp5)) {
    temp5$including[i] <- 
      text_list(
        paste0(
          temp4$common_name[grepl(pattern = temp5$where[i], 
                                  x = temp4$where, 
                                  ignore.case = TRUE)], 
          " (*", 
          temp4$species_name[grepl(pattern = temp5$where[i], 
                                   x = temp4$where, 
                                   ignore.case = TRUE)],
          "*)"))
  }
  
  str0 <- paste0(str0, "In ", maxyr, ", ", 
                   
                   text_list(
                     paste0(xunits(temp5$n), 
                            " flatfish species ", ifelse(temp5$n>1, "were", "was"), " ", 
                            temp5$where0, " (",
                            temp5$including, ")"), 
                     sep = "; "),
                   " (Table \\@ref(tab:tab-species-composition)).")
  
str0 <- gsub(pattern = ") (", replacement = "; ", x = str0, fixed = TRUE)
}
```

`r str0`

```{r tab-species-composition0, eval = (SRVY == "NEBS")}
nickname <- "tab-species-composition"
```

```{r tab-species-composition-child, child = paste0(dir_code, "_child_report_figtab.Rmd"), eval = (SRVY == "NEBS" & "NBS" %in% haul_cruises_maxyr$SRVY)}
```

<!-- <br> -->

## Biomass, Abundance, and Catch per Unit Effort

```{r results-tot-biomass}

# example output: 
# [1] "The total demersal organismal biomass for the eastern Bering Sea was estimated at 12 million t and total demersal organismal biomass for the northern Bering Sea was estimated at 2.9 million t. In the eastern Bering Sea, the proportion of fishes (76%; Table \\@ref(tab:tab-biomass-est-EBS-fish)) was higher than invertebrates (24%; Table \\@ref(tab:tab-biomass-est-EBS-invert)) and in the northern Bering Sea, the proportion of fishes (48%; Table \\@ref(tab:tab-biomass-est-NBS-fish)) was lower than invertebrates (52%; Table \\@ref(tab:tab-biomass-est-NBS-invert)). The lower relative fish biomass in the northern Bering Sea than in the eastern Bering Sea is consistent with results of a broader analysis of all survey years presented by @RN936, which showed decreasing fish biomass with increasing latitude on the eastern Bering Sea continental shelf. "

total_biomass0 <- total_biomass %>% 
  dplyr::filter(year == maxyr) %>% 
  dplyr::group_by(SRVY, year, SRVY_long) %>% 
  dplyr::summarise(total = sum(total, na.rm = TRUE)) %>% 
  dplyr::ungroup()

temp2 <- dplyr::full_join(
  y = total_biomass0, 
  x = total_biomass  %>% 
    dplyr::filter(year == maxyr) %>% 
    dplyr::rename(total_taxon = total)) %>% 
  dplyr::mutate(
    prop = (total_taxon/total), 
    perc = paste0(formatC(x = prop*100, 
                          digits = 0, format = "f", big.mark = ","), 
                  "%"), 
    group = gsub(pattern = "Total ", replacement = "", x = taxon) ) %>% 
  tidyr::pivot_wider(id_cols = "SRVY", 
                     names_from = "taxon", 
                     values_from = c(total_taxon, "perc", "prop")) %>%
  dplyr::mutate(case = dplyr::case_when(
    perc_fish == perc_invert ~ "about the same as", 
      prop_fish>prop_invert ~ "higher than",
      prop_fish<prop_invert ~ "lower than")) %>% 
  dplyr::left_join(
    y = data.frame(SRVY = SRVY1, 
                   SRVY_long = SRVY11))

temp1 <- left_join(
  x = total_biomass %>% 
    dplyr::filter(year == maxyr), 
  y = stratum %>% 
    dplyr::group_by(SRVY) %>% 
    dplyr::summarise(area_km2 = sum(area_km2, na.rm = TRUE)), 
  by = "SRVY") %>% 
  dplyr::mutate(prop = total/area_km2, 
                taxon = gsub(pattern = "Total ", replacement = "", x = taxon)) %>% 
  dplyr::filter(taxon == "fish")

str0 <- paste0("The ", 
               text_list(paste0(
                 "total demersal organismal biomass for the ", total_biomass0$SRVY_long, 
                 " was estimated at ", xunits(total_biomass0$total), " t")), 
               ifelse(plural_surveys == "", "", ". ") )

str00 <- ""
for (ii in 1:length(temp2$SRVY)) {
  
  str000 <- ifelse(ii != 1 & temp2$prop_fish[ii]>temp2$prop_invert[ii], "also ","")
  
  # sentence transitions
  if (ii == 2) { # second of 2 surveys being assessed
  str00 <- paste0(str00, " and in the ")
  } else if (plural_surveys == "") { # only one survey being assessed
  str00 <- paste0(str00, " and")
  } else { # first of 2 surveys being assessed
  str00 <- paste0(str00, "In the ")
  }
  
  str00 <- paste0(str00, 
                  # ifelse(ii==2, " and in the ", ifelse(plural_surveys == "", "", "In the ")), 
                  paste0(ifelse(plural_surveys == "", "", paste0(temp2$SRVY_long[ii], ", ")), 
                         " the proportion of fishes (", 
                         temp2$perc_fish[ii], 
                         "; Table \\@ref(tab:tab-biomass-est-",  temp2$SRVY[ii],
                         "-fish)) was ", str000,  
                         temp2$case[ii],
                         " invertebrates (", 
                         temp2$perc_invert[ii], 
                         "; Table \\@ref(tab:tab-biomass-est-", temp2$SRVY[ii], 
                         "-invert))"))
}
str0 <- paste0(str0, str00, ". ")

if (SRVY == "NEBS") {
  str0 <- paste0(str0, 
                 paste0(ifelse(temp1$prop[temp1$SRVY=="EBS"]>temp1$prop[temp1$SRVY=="NBS"], 
                               "The lower relative fish biomass in the northern Bering Sea than in the eastern Bering Sea is consistent", 
                               "The higher relative fish biomass in the northern Bering Sea than in the eastern Bering Sea is inconsistent"), 
                        " with results of a broader analysis of all survey years presented by @RN936, which showed decreasing fish biomass with increasing latitude on the eastern Bering Sea continental shelf. ", 
                        "") ) 
}

str0 <- gsub(pattern = ") (", replacement = "; ", x = str0, fixed = TRUE)

```

`r str0`

```{r results-tot-biomass2}

# example output:
# [1] "Pleuronectidae (flatfishes) and Gadidae (cods) were the fish families with highest biomass in both the eastern Bering Sea (49.7% and 7.3% of the total biomass, respectively), and the northern Bering Sea (57.5% and 10.6% of the total biomass, respectively; Tables \\@ref(tab:tab-biomass-est-EBS-fish) and \\@ref(tab:tab-biomass-est-NBS-fish)). In the eastern Bering Sea, the family Gadidae was primarily comprised of walleye pollock (*Gadus chalcogrammus*, 34.5%) and Pacific cod (*Gadus macrocephalus*, 7.3%); and the family Pleuronectidae was primarily comprised of yellowfin sole (*Limanda aspera*, 15.2%) and northern rock sole (*Lepidopsetta polyxystra*, 15.1%). In the northern Bering Sea, the family Gadidae was primarily comprised of walleye pollock (*Gadus chalcogrammus*, 26.2%) and Pacific cod (*Gadus macrocephalus*, 7.8%); and the family Pleuronectidae was primarily comprised of yellowfin sole (*Limanda aspera*, 28.3%) and Alaska plaice (*Pleuronectes quadrituberculatus*, 22.2%). "

str0 <- ""
if (SRVY == "NEBS" & "NBS" %in% haul_cruises_maxyr$SRVY) {
  
  temp1 <- temp2 <- temp3 <- data.frame()
  
  for (i in 1:length(SRVY1)) {
    load(file = paste0(dir_out_figtab, "tab-biomass-est-", SRVY1[i], "-fish.rdata"))
    temp1 <- obj$raw %>%
      dplyr::mutate(SRVY = SRVY1[i]) %>%
      dplyr::filter(is.na(taxon) |
                      grepl(pattern = "Total", x = taxon, ignore.case = TRUE )) %>% 
      dplyr::filter(!grepl(pattern = "Total", x = group, ignore.case = TRUE ) &
                      !grepl(pattern = "Other", x = group, ignore.case = TRUE )) %>% 
      dplyr::select(SRVY, group, `999`, prop = prop0) %>% 
      dplyr::arrange(-prop) %>% 
      dplyr::mutate(order = 1:nrow(.)) %>% 
      dplyr::bind_rows(temp1, .)
    
    temp2 <- obj$raw %>%
      dplyr::mutate(SRVY = SRVY1[i]) %>%
      dplyr::filter(group %in% temp1$group[1:2] & 
                      !grepl(pattern = "Total ", x = taxon, ignore.case = TRUE )) %>% 
      dplyr::select(SRVY, group, taxon, `999`, prop = prop0) %>% 
      dplyr::arrange(-prop) %>% 
      dplyr::mutate(order = 1:nrow(.)) %>% 
      dplyr::bind_rows(temp2, .)
  }
  
  temp1 <- temp1 %>% 
    tidyr::pivot_wider(id_cols = c("group"), 
                       names_from = "SRVY", 
                       values_from = c("999", "prop", "order")) %>%
    dplyr::mutate(same = ifelse(order_EBS == order_NBS, TRUE, FALSE)) %>% 
    dplyr::filter(!(is.na(SRVY)))

  
  temp2 <- temp2 %>% 
    tidyr::pivot_wider(id_cols = c("group", "taxon"), 
                       names_from = "SRVY", 
                       values_from = c("999", "prop", "order")) %>%
    dplyr::mutate(same =ifelse(order_EBS == order_NBS, TRUE, FALSE)) %>% 
    dplyr::left_join(
      x = ., 
      y = spp_info_maxyr %>% 
        dplyr::select(species_name, common_name), 
      by = c("taxon" = "common_name")  )
  
  # temp3: top 3 spp in each group
  temp0 <- tidyr::crossing(group = unique(temp2$group), 
                           SRVY = SRVY1) %>% 
    dplyr::arrange(SRVY, group) %>% 
    dplyr::mutate(str0 = NA)
  
  for (i in 1:nrow(temp0)) {
    
    temp3 <- temp2 %>% 
      dplyr::rename(prop = paste0("prop_", temp0$SRVY[i]),
                    order = paste0("order_", temp0$SRVY[i])) %>%
      dplyr::arrange(order) %>% 
      dplyr::filter(
        group == temp0$group[i]) %>% 
      head(3) %>%
      dplyr::mutate(prop = paste0(round(x = prop*100, digits = 1), "%"), 
                    SRVY = temp0$SRVY[i]) %>%
      dplyr::arrange(order) %>% 
      dplyr::select(SRVY, group, taxon, species_name, prop) %>% # 
      dplyr::filter(prop != "0%") %>% 
      dplyr::filter(!grepl(pattern = "Total", x = taxon, ignore.case = TRUE ) &
                      !grepl(pattern = "Other", x = taxon, ignore.case = TRUE )) 

    
    if (nrow(temp3)>1) {
      temp0$str0[temp0$SRVY == temp0$SRVY[i] & 
                   temp0$group == temp0$group[i]] <- 
        text_list(paste0(temp3$taxon, " (*", temp3$species_name, 
                         "*, ",temp3$prop,")"))
      temp0$group1 <- unlist(regmatches(temp0$group,
                                        gregexpr(
                                          "(?<=\\().*?(?=\\))", # everything within a (*)
                                          temp0$group, perl=T)))
      temp0$group0 <- unlist(lapply(strsplit(x = temp0$group, split = " ", fixed = TRUE), `[[`, 1))
    }
  }
  
  temp0$group0 <- paste0("the family ", temp0$group0)
  
  temp0$str0 <- gsub(pattern = "*NA*, ", replacement = "", x = temp0$str0, fixed = TRUE)
  temp0$str0 <- gsub(pattern = "  ", replacement = " ", x = temp0$str0, fixed = TRUE)
  
  temp3 <- c()
  for (i in 1:length(SRVY1)){
    temp00 <- temp0[temp0$SRVY == SRVY1[i],]
    temp4 <- text_list(paste0(
      temp00$group0, 
      c(", by biomass,", rep_len(x = "", length.out = nrow(temp00)-1)), 
      " was primarily comprised of ", 
      temp00$str0), sep_last2 = "; and ")
    temp3 <- paste0(temp3, 
                    paste0("In the ", SRVY11[i], ", ", temp4, ". "))
  }
  
  str0 <- paste0(
    text_list(temp1$group[1:2]),
    " were the fish families with highest biomass in both the eastern Bering Sea (",
    text_list(
      paste0(round(x = temp1$prop_EBS[1:2]*100, digits = 1), "%")), 
    " of the total fish biomass, respectively) and the northern Bering Sea (",
    text_list(
      paste0(round(x = temp1$prop_NBS[1:2]*100, digits = 1), "%")), 
    " of the total fish biomass; Tables \\@ref(tab:tab-biomass-est-EBS-fish) and \\@ref(tab:tab-biomass-est-NBS-fish)). ", 
    temp3)
}
```

`r str0`

```{r results-benthic-community}

str0 <- c()
  # paste0("Changes were observed in the ", SURVEY," benthic communities between ",
  #              compareyr," and ", maxyr,". ")

for (i in 1:length(SRVY1)) {
  load(file = paste0(dir_out_figtab, "tab-majortaxa-pchange-", haul_cruises_maxyr$SRVY[i], ".rdata"))
  temp0 <- obj$raw
  temp <- 
    temp0 %>% 
    dplyr::filter(!is.na(change0) &
                    SRVY == SRVY1[i]) %>%
    dplyr::mutate(case = case_when(
      change0 > 0 ~ "increased", 
      change0 < 0 ~ "decreased"), 
      print_name = print_name1 ) %>% 
    dplyr::arrange(-change0) %>%
    dplyr::select(print_name, maxyr, compareyr, change, case) 
  
  temp <-  
    dplyr::bind_rows(
      temp %>% 
        dplyr::filter(case == "increased") %>% 
        head(5), 
      temp %>% 
        dplyr::filter(case == "decreased") %>% 
        tail(5) ) %>% 
    dplyr::mutate(print_name = gsub(pattern = "include", replacement = ", which", x = print_name))
  
    temp1 <- data.frame(maxyr = sum(total_biomass$total[
    total_biomass$SRVY == SRVY1[i] & 
      total_biomass$year == maxyr], na.rm = TRUE), 
    compareyr = sum(total_biomass$total[
      total_biomass$SRVY == SRVY1[i] & 
        total_biomass$year == compareyr], na.rm = TRUE))
  
  str0 <- paste0(str0, 
                 "The total estimated biomass ", 
                 ifelse(plural_surveys == "", "", paste0("in the ",SRVY11[i], " ")),
                 ifelse(temp1$compareyr<temp1$maxyr, "increased", "decreased"),
                 " from ",
                 xunits(temp1$compareyr)," t in ", compareyr," to ",
                 xunits(temp1$maxyr)," t in ", maxyr, ". ", 
                 
                 # taxa increased
                 "Large increases in ",
                 ifelse(plural_surveys == "", "", paste0(SRVY11[i], " ")),
                 "biomass were observed for ", 
                 text_list(paste0(temp$print_name[temp$case == "increased"],
                                  " (", temp$change[temp$case == "increased"], ")")), 
                 " (Table \\@ref(tab:tab-majortaxa-pchange-", SRVY1[i], ")). ",
                 # taxa decreased
                 "Large decreases in ", 
                                  ifelse(plural_surveys == "", "", paste0(SRVY11[i], " ")),
                 " biomass were observed for ", 
                 text_list(paste0(temp$print_name[temp$case == "decreased"],
                                  " (", temp$change[temp$case == "decreased"], ")")), 
                 " (Table \\@ref(tab:tab-majortaxa-pchange-", SRVY1[i], ")). "
  )
}

str0 <- gsub(x = str0, pattern = ") (", replacement = "; ", fixed = TRUE)

```

`r str0`While exhaustive efforts are made to standardize catch processing and data collection, variation in catchability may cause some differences in these results between years [@KotwickiOno2019].

```{r results-top-10-taxon}
temp <- data.frame()
load(file = paste0(dir_out_figtab, "tab-est-spp-wt.rdata"))

for (i in 1:nrow(haul_cruises_maxyr)) {
  
  temp <- obj$raw %>% 
    dplyr::filter(SRVY == haul_cruises_maxyr$SRVY[i]) %>%
    dplyr::select(cpue_kgkm2_mean, print_name) %>%
    dplyr::arrange(-cpue_kgkm2_mean) %>% 
    dplyr::ungroup() %>% 
    head(10) %>% 
    dplyr::summarise(cpue_kgkm2_mean = sum(cpue_kgkm2_mean, na.rm = TRUE)) %>% 
    dplyr::mutate(SRVY = haul_cruises_maxyr$SRVY[i], 
                  taxon = "topfish") %>% 
    dplyr::bind_rows(temp, .)
}  

temp <- biomass %>% 
  dplyr::filter(year == maxyr & 
                  stratum == 999) %>%
  dplyr::select(cpue_kgkm2_mean, SRVY, taxon) %>% 
  dplyr::group_by(SRVY, taxon) %>% 
  dplyr::summarise(cpue_kgkm2_mean = sum(cpue_kgkm2_mean, na.rm = TRUE)) %>% 
  dplyr::ungroup() %>% 
  dplyr::bind_rows(temp, .) %>% 
  pivot_wider(data = ., id_cols = "SRVY", names_from = taxon, values_from = cpue_kgkm2_mean ) %>% 
  dplyr::mutate(all = fish + invert, 
                perc_topfish = paste0(round(x = (topfish/all)*100, digits = 1), "%"), # the % of the top 10 fish caught out of the survey
                perc_topfishoffish = paste0(round(x = (topfish/fish)*100, digits = 1), "%"), # the % of the top 10 fish caught out of the survey
                perc_invert = paste0(round(x = (invert/all)*100, digits = 1), "%"), 
                perc_fish = paste0(round(x = (fish/all)*100, digits = 1), "%"), 
                dplyr::across(where(is.numeric), formatC, digits = 1, big.mark = ",", format = "f")) %>% 
  dplyr::left_join(
    y = data.frame(SRVY = SRVY1, 
                   SRVY_long = SRVY11))

str0 <- text_list(paste0(
  "The ten most-abundant fish taxa in the ",temp$SRVY_long,
  " accounted for ", temp$perc_topfish,
  " (an average of ",temp$topfish," kg/km^2^ per station) ", 
  "of total mean fish and invertebrate CPUE (an average of ",
  temp$all," kg/km^2^ per station) and ",
  temp$perc_topfishoffish," of total mean fish CPUE (an average of ",temp$fish,
  " kg/km^2^ per station). "), sep = "", sep_last = "", sep_last2 = "") # ; Tables \\@ref(tab:tab-est-spp-wt) and \\@ref(tab:tab-est-spp-num)
```

`r str0`

<!---BLOCK_LANDSCAPE_START--->

```{r tab-biomass-est-EBS-0}
nickname <- "tab-biomass-est-EBS-"
# sep0 <- "\\pagebreak"
```

```{r tab-biomass-est-EBS-child, child = paste0(dir_code, "_child_report_figtab.Rmd")}
```

<!---BLOCK_LANDSCAPE_STOP--->

```{r tab-biomass-est-NBS-0}
nickname <- "tab-biomass-est-NBS-"
```

```{r tab-biomass-est-NBS-child, child = paste0(dir_code, "_child_report_figtab.Rmd"), eval = ("NBS" %in% haul_cruises_maxyr$SRVY)}
```

\pagebreak

```{r tab-majortaxa-pchange-0}
nickname <- "tab-majortaxa-pchange-"
sep0 <- "\\pagebreak"
```

```{r tab-majortaxa-pchange-child, child = paste0(dir_code, "_child_report_figtab.Rmd")}
```

\pagebreak

## Summary of Results for Selected Fish and Invertebrate Fauna of the `r gsub(pattern = "And", replacement = "and", x = stringr::str_to_title(SURVEY))`

```{r results-spatial-distribution_fish}
temp <- report_spp1 %>% 
  dplyr::filter(plot_idw == TRUE) %>% 
  dplyr::select(file_name, taxon) %>% 
  dplyr::distinct()

temp2 <- report_spp1 %>% 
  dplyr::filter(table_cpue == TRUE) %>% 
  dplyr::select(file_name, taxon) %>% 
  dplyr::distinct()
```

Summary results for `r xunits(sum(!is.na(report_spp$order[report_spp$taxon == "fish"])))` major fish and `r xunits(sum(!is.na(report_spp$order[report_spp$taxon == "invert"])))` major invertebrate taxa caught during the `r SURVEY` surveys are presented below. Plots of biomass and abundance time series, spatial distribution, abundance-at-length estimates, and stratum-level CPUE (kg/km^2^ and no/km^2^) tables are provided, as appropriate for each taxa. The spatial distribution maps illustrate where the taxa were found during the surveys. These distributions are presented as inverse-distance-weighted interpolations of CPUE (kg/km^2^), which uses a weighted average of nearby measured stations to estimate values at unmeasured locations between stations. Similar interactive maps of these highlighted taxa and others are available through the NOAA Distribution Mapping and Analysis Portal (https://apps-st.fisheries.noaa.gov/dismap/; @DisMAPDataPortal). More information on how to find, download, and interact with the data used to produce this report is available in the [Data Sources](#data-sources) section. Differences in estimates and totals may be due to rounding. Taxa are presented in alphabetical order by common name.

