---
output:
  officedown::rdocx_document: 
    pandoc_args: ["--metadata-file=header.yaml"]
    reference_docx: styles_reference.docx
    df_print: kable
bibliography: "../cite/bibliography.bib"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, error = FALSE, message = FALSE, comment = FALSE)
```

# Results and Discussion

A total of `r NMFSReports::text_list(paste0(haul_cruises_maxyr$stations_completed, " ", haul_cruises_maxyr$SRVY, " stations")) ` were successfully sampled in `r maxyr` (Figure `r crossref(list_obj = list_figures, nickname = "fig_sampled_survey_stations", sublist = "number")`). Haul and catch sample data for successfully trawled stations used in the analyses can be found and downloaded from the Fisheries One Stop Shop (<https://www.fisheries.noaa.gov/foss/f?p=215:200:1099772399154:Mail:NO:::>). 

## Ocean Temperatures and the Cold Pool

```{r ocean_temps}
temp <- dplyr::left_join(
  x = temps_avg_yr %>% 
    dplyr::filter(year %in% c(maxyr)), 
  y = temps_avg_yr %>% 
    dplyr::filter(year %in% c(lastyr)) %>% 
    dplyr::select(SRVY, bt, st) %>% 
    dplyr::rename(bt_1 = bt,
                  st_1 = st),
  by = "SRVY") %>% 
  dplyr::mutate(bt_diff = (bt_1 - bt)) %>% 
  dplyr::mutate(st_diff = (st_1 - st)) %>% 
  dplyr::mutate(bt_mean_diff = (bt_mean - bt)) %>% 
  dplyr::mutate(st_mean_diff = (st_mean - st)) 

temp2 <- dplyr::left_join(
  x = haul_maxyr, 
  y = station_info, 
  by = c("stratum", "stationid", "SRVY")) %>% 
  dplyr::filter(reg == "Norton Sound")

a <- summary(lm(haul_maxyr$surface_temperature ~ haul_maxyr$start_longitude))

str0 <- paste0(
  "Sea surface temperatures recorded during the ", maxyr," ", NMFSReports::text_list(SRVY1),
  " survey ranged from ", 
  round(x = min(haul_maxyr$surface_temperature, na.rm = TRUE), digits = 1), "° to ", 
  round(x = max(haul_maxyr$surface_temperature, na.rm = TRUE), digits = 1),
  "°C and bottom temperatures ranged from ", 
  round(x = min(haul_maxyr$gear_temperature, na.rm = TRUE), digits = 1), "° to ", 
  round(x = max(haul_maxyr$gear_temperature, na.rm = TRUE), digits = 1),
  "°C. The mean sea surface temperature for the EBS in ", maxyr," was ", 
  round(x = temp$st, digits = 1),"°C, which was ", 
  round(x = temp$st_diff*ifelse(temp$st_diff > 0, 1, -1), digits = 1),"°C ", 
  ifelse((temp$st_diff > 0), "lower", "higher"),
  " than ", lastyr," (", 
  round(x = temp$st_1, digits = 1),"°C) and ", 
  round(x = temp$st_mean_diff*ifelse(temp$st_mean_diff > 0, 1, -1), digits = 1),"°C ", 
  ifelse((temp$st_mean_diff > 0), "lower", "higher"),
  " than the time-series mean (", round(x = temp$st_mean, digits = 1),"°C) (Figure ", 
  NMFSReports::crossref(list_obj = list_figures, 
                        nickname = c('fig_mean_temperature', 'fig_cold_pool_area', 'fig_st_maxyr'), 
                        sublist = 'number'),"). ", 
  ifelse(SRVY == "NEBS", 
         paste0(
                ifelse(a$coefficients[2]<0 & a$coefficients[8] <= 0.05, 
                       paste0("In the EBS south of 60°N, surface temperatures increased from east to west across the shelf (Figure ",NMFSReports::crossref(list_obj = list_figures, 
                                      nickname = 'fig_st_temperature_nebs_surveys', sublist = 'number'),"). "), ""),
                "An average of ", 
                round(x = mean(temp2$surface_temperature), digits = 1),
                "°C was observed in Norton Sound (Figure ", 
                NMFSReports::crossref(list_obj = list_figures, 
                                      nickname = 'fig_st_temperature_nebs_surveys', sublist = 'number'), 
                ")."), 
         ""))

str0 <- gsub(x = str0, pattern = ") (", replacement = "; ", fixed = TRUE)

```

`r str0 ` During the EBS time series (`r haul_cruises_maxyr$SRVY_start[haul_cruises_maxyr$SRVY == "EBS"] `–`r maxyr`), mean summer bottom temperatures were highly variable, ranging from a low of `r round(x = min(temps_avg_yr$bt), digits = 1)`°C to a high of `r round(x = max(temps_avg_yr$bt), digits = 1)`°C. The grand mean for all years was `r round(x = min(temps_avg_yr$bt_mean[1]), digits = 1)`°C (Figure `r crossref(list_obj = list_figures, nickname = 'fig_mean_temperature', sublist = 'number')`). The mean survey bottom temperature for the EBS in `r maxyr` was `r round(x = (temps_avg_yr_maxyr$bt), digits = 1)`°C (Figure `r crossref(list_obj = list_figures, nickname = 'fig_mean_temperature', sublist = 'number')`), which was `r round(x = abs(temp$bt_mean_diff), digits = 1) `°C `r ifelse(temps_avg_yr_maxyr$bt_above_mean, "warmer", "colder")` than the long term mean [@RohanColdPool].

The size of the cold pool each summer is defined by the extent of bottom temperatures below 2°C and depends on sea ice coverage from the previous winter, the timing of sea ice retreat during the spring and early summer, as well as other oceanographic and meteorological conditions [@RN941]. During the coldest years, sea ice extended farther south and lasted later into spring resulting in cold pools that extended farther south through the middle domain into Bristol Bay and near the Alaska Peninsula (Figure `r crossref(list_obj = list_figures, nickname = 'fig_bt_temperature_ebs_below', sublist = 'number')` and `r crossref(list_obj = list_figures, nickname = 'fig_bt_temperature_ebs_above', sublist = 'number')`). Interannual variability in the dynamics of seasonal ice is a major environmental driver on the Bering Sea shelf [@RN930; @RN931; @RN932] that can change recruitment and migration patterns, as well as cause major distributional shifts in groundfish and crab species [@RN905; @RN913; @RN977]. 

```{r cold_pool}
temp <- coldpool_ebs_total_area

# A large cold pool year
temp4 <- ""
if (temp$rank[temp$year == maxyr] < 6) {
  
  temp0 <- temp[temp$rank <= temp$rank[temp$year == maxyr],] %>% 
    dplyr::mutate(rank_ = "") %>% 
    dplyr::arrange(rank)
  for (i in 1:nrow(temp0)) {
    temp0$rank_[i] <- NMFSReports::numbers2words_th(x = temp0$rank[i])
  }
  
  temp4 <- paste0(ifelse(temp0$rank_[temp0$year == maxyr] != "first", 
                         paste0(temp0$rank_[temp0$year == maxyr], " "), ""),
                  "highest") 
} 

# A small cold pool year
if (abs(temp$rank[temp$year == maxyr]-length(temp$rank)) < 6) {
  temp0 <- temp[temp$rank >= temp$rank[temp$year == maxyr],] %>% 
    dplyr::mutate(rank = abs(rank-(nrow(temp)+1)), 
                  rank_ = "") %>% 
    dplyr::arrange(rank)
  for (i in 1:nrow(temp0)) {
    temp0$rank_[i] <- NMFSReports::numbers2words_th(x = temp0$rank[i])
  }
  
  temp4 <- paste0(ifelse(temp0$rank_[temp0$year == maxyr] != "first", 
                         paste0(temp0$rank_[temp0$year == maxyr], " "), ""),
                  "lowest") 
}

# put sentence together
if (temp$rank[temp$year == maxyr] < 6 | abs(temp$rank[temp$year == maxyr]-length(temp$rank)) < 6) {
  
    temp4a <- ifelse(temp0$rank_[temp0$year == maxyr] != "first", 
                          paste0(" followed by ", NMFSReports::text_list(paste0(temp0$year[temp0$year != maxyr], 
                                                        " (", temp0$rank_[temp0$year != maxyr], ")"))), 
                          "")
  
    temp4 <- paste0(", which was the ", temp4," areal coverage in the ", 
                haul_cruises_maxyr$yrofsurvey[haul_cruises_maxyr$SRVY == 'EBS'], 
                "-year EBS shelf bottom trawl survey time-series", 
                temp4a, ". ")
}

```

During the last `r length(unlist(temps_avg_yr_abovebelow))` years, `r NMFSReports::range_text(x = temps_avg_yr_abovebelow$below)` were colder than average ("cold stanza"; Figure `r crossref(list_obj = list_figures, nickname = 'fig_bt_temperature_ebs_below', sublist = 'number')`), while `r NMFSReports::range_text(x = temps_avg_yr_abovebelow$above)` were warmer than average ("warm stanza"; Figure `r NMFSReports::crossref(list_obj = list_figures, nickname = 'fig_bt_temperature_ebs_above', sublist = 'number')`). `r ifelse((maxyr>2020 & maxyr<(2021+length(unlist(temps_avg_yr_abovebelow)))), "There was no survey in 2020 due to the COVID-19 pandemic.", "")` The highly variable survey bottom temperatures in the EBS shelf are related to the area occupied by the summer cold pool (Figure `r crossref(list_obj = list_figures, nickname = 'fig_cold_pool_area', sublist = 'number')`). Over the period of the `r haul_cruises_maxyr$yrofsurvey[haul_cruises_maxyr$SRVY == "EBS"] `-year time series, the areal coverage of the summer survey cold pool in the EBS varied in size from `r NMFSReports::xunits(min(temp$area_km2, na.rm = TRUE)) ` km^2^ in `r temp$year[temp$area_km2 == min(temp$area_km2, na.rm = TRUE)] ` to `r NMFSReports::xunits(max(temp$area_km2, na.rm = TRUE)) ` km^2^ in `r temp$year[temp$area_km2 == max(temp$area_km2, na.rm = TRUE)] `, respectively comprising `r round(temp$perc[temp$area_km2 == min(temp$area_km2, na.rm = TRUE)], digits = 1)`% to `r round(temp$perc[temp$area_km2 == max(temp$area_km2, na.rm = TRUE)], digits = 1)`% of EBS shelf area (Figure `r crossref(list_obj = list_figures, nickname = 'fig_cold_pool_area', sublist = 'number')`). In `r maxyr`, the cold pool covered `r formatC(temp$area_km2[temp$year == maxyr], digits = 0, big.mark = ",", format = "f") ` km^2^ (`r round(temp$perc[temp$year == maxyr], digits = 1) `%) of the EBS shelf survey area`r temp4`

The `r compareyr` and `r maxyr` `r NMFSReports::text_list(SRVY1)` surveys provided a quasi-synoptic view of the spatial pattern of bottom temperatures across the entire `r NMFSReports::text_list(SRVY1)` shelf, providing an index of annual differences in demersal fauna distribution patterns. Cold water in the middle of the EBS can restrict marine fauna from moving east-west across the shelf or north-south along the inner domain.


```{r cold_pool_insert}
# insert <- readtext(file = paste0(dir_out_rawdata, "/doc_abstract_conclusion.docx"))
insert <- readtext2(file = paste0(dir_out_rawdata, "/0_cold_pool_description.docx"), 
                    refcontent = refcontent)
```

`r insert`

\newpage

`r NMFSReports::crossref(list_obj = list_figures, nickname = "fig_mean_temperature", sublist = "res") `

`r NMFSReports::crossref(list_obj = list_figures, nickname = "fig_cold_pool_area", sublist = "res") `

`r NMFSReports::crossref(list_obj = list_figures, nickname = "fig_st_maxyr", sublist = "res") `

`r NMFSReports::crossref(list_obj = list_figures, nickname = "fig_bt_temperature_ebs_", sublist = "res", exact = FALSE) ` 

`r NMFSReports::crossref(list_obj = list_figures, nickname = "_temperature_nebs_surveys", sublist = "res", exact = FALSE) `

## Survey Data and Specimen Collections 

```{r num_taxa}
temp0 <- function(cols, SRVY, report_spp1) {
  nspec <- c()
  ntaxa <- c()
  ctaxa <- c()
  a <- report_spp1
  a$taxon[a$taxon == "invert" & 
            grepl(pattern = "crab", x = a$print_name)] <- "crab"
  
  for (i in 1:length(cols)){
    
    col <- cols[i]
    if (SRVY == "NEBS") {
      temp <- dplyr::bind_rows(
        list_tables$tab_specimen_samples_EBS$raw, 
        list_tables$tab_specimen_samples_NBS$raw)      
    } else {
      temp <- list_tables$tab_specimen_samples_EBS$raw      
    }
    
    temp <- temp[temp[,col]!=0,]
    
    nspec <- c(nspec, 
               xunits(sum(temp[temp$common_name == "Total", 
                               names(temp) %in% col]))) # how many specimen
    ntaxa <- c(ntaxa, 
               xunits(length(unique(temp$common_name)[unique(temp$common_name) != "Total"]))) # number of taxa
    
    ctaxa <- c(ctaxa,
               NMFSReports::text_list(unique(a$taxon[a$print_name %in% 
                                                       unique(temp$common_name)])) )
  }
  
cols <- gsub(pattern = "\n", replacement = " ", x = cols)
cols <- gsub(pattern = " Measurements", replacement = "s", x = cols)
  
  return(list("col" = tolower(cols), 
              "nspec" = nspec, 
              "ctaxa" = ctaxa, # kinds of taxa
              "ntaxa" = ntaxa))
}

cols <- names(list_tables$tab_specimen_samples_EBS$raw)
cols <- cols[!(cols %in% c("common_name", "SRVY"))]


# "", "stomachs collected"	count_pathobiology_samples	count_fecundity_and_maturity_(ovaries)_samples

temp <- temp0(cols, SRVY, a)

str0 <- paste0("A total of ", NMFSReports::text_list(sep="; ", paste0(temp$nspec, " ", temp$col, " were collected from ", temp$ntaxa, " ", temp$ctaxa, ifelse(temp$ntaxa==1, "taxon", "taxa"))), ". ")

```

Specimens collected during the `r NMFSReports::text_list(SRVY1)` shelf trawl survey are shown in Table`r ifelse(SRVY == "NEBS", "s", "")` `r crossref(list_obj = list_tables, nickname = "tab_specimen_samples_", sublist = "number", exact = FALSE)`. `r str0` Other special collections are listed in table `r crossref(list_obj = list_tables, nickname = "tab_special_projects", sublist = "number")`. 

`r NMFSReports::crossref(list_obj = list_tables, nickname = "tab_specimen_samples_", sublist = "res", exact = FALSE) `

## Species Composition

```{r species_composition}
insert <- ""

# count spp
temp <- dplyr::left_join(
  x = catch_haul_cruises_maxyr %>% 
    dplyr::select(SRVY, species_code) %>% 
    dplyr::distinct(), 
  y = spp_info %>% 
    dplyr::filter(used_in_counts) %>%
    dplyr::select(species_code, species_taxon, family_taxon, genus_taxon, taxon) %>%
    dplyr::distinct(), 
  by = "species_code") %>% 
  dplyr::filter(taxon == "fish") %>% 
  dplyr::select(species_code, species_taxon, family_taxon, genus_taxon, taxon, SRVY) %>% 
  dplyr::distinct()

temp0 <- dplyr::full_join(
  x = temp %>% 
    dplyr::filter(!is.na(species_taxon)) %>% 
    dplyr::select(SRVY, species_taxon) %>% 
    dplyr::distinct() %>% 
    dplyr::group_by(SRVY) %>% 
    dplyr::summarise(species_taxon = n()),
  y = temp %>% 
    dplyr::filter(!is.na(species_code)) %>% 
    dplyr::select(SRVY, species_code) %>% 
    dplyr::distinct() %>% 
    dplyr::group_by(SRVY) %>%
    dplyr::summarise(species_code = n()),
  by = "SRVY") %>% 
  dplyr::left_join(
    x = ., 
    y = temp %>% 
    dplyr::filter(!is.na(family_taxon)) %>% 
    dplyr::select(SRVY, family_taxon) %>% 
    dplyr::distinct() %>% 
    dplyr::group_by(SRVY) %>%
    dplyr::summarise(family_taxon = n()),
  by = "SRVY")  %>% 
  dplyr::left_join(
    x = ., 
    y = temp %>% 
    dplyr::filter(!is.na(genus_taxon)) %>% 
    dplyr::select(SRVY, genus_taxon) %>% 
    dplyr::distinct() %>% 
    dplyr::group_by(SRVY) %>%
    dplyr::summarise(genus_taxon = n()),
  by = "SRVY") #%>%
  # dplyr::mutate(perc = round(((species_code - species_taxon)/species_code)*100, digits = 2))

temp1 <- dplyr::bind_cols(
  temp %>% 
    dplyr::filter(!is.na(species_taxon)) %>% 
    dplyr::select(species_taxon) %>% 
    dplyr::distinct() %>% 
    dplyr::summarise(species_taxon = n()),
  temp %>% 
    dplyr::filter(!is.na(species_code)) %>% 
    dplyr::select(species_code) %>% 
    dplyr::distinct() %>% 
    dplyr::summarise(species_code = n()), 
  temp %>% 
    dplyr::filter(!is.na(family_taxon)) %>% 
    dplyr::select(family_taxon) %>% 
    dplyr::distinct() %>% 
    dplyr::summarise(family_taxon = n()),
  temp %>% 
    dplyr::filter(!is.na(genus_taxon)) %>% 
    dplyr::select(genus_taxon) %>% 
    dplyr::distinct() %>% 
    dplyr::summarise(genus_taxon = n())) #%>% 
  # dplyr::mutate(perc = round(((species_code - species_taxon)/species_code)*100, digits = 2))

if (SRVY == "NEBS") {
# how many species in one survey area but noth the other?

  temp3 <- list_tables$tab_species_composition$raw %>%
    dplyr::left_join(x = .,
                     y = spp_info %>%
                       dplyr::select(species_code, order_taxon, species_name),
                     by = c("species_code"))

  insert <- paste0( 
    "Of the fish species found in the EBS, ",
                   xunits(nrow(temp3[temp3$where == 
                                       "Present in EBS but absent in NBS",])), 
                   " did not occur in the NBS (Table ",
                   crossref(list_obj = list_tables, 
                            nickname = "tab_species_composition", 
                            sublist = "number"),
                   "). In comparison, ",
                   xunits(nrow(temp3[temp3$where == 
                                       "Present in the NBS but absent in EBS",])), 
                   " species were present in the NBS but absent in EBS (Table ", 
                   crossref(list_obj = list_tables, 
                            nickname = "tab_species_composition", 
                            sublist = "number"), "). ")
  
  # flatfish
  temp4 <- temp3[temp3$order_taxon %in% c("Pleuronectiformes"), ]
  temp5 <- temp4 %>% 
    dplyr::filter(where != "Present in the EBS and the NBS") %>% 
    dplyr::group_by(where) %>% 
    dplyr::summarise(n = n()) %>% 
    dplyr::mutate(where = paste0(tolower(substr(x = where, start = 1, stop = 1)), 
                                 substr(x = where, start = 2, stop = nchar(where))), 
                  including = NA)
  for (i in 1:nrow(temp5)) {
    temp5$including[i] <- 
      NMFSReports::text_list(
        paste0(
          temp4$common_name[grepl(pattern = temp5$where[i], 
                                  x = temp4$where, 
                                  ignore.case = TRUE)], 
          " (*", 
          temp4$species_name[grepl(pattern = temp5$where[i], 
                                   x = temp4$where, 
                                   ignore.case = TRUE)],
          "*)"))
  }
  
  insert <- paste0(insert, "In ", maxyr, ", ", 
                   
                   NMFSReports::text_list(
                     paste0(xunits(temp5$n), 
                            " flatfish species ", ifelse(temp5$n>1, "were", "was"), " ", 
                            temp5$where, " (",
                            temp5$including, ")"), 
                     # sep_last = ";", 
                     sep = "; "),
                   " (Table ", 
                   crossref(list_obj = list_tables, 
                            nickname = "tab_species_composition", 
                            sublist = "number"), ").")
}

insert <- gsub(pattern = ") (", replacement = "; ", x = insert, fixed = TRUE)

```

A total of `r xunits(temp1$species_code) ` different fish species representing `r xunits(temp1$family_taxon)` families and `r xunits(temp1$genus_taxon)` genera were identified during the `r maxyr` `r NMFSReports::text_list(SRVY1)` survey`r ifelse(length(SRVY1)>1, "s", "")` (`r ifelse(SRVY == "NEBS", "appendices", "appendix")` `r NMFSReports::crossref(list_tables, "tab_app_taxa_encountered_*_fish", "number", exact = FALSE)`). In `r maxyr`, `r NMFSReports::text_list(paste0("the ", temp0$SRVY, " survey recorded a total of ", xunits(temp0$species_code), " taxa, of which ", xunits(temp0$species_taxon), " were identified to the species level"))`. The remaining fish taxa in each survey area were identified to the genus level or higher. `r insert `

```{r taxon_count}
# count spp - invert
temp <- dplyr::left_join(
  x = catch_haul_cruises_maxyr %>% 
    dplyr::select(SRVY, species_code) %>% 
    dplyr::distinct(), 
  y = spp_info %>% 
    dplyr::filter(used_in_counts) %>%
    dplyr::select(species_code, species_taxon, phylum_taxon, taxon) %>%
    dplyr::distinct(), 
  by = "species_code") %>% 
  dplyr::filter(taxon == "invert") %>% 
  dplyr::select(species_code, species_taxon, phylum_taxon, taxon, SRVY) %>% 
  dplyr::distinct()

temp0 <- dplyr::full_join(
  x = temp %>% 
    dplyr::filter(!is.na(species_taxon)) %>% 
    dplyr::select(SRVY, species_taxon) %>% 
    dplyr::distinct() %>% 
    dplyr::group_by(SRVY) %>% 
    dplyr::summarise(species_taxon = n()),
  y = temp %>% 
    dplyr::filter(!is.na(species_code)) %>% 
    dplyr::select(SRVY, species_code) %>% 
    dplyr::distinct() %>% 
    dplyr::group_by(SRVY) %>%
    dplyr::summarise(species_code = n()),
  by = "SRVY") %>% 
  dplyr::mutate(perc = round(((species_code - species_taxon)/species_code)*100, digits = 2))

temp1 <- dplyr::bind_cols(
  temp %>% 
    # dplyr::filter(!is.na(species_taxon)) %>%
    dplyr::select(phylum_taxon, species_taxon) %>% 
    dplyr::distinct() %>% 
    dplyr::summarise(phylum_taxon = length(unique(phylum_taxon)), 
                     species_taxon = length(unique(species_taxon))),
  temp %>% 
    dplyr::filter(!is.na(species_code)) %>% 
    dplyr::select(species_code) %>% 
    dplyr::distinct() %>% 
    dplyr::summarise(species_code = n())) %>% 
  dplyr::mutate(perc = round(((species_code - species_taxon)/species_code)*100, digits = 2))

```

A total of `r xunits(temp1$species_code) ` different invertebrate taxa representing `r xunits(temp1$phylum_taxon)` phyla were identified during the `r maxyr` `r NMFSReports::text_list(SRVY1)` survey (`r ifelse(SRVY == "NEBS", "appendices", "appendix")` `r NMFSReports::crossref(list_tables, "tab_app_taxa_encountered_*_invertebrate", "number", exact = FALSE)`). In `r maxyr`, `r NMFSReports::text_list(paste0("the ", temp0$SRVY, " survey recorded a total of ", xunits(temp0$species_code), " taxa of which ", xunits(temp0$species_taxon), " were identified to the species level"))`. The remaining invertebrate taxa in each survey area were identified to the genus level or higher. The lack of species level identifications among invertebrates was due to a variety of factors that are outlined in @RN934. Additionally, trawl catchability of small invertebrates is not known.

```{r dummy}
# All species are identified using as Eschmeyer’s Catalog of Fishes (found at https://www.calacademy.org/scientists/projects/eschmeyers-catalog-of-fishes) which is regularly updated [@Frickeetal2022] and An Annotated Checklist of the Marine Macroinvertebrates of Alaska [@Drummetal2016] and logged in AFSC’s databases.
```

`r list_tables$tab_species_composition$res `

## Biomass, Abundance, and Catch per Unit Effort

```{r tot_biomass}
temp <- data.frame()
temp0 <- tidyr::crossing(SRVY = SRVY1, type = c("fish", "invert"))
for (i in 1:nrow(temp0)) {
  temp <- list_tables[names(list_tables) ==
                        paste0("tab_biomass_est_",temp0$type[i],"_", temp0$SRVY[i])][[1]]$raw %>%
    dplyr::filter(grepl(pattern = "Total", x = group, ignore.case = TRUE )) %>% 
    dplyr::mutate(SRVY = temp0$SRVY[i], 
                  group = temp0$type[i]) %>%
    dplyr::select(SRVY, group, `999`) %>% 
    dplyr::bind_rows(temp, .)
}

temp2 <- dplyr::left_join(
  x = temp, 
  y = total_biomass %>% 
    dplyr::group_by(SRVY),
  by = "SRVY") %>% 
  dplyr::mutate(
    prop = (`999`/total), 
    perc = paste0(formatC(x = prop*100, 
                          digits = 0, format = "f", big.mark = ","), 
                  "%"), 
    group = gsub(pattern = "Total ", replacement = "", x = group)) %>% 
  tidyr::pivot_wider(id_cols = "SRVY", 
                     names_from = "group", 
                     values_from = c("999", "perc", "prop"))

temp1 <- left_join(
  x = temp, 
  y = stratum_info %>% 
    dplyr::group_by(SRVY) %>% 
    dplyr::summarise(area = sum(area, na.rm = TRUE)), 
  by = "SRVY") %>% 
  dplyr::mutate(prop = `999`/area, 
                group = gsub(pattern = "Total ", replacement = "", x = group)) %>% 
  dplyr::filter(group == "fish")

str0 <- paste0("The ", 
               NMFSReports::text_list(paste0(
                 "total demersal animal biomass for the ", 
                 total_biomass$SRVY, 
                        " was estimated at ", 
                        NMFSReports::xunits(total_biomass$total), 
                        " metric tons (mt)")), ". " )

str00 <- ""
for (ii in 1:length(temp2$SRVY)) {
  
  str000 <- ifelse(ii != 1 & temp2$prop_fish[ii]>temp2$prop_invert[ii], "also ","")
  
str00 <- paste0(str00, 
                ifelse(ii==2, " and in the ", "In the "), 
                 paste0(temp2$SRVY[ii], 
                        ", the proportion of fishes (", 
                        temp2$perc_fish[ii], 
                        "; Table ", crossref(list_obj = list_tables, 
                                       nickname = paste0("tab_biomass_est_fish_", temp2$SRVY[ii]), 
                                       sublist = "number"), 
                        ") was ", str000,  
                        ifelse(temp2$prop_fish[ii]>temp2$prop_invert[ii], "higher","lower"),
                        " than invertebrates (", 
                        temp2$perc_invert[ii], 
                        "; Table ", 
                        crossref(list_obj = list_tables, 
                                       nickname = paste0("tab_biomass_est_invert_", temp2$SRVY[ii]), 
                                       sublist = "number"), 
                        ")"))
}
str0 <- paste0(str0, str00, ". ")

if (SRVY == "NEBS") {
  str0 <- paste0(str0, 
                 paste0(ifelse(temp1$prop[temp1$SRVY=="EBS"]>temp1$prop[temp1$SRVY=="NBS"], 
                               "The lower relative fish biomass in the NBS than in the EBS is consistent", 
                               "The higher relative fish biomass in the NBS than in the EBS is inconsistent"), 
                        " with results of a broader analysis of all survey years in @RN936 showing decreasing fish biomass with increasing latitude on the Bering Sea continental shelf (Tables ", 
                        NMFSReports::text_list(crossref(list_obj = list_tables, 
                                       nickname = "tab_biomass_est_fish_", 
                                       sublist = "number", 
                                 exact = FALSE)),"). This trend may change over time with warming ocean temperatures.", 
                        "") ) 
}

str0 <- gsub(pattern = ") (", replacement = "; ", x = str0, fixed = TRUE)

```

`r str0 `

```{r tot_biomass2}
str0 <- ""
if (SRVY == "NEBS") {
  
  #temp1
  temp1 <- data.frame()
  for (i in 1:length(SRVY1)) {
    
    temp1 <- list_tables[names(list_tables) ==
                           paste0("tab_biomass_est_fish_", SRVY1[i])][[1]]$raw %>%
      dplyr::mutate(SRVY = SRVY1[i]) %>%
      dplyr::filter(is.na(taxon) |
                      grepl(pattern = "Total", x = taxon, ignore.case = TRUE )) %>% 
      dplyr::filter(!grepl(pattern = "Total", x = group, ignore.case = TRUE ) &
                      !grepl(pattern = "Other", x = group, ignore.case = TRUE )) %>% 
      dplyr::select(SRVY, group, `999`, prop) %>% 
      dplyr::arrange(-prop) %>% 
      dplyr::mutate(order = 1:nrow(.)) %>% 
      dplyr::bind_rows(temp1, .)
  }
  
  temp1 <- temp1 %>% 
    tidyr::pivot_wider(id_cols = c("group"), 
                       names_from = "SRVY", 
                       values_from = c("999", "prop", "order")) %>%
    dplyr::mutate(same = ifelse(order_EBS == order_NBS, TRUE, FALSE))
  
  # temp2
  temp2 <- data.frame()
  
  for (i in 1:length(SRVY1)) {
    
    temp2 <- list_tables[names(list_tables) ==
                           paste0("tab_biomass_est_fish_", SRVY1[i])][[1]]$raw %>%
      dplyr::mutate(SRVY = SRVY1[i]) %>%
      dplyr::filter(group %in% temp1$group[1:2] & 
                      !grepl(pattern = "Total ", x = taxon, ignore.case = TRUE )) %>% 
      dplyr::select(SRVY, group, taxon, `999`, prop) %>% 
      dplyr::arrange(-prop) %>% 
      dplyr::mutate(order = 1:nrow(.)) %>% 
      dplyr::bind_rows(temp2, .)
  }
  
  temp2 <- temp2 %>% 
    tidyr::pivot_wider(id_cols = c("group", "taxon"), 
                       names_from = "SRVY", 
                       values_from = c("999", "prop", "order")) %>%
    dplyr::mutate(same =ifelse(order_EBS == order_NBS, TRUE, FALSE)) %>% 
    dplyr::left_join(
      x = ., 
      y = spp_info_maxyr %>% 
        dplyr::select(species_name, common_name), 
      by = c("taxon" = "common_name")  )
  
  # temp3: top 3 spp in each group
  temp3 <- data.frame()
  temp0 <- tidyr::crossing(group = unique(temp2$group), 
                           SRVY = SRVY1) %>% 
    dplyr::arrange(SRVY, group) %>% 
    dplyr::mutate(str0 = NA)
  
  for (i in 1:nrow(temp0)) {
    temp3 <- temp2 %>% 
      dplyr::rename(prop = paste0("prop_", temp0$SRVY[i]), 
                    order = paste0("order_", temp0$SRVY[i])) %>%
      dplyr::filter(#order %in% c(1:3) & 
        group == temp0$group[i]) %>% 
      head(3) %>%
      dplyr::mutate(prop = paste0(round(x = prop*100, digits = 1), "%"), 
                    SRVY = temp0$SRVY[i]) %>%
      dplyr::arrange(order) %>% 
      dplyr::select(SRVY, group, taxon, species_name, prop) %>% 
      dplyr::filter(prop != "0%")
    # dplyr::bind_rows(temp3, .)
    
    if (nrow(temp3)>1) {
      temp0$str0[temp0$SRVY == temp0$SRVY[i] & temp0$group == temp0$group[i]] <- 
        NMFSReports::text_list(paste0(temp3$taxon, " (*", temp3$species_name, 
                                      "*, ",temp3$prop,")"))
      temp0$group1 <- unlist(regmatches(temp0$group,
                                        gregexpr(
                                          "(?<=\\().*?(?=\\))", # everything within a (*)
                                                 temp0$group, perl=T)))
      temp0$group0 <- unlist(lapply(strsplit(x = temp0$group, split = " ", fixed = TRUE), `[[`, 1))
      # temp0$group0 <- temp$group
    }
  }
  
  temp0$group0 <- paste0("the family ", temp0$group0)
  
  temp0$str0 <- gsub(pattern = "*NA*, ", replacement = "", x = temp0$str0, fixed = TRUE)
  temp0$str0 <- gsub(pattern = "  ", replacement = " ", x = temp0$str0, fixed = TRUE)
  
  temp3 <- c()
  for (i in 1:length(SRVY1)){
    temp4 <- NMFSReports::text_list(paste0(
                             temp0$group0[temp0$SRVY == SRVY1[i]], 
                             " was primarily comprised of ", 
                             temp0$str0[temp0$SRVY == SRVY1[i]]))
    temp3 <- paste0(temp3, 
                    paste0("In the ", SRVY1[i], ", ", 
                           substr(temp4, start = 1, stop = (nchar(temp4)-1)), # get rid of last ")" 
                           "; ", 
                           NMFSReports::crossref(list_obj = list_tables, sublist = "number", 
                                                 nickname = "tab_biomass_est_fish_", exact = FALSE), 
                           "). "))
  }
  
  str0 <- paste0(
    NMFSReports::text_list(temp1$group[1:2]),
    " were the fish families with greatest biomass in both the EBS (",
    NMFSReports::text_list(
      paste0(round(x = temp1$prop_EBS[1:2]*100, digits = 1), "%")), 
    " of the total biomass, respectively) and the NBS (",
    NMFSReports::text_list(
      paste0(round(x = temp1$prop_NBS[1:2]*100, digits = 1), "%")), 
    " of the total biomass, respectively; ", 
    NMFSReports::crossref(list_obj = list_tables, sublist = "number", nickname = "tab_biomass_est_fish_EBS"), 
    " and ", 
    NMFSReports::crossref(list_obj = list_tables, sublist = "number", nickname = "tab_biomass_est_fish_NBS"), "). ", 
    temp3)
  
}

```

`r str0 ` 

```{r benthic_community}

str0 <- paste0("There were noticeable changes in the benthic communities of the ",
               NMFSReports::text_list(SRVY1)," between ", compareyr," and ", maxyr,". ")

for (i in 1:length(SRVY1)) {
  
  temp0 <- list_tables[names(list_tables) %in% paste0("tab_majortaxa_pchange_", SRVY1[i])][[1]]$raw

  temp <- dplyr::bind_rows(
    temp0 %>%
      dplyr::rename("maxyr" = paste0(maxyr), 
                    "compareyr" = paste0(compareyr)) %>%
      dplyr::select(print_name, maxyr, compareyr, change),
    temp0 %>%
      dplyr::select(-print_name, -change) %>% 
      dplyr::rename("maxyr" = paste0(maxyr, " "), 
                    "compareyr" = paste0(compareyr, " "), 
                    "print_name" = "print_name ", 
                    "change" = "change ") %>%
      dplyr::select(print_name, maxyr, compareyr, change)
    ) %>% 
    dplyr::filter(!is.na(change)) %>% 
    dplyr::mutate(case = case_when(
                      change>0 ~ "increased", 
                      change<0 ~ "decreased")) %>% 
    dplyr::arrange(-change)
  
  temp <-  
    dplyr::bind_rows(
      temp %>% 
        dplyr::filter(case == "increased") %>% 
        head(5), 
      temp %>% 
        dplyr::filter(case == "decreased") %>% 
        tail(5)
    ) %>% 
    dplyr::mutate(print_name = gsub(pattern = "include", replacement = ", which", x = print_name))

  temp1 <- data.frame(maxyr = sum(biomass_maxyr$biomass[biomass_maxyr$SRVY == SRVY1[i]]), 
                      compareyr = sum(biomass_compareyr$biomass[biomass_compareyr$SRVY == SRVY1[i]]))
  
  
str0 <- paste0(str0, 

               "The total estimated biomass in the ",SRVY1[i]," ", 
               ifelse(temp1$compareyr<temp1$maxyr, "increased", "decreased"),
               " from ",
               NMFSReports::xunits(temp1$compareyr)," mt in ", compareyr," to ",
               NMFSReports::xunits(temp1$maxyr)," mt in ", maxyr, ". ", 

               # taxa increased
               "Taxa that significantly increased in biomass included ", 
               NMFSReports::text_list(paste0(temp$print_name[temp$case == "increased"],
                                             " (", formatC(x = temp$change[temp$case == "increased"], 
                                                           digits = 0, format = "f", big.mark = ","), "%)")), 
               " (Table ",
               NMFSReports::crossref(list_obj = list_tables, 
                                     nickname = paste0("tab_majortaxa_pchange_", SRVY1[i]), sublist = "number"),
               "). ",
               # taxa decreased
               "Large decreases in biomass were observed for ", 
               NMFSReports::text_list(paste0(temp$print_name[temp$case == "decreased"],
                                             " (", formatC(x = temp$change[temp$case == "decreased"], 
                                                           digits = 0, format = "f", big.mark = ","), "%)")), 
               " (Table ",
               NMFSReports::crossref(list_obj = list_tables, 
                                     nickname = paste0("tab_majortaxa_pchange_", SRVY1[i]), sublist = "number"),
               "). While all efforts are made at standardizing catch processing over time, some differences may exist between years, vessels, and crews which may impact the interpretation of these differences."
               # something else
               # "Although there were large percentage increases in biomass for many invertebrate taxa, there was relatively little change in the combined total biomass of invertebrates (-0.2 million t) compared to 2010 (Table ",
               # NMFSReports::crossref(list_obj = list_tables, 
               #                       nickname = "tab_majortaxa_pchange_NBS", sublist = "number"),
               # "). "
               )

}

str0 <- gsub(x = str0, pattern = ") (", replacement = "; ", fixed = TRUE)

```

`r str0`

```{r top_10_taxon}
temp <- data.frame()
for (i in 1:nrow(haul_cruises_maxyr)) {
  temp <- list_tables$tab_estimates_maxyr_spp_wt$raw %>% 
    dplyr::filter(SRVY == haul_cruises_maxyr$SRVY[i]) %>%
    dplyr::select(meanwgtcpue , print_name) %>%
    dplyr::arrange(-meanwgtcpue) %>% 
    dplyr::ungroup() %>% 
    head(10) %>% 
    dplyr::summarise(meanwgtcpue = sum(meanwgtcpue, na.rm = TRUE)) %>% 
    dplyr::mutate(SRVY = haul_cruises_maxyr$SRVY[i], 
                  taxon = "topfish") %>% 
    dplyr::bind_rows(temp, .)
}  
  
  temp <- biomass %>% 
    dplyr::filter(year == maxyr & 
                   stratum == 999) %>%
    dplyr::select(meanwgtcpue, SRVY, taxon) %>% 
  dplyr::group_by(SRVY, taxon) %>% 
  dplyr::summarise(meanwgtcpue = sum(meanwgtcpue, na.rm = TRUE)) %>% 
  dplyr::ungroup() %>% 
    dplyr::bind_rows(temp, .) %>% 
    pivot_wider(data = ., id_cols = "SRVY", names_from = taxon, values_from = meanwgtcpue ) %>% 
    dplyr::mutate(all = fish + invert, 
                  top_fish = paste0(round(x = (topfish/fish)*100, digits = 0), "%"), 
                top_all = paste0(round(x = (topfish/(all))*100, digits = 0), "%"), 
                dplyr::across(where(is.numeric), formatC, digits = 0, big.mark = ",", format = "f"))
# temp[,1:4]<-NMFSReports::mod_number(x = temp[,1:4], comma_seperator = T, digits = 0)
# temp[,2:5] <- format(temp[,2:5], digits = 0, trim = F, big.mark = ",", scientific = F)

str0 <- NMFSReports::text_list(paste0(
  "The top 10 fish taxa in the ",temp$SRVY,
  " accounted for ",temp$top_all,
  " (an average of ",temp$topfish," kg/ha per station) ", 
  "of total mean fish and invertebrate CPUE (an average of ",
  temp$all," kg/ha per station) and ",
  temp$top_fish," of total mean fish CPUE (an average of ",temp$fish,
  " kg/ha per station; Table ", NMFSReports::crossref(
    list_obj = list_tables, 
    nickname = "tab_estimates_maxyr_spp_wt",
    sublist = "number"), ")."), sep = "", sep_last = "")

```

`r str0 `

<!---BLOCK_LANDSCAPE_START--->

`r NMFSReports::crossref(list_obj = list_tables, nickname = "tab_biomass_est_", sublist = "res", exact = FALSE) `

`r NMFSReports::crossref(list_obj = list_tables, nickname = "tab_majortaxa_pchange_", sublist = "res", exact = FALSE) `

`r NMFSReports::crossref(list_obj = list_tables, nickname = "tab_estimates_maxyr_spp_", sublist = "res", exact = FALSE) `

<!---BLOCK_LANDSCAPE_STOP--->


## Summary of Results for Selected `r NMFSReports::text_list(stringr::str_to_title(haul_cruises_maxyr$SRVY_long)) ` Fish and Invertebrate Fauna

An interactive map of species CPUE can be found at <https://apps-st.fisheries.noaa.gov/dismap/>. The CPUE data with associated station information including position, surface and bottom temperatures, and bottom depth can be downloaded from the NOAA Fisheries One Stop Shop data platform (FOSS; <https://www.fisheries.noaa.gov/foss/f?p=215:200:1099772399154:Mail:NO:::>). Users can interactively select, view, and download data on the platform for this survey and others. 

### Selected Fish Species Estimates

```{r spatial_distribution_fish}
# major fish 
temp0 <- report_spp1 %>% 
  dplyr::filter(taxon == "fish" & 
                  text_spp == TRUE) %>% 
  dplyr::select(file_name, print_name) %>% 
  dplyr::distinct()

  # compile
temp <- c()
for (i in 1:nrow(temp0)) {
  temp <- c(temp, 
                 paste0(
  temp0$print_name[i], " (Figure",
  ifelse(length(NMFSReports::crossref(list_obj = list_figures, 
                      nickname = paste0("fig_idw_cpue_*_",temp0$file_name[i], "*"), 
                      sublist = "number", exact = FALSE, text = FALSE))>1, "s", ""),
  " ", 
  NMFSReports::crossref(list_obj = list_figures, 
                        nickname = paste0("fig_idw_cpue_*_",temp0$file_name[i], "*"), 
                        sublist = "number", exact = FALSE),
  " and Tables ",
  NMFSReports::crossref(list_obj = list_tables, 
                        nickname = paste0("tab_estimates_maxyr_*_",temp0$file_name[i],"_*"), 
                        sublist = "number", exact = FALSE), 
  ")"))
}
str0 <- NMFSReports::text_list(temp)

# not major fish
temp2 <- report_spp1 %>% 
  dplyr::filter(taxon == "fish" &
                  (isFALSE(text_spp) | is.na(text_spp))) %>% 
  dplyr::select(file_name, print_name) %>% 
  dplyr::distinct()

```

Plots of the spatial distribution and tables of CPUE (kg/hectare and no./hectare) for `r length(NMFSReports::crossref(list_obj = list_figures, nickname = "fig_idw_cpue_fish_", sublist = "number", exact = FALSE, text = FALSE)) ` major fish species caught during the `r NMFSReports::text_list(SRVY1)` continental shelf survey are presented in the subsections below (Figures `r NMFSReports::crossref(list_obj = list_figures, nickname = "fig_idw_cpue_fish_", sublist = "number", exact = FALSE) ` and Tables `r NMFSReports::crossref(list_obj = list_tables, nickname = "tab_estimates_maxyr_fish_", sublist = "number", exact = FALSE)`). Differences in sums of estimates and totals are due to rounding. Total abundance-at-length and mean length estimates for major fish species are also presented in the subsections below (Figures `r NMFSReports::crossref(list_obj = list_figures, nickname = "fig_sizecomp_fish_", sublist = "number", exact = FALSE) `). Appendices `r NMFSReports::crossref(list_tables, "tab_app_principal_fish_", "number", exact = FALSE)` contain population estimates by sex and size class for `r nrow(temp0)` fish species. 

### Selected Invertebrates Estimates

```{r spatial_distribution_invert}
# invert 
temp0 <- report_spp1 %>% 
  dplyr::filter(taxon == "invert") %>% 
  dplyr::select(file_name, print_name) %>% 
  dplyr::distinct()

```

Plots of spatial distribution and tables of CPUE (kg/hectare and no./hectare) for `r xunits(length(NMFSReports::crossref(list_obj = list_figures, nickname = "fig_idw_cpue_invert_", sublist = "number", exact = FALSE, text = FALSE))) ` major invertebrate species caught during the `r NMFSReports::text_list(SRVY1)` continental shelf are presented below (Figures `r NMFSReports::crossref(list_obj = list_figures, nickname = "fig_idw_cpue_invert_", sublist = "number", exact = FALSE) ` and Tables `r NMFSReports::crossref(list_obj = list_tables, nickname = "tab_estimates_maxyr_invert_", sublist = "number", exact = FALSE)`). Differences in sums of estimates and totals are due to rounding. The crab species listed in this report and others are discussed and analyzed in more detail in `r paste0("@SAPcrab", maxyr) ` prepared by the AFSC Shellfish Assessment Program.

```{r taxon_pchange}
if (SRVY == "NEBS") {
  temp <- dplyr::bind_rows(
    list_tables$tab_majortaxa_pchange_EBS$raw, 
    list_tables$tab_majortaxa_pchange_NBS$raw) 
} else {
  temp <- list_tables$tab_majortaxa_pchange_EBS$raw
}
  temp <- temp %>% 
    dplyr::select(print_name, species_name1, paste(maxyr)) %>% 
    dplyr::rename(bio = paste0(maxyr)) %>%
    dplyr::group_by(print_name, species_name1) %>% 
    dplyr::summarise(bio = sum(bio, na.rm = TRUE)) %>% 
    dplyr::ungroup() %>%
    dplyr::filter(!is.na(bio) &
                    bio == max(bio, na.rm = TRUE))

if (length(unique(temp$print_name))==1) {
  
  temp0 <- paste0("tab_estimates_maxyr_invert_",report_spp1$file_name[report_spp1$print_name == temp$print_name[1]],"_wt")
  
  temp1 <- list_tables[names(list_tables) %in% temp0][[1]]$raw %>% 
    dplyr::select(SRVY, stratum, meanwgtcpue) %>% 
    dplyr::filter(!grepl(pattern = "Total", x = stratum, ignore.case = TRUE) & 
                  meanwgtcpue == max(meanwgtcpue, na.rm = TRUE)) %>% 
    dplyr::left_join(x = ., 
                     y = stratum_info %>% 
                       dplyr::select(stratum, description) %>% 
                       dplyr::mutate(stratum = as.character(stratum)), 
                     by = "stratum") %>% 
    dplyr::mutate(tidyr::separate(data = ., col = description, 
                                          sep = "- ", into = c("d1", "d2"), 
                                          remove = TRUE), 
                  d2 = stringr::str_to_lower(d2), 
                  d2 = gsub(pattern = "domain", replacement = "shelf", x = d2)) 

  str0 <- paste0("The ",temp$print_name[1]," (*",temp$species_name1[1],"*) is common in the Bering ",
                 ifelse(temp$species_name1[1] == "Asterias amurensis", 
                        "and Chukchi Seas [@Hamazakietal2005; @Federetal2005]", "") , 
                 " and was the invertebrate taxon with the highest catch rate by weight in the " , 
                 NMFSReports::text_list(SRVY1)," (Table",ifelse(SRVY == "NEBS", "s", "")," ",
                 NMFSReports::crossref(list_obj = list_tables, nickname = "tab_majortaxa_pchange_", sublist = "number", exact = FALSE),
                 "). Catch rates for the ",temp$print_name[1]," were highest in the ",
                 temp1$d2," (", #,temp1$d1,
                 # "; "
                 "Figure ", 
                 NMFSReports::crossref(list_obj = list_figures, 
                                       nickname = paste0(report_spp1$file_name[report_spp1$print_name == temp$print_name[1]]), 
                                       sublist = "number", exact = FALSE), 
                 " and Tables ", 
                 NMFSReports::crossref(list_obj = list_tables, 
                                       nickname = paste0(report_spp1$file_name[report_spp1$print_name == temp$print_name[1]]), 
                                       sublist = "number", exact = FALSE), 
                 # NMFSReports::crossref(list_obj = list_tables, 
                 #                       nickname = paste0("fig_idw_cpue_invert_",report_spp1$file_name[report_spp1$print_name == temp$print_name[1]]), 
                 #                       sublist = "number"),
                 ").")
  
} else {
  str0<-""
}
  
```

`r str0 `

Shelf-wide distributions of the four major commercial crab species: blue king crab (*Paralithodes platypus*), red king crab (*Paralithodes camtschaticus*), snow crab (*Chionoecetes opilio*), and Tanner crab (*Chionoecetes bairdi*) are shown in Figures `r NMFSReports::crossref(list_obj = list_figures, nickname = "fig_idw_cpue_*_crab", sublist = "number", exact = FALSE) `. Commercial crab stocks are managed by the ADF&G with federal oversight by NOAA Fisheries For more detailed information on bottom trawl survey results for commercial crab, refer to @RNChilton2011 and @RN973. The most recent modeling results on the status of these commercial crab stocks, refer to the annual Stock Assessment and Fishery Evaluation report prepared by the NPFMC [`r paste0("@NPFMC", maxyr)`].

\pagebreak

<!-- ## Summary of Results for Selected `r NMFSReports::text_list(stringr::str_to_title(haul_cruises_maxyr$SRVY_long))` Fish and Invertebrate Fauna -->

