
# Results and Discussion

A total of `r text_list(paste0(haul_cruises_maxyr$stations_completed, " ", haul_cruises_maxyr$SRVY_long, " stations"))` were successfully sampled in `r maxyr` (Fig. \@ref(fig:fig-sampled-survey-stations)). Haul and catch data from successfully trawled stations that were used for analyses in this section are available for download from the Fisheries One Stop Shop [@FOSSAFSCData].

## Ocean Temperatures and the Cold Pool

```{r results-cold-pool-insert, child=paste0(dir_out_rawdata, "/0-cold-pool.Rmd")}
```

\newpage

```{r fig-bt-temperature-}
nickname <- "fig-temperature-"
```

```{r temperature--child, child = paste0(dir_code, "_child_report_figtab.Rmd")}
```

```{r fig-mean-temperature}
nickname <- "fig-mean-temperature"
```

```{r fig-mean-temperature-child, child = paste0(dir_code, "_child_report_figtab.Rmd")}
```

```{r fig-cold-pool-area}
nickname <- "fig-cold-pool-area"
```

```{r fig-cold-pool-area-child, child = paste0(dir_code, "_child_report_figtab.Rmd")}
```

## Survey Data and Specimen Collections

Specimens collected during the `r maxyr` `r SURVEY` shelf trawl survey`r plural_surveys` are shown in Table`r plural_surveys` \@ref(fig:tab-specimen-samples-ebs) and \@ref(fig:tab-specimen-samples-nbs). Other special collections are listed in Table \@ref(tab:tab-special-projects).

```{r tab-specimen-samples-}
nickname <- "tab-specimen-samples-"
```

```{r tab-specimen-samples--child, child = paste0(dir_code, "_child_report_figtab.Rmd")}
```

## Species Composition

```{r results-species-composition}
str0 <- ""

# count spp
temp <- dplyr::left_join(
  x = catch_haul_cruises_maxyr %>% 
    dplyr::select(SRVY, species_code) %>% 
    dplyr::distinct(), 
  y = spp_info %>% 
    dplyr::filter(used_in_counts) %>%
    dplyr::select(species_code, species, family, genus, taxon) %>%
    dplyr::distinct(), 
  by = "species_code") %>% 
  dplyr::filter(taxon == "fish") %>% 
  dplyr::select(species_code, species, family, genus, taxon, SRVY) %>% 
  dplyr::distinct()

temp0 <- dplyr::full_join(
  x = temp %>% 
    dplyr::filter(!is.na(species)) %>% 
    dplyr::select(SRVY, species) %>% 
    dplyr::distinct() %>% 
    dplyr::group_by(SRVY) %>% 
    dplyr::summarise(species = n()),
  y = temp %>% 
    dplyr::filter(!is.na(species_code)) %>% 
    dplyr::select(SRVY, species_code) %>% 
    dplyr::distinct() %>% 
    dplyr::group_by(SRVY) %>%
    dplyr::summarise(species_code = n()),
  by = "SRVY") %>% 
  dplyr::left_join(
    x = ., 
    y = temp %>% 
      dplyr::filter(!is.na(family)) %>% 
      dplyr::select(SRVY, family) %>% 
      dplyr::distinct() %>% 
      dplyr::group_by(SRVY) %>%
      dplyr::summarise(family = n()),
    by = "SRVY")  %>% 
  dplyr::left_join(
    x = ., 
    y = temp %>% 
      dplyr::filter(!is.na(genus)) %>% 
      dplyr::select(SRVY, genus) %>% 
      dplyr::distinct() %>% 
      dplyr::group_by(SRVY) %>%
      dplyr::summarise(genus = n()),
    by = "SRVY") 

temp1 <- dplyr::bind_cols(
  temp %>% 
    dplyr::filter(!is.na(species)) %>% 
    dplyr::select(species) %>% 
    dplyr::distinct() %>% 
    dplyr::summarise(species = n()),
  temp %>% 
    dplyr::filter(!is.na(species_code)) %>% 
    dplyr::select(species_code) %>% 
    dplyr::distinct() %>% 
    dplyr::summarise(species_code = n()), 
  temp %>% 
    dplyr::filter(!is.na(family)) %>% 
    dplyr::select(family) %>% 
    dplyr::distinct() %>% 
    dplyr::summarise(family = n()),
  temp %>% 
    dplyr::filter(!is.na(genus)) %>% 
    dplyr::select(genus) %>% 
    dplyr::distinct() %>% 
    dplyr::summarise(genus = n())) 

if (SRVY == "NEBS") {
  # how many species encountered in one survey area but noth the other?
  load(file = paste0(dir_out_figtab, "tab-species-composition.rdata"))
  temp3 <- obj$raw %>%
    dplyr::left_join(x = .,
                     y = spp_info %>%
                       dplyr::select(species_code, order, species_name),
                     by = c("species_code"))
  
  str0 <- paste0( 
    "Of the ", 
    xunits(nrow(temp[temp$SRVY == "EBS",])),
    " fish species found in the EBS, ",
    xunits(nrow(temp3[temp3$where == "ebs",])), 
    " did not occur in the NBS (Table \\@ref(tab:tab-species-composition)). In comparison, ",
    xunits(nrow(temp3[temp3$where == "nbs",])), 
    " of the ",
    xunits(nrow(temp[temp$SRVY == "NBS",])),
    " fish species encountered in the NBS were not encountered in EBS (Table \\@ref(tab:tab-species-composition)). ")
  
  # flatfish
  temp4 <- temp3[temp3$order %in% c("Pleuronectiformes"), ]
  temp5 <- temp4 %>% 
    dplyr::filter(where != "both") %>% 
    dplyr::group_by(where) %>% 
    dplyr::summarise(n = n()) %>% 
    dplyr::mutate(
                  including = NA, 
                  where0 = dplyr::case_when(
                    where == "nbs" ~ "encountered in the NBS but not in the EBS",
                    where == "ebs" ~ "encountered in the EBS but not in the NBS"
                  ))
  for (i in 1:nrow(temp5)) {
    temp5$including[i] <- 
      text_list(
        paste0(
          temp4$common_name[grepl(pattern = temp5$where[i], 
                                  x = temp4$where, 
                                  ignore.case = TRUE)], 
          " (*", 
          temp4$species_name[grepl(pattern = temp5$where[i], 
                                   x = temp4$where, 
                                   ignore.case = TRUE)],
          "*)"))
  }
  
  str0 <- paste0(str0, "In ", maxyr, ", ", 
                   
                   text_list(
                     paste0(xunits(temp5$n), 
                            " flatfish species ", ifelse(temp5$n>1, "were", "was"), " ", 
                            temp5$where0, " (",
                            temp5$including, ")"), 
                     sep = "; "),
                   " (Table \\@ref(tab:tab-species-composition)).")
}

str0 <- gsub(pattern = ") (", replacement = "; ", x = str0, fixed = TRUE)
```

A total of `r xunits(temp1$species_code)` different fish species representing `r xunits(temp1$family)` families and `r xunits(temp1$genus)` genera were identified during the `r maxyr` `r SURVEY` survey`r plural_surveys` (Appendix Table`r plural_surveys` A \@ref(tab:tab-app-taxa-found-EBS-fish)`r ifelse(plural_surveys == "s", " and B \\@ref(tab:tab-app-taxa-found-NBS-fish)", "")`). In `r maxyr`, `r text_list(paste0("the ", temp0$SRVY, " survey recorded ", xunits(temp0$species_code), " total taxa, of which ", xunits(temp0$species), " were identified to the species level"))`. The remaining fish taxa in each survey area were identified to the genus level or higher. `r str0`

```{r results-count}
# count spp - invert
temp <- dplyr::left_join(
  x = catch_haul_cruises_maxyr %>% 
    dplyr::select(SRVY, species_code) %>% 
    dplyr::distinct(), 
  y = spp_info %>% 
    dplyr::filter(used_in_counts) %>%
    dplyr::select(species_code, species, phylum, taxon) %>%
    dplyr::distinct(), 
  by = "species_code") %>% 
  dplyr::filter(taxon == "invert") %>% 
  dplyr::select(species_code, species, phylum, taxon, SRVY) %>% 
  dplyr::distinct()

temp0 <- dplyr::full_join(
  x = temp %>% 
    dplyr::filter(!is.na(species)) %>% 
    dplyr::select(SRVY, species) %>% 
    dplyr::distinct() %>% 
    dplyr::group_by(SRVY) %>% 
    dplyr::summarise(species = n()),
  y = temp %>% 
    dplyr::filter(!is.na(species_code)) %>% 
    dplyr::select(SRVY, species_code) %>% 
    dplyr::distinct() %>% 
    dplyr::group_by(SRVY) %>%
    dplyr::summarise(species_code = n()),
  by = "SRVY") %>% 
  dplyr::mutate(perc = round(((species_code - species)/species_code)*100, digits = 2))

temp1 <- dplyr::bind_cols(
  temp %>% 
    dplyr::select(phylum, species) %>% 
    dplyr::distinct() %>% 
    dplyr::summarise(phylum = length(unique(phylum)), 
                     species = length(unique(species))),
  temp %>% 
    dplyr::filter(!is.na(species_code)) %>% 
    dplyr::select(species_code) %>% 
    dplyr::distinct() %>% 
    dplyr::summarise(species_code = n())) %>% 
  dplyr::mutate(perc = round(((species_code - species)/species_code)*100, digits = 2))

```

`r stringr::str_to_sentence(numbers2words(temp1$species_code))` different invertebrate taxa representing `r xunits(temp1$phylum)` phyla were identified during the `r maxyr` `r SURVEY` survey`r plural_surveys` (Appendix Table`r plural_surveys` A \@ref(tab:tab-app-taxa-found-EBS-invertebrate)`r ifelse(plural_surveys == "s", paste0(" and B \\@ref(tab:tab-app-taxa-found-NBS-invertebrate)"), "")`). In `r maxyr`, `r text_list(paste0(xunits(temp0$species_code), " invertebrate taxa ", "were recorded in the ", temp0$SRVY, " survey",  ", of which ", xunits(temp0$species), " were identified to the species level"))`. The remaining invertebrate taxa `r ifelse(plural_surveys == "s", "in each survey area ", "")`were identified to the genus level or higher. The lack of species level identifications among invertebrates was due to a variety of factors that are outlined in @RN934 and @Stevensonetal2016.

<br>

```{r tab-species-composition}
nickname <- "tab-species-composition"
```

```{r tab-species-composition-child, child = paste0(dir_code, "_child_report_figtab.Rmd")}
```

<br>

## Biomass, Abundance, and Catch per Unit Effort

```{r results-tot-biomass}
temp <- data.frame()
temp0 <- tidyr::crossing(SRVY = SRVY1, type = c("fish", "invert"))
for (i in 1:nrow(temp0)) {
  load(file = paste0(dir_out_figtab, "tab-biomass-est-", temp0$SRVY[i],"-", temp0$type[i],".rdata"))
  
  temp <- obj$raw %>%
    dplyr::filter(group == "Total") %>%
    # dplyr::filter(grepl(pattern = "Total", x = group, ignore.case = TRUE )) %>% 
    dplyr::mutate(SRVY = temp0$SRVY[i], 
                  taxon = temp0$type[i]) %>% 
    # dplyr::distinct() %>%
    dplyr::select(SRVY, taxon, `999`) %>% 
    dplyr::bind_rows(temp, .)
}

temp2 <- dplyr::full_join(
  x = temp, 
  y = total_biomass %>% 
    dplyr::filter(year == maxyr) %>%
    dplyr::select(-year) %>% 
    dplyr::group_by(SRVY),
  by = c("SRVY", "taxon")) %>% 
  dplyr::mutate(
    prop = (`999`/total), 
    perc = paste0(formatC(x = prop*100, 
                          digits = 0, format = "f", big.mark = ","), 
                  "%"), 
    group = gsub(pattern = "Total ", replacement = "", x = taxon) ) %>% 
  tidyr::pivot_wider(id_cols = "SRVY", 
                     names_from = "taxon", 
                     values_from = c("999", "perc", "prop")) %>%
  dplyr::mutate(case = dplyr::case_when(
    perc_fish == perc_invert ~ "about the same as", 
      prop_fish>prop_invert ~ "higher than",
      prop_fish<prop_invert ~ "lower than"))

temp1 <- left_join(
  x = temp, 
  y = stratum %>% 
    dplyr::group_by(SRVY) %>% 
    dplyr::summarise(area_km2 = sum(area_km2, na.rm = TRUE)), 
  by = "SRVY") %>% 
  dplyr::mutate(prop = `999`/area_km2, 
                taxon = gsub(pattern = "Total ", replacement = "", x = taxon)) %>% 
  dplyr::filter(taxon == "fish")

str0 <- paste0("The ", 
               text_list(paste0(
                 "total demersal animal biomass for the ", 
                 total_biomass$SRVY[total_biomass$year == maxyr], 
                 " was estimated at ", 
                 xunits(total_biomass$total[total_biomass$year == maxyr]), 
                 " t")), ". " )

str00 <- ""
for (ii in 1:length(temp2$SRVY)) {
  
  str000 <- ifelse(ii != 1 & temp2$prop_fish[ii]>temp2$prop_invert[ii], "also ","")
  
  str00 <- paste0(str00, 
                  ifelse(ii==2, " and in the ", "In the "), 
                  paste0(temp2$SRVY[ii], 
                         ", the proportion of fishes (", 
                         temp2$perc_fish[ii], 
                         "; Table \\@ref(tab:tab-biomass-est-",  temp2$SRVY[ii],
                         "-fish)) was ", str000,  
                         temp2$case[ii],
                         " invertebrates (", 
                         temp2$perc_invert[ii], 
                         "; Table \\@ref(tab:tab-biomass-est-", temp2$SRVY[ii], 
                         "-invert))"))
}
str0 <- paste0(str0, str00, ". ")

if (SRVY == "NEBS") {
  str0 <- paste0(str0, 
                 paste0(ifelse(temp1$prop[temp1$SRVY=="EBS"]>temp1$prop[temp1$SRVY=="NBS"], 
                               "The lower relative fish biomass in the NBS than in the EBS is consistent", 
                               "The higher relative fish biomass in the NBS than in the EBS is inconsistent"), 
                        " with results of a broader analysis of all survey years presented by @RN936 which showed decreasing fish biomass with increasing latitude on the eastern Bering Sea continental shelf. ", 
                        "") ) 
}

str0 <- gsub(pattern = ") (", replacement = "; ", x = str0, fixed = TRUE)

```

`r str0`

```{r results-tot-biomass2}
str0 <- ""
if (SRVY == "NEBS") {
  
  temp1 <- temp2 <- temp3 <- data.frame()
  
  for (i in 1:length(SRVY1)) {
    load(file = paste0(dir_out_figtab, "tab-biomass-est-", SRVY1[i], "-fish.rdata"))
    temp1 <- obj$raw %>%
      dplyr::mutate(SRVY = SRVY1[i]) %>%
      dplyr::filter(is.na(taxon) |
                      grepl(pattern = "Total", x = taxon, ignore.case = TRUE )) %>% 
      dplyr::filter(!grepl(pattern = "Total", x = group, ignore.case = TRUE ) &
                      !grepl(pattern = "Other", x = group, ignore.case = TRUE )) %>% 
      dplyr::select(SRVY, group, `999`, prop) %>% 
      dplyr::arrange(-prop) %>% 
      dplyr::mutate(order = 1:nrow(.)) %>% 
      dplyr::bind_rows(temp1, .)
    
    temp2 <- obj$raw %>%
      dplyr::mutate(SRVY = SRVY1[i]) %>%
      dplyr::filter(group %in% temp1$group[1:2] & 
                      !grepl(pattern = "Total ", x = taxon, ignore.case = TRUE )) %>% 
      dplyr::select(SRVY, group, taxon, `999`, prop) %>% 
      dplyr::arrange(-prop) %>% 
      dplyr::mutate(order = 1:nrow(.)) %>% 
      dplyr::bind_rows(temp2, .)
    
  }
  
  temp1 <- temp1 %>% 
    tidyr::pivot_wider(id_cols = c("group"), 
                       names_from = "SRVY", 
                       values_from = c("999", "prop", "order")) %>%
    dplyr::mutate(same = ifelse(order_EBS == order_NBS, TRUE, FALSE)) %>% 
    dplyr::filter(!(is.na(SRVY)))

  
  temp2 <- temp2 %>% 
    tidyr::pivot_wider(id_cols = c("group", "taxon"), 
                       names_from = "SRVY", 
                       values_from = c("999", "prop", "order")) %>%
    dplyr::mutate(same =ifelse(order_EBS == order_NBS, TRUE, FALSE)) %>% 
    dplyr::left_join(
      x = ., 
      y = spp_info_maxyr %>% 
        dplyr::select(species_name, common_name), 
      by = c("taxon" = "common_name")  )
  
  # temp3: top 3 spp in each group
  temp0 <- tidyr::crossing(group = unique(temp2$group), 
                           SRVY = SRVY1) %>% 
    dplyr::arrange(SRVY, group) %>% 
    dplyr::mutate(str0 = NA)
  
  for (i in 1:nrow(temp0)) {
    
    temp3 <- temp2 %>% 
      dplyr::rename(prop = paste0("prop_", temp0$SRVY[i]),
                    order = paste0("order_", temp0$SRVY[i])) %>%
      dplyr::arrange(order) %>% 
      dplyr::filter(
        group == temp0$group[i]) %>% 
      head(3) %>%
      dplyr::mutate(prop = paste0(round(x = prop*100, digits = 1), "%"), 
                    SRVY = temp0$SRVY[i]) %>%
      dplyr::arrange(order) %>% 
      dplyr::select(SRVY, group, taxon, species_name, prop) %>% # 
      dplyr::filter(prop != "0%") 
    
    if (nrow(temp3)>1) {
      temp0$str0[temp0$SRVY == temp0$SRVY[i] & 
                   temp0$group == temp0$group[i]] <- 
        text_list(paste0(temp3$taxon, " (*", temp3$species_name, 
                         "*, ",temp3$prop,")"))
      temp0$group1 <- unlist(regmatches(temp0$group,
                                        gregexpr(
                                          "(?<=\\().*?(?=\\))", # everything within a (*)
                                          temp0$group, perl=T)))
      temp0$group0 <- unlist(lapply(strsplit(x = temp0$group, split = " ", fixed = TRUE), `[[`, 1))
    }
  }
  
  temp0$group0 <- paste0("the family ", temp0$group0)
  
  temp0$str0 <- gsub(pattern = "*NA*, ", replacement = "", x = temp0$str0, fixed = TRUE)
  temp0$str0 <- gsub(pattern = "  ", replacement = " ", x = temp0$str0, fixed = TRUE)
  
  temp3 <- c()
  for (i in 1:length(SRVY1)){
    temp4 <- text_list(paste0(
      temp0$group0[temp0$SRVY == SRVY1[i]], 
      " was primarily comprised of ", 
      temp0$str0[temp0$SRVY == SRVY1[i]]), sep_last2 = "; ")
    temp3 <- paste0(temp3, 
                    paste0("In the ", SRVY1[i], ", ", temp4, ". "))
  }
  
  str0 <- paste0(
    text_list(temp1$group[1:2]),
    " were the fish families with highest biomass in both the EBS (",
    text_list(
      paste0(round(x = temp1$prop_EBS[1:2]*100, digits = 1), "%")), 
    " of the total biomass, respectively), and the NBS (",
    text_list(
      paste0(round(x = temp1$prop_NBS[1:2]*100, digits = 1), "%")), 
    " of the total biomass, respectively; Tables \\@ref(tab:tab-biomass-est-EBS-fish) and \\@ref(tab:tab-biomass-est-NBS-fish)). ", 
    temp3)
}
```

`r str0`

```{r results-benthic-community}

str0 <- paste0("Noticeable changes were observed in the ", SURVEY," the benthic communities between ",
               compareyr," and ", maxyr,". ")

for (i in 1:length(SRVY1)) {
  load(file = paste0(dir_out_figtab, "tab-majortaxa-pchange-", SRVY1[i], ".rdata"))

  temp0 <- obj$raw
  temp <- 
    temp0 %>% 
    dplyr::filter(!is.na(change0)) %>%
    dplyr::mutate(case = case_when(
      change>0 ~ "increased", 
      change<0 ~ "decreased")) %>% 
    dplyr::arrange(-change0) %>%
      dplyr::select(print_name, maxyr, compareyr, change, case) 
  
  temp <-  
    dplyr::bind_rows(
      temp %>% 
        dplyr::filter(case == "increased") %>% 
        head(5), 
      temp %>% 
        dplyr::filter(case == "decreased") %>% 
        tail(5) ) %>% 
    dplyr::mutate(print_name = gsub(pattern = "include", replacement = ", which", x = print_name))
  
    temp1 <- data.frame(maxyr = sum(total_biomass$total[
    total_biomass$SRVY == SRVY1[i] & 
      total_biomass$year == maxyr], na.rm = TRUE), 
    compareyr = sum(total_biomass$total[
      total_biomass$SRVY == SRVY1[i] & 
        total_biomass$year == compareyr], na.rm = TRUE))
  
  str0 <- paste0(str0, 
                 "The total estimated biomass in the ",SRVY1[i]," ", 
                 ifelse(temp1$compareyr<temp1$maxyr, "increased", "decreased"),
                 " from ",
                 xunits(temp1$compareyr)," t in ", compareyr," to ",
                 xunits(temp1$maxyr)," t in ", maxyr, ". ", 
                 
                 # taxa increased
                 "Taxa that significantly increased in biomass in the ", SRVY1[i], " included ", 
                 text_list(paste0(temp$print_name[temp$case == "increased"],
                                  " (", temp$change[temp$case == "increased"], ")")), 
                 " (Table \\@ref(tab:tab-majortaxa-pchange-", SRVY1[i], ")). ",
                 # taxa decreased
                 "Large decreases in ", SRVY1[i], " biomass were observed for ", 
                 text_list(paste0(temp$print_name[temp$case == "decreased"],
                                  " (", temp$change[temp$case == "decreased"], ")")), 
                 " (Table \\@ref(tab:tab-majortaxa-pchange-", SRVY1[i], ")). "
  )
}

str0 <- gsub(x = str0, pattern = ") (", replacement = "; ", fixed = TRUE)

```

`r str0`While exhaustive efforts are made to standardize catch processing and data collection, variation in catchability may cause some differences in these results between years (@KotwickiOno2019).

```{r results-top-10-taxon}
temp <- data.frame()
load(file = paste0(dir_out_figtab, "tab-est-spp-wt.rdata"))

for (i in 1:nrow(haul_cruises_maxyr)) {
  
  temp <- obj$raw %>% 
    dplyr::filter(SRVY == haul_cruises_maxyr$SRVY[i]) %>%
    dplyr::select(cpue_kgkm2_mean, print_name) %>%
    dplyr::arrange(-cpue_kgkm2_mean) %>% 
    dplyr::ungroup() %>% 
    head(10) %>% 
    dplyr::summarise(cpue_kgkm2_mean = sum(cpue_kgkm2_mean, na.rm = TRUE)) %>% 
    dplyr::mutate(SRVY = haul_cruises_maxyr$SRVY[i], 
                  taxon = "topfish") %>% 
    dplyr::bind_rows(temp, .)
}  

temp <- biomass %>% 
  dplyr::filter(year == maxyr & 
                  stratum == 999) %>%
  dplyr::select(cpue_kgkm2_mean, SRVY, taxon) %>% 
  dplyr::group_by(SRVY, taxon) %>% 
  dplyr::summarise(cpue_kgkm2_mean = sum(cpue_kgkm2_mean, na.rm = TRUE)) %>% 
  dplyr::ungroup() %>% 
  dplyr::bind_rows(temp, .) %>% 
  pivot_wider(data = ., id_cols = "SRVY", names_from = taxon, values_from = cpue_kgkm2_mean ) %>% 
  dplyr::mutate(all = fish + invert, 
                perc_topfish = paste0(round(x = (topfish/all)*100, digits = 1), "%"), # the % of the top 10 fish caught out of the survey
                perc_topfishoffish = paste0(round(x = (topfish/fish)*100, digits = 1), "%"), # the % of the top 10 fish caught out of the survey
                perc_invert = paste0(round(x = (invert/all)*100, digits = 1), "%"), 
                perc_fish = paste0(round(x = (fish/all)*100, digits = 1), "%"), 
                dplyr::across(where(is.numeric), formatC, digits = 1, big.mark = ",", format = "f"))

str0 <- text_list(paste0(
  "The 10 most abundant fish taxa in the ",temp$SRVY,
  " accounted for ", temp$perc_topfish,
  " (an average of ",temp$topfish," kg/ha per station) ", 
  "of total mean fish and invertebrate CPUE (an average of ",
  temp$all," kg/ha per station) and ",
  temp$perc_topfishoffish," of total mean fish CPUE (an average of ",temp$fish,
  " kg/ha per station; Tables \\@ref(tab:tab-est-spp-wt) and \\@ref(tab:tab-est-spp-num))."), sep = "", sep_last = "", sep_last2 = "")

```

`r str0`

<!---BLOCK_LANDSCAPE_START--->

```{r tab-biomass-est-}
nickname <- "tab-biomass-est-"
sep0 <- "\\pagebreak"
```

```{r tab-biomass-est-child, child = paste0(dir_code, "_child_report_figtab.Rmd")}
```

<!---BLOCK_LANDSCAPE_STOP--->

\pagebreak

```{r tab-majortaxa-pchange-}
nickname <- "tab-majortaxa-pchange-"
sep0 <- "\\pagebreak"
```

```{r tab-majortaxa-pchange-child, child = paste0(dir_code, "_child_report_figtab.Rmd")}
```

\pagebreak

```{r tab-est-spp-wt}
nickname <- "tab-est-spp-wt"
```

```{r tab-est-spp-wt-child, child = paste0(dir_code, "_child_report_figtab.Rmd")}
```

```{r tab-est-spp-num}
nickname <- "tab-est-spp-num"
```

```{r tab-est-spp-num-child, child = paste0(dir_code, "_child_report_figtab.Rmd")}
```

## Summary of Results for Selected Fish and Invertebrate Fauna of the `r gsub(pattern = "And", replacement = "and", x = stringr::str_to_title(SURVEY))`

An interactive map of species CPUE is available through the NOAA Distribution Mapping and Analysis Portal (https://apps-st.fisheries.noaa.gov/dismap/; @DisMAPDataPortal). The CPUE data with associated station information including position, surface and bottom temperatures, and bottom depth can be downloaded from the NOAA Fisheries One Stop Shop data platform (FOSS; @FOSSAFSCData). Users can interactively select, view, and download data on the platform for this survey and others.

The spatial distribution maps below illustrate where species were found during the surveys. The distributions are presented as inverse distance weighted interpolations, and assumes that data from stations that are closer to one another are more alike than those that are farther apart.

### Selected Fish Species Estimates

```{r results-spatial-distribution_fish}

temp <- report_spp1 %>% 
  dplyr::filter(plot_idw == TRUE) %>% # | plot_pa == TRUE) %>% 
  dplyr::select(file_name, taxon) %>% 
  dplyr::distinct()

temp2 <- report_spp1 %>% 
  dplyr::filter(table_cpue == TRUE) %>% 
  dplyr::select(file_name, taxon) %>% 
  dplyr::distinct()

```

Plots of the spatial distribution, abundance-at-length estimates, and tables of CPUE (kg/hectare and no./hectare) for `r length(unique(report_spp1$file_name[report_spp1$taxon == "fish"]))` major fish species caught during the `r SURVEY` continental shelf survey are presented in Figs. `r paste0("\\@ref(fig:fig-dist-",temp$taxon[1],"-",temp$file_name[1],"-data)")` to `r paste0("\\@ref(fig:fig-dist-",temp$taxon[nrow(temp)],"-",temp$file_name[nrow(temp)],"-data)")` and Tables `r paste0("\\@ref(tab:tab-est-",temp2$taxon[1],"-",temp2$file_name[1],"-wt)")` to `r paste0("\\@ref(tab:tab-est-",temp2$taxon[nrow(temp2)],"-",temp2$file_name[nrow(temp2)],"-num)")`. Differences in estimates and totals may be due to rounding.

### Selected Invertebrates Estimates

Plots of spatial distribution and tables of CPUE (kg/hectare and no./hectare) for the `r length(unique(report_spp1$file_name[report_spp1$taxon == "invert"]))` major invertebrate species caught during the `r SURVEY` continental shelf surveys presented below. Differences in estimates and totals may be due to rounding. 

Detailed information on bottom trawl survey results for commercial crab species are discussed and analyzed in the AFSC Shellfish Assessment Program's annual data report [`r paste0("@SAPcrab", maxyr)`]. Commercial crab stocks are managed by the ADF&G with federal oversight by NOAA Fisheries. The most recent modeling results on the status of these commercial crab stocks are reported in the annual Stock Assessment and Fishery Evaluation report prepared by the NPFMC [`r paste0("@NPFMCBSAIcrab", maxyr)`].

