
```{r res_spp_vars_{{jj}} }
a <- report_spp1[report_spp1$file_name == unique(report_spp1$file_name)[jj], ]

spp_sci <- a$species_name[1]
spp_sci1 <- a$species_name1[1]
spp_code <- a$species_code # eval(expr = parse(text = a$species_code[1]))
spp_print <- a$print_name[1]
spp_file <- a$file_name[1]
spp_taxon <- a$taxon[1]

# report_title == "community"
spp_plot_sizecomp <- ifelse(is.na(a$plot_sizecomp[1]), FALSE, a$plot_sizecomp[1])
spp_plot_idw_coldwarm <- FALSE
spp_plot_idw <- ifelse(is.na(a$plot_idw[1]), FALSE, a$plot_idw[1])
spp_plot_pa <- FALSE
spp_table_cpue <- FALSE
text_spp <- TRUE

if (report_title == "data") {
spp_plot_pa <- ifelse(is.na(a$plot_pa[1]), FALSE, a$plot_pa[1])
spp_plot_idw_coldwarm <- ifelse(is.na(a$plot_idw_coldwarm[1]), FALSE, a$plot_idw_coldwarm[1])
spp_table_cpue <- ifelse(is.na(a$table_cpue[1]), FALSE, a$table_cpue[1])
text_spp <- ifelse(is.na(a$text_spp[1]), FALSE, a$text_spp[1])
}
```


```{r res_spp_lang_{{jj}} }
# Native Languages Names
lang <- ""

if (report_title == "community") {

temp <- readr::read_csv(file = paste0(dir_out_rawdata, "/0_species_local_names.csv"))

lang <- data.frame(lang_long = as.character(names(temp)[grepl(pattern = "lang_", x = temp[1,])]), 
                   lang = as.character(temp[1,grepl(pattern = "lang_", x = temp[1,])]), 
                   name = as.character(t(report_spp[jj,] %>% dplyr::select( dplyr::starts_with("lang_")) )) )

lang <- rbind.data.frame(data.frame(name = c(ifelse(is.na(a$scientific_name_prev[a$print_name == spp_print][1]), NA, 
                                                    paste0("*", a$scientific_name_prev[a$print_name == spp_print][1], "*")), 
                                             ifelse(is.na(a$common_name_prev[a$print_name == spp_print][1]), NA, 
                                                    a$common_name_prev[a$print_name == spp_print][1])), 
                                    lang = c("scientific_name_prev", "common_name_prev"), 
                                    lang_long = c("Previous Scientific Name", "Other Common Names")), 
                         lang) %>%
  dplyr::filter(!is.na(name))

if (nrow(lang)>0) {
  lang  <- paste(paste0("**",lang$lang_long,"**: ",lang$name,"\n\n"), sep = "", collapse = "")
} else {
  lang <- ""
}
}
```

## `r stringr::str_to_title(spp_print)` `r ifelse(is.na(spp_sci), "", paste0("(",spp_sci,")")) `

`r lang `

```{r res_spp_data_wrangle_{{jj}} }
# find basic info about species
haul0 <- catch_haul_cruises %>% 
    dplyr::select("stationid", "stratum", "start_latitude", "start_longitude", 
                  "bottom_depth", "gear_temperature" ,"surface_temperature", 
                  "survey_name", "SRVY", "year", "species_code", 
                  "weight", "number_fish", "hauljoin")

biomass_cpue <- cpue_biomass_total %>%
  dplyr::select("year", "print_name", "SRVY", "weighted_CPUE", "biomass_mt") %>%
  dplyr::rename(biomass = biomass_mt,
                cpue_kgha = weighted_CPUE)

# biomass_cpue <- biomass %>% 
#   dplyr::filter(species_code == spp_code[1]) %>%
#   dplyr::select(year, SRVY, varmnwgtcpue, biomass) %>% 
#   dplyr::rename(biomass = biomass, 
#                 cpue_kgha = varmnwgtcpue) %>% 
#   dplyr::mutate(print_name = spp_print)

length_maxyr0 <- length_data %>% 
  ungroup() %>% 
  dplyr::filter(species_code %in% spp_code) %>% 
  dplyr::select(SRVY, species_code, frequency, sex, length,
                length_type, name, sentancefrag)

```

`r ifelse(refcontent & text_spp, "*REFERENCE MATERIAL FOR WRITERS - START*", "")`

```{r res_spp_ebs_{{jj}} }
temp <- ""
temp1 <- ""
show <- refcontent & (nrow(biomass_cpue[(biomass_cpue$SRVY == "EBS" & biomass_cpue$print_name == spp_print),])>0)
if (show) {
  if (report_title == "community") {
    biomass_cpue_tab_name = c("tab_majortaxa_pchange")
  } else if (report_title == "data") {
    biomass_cpue_tab_name = c("tab_majortaxa_pchange_EBS", "table_est_wt", "table_est_num")
  }
  
temp<-species_content(
  SURVEY000 = "eastern Bering Sea", 
  SRVY000 = "EBS", 
  haul0 = haul0,
  biomass_cpue = biomass_cpue, 
  length_maxyr0 = length_maxyr0,
  spp_print = spp_print, 
  spp_code = spp_code,
  maxyr = maxyr, 
  compareyr = compareyr, 
  biomass_cpue_tab_name = biomass_cpue_tab_name)

temp1<-temp$table_spp
temp <- temp$text_spp

}
```

`r ifelse(show, "**Eastern Bering Sea (EBS)**", "")`

`r temp1`

`r temp`


```{r res_spp_nbs_{{jj}} }
temp <- ""
temp1 <- ""
show <- refcontent & (nrow(biomass_cpue[(biomass_cpue$SRVY == "NBS" & biomass_cpue$print_name == spp_print),])>0)
if (show) {
    if (report_title == "community") {
    biomass_cpue_tab_name = c("tab_majortaxa_pchange")
  } else if (report_title == "data") {
    biomass_cpue_tab_name = c("tab_majortaxa_pchange_NBS", "table_est_wt", "table_est_num")
  }
temp<-species_content(
  SURVEY000 = "northern Bering Sea", 
  SRVY000 = "NBS", 
  haul0 = haul0,
  biomass_cpue = biomass_cpue, 
  length_maxyr0 = length_maxyr0,
  spp_print = spp_print, 
  spp_code = spp_code,
  maxyr = maxyr, 
  compareyr = compareyr, 
  biomass_cpue_tab_name = biomass_cpue_tab_name)
temp1<-temp$table_spp
temp <- temp$text_spp
}
```

`r ifelse(show, ifelse(SRVY %in% "NEBS", "**Northern Bering Sea (NBS)**", ""), "")`

`r temp1`

`r temp`

```{r res_spp_nebs_{{jj}} }
temp <- ""
temp1 <- ""
show <- refcontent & 
  (nrow(biomass_cpue[(biomass_cpue$SRVY == "EBS" & biomass_cpue$print_name == spp_print),])>0 &
     nrow(biomass_cpue[(biomass_cpue$SRVY == "NBS" & biomass_cpue$print_name == spp_print),])>0)
if (show) {
  if (report_title == "community") {
    biomass_cpue_tab_name = c("tab_majortaxa_pchange")
  } else if (report_title == "data") {
    biomass_cpue_tab_name = c("tab_majortaxa_pchange_EBS", "tab_majortaxa_pchange_NBS", 
                              "table_est_wt", "table_est_num")
  }
temp<-species_content(
  SURVEY000 = "eastern and northern Bering Sea",
  SRVY000 = c("NBS", "EBS"),
  haul0 = haul0,
  biomass_cpue = biomass_cpue, 
  length_maxyr0 = length_maxyr0,
  spp_print = spp_print, 
  spp_code = spp_code,
  maxyr = maxyr, 
  compareyr = compareyr, 
  biomass_cpue_tab_name = biomass_cpue_tab_name)
temp1<-temp$table_spp
temp <- temp$text_spp
}
```

`r ifelse(show, ifelse(SRVY %in% "NEBS", "**Northern and Eastern Bering Sea Combined (NEBS)**", ""), "")`

`r temp1`

`r temp `

`r ifelse(refcontent & text_spp, "*REFERENCE MATERIAL FOR WRITERS - END*", "")`

```{r res_spp_insert_text_{{jj}} }
insert<-""

if (report_title == "data") {
  
  # Species specific
  table_est_both <- NMFSReports::crossref(
    list_obj = list_tables, 
    nickname = paste0("tab_estimates_maxyr_*", spp_file, "*"), 
    sublist = "number", 
    exact = FALSE)
  table_est_wt <- NMFSReports::crossref(
    list_obj = list_tables, 
    nickname = paste0("tab_estimates_maxyr_*", spp_file, "_wt"), 
    sublist = "number", 
    exact = FALSE)
  table_est_num <- NMFSReports::crossref(
    list_obj = list_tables, 
    nickname = paste0("tab_estimates_maxyr_*", spp_file, "_num"), 
    sublist = "number", 
    exact = FALSE)
  
if (text_spp) {
  
  # general coldpool figures
  figure_coldpool_warm_stanza <- NMFSReports::crossref(
    list_obj = list_figures, 
    nickname = paste0("fig_bt_temperature_ebs_above"), 
    sublist = "number")
  figure_coldpool_cold_stanza <- NMFSReports::crossref(
    list_obj = list_figures, 
    nickname = paste0("fig_bt_temperature_ebs_below"), 
    sublist = "number")
  figure_coldpool_both_stanza <- NMFSReports::crossref(
    list_obj = list_figures, 
    nickname = paste0("fig_bt_temperature_*"), 
    sublist = "number", 
    exact = FALSE)
  
  # General biomass table
  tab_majortaxa_pchange_EBS <- NMFSReports::crossref(
    list_obj = list_tables, 
    nickname = paste0("tab_majortaxa_pchange_EBS"), 
    sublist = "number")
   table_bio_pchange_ebs <- table_bio_ebs <- NMFSReports::crossref(
    list_obj = list_tables, 
    nickname = paste0("tab_biomass_est_fish_EBS"), 
    sublist = "number")
  table_bio_nbs <- table_bio_pchange_nbs <- ""
  
  if (SRVY == "NEBS"){
  table_bio_pchange_nbs <- table_bio_nbs <- NMFSReports::crossref(
    list_obj = list_tables, 
    nickname = paste0("tab_biomass_est_fish_NBS"), 
    sublist = "number")
  tab_majortaxa_pchange_NBS <- NMFSReports::crossref(
    list_obj = list_tables, 
    nickname = paste0("tab_majortaxa_pchange_NBS"), 
    sublist = "number")
  }
  

  
  if (spp_plot_sizecomp) {
    figure_sizecomp <- NMFSReports::crossref(
      list_obj = list_figures, 
      nickname = paste0("fig_sizecomp_fish_", spp_file), 
      sublist = "number")
    } 
  
  if (spp_plot_idw) {
    figure_idw <- NMFSReports::crossref(
      list_obj = list_figures, 
      nickname = paste0("fig_idw_cpue_fish_", spp_file), 
      sublist = "number")    
  }
 
  if (spp_plot_idw_coldwarm) {
      figure_idw_both_stanza <- NMFSReports::crossref(
        list_obj = list_figures, 
        nickname = paste0("fig_idw_cpue_fish_", spp_file, "_*"), 
        sublist = "number", 
        exact = FALSE)
      figure_idw_warm_stanza <- NMFSReports::crossref(
        list_obj = list_figures, 
        nickname = paste0("fig_idw_cpue_fish_", spp_file, "_above"), 
        sublist = "number")
      figure_idw_cold_stanza <- NMFSReports::crossref(
        list_obj = list_figures, 
        nickname = paste0("fig_idw_cpue_fish_", spp_file, "_below"), 
        sublist = "number")
  }

  insert <- readtext2(file = paste0(dir_out_rawdata, "/",spp_file,".docx"), 
                    refcontent = refcontent)
}

  
land_start <- ifelse(table_est_both != "[](#)", "<!---BLOCK_LANDSCAPE_START--->", "")
land_end <- ifelse(table_est_both != "[](#)", "<!---BLOCK_LANDSCAPE_STOP--->", "")

# `r NMFSReports::crossref(list_obj = list_figures, nickname = paste0("fig_sizecomp_*_", spp_file), sublist = "res", exact = FALSE)`

# `r NMFSReports::crossref(list_obj = list_figures, nickname = paste0("fig_idw_cpue_*_", spp_file, "*"), sublist = "res", exact = FALSE)`

}

if (report_title == "community") {

# Main text
fig_bot_temp_map <- NMFSReports::crossref(
  list_obj = list_figures,
  nickname = paste0("fig_bt_all_nebs_surveys"),
  sublist = "number")

fig_surf_temp_map <- NMFSReports::crossref(
  list_obj = list_figures,
  nickname = paste0("fig_st_all_nebs_surveys"),
  sublist = "number")

fig_both_temp_maps <- NMFSReports::crossref(
  list_obj = list_figures,
  nickname = paste0("fig_*_all_nebs_surveys"),
  sublist = "number", 
  exact = FALSE)

tab_majortaxa_pchange <- NMFSReports::crossref(
  list_obj = list_tables,
  nickname = paste0("tab_majortaxa_pchange"),
  sublist = "number")

# Species specific
# Species specific
if (spp_plot_sizecomp) {
  fig_sizecomp <- NMFSReports::crossref(
    list_obj = list_figures, 
    nickname = paste0("fig_sizecomp*", spp_file), 
    sublist = "number", 
    exact = FALSE)
} 

if (spp_plot_idw) {
  fig_idw <- NMFSReports::crossref(
    list_obj = list_figures, 
    nickname = paste0("fig_idw*", spp_file), 
    sublist = "number", 
    exact = FALSE)    
}

land_start <- ""
land_end <- ""

insert <- readtext2(file = paste0(dir_out_rawdata, "/",spp_file,".docx"), 
                    refcontent = refcontent)
}

```

`r paste0(insert, "\n\n") `

<div id="refs"></div>

`r NMFSReports::crossref(list_obj = list_figures, nickname = paste0("fig_sizecomp_*_", spp_file), sublist = "res", exact = FALSE)`

`r NMFSReports::crossref(list_obj = list_figures, nickname = paste0("fig_idw_cpue_*_", spp_file, "*"), sublist = "res", exact = FALSE)`

<!-- data report only (shouldn't show up if table doesn't exist) -->

`r land_start `

`r NMFSReports::crossref(list_obj = list_tables, nickname = paste0("tab_estimates_maxyr_*_", spp_file, "*"), sublist = "res", exact = FALSE) `

`r land_end `
