---
output:
  word_document:
    pandoc_args: ["--metadata-file=header.yaml"]
    reference_docx: styles_reference.docx
    df_print: kable
bibliography: "../cite/bibliography.bib"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, error = FALSE, message = FALSE)
```

```{r}
a <- report_spp1[report_spp1$file_name == unique(report_spp1$file_name)[jj], ]

spp_sci <- a$species_name[1]
spp_sci1 <- a$species_name1[1]
spp_code <- a$species_code # eval(expr = parse(text = a$species_code[1]))
spp_print <- a$print_name[1]
spp_file <- a$file_name[1]

spp_plot_sizecomp <- 
#   ifelse(sizecomp %>% 
#            dplyr::filter(species_code %in% spp_code & 
#                            SRVY == "NBS") %>% 
#            nrow() == 0, 
#     FALSE, 
    a$plot_sizecomp[1]#)
# 
spp_plot_idw <-
#   ifelse(cpue_biomass_station %>%
#     dplyr::ungroup() %>% 
#     dplyr::select(year, stationid, #hauljoin, 
#                   SRVY, cpue_kgha, 
#                   group, species_name) %>%
#     dplyr::filter(!is.na(cpue_kgha)) %>%
#     dplyr::arrange(-year) %>%
#     dplyr::filter(tolower(group) %in% tolower(spp_print) &
#                     year %in% nbsyr) %>% 
#     dplyr::left_join(
#       x = ., 
#       y = station_info %>% 
#         dplyr::select(-reg), 
#       by = c("stationid", "SRVY")) %>% 
#     dplyr::filter(!is.na(latitude) & !is.na(longitude)) %>% 
#            nrow() == 0, 
#          FALSE, 
         a$plot_idw[1]#)

plot_idw_coldwarm <- a$plot_idw_coldwarm[1]

text_spp <- a$text_spp[1]
table_cpue <- a$table_cpue[1]
table_bio_portion <- a$table_bio_portion[1]
table_bio_spp <- a$table_bio_spp[1]

```

## `r stringr::str_to_title(spp_print)` `r ifelse(is.na(spp_sci), "", paste0("(",spp_sci,")")) `

```{r}
# find basic info about species
haul0 <- catch_haul_cruises %>% 
    dplyr::select("stationid", "stratum", "start_latitude", "start_longitude", 
                  "bottom_depth", "gear_temperature" ,"surface_temperature", 
                  "survey_name", "SRVY", "year", "species_code", 
                  "weight", "number_fish", "hauljoin")


# biomass_cpue <- dplyr::full_join(
#   x = cpue %>%
#     dplyr::select("year", "SRVY", "species_code", "cpue_kgha") %>%
#     dplyr::group_by(year, SRVY, species_code) %>%
#     dplyr::summarise(cpue_kgha = sum(cpue_kgha, na.rm = TRUE)),
#   y = biomass %>%
#     dplyr::filter(stratum == 999) %>%
#     dplyr::select("year", "SRVY", "species_code", "common_name",
#                   "biomass"),
#   by = c("year", "SRVY", "species_code"))

biomass_cpue <- cpue_biomass_total %>% 
  # dplyr::filter(group == spp_common) %>% 
  dplyr::select("year", "print_name", #"species_name1", 
                "SRVY", #"mean_CPUE_all_strata_times_area"
                "weighted_CPUE", "biomass_mt") %>% 
  dplyr::rename(biomass = biomass_mt, 
                cpue_kgha = weighted_CPUE)#, 
                # species_name = species_name1)


length_maxyr0 <- length_data %>% #dplyr::left_join(
  ungroup() %>% 
  # x = length_maxyr, 
  # y = length_type, 
  # by = c("length_type" = "length_type_id")) %>% 
  dplyr::filter(species_code %in% spp_code) %>% 
  dplyr::select(SRVY, species_code, frequency, sex, length,
                # sample_type, 
                length_type, name, 
                sentancefrag)

```


```{r ebs}
temp <- ""
temp1 <- ""
if (refcontent) {
temp<-species_content(
  SURVEY000 = "eastern Bering Sea", 
  SRVY000 = "EBS", 
  haul0 = haul0,
  biomass_cpue = biomass_cpue, 
  length_maxyr0 = length_maxyr0,
  spp_print = spp_print, 
  spp_code = spp_code,
  maxyr = maxyr, 
  compareyr = compareyr, 
  biomass_cpue_tab_name = "tab_majortaxa_pchange_EBS")

temp1<-temp$table_spp
temp <- temp$text_spp
}
```

`r ifelse(refcontent, "**Southeastern Bering Sea (EBS)**", "")`

`r temp1`

`r temp`


```{r nbs}
temp <- ""
temp1 <- ""
if (refcontent) {
if (SRVY %in% "NEBS") {
temp<-species_content(
  SURVEY000 = "northern Bering Sea", 
  SRVY000 = "NBS", 
  haul0 = haul0,
  biomass_cpue = biomass_cpue, 
  length_maxyr0 = length_maxyr0,
  spp_print = spp_print, 
  spp_code = spp_code,
  maxyr = maxyr, 
  compareyr = compareyr, 
  biomass_cpue_tab_name = "tab_majortaxa_pchange_NBS")
temp1 <- temp$table_spp
temp <- temp$text_spp
}
}
```

`r ifelse(refcontent, ifelse(SRVY %in% "NEBS", "**Northeastern Bering SEa (NBS)**", ""), "")`

`r temp1`

`r temp`


```{r nebs}
temp <- ""
temp1 <- ""
if (refcontent) {
temp<-species_content(
  SURVEY000 = "eastern and northern Bering Sea",
  SRVY000 = c("NBS", "EBS"),
  haul0 = haul0,
  biomass_cpue = biomass_cpue, 
  length_maxyr0 = length_maxyr0,
  spp_print = spp_print, 
  spp_code = spp_code,
  maxyr = maxyr, 
  compareyr = compareyr, 
  biomass_cpue_tab_name = c("tab_majortaxa_pchange_EBS", 
                            "tab_majortaxa_pchange_NBS"))
temp1<-temp$table_spp
temp <- temp$text_spp
}

```

`r ifelse(refcontent, ifelse(SRVY %in% "NEBS", "**Northern and Southern Eastern Bering Sea Combined (NEBS)**", ""), "")`

`r temp1`

`r temp `

```{r insert_text}
insert<-""
if (text_spp) {
  insert <- readtext2(file = paste0(dir_out_rawdata, "/",spp_file,".docx"), 
                    refcontent = refcontent)
}
```

`r insert `

`r ifelse(spp_plot_sizecomp, list_figures[names(list_figures) == paste0("fig_sizecomp_", spp_file)][[1]]$res, "") `

`r ifelse(spp_plot_idw, list_figures[paste0("fig_idw_", spp_file)][[1]]$res, "") `

`r list_figures[paste0("fig_idw_bottemp_", spp_file, "_above")]$res `

`r list_figures[paste0("fig_idw_bottemp_", spp_file, "_below")]$res `

`r list_tables[paste0("tab_cpue_biomass_", spp_file)]$res `


