
```{r res_spp_vars_{{jj}} }
a <- report_spp1[report_spp1$file_name == unique(report_spp1$file_name)[{{jj}}], ]

spp_sci <- a$species_name[1]
spp_sci1 <- a$species_name1[1]
spp_code <- a$species_code # eval(expr = parse(text = a$species_code[1]))
spp_print <- a$print_name[1]
spp_file <- a$file_name[1]
spp_taxon <- a$taxon[1]

# report_title == "community"
spp_plot_sizecomp <- ifelse(is.na(a$plot_sizecomp[1]), FALSE, a$plot_sizecomp[1])
spp_plot_idw <- ifelse(is.na(a$plot_idw[1]), FALSE, a$plot_idw[1])
spp_plot_pa <- FALSE
spp_table_cpue <- FALSE
spp_text <- TRUE

if (report_title == "data") {
spp_plot_pa <- ifelse(is.na(a$plot_pa[1]), FALSE, a$plot_pa[1])
spp_table_cpue <- ifelse(is.na(a$table_cpue[1]), FALSE, a$table_cpue[1])
spp_text <- ifelse(is.na(a$text_spp[1]), FALSE, a$text_spp[1])
}

land_start <- ifelse(spp_table_cpue & report_title == "data", "<!---BLOCK_LANDSCAPE_START--->", "")
land_end <- ifelse(spp_table_cpue & report_title == "data", "<!---BLOCK_LANDSCAPE_STOP--->", "")

```


```{r res_spp_lang_{{jj}} }
# Native Languages Names
lang <- ""

if (report_title == "community") {

temp <- readr::read_csv(file = paste0(dir_out_rawdata, "/0_species_local_names.csv"))

lang <- data.frame(lang_long = as.character(names(temp)[grepl(pattern = "lang_", x = temp[1,])]), 
                   lang = as.character(temp[1,grepl(pattern = "lang_", x = temp[1,])]), 
                   name = as.character(t(report_spp[jj,] %>% dplyr::select( dplyr::starts_with("lang_")) )) )

lang <- rbind.data.frame(data.frame(name = c(ifelse(is.na(a$scientific_name_prev[a$print_name == spp_print][1]), NA, 
                                                    paste0("*", a$scientific_name_prev[a$print_name == spp_print][1], "*")), 
                                             ifelse(is.na(a$common_name_prev[a$print_name == spp_print][1]), NA, 
                                                    a$common_name_prev[a$print_name == spp_print][1])), 
                                    lang = c("scientific_name_prev", "common_name_prev"), 
                                    lang_long = c("Previous Scientific Name", "Other Common Names")), 
                         lang) %>%
  dplyr::filter(!is.na(name))

if (nrow(lang)>0) {
  lang  <- paste(paste0("**",lang$lang_long,"**: ",lang$name,"\n\n"), sep = "", collapse = "")
} else {
  lang <- ""
}
}
```

## `r stringr::str_to_title(spp_print)` `r ifelse(is.na(spp_sci), "", paste0("(",spp_sci,")")) `

`r lang `

```{r res_spp_data_wrangle_{{jj}} }
# find basic info about species
haul0 <- catch_haul_cruises %>% 
    dplyr::select("stationid", "stratum", "start_latitude", "start_longitude", 
                  "bottom_depth", "gear_temperature" ,"surface_temperature", 
                  "survey_name", "SRVY", "year", "species_code", 
                  "weight", "number_fish", "hauljoin")

biomass_cpue <- biomass %>% 
  dplyr::filter(year %in% c(maxyr, compareyr) & 
                  species_code %in% spp_code[1] &
                  stratum %in% 999) %>%
  dplyr::select(SRVY, year, biomass, population, meanwgtcpue, meannumcpue) %>% 
  dplyr::mutate(print_name = spp_print) %>% 
  dplyr::rename(cpue_kgha = meanwgtcpue, 
                cpue_noha = meannumcpue)

# biomass_cpue <- cpue_biomass_total %>%
#   dplyr::select("year", "print_name", "SRVY", "weighted_CPUE", "biomass_mt") %>%
#   dplyr::rename(biomass = biomass_mt,
#                 cpue_kgha = weighted_CPUE)

# biomass_cpue <- biomass %>% 
#   dplyr::filter(species_code == spp_code[1]) %>%
#   dplyr::select(year, SRVY, varmnwgtcpue, biomass) %>% 
#   dplyr::rename(biomass = biomass, 
#                 cpue_kgha = varmnwgtcpue) %>% 
#   dplyr::mutate(print_name = spp_print)

length_maxyr0 <- length_data %>% 
  ungroup() %>% 
  dplyr::filter(species_code %in% spp_code) %>% 
  dplyr::select(SRVY, species_code, frequency, sex, length,
                length_type, name, sentancefrag)

```





```{r res_spp_ebs_{{jj}}, results='asis'}
tab0 <- str0 <- ""
show <- refcontent & spp_text & (nrow(biomass_cpue[(biomass_cpue$SRVY == "EBS" & biomass_cpue$print_name == spp_print),])>0)
if (show) {
  if (report_title == "community") {
    tab_majorspp_bio = c("tab_majortaxa_pchange")
  } else if (report_title == "data") {
    tab_majorspp_bio = "\\@ref(tab:tab_majortaxa_pchange_EBS)"
  }
  
temp <- species_content(
  SURVEY000 = "eastern Bering Sea", 
  SRVY000 = "EBS", 
  haul0 = haul0,
  biomass_cpue = biomass_cpue, 
  length_maxyr0 = length_maxyr0,
  spp_print = spp_print, 
  spp_code = spp_code,
  maxyr = maxyr, 
  compareyr = compareyr, 
  tab_majorspp_bio = tab_majorspp_bio, 
  total_biomass = total_biomass, 
  spp_info = spp_info)

tab0 <- temp$table_spp
str0 <- (temp$text_spp)
names(str0) <-  NULL
str0 <- (paste0(unlist(str0), collapse = "\n\n"))
}
# `r tab0`
```
`r ifelse(show, "*REFERENCE MATERIAL FOR WRITERS - START*", "")`

`r ifelse(show, "**Eastern Bering Sea (EBS)**", "")`

`r str0`

```{r res_spp_nbs_{{jj}} }
tab0 <- str0 <- ""
show <- refcontent & spp_text & (nrow(biomass_cpue[(biomass_cpue$SRVY == "NBS" & biomass_cpue$print_name == spp_print),])>0)
if (show) {
    if (report_title == "community") {
    tab_majorspp_bio = c("tab_majortaxa_pchange")
  } else if (report_title == "data") {
    tab_majorspp_bio = "\\@ref(tab:tab_majortaxa_pchange_NBS)"
  }
temp <- species_content(
  SURVEY000 = "northern Bering Sea", 
  SRVY000 = "NBS", 
  haul0 = haul0,
  biomass_cpue = biomass_cpue, 
  length_maxyr0 = length_maxyr0,
  spp_print = spp_print, 
  spp_code = spp_code,
  maxyr = maxyr, 
  compareyr = compareyr, 
  tab_majorspp_bio = tab_majorspp_bio, 
  total_biomass = total_biomass, 
  spp_info = spp_info)

tab0 <- temp$table_spp
str0 <- (temp$text_spp)
names(str0) <-  NULL
str0 <- (paste0(unlist(str0), collapse = "\n\n"))
}
# `r tab0`
```

`r ifelse(show, ifelse(SRVY %in% "NEBS", "**Northern Bering Sea (NBS)**", ""), "")`

`r str0`

```{r res_spp_nebs_{{jj}} }
tab0 <- str0 <- ""
show <- refcontent & spp_text & 
  (nrow(biomass_cpue[(biomass_cpue$SRVY == "EBS" & biomass_cpue$print_name == spp_print),])>0 &
     nrow(biomass_cpue[(biomass_cpue$SRVY == "NBS" & biomass_cpue$print_name == spp_print),])>0)
if (show) {
  if (report_title == "community") {
    tab_majorspp_bio = c("tab_majortaxa_pchange")
  } else if (report_title == "data") {
    tab_majorspp_bio = "\\@ref(tab:tab_majortaxa_pchange_EBS) and \\@ref(tab:tab_majortaxa_pchange_NBS)"

  }
temp <- species_content(
  SURVEY000 = "eastern and northern Bering Sea",
  SRVY000 = c("NBS", "EBS"),
  haul0 = haul0,
  biomass_cpue = biomass_cpue, 
  length_maxyr0 = length_maxyr0,
  spp_print = spp_print, 
  spp_code = spp_code,
  maxyr = maxyr, 
  compareyr = compareyr, 
  tab_majorspp_bio = tab_majorspp_bio, 
  total_biomass = total_biomass, 
  spp_info = spp_info)

tab0 <- temp$table_spp
str0 <- (temp$text_spp)
names(str0) <-  NULL
str0 <- (paste0(unlist(str0), collapse = "\n\n"))
}
# `r tab0`
```

`r ifelse(show, ifelse(SRVY %in% "NEBS", "**Northern and Eastern Bering Sea Combined (NEBS)**", ""), "")`

`r str0 `

`r ifelse(refcontent & spp_text, "*REFERENCE MATERIAL FOR WRITERS - END*", "")`

```{r}
# fig_dist <- fig_sizecomp <- tab_wt <- tab_no <- NA

if (spp_plot_idw) {
  fig_dist <- paste0("\\@ref(fig:fig-dist-",spp_taxon,"-", spp_file, ")")
}

if (spp_plot_sizecomp) {
  fig_sizecomp <- paste0("\\@ref(fig:fig-sizecomp-",spp_taxon,"-", spp_file, ")")
} 

if (spp_table_cpue) {
  tab_wt <- paste0("\\@ref(tab:tab-estimates-maxyr-",spp_taxon,"-", spp_file, "-wt)")
  tab_no <- paste0("\\@ref(tab:tab-estimates-maxyr-",spp_taxon,"-", spp_file, "-num)")
}

fig_bt <- "\\@ref(fig:fig-temperature-bt-1) and \\@ref(fig:fig-temperature-bt-2)"
fig_st <- "\\@ref(fig:fig-temperature-st-1) and \\@ref(fig:fig-temperature-st-2)"

  if (report_title == "community") {
    tab_majorspp_bio = c("\\@ref(tab_majortaxa_pchange)")
  } else if (report_title == "data") {
    tab_majorspp_bio = "\\@ref(tab:tab_majortaxa_pchange_EBS) and \\@ref(tab:tab_majortaxa_pchange_NBS)"
  }

```

```{r spp_text-{{jj}}, child=paste0(dir_out_rawdata, spp_file,".Rmd"), eval=spp_text, results='asis'}
```

```{r fig-dist-{{jj}}}
nickname <- paste0("fig-dist-",spp_taxon,"-", spp_file)
```

```{r fig-dist-{{jj}}-child, child = paste0(dir_code, "_child_report_figtab.Rmd"), eval=(spp_plot_idw | spp_plot_pa)}
```

```{r fig-sizecomp-{{jj}}}
nickname <- paste0("fig-sizecomp-",spp_taxon,"-", spp_file)
```

```{r fig-sizecomp-{{jj}}-child, child = paste0(dir_code, "_child_report_figtab.Rmd"), eval=spp_plot_sizecomp}
```

`r land_start `

```{r tab-estimates-maxyr-{{jj}}}
nickname <- paste0("tab-estimates-maxyr-",spp_taxon,"-", spp_file)
```

```{r tab-estimates-maxyr-{{jj}}-child, child = paste0(dir_code, "_child_report_figtab.Rmd"), eval=spp_table_cpue}
```

`r land_end `
