---
output:
  officedown::rdocx_document: 
    pandoc_args: ["--metadata-file=header.yaml"]
    reference_docx: styles_reference.docx
    df_print: kable
bibliography: "../cite/bibliography.bib"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, error = FALSE, message = FALSE)
```

```{r}
a <- report_spp1[report_spp1$file_name == unique(report_spp1$file_name)[jj], ]

spp_sci <- a$species_name[1]
spp_sci1 <- a$species_name1[1]
spp_code <- a$species_code # eval(expr = parse(text = a$species_code[1]))
spp_print <- a$print_name[1]
spp_file <- a$file_name[1]

spp_plot_sizecomp <- ifelse(is.na(a$plot_sizecomp[1]), FALSE, a$plot_sizecomp[1])
spp_plot_idw <- ifelse(is.na(a$plot_idw[1]), FALSE, a$plot_idw[1])
spp_plot_idw_coldwarm <- ifelse(is.na(a$plot_idw_coldwarm[1]), FALSE, a$plot_idw_coldwarm[1])
# spp_table_cpue <- ifelse(is.na(a$table_cpue[1]), FALSE, a$table_cpue[1])
text_spp <- ifelse(is.na(a$text_spp[1]), FALSE, a$text_spp[1])

```

### `r stringr::str_to_title(spp_print)` `r ifelse(is.na(spp_sci), "", paste0("(",spp_sci,")")) `

```{r}
# find basic info about species
haul0 <- catch_haul_cruises %>% 
    dplyr::select("stationid", "stratum", "start_latitude", "start_longitude", 
                  "bottom_depth", "gear_temperature" ,"surface_temperature", 
                  "survey_name", "SRVY", "year", "species_code", 
                  "weight", "number_fish", "hauljoin")

# biomass_cpue <- dplyr::full_join(
#   x = cpue %>%
#     dplyr::select("year", "SRVY", "species_code", "cpue_kgha") %>%
#     dplyr::group_by(year, SRVY, species_code) %>%
#     dplyr::summarise(cpue_kgha = sum(cpue_kgha, na.rm = TRUE)),
#   y = biomass %>%
#     dplyr::filter(stratum == 999) %>%
#     dplyr::select("year", "SRVY", "species_code", "common_name",
#                   "biomass"),
#   by = c("year", "SRVY", "species_code"))

biomass_cpue <- cpue_biomass_total %>% 
  # dplyr::filter(group == spp_common) %>% 
  dplyr::select("year", "print_name", #"species_name1", 
                "SRVY", #"mean_CPUE_all_strata_times_area"
                "weighted_CPUE", "biomass_mt") %>% 
  dplyr::rename(biomass = biomass_mt, 
                cpue_kgha = weighted_CPUE)#, 
                # species_name = species_name1)


length_maxyr0 <- length_data %>% #dplyr::left_join(
  ungroup() %>% 
  # x = length_maxyr, 
  # y = length_type, 
  # by = c("length_type" = "length_type_id")) %>% 
  dplyr::filter(species_code %in% spp_code) %>% 
  dplyr::select(SRVY, species_code, frequency, sex, length,
                # sample_type, 
                length_type, name, 
                sentancefrag)

```


```{r ebs}
temp <- ""
temp1 <- ""
if (refcontent) {
temp<-species_content(
  SURVEY000 = "eastern Bering Sea", 
  SRVY000 = "EBS", 
  haul0 = haul0,
  biomass_cpue = biomass_cpue, 
  length_maxyr0 = length_maxyr0,
  spp_print = spp_print, 
  spp_code = spp_code,
  maxyr = maxyr, 
  compareyr = compareyr, 
  biomass_cpue_tab_name = "tab_majortaxa_pchange_EBS")

temp1<-temp$table_spp
temp <- temp$text_spp
}
```

`r ifelse(refcontent, "**Eastern Bering Sea (EBS)**", "")`

`r temp1`

`r temp`


```{r nbs}
temp <- ""
temp1 <- ""
if (refcontent) {
if (SRVY %in% "NEBS") {
temp<-species_content(
  SURVEY000 = "northern Bering Sea", 
  SRVY000 = "NBS", 
  haul0 = haul0,
  biomass_cpue = biomass_cpue, 
  length_maxyr0 = length_maxyr0,
  spp_print = spp_print, 
  spp_code = spp_code,
  maxyr = maxyr, 
  compareyr = compareyr, 
  biomass_cpue_tab_name = "tab_majortaxa_pchange_NBS")
temp1<-temp$table_spp
temp <- temp$text_spp
}
}
```

`r ifelse(refcontent, ifelse(SRVY %in% "NEBS", "**Northeastern Bering Sea (NBS)**", ""), "")`

`r temp1`

`r temp`

```{r nebs}
temp <- ""
temp1 <- ""
if (refcontent) {
if (SRVY %in% "NEBS") {
temp<-species_content(
  SURVEY000 = "eastern and northern Bering Sea",
  SRVY000 = c("NBS", "EBS"),
  haul0 = haul0,
  biomass_cpue = biomass_cpue, 
  length_maxyr0 = length_maxyr0,
  spp_print = spp_print, 
  spp_code = spp_code,
  maxyr = maxyr, 
  compareyr = compareyr, 
  biomass_cpue_tab_name = c("tab_majortaxa_pchange_EBS", 
                            "tab_majortaxa_pchange_NBS"))
temp1<-temp$table_spp
temp <- temp$text_spp
}
}
```

`r ifelse(refcontent, ifelse(SRVY %in% "NEBS", "**Northern and Eastern Bering Sea Combined (NEBS)**", ""), "")`

`r temp1`

`r temp `

```{r insert_text}
insert<-""

  # Species specific
  table_est_both <- NMFSReports::crossref(
    list_obj = list_tables, 
    nickname = paste0("tab_estimates_maxyr_*", spp_file, "*"), 
    sublist = "number", 
    exact = FALSE)
  table_est_wt <- NMFSReports::crossref(
    list_obj = list_tables, 
    nickname = paste0("tab_estimates_maxyr_*", spp_file, "_wt"), 
    sublist = "number", 
    exact = FALSE)
  table_est_num <- NMFSReports::crossref(
    list_obj = list_tables, 
    nickname = paste0("tab_estimates_maxyr_*", spp_file, "_num"), 
    sublist = "number", 
    exact = FALSE)
  
if (text_spp) {
  
  # general coldpool figures
  figure_coldpool_warm_stanza <- NMFSReports::crossref(
    list_obj = list_figures, 
    nickname = paste0("fig_bt_temperature_ebs_above"), 
    sublist = "number")
  figure_coldpool_cold_stanza <- NMFSReports::crossref(
    list_obj = list_figures, 
    nickname = paste0("fig_bt_temperature_ebs_below"), 
    sublist = "number")
  figure_coldpool_both_stanza <- NMFSReports::crossref(
    list_obj = list_figures, 
    nickname = paste0("fig_bt_temperature_*"), 
    sublist = "number", 
    exact = FALSE)
  
  # General biomass table
  table_bio_pchange_ebs <- NMFSReports::crossref(
    list_obj = list_tables, 
    nickname = paste0("tab_majortaxa_pchange_EBS"), 
    sublist = "number")
  table_bio_ebs <- NMFSReports::crossref(
    list_obj = list_tables, 
    nickname = paste0("tab_biomass_est_fish_EBS"), 
    sublist = "number")
  table_bio_nbs <- table_bio_pchange_nbs <- ""
  if (SRVY == "NEBS"){
  table_bio_nbs <- NMFSReports::crossref(
    list_obj = list_tables, 
    nickname = paste0("tab_biomass_est_fish_NBS"), 
    sublist = "number")
  table_bio_pchange_nbs <- NMFSReports::crossref(
    list_obj = list_tables, 
    nickname = paste0("tab_majortaxa_pchange_NBS"), 
    sublist = "number")
  }
  

  
  if (spp_plot_sizecomp) {
    figure_sizecomp <- NMFSReports::crossref(
      list_obj = list_figures, 
      nickname = paste0("fig_sizecomp_fish_", spp_file), 
      sublist = "number")
    } 
  
  if (spp_plot_idw) {
    figure_idw <- NMFSReports::crossref(
      list_obj = list_figures, 
      nickname = paste0("fig_idw_cpue_fish_", spp_file), 
      sublist = "number")    
  }
 
  if (spp_plot_idw_coldwarm) {
      figure_idw_both_stanza <- NMFSReports::crossref(
        list_obj = list_figures, 
        nickname = paste0("fig_idw_cpue_fish_", spp_file, "_*"), 
        sublist = "number", 
        exact = FALSE)
      figure_idw_warm_stanza <- NMFSReports::crossref(
        list_obj = list_figures, 
        nickname = paste0("fig_idw_cpue_fish_", spp_file, "_above"), 
        sublist = "number")
      figure_idw_cold_stanza <- NMFSReports::crossref(
        list_obj = list_figures, 
        nickname = paste0("fig_idw_cpue_fish_", spp_file, "_below"), 
        sublist = "number")
  }

  insert <- readtext2(file = paste0(dir_out_rawdata, "/",spp_file,".docx"), 
                    refcontent = refcontent)
}
  
  
  
land_start <- ifelse(table_est_both != "[](#)", "<!---BLOCK_LANDSCAPE_START--->", "")
land_end <- ifelse(table_est_both != "[](#)", "<!---BLOCK_LANDSCAPE_STOP--->", "")

```

`r insert `

<div id="refs"></div>

`r NMFSReports::crossref(list_obj = list_figures, nickname = paste0("fig_idw_cpue_*_", spp_file, "*"), sublist = "res", exact = FALSE)`

`r NMFSReports::crossref(list_obj = list_figures, nickname = paste0("fig_sizecomp_*_", spp_file), sublist = "res", exact = FALSE)`

`r land_start `

`r NMFSReports::crossref(list_obj = list_tables, nickname = paste0("tab_estimates_maxyr_*_", spp_file, "*"), sublist = "res", exact = FALSE)`

`r land_end `
