
\pagebreak

`r ifelse((report_title == "community"), "## Science Author Profiles", "") `

```{r sci-profile, eval = (report_title == "community")}
#| tbl-cap: "NOAA report writing science team members. "

nickname <- "tab-sci-profile"

table_raw <- readr::read_csv(file = paste0(dir_out_rawdata, "/0-survey-team-bios.csv"), 
                             show_col_types = FALSE)|> 
  dplyr::mutate(img = here::here("img", image)) |> 
  dplyr::mutate(order = gsub(pattern = ".jpg", replacement = "", x = gsub(pattern = "bio-", replacement = "", x = image))) |>
  dplyr::arrange(order) |> 
  dplyr::select(-order)

table_print <- table_raw|> 
  flextable::flextable(
    col_keys = c("img", "dummy"))|>
  flextable::compose(j = "dummy", part = "body",
                     value = as_paragraph(
                       as_chunk(paste0(name, "\n"),
                                props = fp_text_default(bold = TRUE, font.size = 12)), 
                       # as_chunk(paste0(title, "\n"),
                       #          props = fp_text_default(italic = TRUE, bold = TRUE, font.size = 10)), 
                       as_chunk(bio,
                                props = fp_text_default(font.size = 10))))|>  
  flextable::colformat_image(j = "img" , 
                             width = 2, 
                             height = 2)|> 
  flextable::width(width = c(2, full_page_portrait_width-2))|>
  flextable::delete_part(part = "header")|> 
  flextable::border_remove()

table_print
```

\pagebreak

## Data Sources{#data-sources}

The Groundfish Assessment Program’s Bering Sea team and the Shellfish Assessment Program conduct the Bering Sea surveys each summer. Haul-level data are expanded to CPUE, population abundance, size-class abundance, and biomass estimates. These results are presented in this document, produced using R and R Markdown. For earlier survey results, see AFSC technical memoranda on the NOAA repository^[https://repository.library.noaa.gov/], the AFSC website^[https://www.fisheries.noaa.gov/resource/publication-database/alaska-fisheries-science-center-technical-memorandums], and the Groundfish Assessment Program website^[https://www.fisheries.noaa.gov/alaska/science-data/groundfish-assessment-program-bottom-trawl-surveys].

Several tools used in this report were developed through the AFSC Groundfish Assessment Program. The *akgfmaps* package^[https://github.com/afsc-gap-products/akgfmaps] (v`r packageVersion("akgfmaps")`) generated distribution maps. The *coldpool* package^[https://github.com/afsc-gap-products/coldpool] (v`r packageVersion("coldpool")`) describes temperature patterns and the cold pool. The *gapindex* package^[https://github.com/afsc-gap-products/gapindex] (v`r packageVersion("gapindex")`) calculates design-based indices.

Catch, environmental, and location data are available through FOSS^[https://www.fisheries.noaa.gov/foss], while biomass and composition estimates are provided through AKFIN^[https://www.psmfc.org/program/alaska-fisheries-information-network-akfin]. NOAA survey data also support DisMAP^[https://apps-st.fisheries.noaa.gov/dismap], and additional information is available through ACEPO^[https://shinyfin.psmfc.org/acepo/] and the Human Dimensions Explorer^[https://reports.psmfc.org/akfin].

`r ifelse(report_title == "community", "Please note that this document is for informational purposes only and does not necessarily represent the views or official position of the Department of Commerce, the National Oceanic and Atmospheric Administration, or the National Marine Fisheries Service. Do not cite this document without permission from the authors.", "")`

\pagebreak

## Acknowledgments{#acknowledgments}

Recognition and appreciation are extended to the captains and crews of the `r text_list(paste0(vessels$vessel_ital[vessels$vess_shape != "X"], " of ", vessels$company[vessels$vess_shape != "X"]))`. By providing the vessels and maintaining safe operations throughout, they contribute essential expertise and goodwill that support every phase of the work. Their professionalism, dedication, and commitment to safety make this survey possible. We also extend sincere thanks to the scientists, researchers,`r ifelse(maxyr == 2025, " and", "")` contractors`r ifelse(maxyr == 2025, "", paste0(", interns, and volunteers"))` whose efforts aboard each vessel ensured the survey was completed safely and successfully. Support from other AFSC groups—including the net shed, research survey support team, data management group, and administrative staff—was vital to planning, execution, and data processing. `r ifelse(report_title == "data", paste0("Finally, appreciation is extended to ", readLines(con = paste0(dir_out_rawdata, "/0-acknowledgments-authors.Rmd")), "for reviewing this document. ", collapse = ""), "")`

We also thank the many Bering Sea communities whose knowledge, experience, and feedback help guide and strengthen this document, highlighting locally important issues and species. This document was prepared in the greater Seattle area, on the traditional lands of the Coast Salish peoples, including the Duwamish. This research was conducted on the traditional homelands of the Inupiat, Yupiit, Siberian Yupiit, Unangax, Alutiiq/Sugpiaq, Eyak, Dena’ina Athabascan, Tlingit, Haida, and Tsimshian peoples. We honor their stewardship and deep connections to these lands and waters.

```{r end-orcid}
# <!-- ## ORCID -->

# insert <- readxl::read_xlsx(path = paste0(dir_out_rawdata, "/0_orcid.xlsx"))|> 
#   flextable::flextable(data = .)|>
#   NMFSReports::theme_flextable_nmfstm(x = ., row_lines = FALSE, font = font0)

# `r insert `
# <!-- \pagebreak -->
```

\pagebreak

`r ifelse((report_title == "community"), "## Survey on Social Media", "") `

```{r social-media-insert-text, child=paste0(dir_out_rawdata, "/0-social-media.Rmd"), eval = (report_title == "community")}
```

\pagebreak

`r ifelse((report_title == "community"), "## Glossary of Terms", "") `

```{r tab-glossary, eval = (report_title == "community")}
nickname <- "tab-glossary"
```

```{r tab-glossary-child, child = paste0(dir_code, "_child_report_figtab.Rmd"), eval = (report_title == "community")}
```

## Citations{#citations}

<div id="refs"></div>
