---
output:
  word_document:
    pandoc_args: ["--metadata-file=header.yaml"]
    reference_docx: styles_reference.docx
    df_print: kable
csl: "../cite/citestyle.csl"
bibliography: "../cite/bibliography.bib"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, error = FALSE, message = FALSE, comment = FALSE)
```

### `r spp_common` (*`r spp_sci`*)

```{r}
# find basic info about species
dat_maxyr_spp<-dat_maxyr[dat_maxyr$species_code %in% spp_code,]

dat_maxyr_1_spp <- dat_maxyr_1[dat_maxyr_1$species_code %in% spp_code,]

dat_maxyr_spp_length <- dat_length_maxyr %>% 
  dplyr::filter(species_code %in% spp_code)

```



```{r}
cnt_chapt_content<-auto_counter(cnt_chapt_content)
cnt_figures<-cnt_figures+1
```

`r  ifelse(SRVY %in% "NEBS", "## **NEBS**", "") `


```{r T1c, fig.cap=ifelse(indesign_flowin %in% TRUE, "", table_list[[length(table_list)]]$caption)}

if (indesign_flowin %in% FALSE) {

      
  table_list<-species_table(table_list, dat_maxyr_spp, spp_common, SURVEY, SRVY = SRVY) 
  basiccontenttable_print <- table_list[[length(table_list)]]$print
  table_list[[length(table_list)]]$print  %>%
          format_cells(rows = 0, # make column names
                       cols = 1:ncol(table_list[[length(table_list)]]$print), # for all columns
                       fonttype = "bold") %>% # bold
          knitr::kable(row.names = FALSE, booktabs = TRUE) #print table in text
}
```

`r species_text(dat_maxyr, dat_maxyr_1, basiccontenttable_print, dat_maxyr_spp, dat_maxyr_spp_length, length_type, spp_common, spp_code, SRVY, cnt_figures) `




`r  ifelse(SRVY %in% "NEBS", "## **NBS**", "") `


```{r}
if (indesign_flowin %in% FALSE) {
  if (SRVY %in% "NEBS" && sum(dat_maxyr_spp$SRVY %in% "NBS")>0) {
    
  table_list<-species_table(table_list, 
                            dat_maxyr_spp %>% dplyr::filter(SRVY %in% "NBS"), 
                            spp_common, SURVEY, SRVY = "NBS") 
  basiccontenttable_print_nbs <- table_list[[length(table_list)]]$print
  table_list[[length(table_list)]]$print %>%
          format_cells(rows = 0, # make column names
                       cols = 1:ncol(table_list[[length(table_list)]]$print), # for all columns
                       fonttype = "bold") %>% # bold
          knitr::kable(row.names = FALSE, booktabs = TRUE) #print table in text
  }
}
```  
  
`r ifelse(SRVY %in% "NEBS", species_text(dat_maxyr %>% dplyr::filter(SRVY %in% "NBS"), dat_maxyr_1 %>% dplyr::filter(SRVY %in% "NBS"), basiccontenttable_print_nbs, dat_maxyr_spp %>% dplyr::filter(SRVY %in% "NBS"), dat_maxyr_spp_length %>% dplyr::filter(SRVY %in% "NBS"), length_type, spp_common, spp_code, SRVY = "NBS", cnt_figures), "") `  

`r  ifelse(SRVY %in% "NEBS", "## **EBS**", "") `
  
```{r}
if (indesign_flowin %in% FALSE) {
  if (SRVY %in% "NEBS" && sum(dat_maxyr_spp$SRVY %in% "EBS")>0) {
  # print("NBS")
  table_list<-species_table(table_list, 
                            dat_maxyr_spp %>% dplyr::filter(SRVY %in% "EBS"), 
                            spp_common, SURVEY, SRVY = "EBS") 
    basiccontenttable_print_ebs <- table_list[[length(table_list)]]$print
    table_list[[length(table_list)]]$print  %>%
          format_cells(rows = 0, # make column names
                       cols = 1:ncol(table_list[[length(table_list)]]$print), # for all columns
                       fonttype = "bold") %>% # bold
          knitr::kable(row.names = FALSE, booktabs = TRUE) #print table in text
  }
}
```


`r ifelse(SRVY %in% "NEBS", species_text(dat_maxyr %>% dplyr::filter(SRVY %in% "EBS"), dat_maxyr_1 %>% dplyr::filter(SRVY %in% "EBS"), basiccontenttable_print_ebs, dat_maxyr_spp %>% dplyr::filter(SRVY %in% "EBS"), dat_maxyr_spp_length %>% dplyr::filter(SRVY %in% "EBS"), length_type, spp_common, spp_code, SRVY = "EBS", cnt_figures), "") `


```{r}
# str <- c()
# # if NEBS, then write for NBS and EBS
# if (SRVY %in% "NEBS") {
#   
#   str <- paste0("**NBS**
#                 ", 
#                 species_text(dat_maxyr %>% dplyr::filter(SRVY %in% "NBS"), 
#                       dat_maxyr_1 %>% dplyr::filter(SRVY %in% "NBS"), 
#                       basiccontenttable_print_nbs, 
#                       dat_maxyr_spp %>% dplyr::filter(SRVY %in% "NBS"), 
#                       dat_maxyr_spp_length %>% dplyr::filter(SRVY %in% "NBS"), 
#                       length_type, 
#                       spp_common, 
#                       spp_code, 
#                       SRVY = "NBS",
#                       cnt_figures), 
#          "**EBS**
#          ", 
#          species_text(dat_maxyr %>% dplyr::filter(SRVY %in% "EBS"), 
#                       dat_maxyr_1 %>% dplyr::filter(SRVY %in% "EBS"), 
#                       basiccontenttable_print_ebs, 
#                       dat_maxyr_spp %>% dplyr::filter(SRVY %in% "EBS"), 
#                       dat_maxyr_spp_length %>% dplyr::filter(SRVY %in% "EBS"), 
#                       length_type, 
#                       spp_common, 
#                       spp_code, 
#                       SRVY = "EBS",
#                       cnt_figures)
#          )
#   print(str)
#   
# }



# <!-- <!-- how many stations --> -->
# <!-- <!-- Should I use haul or hauljoin? --> -->
# <!-- Out of the total number of successful hauls (`r length(unique(dat_maxyr$hauljoin))`) `r NMFSReports::tolower2(spp_common)` was found during `r length(unique(dat_maxyr_spp$hauljoin))` (`r formatC(x = (length(unique(dat_maxyr_spp$hauljoin))/length(unique(dat_maxyr$hauljoin)))*100, digits = 1, format = "f") `% of stations). -->
# 
# <!-- During the `r maxyr` survey, `r NMFSReports::tolower2(spp_common)` were present at `r formatC(x = (length(unique(dat_maxyr_spp$hauljoin))/length(unique(dat_maxyr$hauljoin)))*100, digits = 1, format = "f") `% of stations in the `r SRVY` (`r length(unique(dat_maxyr_spp$hauljoin))` of `r length(unique(dat_maxyr$hauljoin))` stations). -->
# 
# 
# <!-- <!-- bottom tempature --> -->
# <!-- `r NMFSReports::tolower2(spp_common, capitalizefirst = TRUE)` were found in bottom temperatures as warm as `r as.numeric(basiccontenttable_print %>% dplyr::filter(Metric == "Surface Temperature") %>% dplyr::select(Max)) `째C and as cold as `r as.numeric(basiccontenttable_print %>% dplyr::filter(Metric == "Surface Temperature") %>% dplyr::select(Min)) `째C (Figure 7). -->
# 
# <!-- <!-- surface temperature --> -->
# <!-- `r NMFSReports::tolower2(spp_common, capitalizefirst = TRUE)` were found in areas where surface temperatures were as warm as `r as.numeric(basiccontenttable_print %>% dplyr::filter(Metric == "Bottom Temperature") %>% dplyr::select(Max)) `째C and as cold as `r as.numeric(basiccontenttable_print %>% dplyr::filter(Metric == "Bottom Temperature") %>% dplyr::select(Min)) `째C (Figure 7). -->
# 
# <!-- <!-- Depth --> -->
# <!-- They were found in waters with depths between `r as.numeric(basiccontenttable_print %>% dplyr::filter(Metric == "Bottom Depth") %>% dplyr::select(Min)) ` m and `r as.numeric(basiccontenttable_print %>% dplyr::filter(Metric == "Bottom Depth") %>% dplyr::select(Max)) ` m.   -->
# 
# 
# <!-- <!-- Sizes caught were between  --> -->
# <!-- The `r NMFSReports::text_list(length_type$sentancefrag[length_type$code %in% unique(dat_maxyr_spp_length$length_type)])` of `r NMFSReports::tolower2(spp_common, capitalizefirst = TRUE)` measured during the survey were between `r min(dat_maxyr_spp_length$length)` and `r max(dat_maxyr_spp_length$length)` `r unique(dplyr::case_when(spp_code %in% 1:31550 ~ "cm", spp_code %in% 68000:69930 ~ "mm"), TRUE ~ "NO MEASUREMENT")`. -->
# 
# 
# <!-- <!-- weight --> -->
# <!-- The total number of `r NMFSReports::tolower2(spp_common)` estimated to have been caught by the survey is `r NMFSReports::xunits(value = sum(dat_maxyr_spp$number_fish, na.rm = TRUE))` individuals, which equates to `r NMFSReports::xunits(value = sum(dat_maxyr_spp$weight, na.rm = TRUE))` kg of biomass.  -->
# 
# <!-- Compared with `r maxyr-1`, abundance experienced `r NMFSReports::pchange(start = sum(dat_maxyr_1_spp$number_fish, na.rm = TRUE), end = sum(dat_maxyr_spp$number_fish, na.rm = TRUE)) ` and there was `r NMFSReports::pchange(start = sum(dat_maxyr_1_spp$weight, na.rm = TRUE), end = sum(dat_maxyr_spp$weight, na.rm = TRUE)) ` in biomass.  -->
```

> questions:

> Should NBS and EBS be different colours and have different legends because they are different surveys?

> Note that figure numbers will change as I produce more of the report


```{r G1a, message = FALSE, comment = FALSE, include = FALSE}
# Edit This:
header <- paste0("CPUE of **", NMFSReports::tolower2(spp_common), "** (*", stringr::str_to_sentence(spp_sci), "*) across the ", SURVEY)
footnote<-c("")

dat_cpue_spp <- dat_cpue %>% 
  filter(species_code %in% spp_code & 
           year %in% maxyr)

# if (length(SRVY1) > 1 && SRVY %in% "NEBS") {
# 
#   dat_cpue_spp_n <- dat_cpue_spp %>%
#     dplyr::filter(survey == "NBS")
# 
#   idwplot <- make_idw_map0(COMMON_NAME = dat_cpue_spp_n$species_name,
#                          LATITUDE = dat_cpue_spp_n$latitude,
#                          LONGITUDE = dat_cpue_spp_n$longitude,
#                          CPUE_KGHA = dat_cpue_spp_n$cpue_kgha,
#                          region = "bs.north",
#                          key.title = spp_common)
# 
#   plot0 <- idwplot$plot +
#     theme(legend.position = "left",
#     panel.background = element_rect(fill = "transparent"), # bg of the panel
#     plot.background = element_rect(fill = "transparent", color = NA), # bg of the plot
#     panel.grid.major = element_blank(), # get rid of major grid
#     panel.grid.minor = element_blank(), # get rid of minor grid
#     legend.background = element_rect(fill = "transparent"), # get rid of legend bg
#     legend.box.background = element_rect(fill = "transparent") # get rid of legend panel bg
#   )
# 
# }

idwplot <- akgfmaps::make_idw_map(COMMON_NAME = dat_cpue_spp$species_name, 
                         LATITUDE = dat_cpue_spp$latitude, 
                         LONGITUDE = dat_cpue_spp$longitude, 
                         CPUE_KGHA = dat_cpue_spp$cpue_kgha, 
                         region = map.area, 
                         key.title = spp_common)
idwplot <- idwplot %>% change_fill_color(new.scheme = "grey", show.plot = FALSE)

plot0 <- idwplot$plot + 
  theme(legend.position = "right") + 
  geom_shadowtext(data = subset(placenames, type %in% c("bathymetry", "islands")),
    aes(x = x, y = y, label = lab), bg.color = "white", color = "black", size = 3, group = 99) + 
  geom_shadowtext(data = subset(placenames, type %in% c("convention line", "peninsula")),
    aes(x = x, y = y, label = lab, angle = 43), bg.color = "white", color = "black", size = 3, group = 99)

if (!(map.area %in% c("nbs", "bs.north"))) {
  plot <- plot + 
      geom_shadowtext(data = subset(placenames, type %in% c("mainland")),
      aes(x = x, y = y, label = lab), bg.color = "white", color = "black", size = 8, group = 99)  
}

plot0

```


```{r G1b}
# Don't Edit This:
# cnt_chapt_content<-auto_counter(cnt_chapt_content)
# cnt_figures<-cnt_figures+1

# Systematically save your plot with this simple function
plot_list<-save_graphs(plot0 = plot0, 
                      plot_list = plot_list, 
                      header = header,
                      footnote = footnote,
                      filename0 = filename0, 
                      cnt_chapt_content = cnt_chapt_content, 
                      cnt = cnt_figures, 
                      path = dir_out_figures, 
                      width = 6, # you can change this if you need to...
                      height = 12) # you can change this if you need to...

```


```{r G1c, fig.cap=ifelse(indesign_flowin %in% TRUE, "", plot_list[[length(plot_list)]]$caption)}
# Print or Don't Print Plot in Text
# You don't want to print this in the document if this text will be flowed into InDesign. 
# However, sometimes its nice to see everything all together, so this variable is 
# something you might like to toggle on and off. 
# Hense, FALSE = print here, TRUE = don't print here, just make the .pdf (coded above)
if (indesign_flowin %in% FALSE) { 
  plot0 # print plot in text
} else if (indesign_flowin %in% TRUE){ # for reports that need to be flowed into InDesign 
  rmarkdown::render(TableFigureHeader, 
                    quiet = TRUE,
                  output_dir = dir_chapters, 
                  output_file = paste0(filename00,cnt_chapt_content,"_Title.docx"))
}
```



```{r, include = FALSE}
filename00 <- paste0(SRVY, "-", maxyr, "-", tolower(spp_common))

out_new<-paste0(dir_out_rawdata, filename00, ".zip")

temp <- tempfile(fileext = ".zip")
dl <- drive_download(file = filename00,
  path = temp, overwrite = TRUE)
1

out <- unzip(temp, exdir = tempdir())

file.rename(from = out,
            to = out_new)

spp_content<-XML::htmlTreeParse(out_new, useInternal = TRUE)

spp_content <- xpathApply(spp_content, "//body//text()[not(ancestor::script)][not(ancestor::style)][not(ancestor::noscript)]", xmlValue)

x <- paste(cat(unlist(spp_content)))

write.table(x = x, 
            file = paste0(dir_out_rawdata, filename00, ".txt"))

```


`r cat(unlist(spp_content)) `

```{r}
# print(cat(unlist(spp_content)))
```


 
