---
output:
  word_document:
    pandoc_args: ["--metadata-file=header.yaml"]
    reference_docx: styles_reference.docx
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, error = FALSE, message = FALSE)

# csl: "../cite/citestyle.csl"
# bibliography: "../cite/bibliography_RPack.bib"
# nocite: '@*'
```

</br>

## Data Sources

```{r}
insert <- readtext2(file = paste0(dir_out_rawdata, "/0_data_sources.docx"), 
                    refcontent = refcontent)
```

`r insert `

## Acknowledgements

```{r}
insert <- readtext2(file = paste0(dir_out_rawdata, "/0_acknowledgements.docx"), 
                    refcontent = refcontent)
```

`r insert `

</br>

## ORCID

```{r}
insert <- readxl::read_xlsx(path = paste0(dir_out_rawdata, "/0_orcid.xlsx")) %>% 
  flextable::flextable(data = .) %>%
  NMFSReports::theme_flextable_nmfstm(x = ., row_lines = FALSE, font = font0)
```

`r insert `

## Recent Technical Memorandums

Copies of this report and other NOAA Technical Memorandums are available from the National Technical Information Service, 5285 Port Royal Road, Springfield, VA 22167 (web site: [www.ntis.gov](www.ntis.gov)). Paper and electronic (.pdf) copies vary in price. The recent Technical Memoranda produced by the Alaska Fisheries Science Center can be found at  [https://www.fisheries.noaa.gov/resource/publication-database/alaska-fisheries-science-center-technical-memorandums](https://www.fisheries.noaa.gov/resource/publication-database/alaska-fisheries-science-center-technical-memorandums). 

</br>


