
# Introduction

```{r intro-text}
# use haul_cruises_maxyr TOLEDO 

temp <- haul_cruises_maxyr|>
  dplyr::filter(srvy == "EBS") #|> 
  # dplyr::mutate(start_mo_long = format(x = as.POSIXlt(x = start_date_haul ), format="%B"))|>
  # dplyr::mutate(end_mo_long = format(x = as.POSIXlt(x = end_date_haul ), format="%B")) #|>
  # dplyr::select(start_mo_long, end_mo_long)

str0_nbs <- ifelse(srvy == "NEBS", 
                      #NBS
                      paste0("In addition, the ", maxyr, 
                             " survey coverage was expanded to include the northern Bering Sea. This is only the ", 
                             numbers2words_th(
                               haul_cruises_maxyr|> 
                                 dplyr::filter(srvy == "NBS")|>
                                 dplyr::select(yrofsurvey )),
                             " time since 2010 that the northern Bering Sea shelf survey was done. The expanded study area covered the entire Bering Sea continental shelf from 20 m (",
                             round(20/divmforft, 1),
                             " ft) to 200 m (",
                             round(200/divmforft, 1),
                             " ft) bottom depth to the U.S.-Russia Maritime Boundary between the Alaska Peninsula and the Bering Strait, including Norton Sound."), 
                             # EBS
                             "The study area covered the eastern Bering Sea continental shelf from 20 to 200 m bottom depth to the U.S.-Russia Maritime Boundary between the Alaska Peninsula and to approximately the latitude of St. Matthew Island (60° 50' N).")


if (sum(haul_cruises_maxyr$stations_avail == haul_cruises_maxyr$stations_completed) == 1) { # diff answers or only 1 srvy
  str0 <- CapFirst(text_list(
    paste0(ifelse(haul_cruises_maxyr$stations_avail ==
                    haul_cruises_maxyr$stations_completed, "all", "most"), 
           " survey stations in the ", 
           haul_cruises_maxyr$srvy, 
           " were sampled successfully")))
} else { # answers both "Most" or "All"
  str0 <- paste0(unique(ifelse(haul_cruises_maxyr$stations_avail ==
                    haul_cruises_maxyr$stations_completed, "All", "Most")), 
           " survey stations in the ",
           text_list(haul_cruises_maxyr$srvy), 
           " were sampled successfully")
} 

nth_yr <- data.frame()
for (i in 1:nrow(haul_cruises_maxyr)){
  srvy_ <- haul_cruises_maxyr$srvy[i]
  nth_yr <- nth_yr|> dplyr::bind_rows(
    data.frame(srvy = srvy_, 
               val = ifelse(haul_cruises_maxyr$yrofsurvey[haul_cruises_maxyr$srvy == srvy_]<=20, 
                            numbers2words_th(haul_cruises_maxyr$yrofsurvey[haul_cruises_maxyr$srvy == srvy_]), 
                                             paste0(haul_cruises_maxyr$yrofsurvey[haul_cruises_maxyr$srvy == srvy_], 
                                                    haul_cruises_maxyr$stndth[haul_cruises_maxyr$srvy == srvy_])) ) )
}

```

In `r maxyr`, NOAA Fisheries’ Alaska Fisheries Science Center conducted two standardized surveys within U.S. territorial waters of the Bering Sea: the eastern Bering Sea Shelf bottom trawl survey (`r nth_yr$val[nth_yr$srvy == "EBS"] ` year) and the northern Bering Sea bottom trawl survey (`r nth_yr$val[nth_yr$srvy == "NBS"] ` year). The northern Bering Sea survey region contains `r haul_cruises_maxyr$stations_avail[haul_cruises_maxyr$srvy == "NBS"] ` stations in an area bounded by the Bering Strait, Norton Sound, and the U.S.–Russia Maritime Boundary (Fig. \@ref(fig:fig-survey-points-nostrata)). The northern Bering Sea region has been same standardized sampling methods as the eastern Bering Sea shelf survey since 2010.

NOAA Fisheries has identified the northern Bering Sea as a region of critical importance for increased scientific monitoring because this marine ecosystem may be rapidly altered by climate change. Together, these surveys represent one part of an extensive research plan to design a long-term time series that identifies and tracks the ecological change throughout the Bering Sea. The scale and extent of fish and crab populations vary from year to year in response to biological and environmental processes. These responses extend beyond the traditional survey boundaries (e.g., eastern Bering Sea) and ultimately require comprehensive coverage of the entire Bering Sea. 

In this document, we provide some of the results of the `r maxyr` Bering Sea surveys and compare these to observations from `r text_list(compareyr)`. The results of the `r text_list(compareyr)` survey`r ifelse(length(compareyr)>1, "s", "")` can be found in the`r ifelse(length(compareyr)>1, "ir respective", "")` data report`r ifelse(length(compareyr)>1, "s", "")` `r paste0("[",ref_compareyr,"; ", ifelse(!is.null(ref_compareyr_ebs), ref_compareyr_ebs, ""),"]")`. Detailed information on bottom trawl survey results for commercial crab species are discussed in the AFSC Shellfish Assessment Program's annual data report `r paste0("[@SAPcrab",maxyr,"]")`. In the future, continued survey efforts in the form of a combined eastern Bering Sea and northern Bering Sea bottom trawl survey will provide more comprehensive monitoring of how fishes, crabs, and other benthic animals respond to ecosystem change on a large spatial scale.

```{r fig-survey-points-nostrata0}
nickname <- "fig-survey-points-nostrata"
```

```{r fig-survey-points-nostrata0-child, child = paste0(dir_code, "_child_report_figtab.Rmd")}
```

