
# Survey Design, Execution, and Analysis

```{r survey-design-intro-text}

str0 <- ""

for (i in 1:length(srvy11)){
  
    # srvy <- srvy11[i]
  cruises_maxyr0  <- haul_cruises_vess_maxyr|> 
    dplyr::filter(srvy %in% srvy1[i] &
                    year %in% maxyr)|> 
    dplyr::select("year", "survey_name", "vessel_id", "vessel_name", 
                  "vessel_ital", "srvy", "srvy_long", 
                  "start_date_cruise", "end_date_cruise", 
                  "start_date_haul", "end_date_haul")|> 
    unique()|> 
    group_by(year, survey_name, vessel_id, vessel_name, 
             vessel_ital, srvy, srvy_long)|> 
    dplyr::summarise(start_date_cruise = as.Date(min(start_date_cruise)), 
                     end_date_cruise = as.Date(max(end_date_cruise)), 
                     start_date_haul = as.Date(min(start_date_haul), 
                                               format = "%m/%d/%Y"), 
                     end_date_haul = as.Date(max(end_date_haul), 
                                             format = "%m/%d/%Y")) 
    str0 <- paste0(str0, 
                   "Sampling for the ", 
                   cruises_maxyr0$srvy_long[1], 
                   # text_list(cruises_maxyr0$vessel_ital), 
                   # ifelse(length(unique(vessels0$vessel)) == 1, 
                   #        "the vessel", "both vessels"), 
                   " survey started on ",
                   format(min(cruises_maxyr0$start_date_haul), format = date_format), 
                   " and ended on ", 
                   format(min(cruises_maxyr0$end_date_haul), format = date_format), ". ")
    }
```

The `r maxyr` `r SURVEY` surveys were conducted aboard the chartered commercial stern-trawlers `r text_list(cruises_maxyr0$vessel_ital)` (Fig. \@ref(fig:fig-vessels)). `r str0 `  

```{r fig-vessels0}
nickname <- "fig-vessels"
```

```{r fig-vessels0-child, child = paste0(dir_code, "_child_report_figtab.Rmd")}
```

The northern Bering Sea survey region is bounded by the Bering Strait, Norton Sound, and the U.S.–Russia Maritime Boundary (Fig. \@ref(fig:fig-survey-points-nostrata)). Designed in 2010 as an extension of the eastern Bering Sea shelf survey, the northern Bering Sea survey uses the same standardized sampling methods and systematic 20 × 20 nautical mile (nmi) grid.

```{r team-desc-insert-text, child=paste0(dir_out_rawdata, "/0-team-desc.Rmd")}
```

Survey vessels use the 83-112 Eastern otter trawl, which has historically been used for the eastern Bering Sea, Chukchi Sea, and Beaufort Sea surveys (Fig. \@ref(fig:fig-trawl-gear-diagram-nolabel)). Each trawl tow was conducted for 30 minutes at a speed of 2.8 - 3.2 knots.

```{r fig-trawl-gear-diagram-nolabel0}
nickname <- "fig-trawl-gear-diagram-nolabel"
```

```{r fig-trawl-gear-diagram-nolabel0-child, child = paste0(dir_code, "_child_report_figtab.Rmd")}
```

Fishes, crabs, and other invertebrates were identified, sorted by species, and weighed. A subsample of fishes were sorted by sex and measured to the nearest centimeter (cm). For the predominant crab species, carapace width (snow crab) or length (king crabs) was measured to the nearest millimeter (mm). Samples of some species of fishes, crabs, and other invertebrates were also retained to gather additional information on size, weight, sex, age, reproductive state, genetics, body condition, and stomach contents.

Trawl survey catch data were used to estimate catch-per-unit-effort (CPUE), biomass, abundance, and size and age composition. CPUE represents the density of a species per unit area. Effort was estimated as the area swept (area sampled in km^2^). Mean CPUE values were calculated for pre-defined subsets of each survey area (known as stratums) that have similar biological and environmental features. Biomass, in kilograms (kg), and abundance, in number of individuals, were estimated for each survey area by multiplying the mean CPUE by the total survey area.

Environmental data, including water temperature in degrees Celsius (°C), depth in meters (m), and underwater light level were also recorded at each sampling station. `r ifelse(maxyr != 2025, "Water column profiles of temperature and salinity at each trawl location were measured using a trawl-mounted conductivity, temperature, and depth profiler (CTD).", "")``r paste0(readLines(con = paste0(dir_out_rawdata, "/0-temperature-gear.Rmd")), collapse = "") ` 

\pagebreak
