
# `r maxyr` Survey Results in Comparisons to `r ifelse(length(compareyr) == 1, compareyr, "Previous Years")`

## Bottom and Surface Temperatures

```{r results-cold-pool_insert, child=paste0(dir_out_rawdata, "/0-cold-pool.Rmd")}
```

```{r fig-temperature-bt}
nickname <- "fig-temperature-bt-data"
```

```{r temperature-bt-child, child = paste0(dir_code, "_child_report_figtab.Rmd")}
```

```{r fig-temperature-st}
nickname <- "fig-temperature-st-data"
```

```{r temperature-st-child, child = paste0(dir_code, "_child_report_figtab.Rmd")}
```

```{r fig-mean-temperature0}
nickname <- "fig-mean-temperature"
```

```{r fig-mean-temperature0-child, child = paste0(dir_code, "_child_report_figtab.Rmd")}
```

```{r fig-cold-pool-area0}
nickname <- "fig-cold-pool-area"
```

```{r fig-cold-pool-area0-child, child = paste0(dir_code, "_child_report_figtab.Rmd")}
```

## Survey Data and Specimen Collections

```{r tab-specimen-samples-howmany}
load(file = paste0(dir_out_figtab, "tab-specimen-samples-EBS.rdata"))
temp <- obj$raw
if (srvy == "NEBS") {
  load(file = paste0(dir_out_figtab, "tab-specimen-samples-NBS.rdata"))
  temp <- temp|> 
    dplyr::bind_rows(obj$raw)
}

temp <- temp |> 
  dplyr::mutate(common_name = common_name0, 
                common_name = ifelse(is.na(common_name), "Total", common_name)) |> 
  dplyr::select(-common_name0)

names(temp) <- gsub(x = names(temp), pattern = "\n", replacement = " ")

temp <- temp |>
  dplyr::filter(common_name == "Total") |> 
  dplyr::select(-common_name)|> 
  dplyr::left_join(cruises_maxyr|> 
                     dplyr::select(srvy, srvy_long)|> 
                     dplyr::distinct()) |> 
  dplyr::mutate(across(where(is.numeric), xunits))

# str00 <- grepl(x = names(temp|> 
#     dplyr::select(-dplyr::starts_with("srvy"))), pattern = " deployed")
# str00 <- ifelse(str00, "deployed ", "")
names(temp) <- gsub(x = names(temp), pattern = "Satellite tags deployed", replacement = "fish for satellite tagging")

str0 <- c()
for (i in 1:nrow(temp)) {
  temp0 <- t(temp[i, ]|> 
               dplyr::select(-dplyr::starts_with("srvy")))
  str0 <- paste0(str0, text_list(paste0(temp0, " ", tolower(rownames(temp0)) )), 
                 " during the ", 
                 ifelse(i == 1, paste0(maxyr, " "), ""), 
                 temp[i, "srvy_long"], " survey", 
                 ifelse(srvy == "NEBS" & i == 1, " and ", ""))
}
```

Survey teams collected `r str0 `. 

## Estimates of Fishes and Invertebrates

```{r biomass-inc-dec-tot}

# million metric tons of biomass collected in each region in each year
temp <- total_biomass|> 
  dplyr::group_by(year, srvy, srvy_long)|> 
  dplyr::summarise(biomass_mmt = round(sum(total, na.rm = TRUE)/1e6, digits = 1))|> 
  dplyr::ungroup()|> 
  dplyr::arrange(desc(year)) |>
  dplyr::right_join(data.frame(srvy = c(names(compareyr), names(compareyr)), 
                               year = c(compareyr, 
                                        rep_len(x = maxyr, length.out = length(compareyr))))) # |> 
# dplyr::filter(year %in% c(maxyr, compareyr))
```

In `r maxyr`, the total benthic animal biomass of the eastern Bering Sea shelf was estimated at `r temp$biomass_mmt[temp$year == maxyr & temp$srvy == "EBS"] ` million metric tons (t) and the northern Bering Sea was estimated at `r temp$biomass_mmt[temp$year == maxyr & temp$srvy == "NBS"] ` million t. Previously, the total benthic animal biomass of the `r text_list(paste0(temp$year[temp$year != maxyr], " ", temp$srvy_long[temp$year != maxyr], " was estimated at ", temp$biomass_mmt[temp$year != maxyr], " million t"))`. 

```{r biomass-inc-dec-spp}

load(file = paste0(dir_out_figtab, "tab-majortaxa-pchange-NBS.rdata"))
temp_nbs <- obj$raw

load(file = paste0(dir_out_figtab, "tab-majortaxa-pchange-EBS.rdata"))
temp_ebs <- obj$raw

temp1 <- dplyr::bind_rows(temp_ebs, temp_nbs) |>
  # dplyr::filter(srvy == "NBS")|>
  dplyr::select(print_name = print_name1, change, change0, maxyr, taxon, srvy) |>
  # I defined "no marked change" in < 25 and > -25% change to get me through the code. What number should it be?
  dplyr::mutate(
    change_case = dplyr::case_when(
      change0 < -25 ~ "decreased",
      change0 > 25 ~ "increased",
      TRUE ~ "" ),
    change_case_pre = dplyr::case_when(
      change0 < -25 ~ "",
      change0 > 25 ~ "",
      TRUE ~ "there was no notable change in " ),
    change_case1 = dplyr::case_when(
      change0 < -25 ~ "decreases",
      change0 > 25 ~ "increases",
      TRUE ~ NA
    )) |>
  dplyr::arrange(desc(change0))

temp44 <- temp1 |> 
  dplyr::group_by(taxon, change_case, change_case_pre, srvy)|>
  dplyr::summarise(n = n())|>
  dplyr::ungroup()|>
  tidyr::pivot_wider(id_cols = c(change_case, change_case_pre, srvy), 
                     names_from = taxon, values_from = n)|>
  dplyr::mutate(
    str0_fish = ifelse(is.na(fish), "", paste0(xunits(fish), " fish")), # , ifelse(fish>1, "es", "")
    str0_invert = ifelse(is.na(invert), "", paste0(xunits(invert), " invertebrate")), # ifelse(invert>1, "s", ""))),
    str0 = paste0(str0_fish, ifelse(str0_invert == "", "", " and "), str0_invert)) |> 
  dplyr::arrange(desc(change_case))

temp3 <- temp1 |>
  dplyr::arrange(desc(change0))|>
  dplyr::filter(#taxon == "fish"  &
    # !grepl(x = print_name, pattern = "other ") &
    !is.na(change_case1))

temp33 <- dplyr::bind_rows(
  head(temp3[which(temp3$srvy == "EBS"),]), 
  tail(temp3[which(temp3$srvy == "EBS"),]), 
  head(temp3[which(temp3$srvy == "NBS"),]), 
  tail(temp3[which(temp3$srvy == "NBS"),]))|>
  dplyr::arrange(desc(abs(change0)))|> 
  dplyr::group_by(change_case1, srvy)|>
  dplyr::summarise(spp_list = text_list(paste0(print_name, " (", change, ")")))|>
  dplyr::ungroup()|>
  dplyr::arrange(change_case1)

str0 <- ""

for (i in 1:length(srvy1)) {
  
  temp3 <- temp33|> dplyr::filter(srvy == srvy1[i])
  temp4 <- temp44|> dplyr::filter(srvy == srvy1[i])
  
  str0 <- paste0(str0, 
                 paste0(
                   "In the ", srvy11[i]," between ", compareyr[names(compareyr) == srvy1[i]], " and ", maxyr , ", ",
                   text_list(paste0(temp4$change_case_pre, "the biomass of ", temp4$str0, " species ", temp4$change_case)),
                   ifelse(i == 1, " (± 25% change from the previous survey year). ", ". "),
                   # paste0("Prominent organisms that exhibited the largest ", 
                   #        temp3$change_case1, " in biomass included ", temp3$spp_list, 
                   #        collapse = ifelse(i == 1, " (Table \\@ref(tab:tab-majortaxa-pchange-NBS)). ", ". ")),  
                   collapse = ". " )#,  ifelse(i == 1, ".\n\n", ". ") 
  )
}

str0 <- gsub(pattern = ") (", replacement = "; ", x = str0, fixed = TRUE)
str0 <- gsub(pattern = ". . ", replacement = ". ", x = str0, fixed = TRUE)
str0 <- gsub(pattern = "  ", replacement = " ", x = str0, fixed = TRUE)
str0 <- gsub(pattern = " .", replacement = ".", x = str0, fixed = TRUE)

```

`r str0`The biomasses of predominant species are listed in Table \@ref(tab:tab-majortaxa-pchange-NBS) in order of largest increase to largest decrease. 

```{r ebs-vs-nbs}
temp5 <- biomass |> 
  dplyr::filter(stratum == 999 & 
                  species_code %in% report_spp1$species_code[(report_spp1$plot_idw)] & 
                  year == maxyr) |> 
  dplyr::select(srvy, biomass_mt, species_code, common_name) |> 
  # dplyr::left_join(report_spp1 |>
  #                    dplyr::select(print_name, species_code, order) |>
  #                    dplyr::distinct()) |>
  # dplyr::arrange(desc(NBS)) 
  # dplyr::arrange(desc(order))|> 
  dplyr::group_by(common_name, srvy) |> 
  # dplyr::summarise(biomass_mt = sum(biomass_mt, na.rm = TRUE))|> 
  tidyr::pivot_wider(names_from = srvy, values_from = biomass_mt)|> 
  dplyr::ungroup()|> 
  dplyr::mutate(NBS_greater = (NBS > EBS), 
                NBS_only = (NBS > 0 & is.na(EBS))) |> 
  dplyr::filter(NBS_greater) |> 
  dplyr::mutate(common_name = sub(" \\s*\\([^)]+\\)", "", x = common_name))

```

Survey catches in the northern Bering Sea were generally smaller than in the eastern Bering Sea shelf. While many species were distributed throughout both survey regions, several key species were more abundant in the northern Bering Sea than in the eastern Bering Sea shelf, including `r text_list(temp5$common_name)`.

```{r biomass-inc-dec}

load(file = paste0(dir_out_figtab, "tab-majortaxa-pchange-NBS.rdata"))
temp_nbs <- obj$raw

load(file = paste0(dir_out_figtab, "tab-majortaxa-pchange-EBS.rdata"))
temp_ebs <- obj$raw

temp1 <- dplyr::bind_rows(temp_ebs, temp_nbs) |>
  dplyr::select(-print_name, print_name = print_name1) 

# calculate top 50% of haul
temp0 <- temp3 <- data.frame()
str0 <- str00 <- c()

for (ii in 1:length(srvy1)) {
  
yrs <- c(maxyr, compareyr[names(compareyr) == srvy1[ii]])

for (i in 1:length(yrs)) {
  
  yr <- as.numeric(sort(yrs, decreasing = TRUE)[i])

# total biomass
  temp <- sum(total_biomass$total[total_biomass$year == yr & total_biomass$srvy == srvy1[ii]])
  
  temp5 <- temp1 |> 
    dplyr::filter(srvy == srvy1[ii])|> 
    dplyr::rename("x" = all_of(as.character(yr)))|> 
    dplyr::arrange(desc(x))|> 
    dplyr::select(print_name, x, taxon)|> # species_name, 
    dplyr::mutate(prop = x/temp)|> 
    dplyr::mutate(cumsum = cumsum(prop)) |> 
    dplyr::mutate(year = yr)
  
  # Top 50% spp
  temp4 <- temp5|> 
    dplyr::filter(dplyr::between(x = cumsum, left = 0, right = .55))
  
  temp3 <- rbind.data.frame(temp3, temp5)
  
  if (yr == maxyr) {
    str0 <- paste0(str0, 
                   paste0("In ", yr, ", the largest contributors of biomass in the ",srvy11[ii]," were ", 
                          text_list(paste0(temp4$print_name, " (", 
                                           round(temp4$prop*100, digits = 0), "%)")), ". "))
  } else if (i==2) {
    str0 <- paste0(str0, 
                   paste0("Previously in ", yr, ", the largest contributors of biomass were ", 
                          text_list(
                            paste0(temp4$print_name, " (", round(temp4$prop*100, digits = 0), "%)")), ". "))
  } else {
    str0 <- paste0(str0, 
                   paste0(ifelse(i==length(nbsyr), "; and in ", "; in "), yr, ", ", 
                          text_list(
                            paste0(temp4$print_name, " (", round(temp4$prop*100, digits = 0), "%)")), ". "))
    
  }
  
  # Other cods: saffron cod and Arctic cod
  temp0 <- rbind.data.frame(temp0, 
                            temp5|> 
                              dplyr::filter(print_name %in% c("saffron cod","Arctic cod")) )
}
}

temp0 <- temp0 |> 
  dplyr::filter(year %in% c(maxyr, compareyr[names(compareyr) == "NBS"]))|>
  dplyr::group_by(year)|> 
  dplyr::summarise(prop = sum(prop, na.rm = TRUE))|> 
  dplyr::arrange(desc(year))|> 
  dplyr::mutate("perc" = paste0(round(x = prop*100, digits = 1), "%"))

temp3 <- temp3 |> 
  # dplyr::mutate(case = dplyr::case_when(
  #   prop*100>0 ~ "increasing", 
  #   TRUE ~ "decreasing"))|> 
  dplyr::filter(year %in% c(maxyr, compareyr))|>
  dplyr::select(taxon, year, x,)|>
  dplyr::group_by(taxon, year)|> 
  dplyr::summarise(biomass_mt = sum(x, na.rm = TRUE))|> 
  tidyr::pivot_wider(names_from = taxon, values_from = biomass_mt, id_cols = year)|> 
  dplyr::mutate(total = (fish + invert), 
                invert_perc = invert/total, 
                invert_perc = formatC(x = invert_perc*100, digits = 0, big.mark = ",", format = "f"))|> 
  dplyr::arrange(desc(year))

```

`r str0` Saffron cod and Arctic cod accounted for `r text_list(paste0(temp0$perc, " of the total biomass in ", temp0$year)) `. Invertebrates (i.e., shrimps, sea squirts, sea stars, jellyfish, crabs, and urchins) made up `r text_list(paste0(temp3$invert_perc, "% of the biomass in ", temp3$year))`. 

\pagebreak

```{r tab-majortaxa-pchange-NBS0}
nickname <- "tab-majortaxa-pchange-NBS"
```

```{r tab-majortaxa-pchange-NBS0-child, child = paste0(dir_code, "_child_report_figtab.Rmd")}
```

\pagebreak

# Summary Results for Select Major Taxa

Survey results for select taxa are summarized below, with CPUE (kg/km^2^) distribution maps, and plots of the population estimates by sex and size. Maps of species distributions include both the `r SURVEY` survey region`r plural_surveys` to better illustrate patterns and trends in fish distribution and movement. For comparison among years, distribution maps and abundance-at-size plots show survey data from the `r text_list(sort(c(compareyr, maxyr))) ` surveys.

**You can help us with this document by providing names in local language(s) and cultural or traditional uses for each fish and invertebrate species reviewed in this report by reaching out to [nmfs.afsc.gap.metadata@noaa.gov](nmfs.afsc.gap.metadata@noaa.gov).**


