
# `r maxyr` Survey Results in Comparisons to `r ifelse(length(compareyr) == 1, compareyr, "Previous years")`

## Bottom and Surface Temperatures

```{r results-cold-pool_insert, child=paste0(dir_out_rawdata, "/0-cold-pool.Rmd")}
```

```{r fig-temperature-bt}
nickname <- "fig-temperature-bt-data"
```

```{r temperature-bt-child, child = paste0(dir_code, "_child_report_figtab.Rmd")}
```

```{r fig-temperature-st}
nickname <- "fig-temperature-st-data"
```

```{r temperature-st-child, child = paste0(dir_code, "_child_report_figtab.Rmd")}
```

```{r fig-mean-temperature0}
nickname <- "fig-mean-temperature"
```

```{r fig-mean-temperature0-child, child = paste0(dir_code, "_child_report_figtab.Rmd")}
```

```{r fig-cold-pool-area0}
nickname <- "fig-cold-pool-area"
```

```{r fig-cold-pool-area0-child, child = paste0(dir_code, "_child_report_figtab.Rmd")}
```

## Survey Data and Specimen Collections

```{r nbs-trawl-survey-area}
# area of nbs trawl stations
# area =  l*w * number of areas
# temp <- haul_cruises_maxyr$stations_completed[haul_cruises_maxyr$srvy == "NBS"] * # number of stations
#   (10 / 1852) * # width of trawl net (m/nmi -> nmi)
#   1.5 # calculate distance nmi = velocity (3 knots) * time (30 min)

temp <- sum((haul_maxyr$net_width_m[haul_maxyr$srvy == "NBS"]/ 1852) * # net width in meters, divided 1852 (m->nmi)
      ((haul_maxyr$distance_fished_km[haul_maxyr$srvy == "NBS"] * 1000)/ 1852), # distance fished in km converted to m,  divided 1852 (m->nmi)
    na.rm = TRUE)

temp1 <- sum((haul_compareyr$net_width_m[haul_compareyr$srvy == "NBS"]/ 1852) * 
      ((haul_compareyr$distance_fished_km[haul_compareyr$srvy == "NBS"] * 1000)/ 1852),
    na.rm = TRUE)

# In `r maxyr`, the cumulative area sampled by trawls at the `r haul_cruises_maxyr$stations_completed[haul_cruises_maxyr$srvy == "NBS"] ` completed stations was approximately `r round(temp, 2)` nmi^2^ (`r round(temp/divnmi2forkm2, 2)` km^2^), covering `r formatC(x = ((temp / sum(stratum$area_nmi2[stratum$srvy == "NBS"], na.rm=TRUE)) * 100), format = "f", digits = 4)`% of the total area of the northern Bering Sea. In `r compareyr`, the cumulative area sampled by trawls at the `r haul_cruises_compareyr$stations_completed[haul_cruises_compareyr$srvy == "NBS"] ` completed stations was approximately `r round(temp1, 2)` nmi^2^ (`r round(temp1/divnmi2forkm2, 2)` km^2^), covering `r formatC(x = ((temp1 / sum(stratum$area_nmi2[stratum$srvy == "NBS"], na.rm=TRUE)) * 100), format = "f", digits = 4)`% of the total area of the northern Bering Sea. 
```

In `r maxyr`, the total area sampled by trawls at the `r haul_cruises_maxyr$stations_completed[haul_cruises_maxyr$srvy == "NBS"] ` completed stations was approximately `r round(temp, 2)` nmi^2^ (`r round(temp/divnmi2forkm2, 2)` km^2^), covering `r formatC(x = ((temp / sum(stratum$area_nmi2[stratum$srvy == "NBS"], na.rm=TRUE)) * 100), format = "f", digits = 4)`% of the total area of the northern Bering Sea. In `r compareyr`, the total area sampled by trawls at the `r haul_cruises_compareyr$stations_completed[haul_cruises_compareyr$srvy == "NBS"] ` completed stations was approximately `r round(temp1, 2)` nmi^2^ (`r round(temp1/divnmi2forkm2, 2)` km^2^), covering `r formatC(x = ((temp1 / sum(stratum$area_nmi2[stratum$srvy == "NBS"], na.rm=TRUE)) * 100), format = "f", digits = 4)`% of the total area of the northern Bering Sea. 

```{r specimen-collections}
  # obtain data
  load(file = paste0(dir_out_figtab, "tab-specimen-samples-EBS.rdata"))

  obj$raw <- obj$raw |> 
      dplyr::mutate(common_name = common_name0) |> 
      dplyr::select(-common_name0)
  
  obj1 <- obj
  
    temp1 <- obj1$raw |> 
      dplyr::filter(common_name != "Total" &
                      !(grepl(x = common_name, pattern = "crab", ignore.case = TRUE)))
  
  if (srvy == "NEBS") {
  load(file = paste0(dir_out_figtab, "tab-specimen-samples-NBS.rdata")) # obj
      temp1 <- temp1|> dplyr::bind_rows(
    obj$raw|> 
      dplyr::filter(common_name != "Total" &
                      !(grepl(x = common_name, pattern = "crab", ignore.case = TRUE))) )    
  }

  temp1 <- dplyr::bind_rows(
    obj1$raw |> 
      dplyr::filter(common_name != "Total" &
                      !(grepl(x = common_name, pattern = "crab", ignore.case = TRUE))), 
    obj$raw|> 
      dplyr::filter(common_name != "Total" &
                      !(grepl(x = common_name, pattern = "crab", ignore.case = TRUE))) )|> 
    dplyr::select(-srvy) |> 
    dplyr::group_by(common_name)|> 
    dplyr::summarise(across(everything(), ~ sum(., na.rm = TRUE)))|> 
    dplyr::ungroup()
  
  # list taxon used in each sample
  temp3 <- c()
  for (i in 2:ncol(temp1)) {
    temp2 <-  temp1[, c(1, i)]
    temp2 <- temp2[temp2[,2]>0,]
    temp2$spp <- text_list(unique(temp2$common_name))
    temp2$spp <- ifelse(grepl(pattern = "shark", x = temp2$spp), 
                    gsub(pattern = "shark", replacement = "sharks", x = temp2$spp), 
                    temp2$spp)
    temp3 <- dplyr::bind_cols(temp3, 
                              data.frame(temp = temp2$spp[1]) )
    names(temp3)[i-1] <- paste0("spp_", names(temp2)[2])
  }
  
  # count taxon used in each sample
  temp1 <- temp1|> 
    dplyr::select(-common_name)|>
    tidyr::pivot_longer(cols = names(temp1|> dplyr::select(-common_name)), 
                        names_to = "var", values_to = "val") |> 
    dplyr::filter(val != 0)|> 
    dplyr::group_by(var)|> 
    dplyr::summarise(n = n())|> 
    dplyr::ungroup()|> 
    dplyr::mutate(var = paste0("n_", var))|> 
    tidyr::pivot_wider(names_from = var, values_from = n)
  
  temp <- dplyr::bind_rows(
    obj$raw|> 
      dplyr::filter(common_name == "Total") , 
    obj1$raw|> 
      dplyr::filter(common_name == "Total") )|>
    # dplyr::filter(!(grepl(x = common_name, pattern = "crab", ignore.case = TRUE)))|> 
    dplyr::select(-srvy, -common_name)|>
    dplyr::ungroup()|> 
    dplyr::summarise(across(everything(), ~ sum(., na.rm = TRUE)))

  temp <- data.frame(t(temp))
  names(temp) <- "n_samples"
  temp$var <- rownames(temp)
  temp1 <- data.frame(t(temp1))
  names(temp1) <- "n_taxa"
  temp1$var <- gsub(pattern = "n_", replacement = "", x = rownames(temp1))
  temp3 <- data.frame(t(temp3))
  names(temp3) <- "text_taxa"
  temp3$var <- gsub(pattern = "spp_", replacement = "", x = rownames(temp3))
  
  temp0 <- dplyr::left_join(temp, temp1, by = "var")|> 
    dplyr::left_join(temp3, by = "var")|> 
    dplyr::mutate(var0 = tolower(gsub(pattern = "\n", x = var, replacement = " ")), 
                  taxa_type = "fish")|> 
    dplyr::arrange(desc(n_samples))

  temp000 <- temp0|>
    dplyr::filter(var == "Length\nmeasurements")
    
  temp00 <- temp0|>
    dplyr::filter(var != "Length\nmeasurements")
  
    str0 <- text_list(
        paste0(xunits(temp00$n_samples), " ",
         (temp00$var0), " ",
         ifelse(temp00$n_samples == 1, "was", "were"),
         " collected from ",
         ifelse(temp00$n_samples == 1, "a", ""), # TOLEDO - what if starts with vowel???
         ifelse(temp00$n_taxa < 4, 
                temp00$text_taxa,
                paste0(xunits(temp00$n_taxa), " taxa")) ), sep = "; ")
    
str0 <- gsub(pattern = "  ", replacement = " ", x = str0)
```

From the `r SURVEY` survey`r plural_surveys`, length measurements were collected from `r xunits(temp000$n_samples)` individual fish representing `r xunits(temp000$n_taxa)` fish taxa. Additionally, `r str0`. 

## Estimates of Fishes and Invertebrates

```{r biomass-inc-dec-tot}

# million metric tons of biomass collected in each region in each year
temp <- total_biomass|> 
  dplyr::group_by(year, srvy, srvy_long)|> 
  dplyr::summarise(biomass_mmt = round(sum(total, na.rm = TRUE)/1e6, digits = 1))|> 
  dplyr::ungroup()|> 
  dplyr::arrange(desc(year)) |>
  dplyr::right_join(data.frame(srvy = c(names(compareyr), names(compareyr)), 
                               year = c(compareyr, 
                                        rep_len(x = maxyr, length.out = length(compareyr))))) # |> 
  # dplyr::filter(year %in% c(maxyr, compareyr))
```

In `r maxyr`, the total bottom-dwelling animal biomass of the eastern Bering Sea shelf was estimated at `r temp$biomass_mmt[temp$year == maxyr & temp$srvy == "EBS"] ` million metric tons (t) and the northern Bering Sea shelf was estimated at `r temp$biomass_mmt[temp$year == maxyr & temp$srvy == "NBS"] ` million t. Previously, the total bottom-dwelling animal biomass of the `r text_list(paste0(temp$year[temp$year != maxyr], " ", temp$srvy_long[temp$year != maxyr], " shelf was estimated at ", temp$biomass_mmt[temp$year != maxyr], " million t"))`. 

```{r biomass-inc-dec-spp}

load(file = paste0(dir_out_figtab, "tab-majortaxa-pchange-NBS.rdata"))

temp1 <- obj$raw |>
      # dplyr::filter(srvy == "NBS")|>
      dplyr::select(print_name = print_name1, change, change0, maxyr, taxon, srvy) |>
 # I defined "no marked change" in < 25 and > -25% change to get me through the code. What number should it be?
  dplyr::mutate(
    change_case = dplyr::case_when(
    change0 < -25 ~ "decreasing",
    change0 > 25 ~ "increasing",
    TRUE ~ "no notable change in" ),
    change_case1 = dplyr::case_when(
    change0 < -25 ~ "decreases",
    change0 > 25 ~ "increases",
    TRUE ~ NA
  )) |>
  dplyr::arrange(desc(change0))

temp44 <- temp1 |> 
  dplyr::group_by(taxon, change_case, srvy)|>
  dplyr::summarise(n = n())|>
  dplyr::ungroup()|>
  tidyr::pivot_wider(id_cols = c(change_case, srvy), 
                     names_from = taxon, values_from = n)|>
  dplyr::mutate(
    str0_fish = ifelse(is.na(fish), "", paste0(xunits(fish), " fish", ifelse(fish>1, "es", ""))),
    str0_invert = ifelse(is.na(invert), "", paste0(xunits(invert), " invertebrate", ifelse(invert>1, "s", ""))),
    str0 = paste0(str0_fish, ifelse(str0_invert == "", "", " and "), str0_invert))

temp3 <- temp1 |>
  dplyr::arrange(desc(change0))|>
  dplyr::filter(#taxon == "fish"  &
                  # !grepl(x = print_name, pattern = "other ") &
                  !is.na(change_case1))

temp33 <- dplyr::bind_rows(
  head(temp3[which(temp3$srvy == "EBS"),]), 
                          tail(temp3[which(temp3$srvy == "EBS"),]), 
                          head(temp3[which(temp3$srvy == "NBS"),]), 
                          tail(temp3[which(temp3$srvy == "NBS"),]))|>
  dplyr::arrange(desc(abs(change0)))|> 
  dplyr::group_by(change_case1, srvy)|>
  dplyr::summarise(spp_list = text_list(paste0(print_name, " (", change, ")")))|>
  dplyr::ungroup()|>
  dplyr::arrange(change_case1)

str0 <- ""

for (i in 2:2) {

  temp3 <- temp33|> dplyr::filter(srvy == srvy1[i])
  temp4 <- temp44|> dplyr::filter(srvy == srvy1[i])
    
str0 <- paste0(str0, 
paste0(
  "In the ",srvy11[i]," between ", compareyr, " and ", maxyr , ", ",
               text_list(paste0(temp4$str0, " experienced ", temp4$change_case, " biomass")),
  ifelse(i == 1, " (± 25% change from the previous survey year). ", ". "),
               # paste0("Prominent organisms that exhibited the largest ", 
               #        temp3$change_case1, " in biomass included ", temp3$spp_list, 
               #        collapse = ifelse(i == 1, " (Table \\@ref(tab:tab-majortaxa-pchange-NBS)). ", ". ")),  
  collapse = ". " )#,  ifelse(i == 1, ".\n\n", ". ") 
)
}

str0 <- gsub(pattern = ") (", replacement = "; ", x = str0, fixed = TRUE)
str0 <- gsub(pattern = ". . ", replacement = ". ", x = str0, fixed = TRUE)

```

`r str0`The biomasses of predominant species are listed in Table \@ref(tab:tab-majortaxa-pchange-NBS) in order of largest increase to largest decrease. 

```{r ebs-vs-nbs}
temp5 <- biomass |> 
  dplyr::filter(stratum == 999 & 
                  species_code %in% report_spp1$species_code[(report_spp1$plot_idw)] & 
                  year == maxyr) |> 
  dplyr::select(srvy, biomass_mt, species_code, common_name) |> 
  dplyr::left_join(report_spp1 |> 
                     dplyr::select(print_name, species_code, order) |> 
                     dplyr::distinct()) |> 
  # dplyr::arrange(desc(NBS)) 
  dplyr::arrange(desc(order))|> 
  dplyr::group_by(print_name, srvy)|> 
  dplyr::summarise(biomass_mt = sum(biomass_mt, na.rm = TRUE))|> 
  tidyr::pivot_wider(names_from = srvy, values_from = biomass_mt)|> 
  dplyr::ungroup()|> 
  dplyr::mutate(NBS_greater = (NBS > EBS), 
                NBS_only = (NBS > 0 & is.na(EBS)))|> 
  dplyr::filter(NBS_greater)|> 
  dplyr::mutate(print_name = sub(" \\(.*", "", x = print_name))
```

Survey catches in the northern Bering Sea were generally smaller than in the eastern Bering Sea. Many predominant species were distributed throughout both survey regions. Several key species were found in the northern Bering Sea in greater biomass than the eastern Bering Sea, including `r text_list(temp5$print_name)`.

```{r biomass-inc-dec}

load(file = paste0(dir_out_figtab, "tab-majortaxa-pchange-NBS.rdata"))
temp1 <- obj$raw |> 
  dplyr::select(-print_name, print_name = print_name1) 

# total biomass
temp2 <- total_biomass |> 
  dplyr::ungroup()|> 
  dplyr::filter(srvy == "NBS")|>
  dplyr::group_by(year)|> 
  dplyr::summarise(total = sum(total, na.rm = TRUE))|> 
  dplyr::ungroup()

# calculate top 50% of haul
temp0 <- temp3 <- data.frame()
str0 <- str00 <- c()

yrs <- c(maxyr, compareyr[names(compareyr) == "NBS"])
  
for (i in 1:length(yrs)) {
  
  yr <- as.numeric(sort(yrs, decreasing = TRUE)[i])
  temp <- temp2$total[temp2$year == yr]
  
  temp5 <- temp1 |> 
  dplyr::filter(srvy == "NBS")|> 
    dplyr::rename("x" = all_of(as.character(yr)))|> 
    dplyr::arrange(desc(x))|> 
    dplyr::select(print_name, x, taxon)|> # species_name, 
    dplyr::mutate(prop = x/temp)|> 
    dplyr::mutate(cumsum = cumsum(prop)) |> 
    dplyr::mutate(year = yr)
  
  # Top 50% spp
  temp4 <- temp5|> 
    dplyr::filter(dplyr::between(x = cumsum, left = 0, right = .55))
  
  temp3 <- rbind.data.frame(temp3, temp5)
  
  if (yr == maxyr) {
    str0 <- paste0(str0, 
                     paste0("In ", yr, ", 50% of the total estimated biomass in the northern Bering Sea was comprised of ", 
                            text_list(paste0(temp4$print_name, " (", 
                                                          round(temp4$prop*100, digits = 0), "%)")), ". "))
  } else if (i==2) {
    str0 <- paste0(str0, 
                     paste0("Previously in ", yr, ", 50% of the estimated biomass was comprised of ", 
                            text_list(
                              paste0(temp4$print_name, " (", round(temp4$prop*100, digits = 0), "%)"))))
  } else {
    str0 <- paste0(str0, 
                     paste0(ifelse(i==length(nbsyr), "; and in ", "; in "), yr, ", ", 
                            text_list(
                              paste0(temp4$print_name, " (", round(temp4$prop*100, digits = 0), "%)"))))
    
  }
  
  # Other cods: saffron cod and Arctic cod
  temp0 <- rbind.data.frame(temp0, 
                            temp5|> 
                              dplyr::filter(print_name %in% c("saffron cod","Arctic cod")) )
}

temp0 <- temp0|> 
  dplyr::filter(year %in% c(maxyr, compareyr))|>
  dplyr::group_by(year)|> 
  dplyr::summarise(prop = sum(prop, na.rm = TRUE))|> 
  dplyr::arrange(desc(year))|> 
  dplyr::mutate("perc" = paste0(round(x = prop*100, digits = 1), "%"))

temp3 <- temp3 |> 
  # dplyr::mutate(case = dplyr::case_when(
  #   prop*100>0 ~ "increasing", 
  #   TRUE ~ "decreasing"))|> 
  dplyr::filter(year %in% c(maxyr, compareyr))|>
  dplyr::select(taxon, year, x,)|>
  dplyr::group_by(taxon, year)|> 
  dplyr::summarise(biomass_mt = sum(x, na.rm = TRUE))|> 
  tidyr::pivot_wider(names_from = taxon, values_from = biomass_mt, id_cols = year)|> 
  dplyr::mutate(total = (fish + invert), 
                invert_perc = invert/total, 
                invert_perc = formatC(x = invert_perc*100, digits = 0, big.mark = ",", format = "f"))|> 
  dplyr::arrange(desc(year))

```

`r str0`. 

Saffron cod and Arctic cod accounted for `r text_list(paste0(temp0$perc, " of the total biomass in ", temp0$year)) `. Invertebrates (i.e., shrimps, sea squirts, sea stars, jellyfish, crabs, and urchins) made up `r text_list(paste0(temp3$invert_perc, "% of the biomass in ", temp3$year))`. 

\pagebreak

```{r tab-majortaxa-pchange-NBS0}
nickname <- "tab-majortaxa-pchange-NBS"
```

```{r tab-majortaxa-pchange-NBS0-child, child = paste0(dir_code, "_child_report_figtab.Rmd")}
```

# Summary Results for Select Major Taxa

Survey results for select taxa are presented with a photograph of the taxon, a summary of results, maps of geographic distribution of CPUE (kg/km^2^), and plots showing total population estimates by sex and size. Maps of species distributions include both the eastern and northern Bering Sea shelf survey regions to better illustrate patterns and trends in fish distribution and movement. For comparison among years, distribution maps and abundance-at-size plots show survey data from the `r text_list(nbsyr) ` surveys.

**You can help us with this document by providing names in local language(s) and cultural or traditional uses for each fish and invertebrate species reviewed in this report by reaching out to [nmfs.afsc.gap.metadata@noaa.gov](nmfs.afsc.gap.metadata@noaa.gov).**

\pagebreak

