---
output:
  officedown::rdocx_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, error = FALSE, message = FALSE)
```

## vars

```{r vars}
a <- report_spp1[which(report_spp1$file_name == comb[jj]), ]

spp_sci <- text_list(unique(a$species_name))
spp_print <- a$print_name[1]
spp_file <- a$file_name[1]
spp_taxon <- a$taxon[1]

# report_title == "community"
spp_plot_sizecomp <- (nrow(sizecomp %>% 
                             dplyr::filter(species_code %in% spp_code) %>% 
                             dplyr::filter(year %in% nbsyr) ) >0)
spp_plot_agecomp <- (nrow(agecomp %>%
                            dplyr::filter(species_code %in% spp_code) %>%
                            dplyr::filter(year %in% nbsyr) ) >0)
spp_plot_idw <- a$plot_idw[1]
spp_table_cpue <- a$table_cpue[1]

spp_bin <- eval(expr = parse(text = a$dist_bin))
```

## fig-[spp]-0-pres

```{r fig-spp, eval = (report_title == "pres")}
header <- spp_file
nickname <- paste0("fig-", jj, "-", spp_file, "-0-pres")
height <- width <- 5

figure_print <- 
  cowplot::ggdraw() +
  cowplot::draw_image(readPNG(paste0(dir_img, spp_file, ".png")) )

res <- knitr::knit_child(text = knitr::knit_expand( file = paste0(dir_code, "_child_save_figtab.Rmd")), quiet = TRUE)
```

## fig-dist-[spp]-prep

```{r fig-dist-[spp]-prep}
fig_width <- width <- full_page_portrait_width # 6.5  
case_yr0 <- 1
place_labels <- FALSE
viridis_palette_option <- "mako"

dist_plot <- function(yrs, height, row0, nickname, report_title0, spp_print, spp_code) {
  
  width <- full_page_portrait_width # 6.5  
  case_yr0 <- 1
  place_labels <- FALSE
  viridis_palette_option <- "mako"
  
  yrs0 <- sort(yrs, decreasing = TRUE)
  key.title <- paste0(stringr::str_to_title(spp_print),
                      ifelse(report_title0 == "pres", " ", '\n'), 
                      'Weight CPUE (kg/km²)')
  
  # Select data ------------------------------------------------------------------
  if (length(spp_code) > 1) {
    table_raw <- cpue %>%
      dplyr::filter(group %in% spp_print)
  } else {
    table_raw <- cpue %>%
      dplyr::filter(species_code %in% spp_code)
  }
  
  table_raw <- table_raw %>% 
    dplyr::mutate(cpue_kgkm2 = ifelse(is.na(cpue_kgkm2), 0, cpue_kgkm2), 
                  HAUL = NA) %>%
    dplyr::filter(
      SRVY %in% SRVY1 &
        year %in% yrs) %>% 
    dplyr::arrange(desc(year)) %>%
    dplyr::select(survey_definition_id, 
                  SRVY,
                  LATITUDE = latitude_dd_start,
                  LONGITUDE = longitude_dd_start,
                  CPUE_KGHA = cpue_kgkm2, 
                  YEAR = year) %>% 
    dplyr::mutate(COMMON_NAME = spp_print) %>% 
    dplyr::ungroup() %>% 
    data.frame()
  
  # is one of the areas zero-filled that for this subset, doesn't need to be?
  # needs to be clean here so the downstream code picks the right map.area extent
  temp <- table_raw %>% 
    dplyr::group_by(SRVY) %>% 
    dplyr::summarise(maxcpue = max(CPUE_KGHA, na.rm = TRUE))
  if (0 %in% temp$maxcpue) {
    table_raw <- table_raw %>% 
      dplyr::filter(!(SRVY %in% temp$SRVY[temp$maxcpue == 0]))
  }
  
  # Find set.breaks --------------------------------------------------------------
  if (!(NA %in% spp_bin) ) {
    # if (spp_bin[1] > max(table_raw$CPUE_KGHA)) {
    #   set.breaks <- c(0, max(table_raw$CPUE_KGHA))
    # } else {
    spp_bin <- spp_bin[!(spp_bin > max(table_raw$CPUE_KGHA))]
    if (length(spp_bin)>0) {
      set.breaks <- c(0, spp_bin, max(table_raw$CPUE_KGHA))
    } else {
      set.breaks <- c(0, max(table_raw$CPUE_KGHA))
    }
    # }
  } else {
    set.breaks <- akgfmaps::eval_plot_breaks(CPUE = table_raw$CPUE_KGHA, n.breaks = 5)
    set.breaks <- as.vector(unlist(set.breaks[set.breaks$style == "pretty", -1]))
  }
  
  set.breaks_pretty0 <- formatC(x = set.breaks, big.mark = ",", format = "f", digits = 0)
  set.breaks_pretty <- set.breaks_pretty0
  set.breaks_pretty[1] <- "No catch"
  for (i in 2:length(set.breaks_pretty)) {
    set.breaks_pretty[i] <- paste0(">", set.breaks_pretty0[i-1], "-", set.breaks_pretty0[i])
  }
  
  # find appropriate map.area0 ---------------------------------------------------
  # only if both species are only found in prt of the region, change the extrp.box
  map.area0 <- map.area
  reg_dat0 <- reg_dat
  if (length(unique(table_raw$SRVY))==1 & SRVY == "NEBS") { # is this species in only 1 of the 2 survey areas (when SRVY == NEBS)?
    map.area0 <- ifelse(unique(table_raw$SRVY) == "EBS", "ebs", "nbs")
    reg_dat0 <- report_types[[unique(table_raw$SRVY)]]$reg_dat
    if (report_title0 != "pres") {
      height <- ifelse(reg_dat0$survey.area$SURVEY == "EBS_SHELF" & 
                         report_title0 == "data", height, height-1)
    }
  }
  
  # Write header for figure_print ------------------------------------------------------
  missing_from_one_but_not_both_surveys <- ""
  if (SRVY == "NEBS") {
    if (length(unique(table_raw$SRVY)) > 1) {
      missing_from_one_but_not_both_surveys <- paste0("This species was not encountered in the ", 
                                                      range_text(yrs), " ",
                                                      haul_cruises_maxyr$SRVY_long[haul_cruises_maxyr$SRVY !=
                                                                                     unique(table_raw$SRVY)], 
                                                      " shelf bottom trawl survey", ifelse(length(yrs)>1, "s", ""), 
                                                      ". ")
    }
  }
  header <- paste0("Weight CPUE (kg/km^2^) distribution of ", 
                   spp_print, 
                   ifelse(is.na(spp_sci), "", 
                          paste0(" (",spp_sci,")")), 
                   " from the ",
                   range_text(yrs), " ", 
                   SURVEY, 
                   " shelf bottom trawl survey", 
                   ifelse(length(unique(table_raw$SRVY))>1, "s", ""), ". ", 
                   missing_from_one_but_not_both_surveys
  )
  
  # find which years need to be prepared with which region # crude, but here we are
  a <- table_raw %>%
    dplyr::select(YEAR, survey_definition_id) %>%
    dplyr::distinct()  %>%
    dplyr::mutate(survey_definition_id = dplyr::case_when(
      survey_definition_id == 98 ~ "EBS",
      survey_definition_id == 143 ~ "NBS")) %>%
    tidyr::pivot_wider(id_cols = YEAR,
                       names_from = survey_definition_id,
                       values_from = survey_definition_id)
  if (ncol(a)<3) {
    a$case <- unlist(a[,2])
  } else {
    a <- a %>% 
      dplyr::mutate(
        case = dplyr::case_when(
          !is.na(EBS) & !is.na(NBS) ~ "both", 
          !is.na(EBS) ~ "EBS", 
          !is.na(NBS) ~ "NBS"
        ))
  }
  
  # dummy empty data
  temp <- table_raw %>% 
    dplyr::filter(YEAR == 2022) %>% 
    dplyr::mutate(cpue_kgkm2 = NA, 
                  cpue_nokm2 = NA, 
                  hauljoin = NA)
  
  if (map.area0 == "bs.all") {
    if ("NBS" %in% a$case) {
      for (i in which(a$case %in% "NBS")){
        table_raw <- table_raw %>% 
          dplyr::bind_rows(temp %>% 
                             dplyr::filter(SRVY == "EBS") %>% 
                             dplyr::mutate(YEAR = a$year[i]))
      }}
    
    if ("EBS" %in% a$case) {
      for (i in which(a$case %in% "EBS")){
        table_raw <- table_raw %>% 
          dplyr::bind_rows(temp %>% 
                             dplyr::filter(SRVY == "NBS") %>% 
                             dplyr::mutate(YEAR = a$year[i]))
      }}
  }
  
  # Create shapefile of species IDW ----------------------------------------------
  idw <- make_idw_stack(
    x = table_raw,
    region = map.area0, 
    grouping.vars = "YEAR", 
    set.breaks = set.breaks,
    out.crs = out.crs, 
    extrapolation.grid.type = "sf")
  
  
  idw$extrapolation.stack$var1.pred <- 
    factor(x = idw$extrapolation.stack$var1.pred, 
           levels = levels(idw$extrapolation.stack$var1.pred), 
           labels = set.breaks_pretty,
           ordered = TRUE)
  
  # Plot -------------------------------------------------------------------------
  for (case_yr in case_yr0) {
    if (length(case_yr0)>1) {
      if (case_yr == 1) {
        yrs <- yrs0[1:(length(yrs0)/2)]
      } else if (case_yr == 2) {
        yrs <- yrs0[((length(yrs0)/2)+1):length(yrs0)]
      }
    }
    
    figure_print <- ggplot() +
      ggplot2::geom_sf(data = reg_dat0$akland,
                       color = NA,
                       fill = "grey50")  +
      ggplot2::geom_sf(data = reg_dat0$graticule,
                       color = "grey80",
                       alpha = 0.2) +
      ggplot2::scale_y_continuous(name = "", #"Latitude",
                                  limits = reg_dat0$plot.boundary$y,
                                  breaks = reg_dat0$lat.breaks) +
      ggplot2::scale_x_continuous(name = "", #"Longitude",
                                  limits = reg_dat0$plot.boundary$x,
                                  breaks = reg_dat0$lon.breaks) + 
      ggplot2::geom_sf(data = idw$extrapolation.stack,
                       mapping = aes(fill = var1.pred),
                       na.rm = FALSE,
                       show.legend = TRUE, 
                       color = NA) +
      ggplot2::facet_wrap( ~ YEAR, nrow = row0) + 
      ggplot2::scale_fill_manual(
        # labels = scales::label_comma(),
        # labels = function(x) format(x, big.mark = ",", scientific = FALSE), 
        name = key.title,
        values =  c("gray90",
                    viridis::viridis(
                      option = viridis_palette_option,
                      direction = -1,
                      n = length(set.breaks)-1,
                      begin = 0.20,
                      end = 0.80)),
        na.translate = FALSE, # Don't use NA
        drop = FALSE) + 
      ggplot2::geom_sf(
        data = reg_dat0$survey.area, 
        mapping = aes(color = SURVEY, 
                      geometry = geometry), 
        fill = "transparent", 
        linewidth = ifelse(row0 > 2, 1.5, 1), 
        show.legend = FALSE) +
      ggplot2::scale_color_manual(
        name = " ", 
        values = reg_dat0$survey.area$color,
        breaks = reg_dat0$survey.area$SURVEY,
        labels = reg_dat0$survey.area$SRVY) + 
      ggplot2::guides(
        fill = guide_legend(
          order = 1,
          title.position = "top",
          label.position = "bottom",
          title.hjust = 0.5,
          override.aes = list(color = NA),
          nrow = 1),
        color = "none")  +
      ggplot2::coord_sf(expand = FALSE) + # coord_sf() + 
      ggplot2::theme( 
        panel.background = element_rect(fill = "white", colour = NA), 
        panel.border = element_rect(fill = NA, colour = "grey20"), 
        axis.text = element_text(size = ifelse(length(yrs)>4 & row0 == 1, 6, 8)),
        
        strip.background = element_blank(), 
        strip.text = element_text(size = 10, face = "bold"), 
        legend.text = element_text(size = 9),
        legend.background = element_rect(colour = "transparent", 
                                         fill = "transparent"),
        legend.key = element_rect(colour = "transparent", 
                                  fill = "transparent"),
        legend.position = "bottom", 
        legend.box = "horizontal",
        legend.box.spacing = unit(0, "pt"), # reduce space between legend & plot
        legend.margin=margin(0, 0, 0, 0) ) 
    
    if (report_title0 == "pres") {
      figure_print <- figure_print +
        ggplot2::theme(legend.title=element_blank() ) +
        ggplot2::ggtitle(key.title) 
    }
    
    # if (report_title0 %in% c("nbspres")) {
    #   
    #   figure_print <- figure_print + 
    #     ggplot2::geom_sf_text(
    #       data = data.frame(y = 64.500126, x = -165.408402) %>% 
    #         sf::st_as_sf(coords=c("x","y"), crs="+proj=longlat") %>% 
    #         sf::st_transform(crs = "EPSG:3338") %>%
    #         dplyr::mutate(label = "Nome"), 
    #       mapping = aes(label = label), 
    #       fontface = "italic", 
    #       size = 4) +
    #     geom_text(data = subset(reg_dat0$place.labels, 
    #                             type == "mainland"), 
    #               aes(x = x, y = y, label = lab), 
    #               size = 7, group = 99) + 
    #     geom_shadowtext(data = subset(reg_dat0$place.labels, 
    #                                   type == "peninsula"), 
    #                     aes(x = x, y = y, label = lab), size = 3, angle = 3, 
    #                     bg.color = "white", color = "black", group = 99) + 
    #     geom_shadowtext(
    #       data = subset(reg_dat0$place.labels, 
    #                     type %in% c("bathymetry", "islands")),
    #       aes(x = x, y = y, label = lab), 
    #       bg.color = "white", color = "black", 
    #       size = 2, group = 99)
    # }  
    
    if (report_title0 %in% c("community")) {
      figure_print <-
        cowplot::ggdraw(figure_print +
                          ggplot2::theme( plot.margin = margin(1.8, 0, 0, 0, "cm") ) ) +
        cowplot::draw_image(image = readPNG(paste0(dir_img, spp_file, ".png")),
                            x = .77, y = .42, # top right
                            # x = 0.09, y = -.35, # lower left
                            hjust = 0, vjust = 0,
                            width = .18)
    }
    return(list("figure_print" = figure_print, 
                "header" = header, 
                "height" = height, 
                "width" = width, 
                "nickname" = nickname))
    # res <- knitr::knit_child(text = knitr::knit_expand( file = paste0(dir_code, "_child_save_figtab.Rmd")), quiet = TRUE)
  }
}
```

## fig-dist-[spp]-data

```{r fig-dist-[spp]-data}
yrs <- nbsyr
# if (spp_file == "greenland-turbot") {
#   yrs <- c(2022, 2023, 2024)
# }
width <- full_page_portrait_width # 6.5  
height <- full_page_portrait_height # + ifelse(SRVY == "EBS", 0, - 1)
row0 <- 3
nickname <- paste0("fig-dist-", spp_file, "-data")
report_title0 <- "data"

temp <- dist_plot(yrs, height, row0, nickname, report_title0, spp_print, spp_code)
for (jjj in 1:length(temp)) { assign(names(temp)[jjj], temp[[jjj]]) }
res <- knitr::knit_child(text = knitr::knit_expand( file = paste0(dir_code, "_child_save_figtab.Rmd")), quiet = TRUE)
```

## fig-dist-[spp]-comm

```{r fig-dist-[spp]-comm, eval = FALSE}
yrs <- unique(sort(c(maxyr, nbsyr, 2020)))
# if (spp_file == "greenland-turbot") {
#   yrs <- c(2022, 2023, 2024)
# }
width <- full_page_portrait_width # 6.5  
height <- full_page_portrait_height-1
row0 <- 2
nickname <- paste0("fig-dist-", spp_file, "-comm")
report_title0 <- "community"

temp <- dist_plot(yrs, height, row0, nickname, report_title0, spp_print, spp_code) 
for (jjj in 1:length(temp)) { assign(names(temp)[jjj], temp[[jjj]]) }
res <- knitr::knit_child(text = knitr::knit_expand( file = paste0(dir_code, "_child_save_figtab.Rmd")), quiet = TRUE)
```

## fig-dist-[spp]-pres

```{r fig-dist-[spp]-pres}
nickname <- paste0("fig-dist-", spp_file, "-pres")
yrs <- c(maxyr-1, maxyr)
height <- ifelse(SRVY == "NEBS", 5, 4)
width <- 5
row0 <- 2
width <- 5
row0 <- 1
report_title0 <- "pres"

temp <- dist_plot(yrs, height, row0, nickname, report_title0, spp_print, spp_code) 
pres_dist <- temp$figure_print
for (jjj in 1:length(temp)) { assign(names(temp)[jjj], temp[[jjj]]) }
res <- knitr::knit_child(text = knitr::knit_expand( file = paste0(dir_code, "_child_save_figtab.Rmd")), quiet = TRUE)
```

## fig-sizecomp-[spp]-prep

```{r fig-sizecomp-[spp]-prep, eval = spp_plot_sizecomp}
width <- full_page_portrait_width # 6.5  
header <- ""
legend_font_size <- 12

size_plot <- function(srvy, yrs, lengths, sizecomp, print_n, height, width, nickname, legend_font_size, report_title0) {
  
  lengths0 <- lengths %>%
    dplyr::filter(species_code %in% spp_code &
                    SRVY %in% srvy &
                    year %in% yrs)
  
  type <- unique(lengths0$sentancefrag)
  
  if (length(spp_code) > 1) {
    table_raw <- sizecomp %>%
      dplyr::filter(group %in% spp_print)
  } else {
    table_raw <- sizecomp %>%
      dplyr::filter(species_code %in% spp_code)
  }
  
  table_raw <- table_raw  %>%
    dplyr::filter(SRVY %in% srvy &
                    year %in% yrs) %>% 
    dplyr::mutate(sex = str_to_sentence(sex), 
                  sex = factor(sex, 
                               levels = c("Unsexed", "Males", "Females", "Immature females", "Mature females"), 
                               labels = c("Unsexed", "Males", "Females", "Immature females", "Mature females"),
                               ordered = TRUE), 
                  SRVY_long = dplyr::case_when(
                    SRVY == "EBS" ~ "eastern Bering Sea", 
                    SRVY == "NBS" ~ "northern Bering Sea") ) %>% 
    dplyr::arrange(sex) 
  
  if (!(nrow(table_raw) == 0)) {
    
    if (report_title0 %in% c("community", "data")) {
      if (report_title0 == "community") {
        
        header <- paste0("Total population estimates at length for ",
                         spp_print, ifelse(is.na(spp_sci), "", 
                                           paste0(" (",spp_sci,")")), 
                         " calculated from ",
                         range_text(yrs)," ",
                         text_list(paste0(unique(table_raw$SRVY_long))), 
                         " shelf bottom trawl survey", 
                         ifelse(length(unique(table_raw$SRVY))==1 & length(unique(table_raw$year))==1, "", "s"),
                         ". ",
                         ifelse(print_n, 
                                "Total number of individuals measured during the survey is indicated in the upper right corner of each plot.", ""))
        
      } else if (report_title0 == "data") {
        
        if (SRVY == "NEBS" & length(unique(table_raw$SRVY))>1) {
          table_raw <- dplyr::bind_rows(
            table_raw, 
            table_raw %>%
              dplyr::filter(species_code %in% spp_code &
                              SRVY %in% SRVY &
                              year %in% yrs) %>% 
              dplyr::group_by(year, taxon, species_code, sex, population_count) %>% 
              dplyr::summarise(length_mm) %>% 
              dplyr::mutate(
                SRVY = factor(x = SRVY, levels = c("EBS", "NBS", "EBS and NBS"), ordered = TRUE), 
                SRVY = "EBS and NBS", 
                SRVY_long = paste0("combined ", SURVEY)))
        }
        
        header <- paste0("Total abundance-at-length estimates of ",
                         spp_print, ifelse(is.na(spp_sci), "", 
                                           paste0(" (",spp_sci,")")), 
                         " by sex (",text_list(tolower(unique(table_raw$sex))),
                         ") in ",
                         ifelse(!grepl(pattern = " crab", x = spp_print, ignore.case = TRUE), 
                                "centimeters (cm)", "millimeters (mm)"),
                         " encountered during the ",
                         range_text(yrs)," ",
                         text_list(paste0(unique(table_raw$SRVY_long))), 
                         " shelf bottom trawl survey", 
                         ifelse(length(unique(table_raw$SRVY))==1 & length(unique(table_raw$year))==1, "", "s"),
                         ". ",
                         ifelse(length(setdiff(SRVY1, unique(table_raw$SRVY)))>0,
                                paste0("There were no lengths collected for this species in the ", 
                                       range_text(yrs), " ",
                                       haul_cruises_maxyr$SRVY_long[haul_cruises_maxyr$SRVY != unique(table_raw$SRVY)],
                                       " shelf trawl survey",ifelse(length(yrs)>1, "s", ""),". "), 
                                ""),
                         
                         "Length distributions are scaled up to the total estimated population size. ", 
                         ifelse(print_n, 
                                "Total number of individuals measured during the survey is indicated in the upper right corner of each plot.", ""))
      }
      
      figure_print <- plot_sizecomp(
        sizecomp0 = table_raw %>% 
          dplyr::mutate(
            SRVY_long = gsub(replacement = "", x = SRVY_long, pattern = SURVEY), 
            SRVY_long = trimws(stringr::str_to_title(SRVY_long))),
        lengths0 = lengths0,
        spp_code = spp_code,
        spp_print = stringr::str_to_title(spp_print),
        type = type,
        print_n = print_n, 
        ridgeline = FALSE)
      
    } else if (report_title0 == "pres") {
      header <- ""
      if ("EBS" %in% table_raw$SRVY) {
        figure1 <- figure_print <- plot_sizecomp(
          sizecomp0 = table_raw %>% 
            dplyr::filter(SRVY == "EBS") %>% 
            dplyr::mutate(SRVY_long = stringr::str_to_title(SRVY_long)),
          lengths0 = lengths0,
          spp_code = spp_code,
          spp_print = stringr::str_to_sentence(spp_print),
          type = type,
          print_n = print_n, 
          ridgeline = FALSE)
      }
      if ("NBS" %in% table_raw$SRVY) {
        figure2 <- figure_print <- plot_sizecomp(
          sizecomp0 = table_raw %>% 
            dplyr::filter(SRVY == "NBS") %>% 
            dplyr::mutate(SRVY_long = stringr::str_to_title(SRVY_long)),
          lengths0 = lengths0,
          spp_code = spp_code,
          spp_print = stringr::str_to_sentence(spp_print),
          type = type,
          print_n = print_n, 
          ridgeline = FALSE)
      }
      if (sum(unique(table_raw$SRVY) %in% c("NBS", "EBS")) == 2) {
        figure_print <- cowplot::plot_grid(figure1, figure2)
      }
    }
    
    figure_print <- figure_print +
      ggplot2::theme(strip.text = element_text(size = legend_font_size, face = "bold"))
    
    if (report_title0 %in% c("community")) { 
      figure_print <-
        cowplot::ggdraw(figure_print + 
                          ggplot2::theme( plot.margin = margin(1.2, 0, 0, 0, "cm") ) ) +
        cowplot::draw_image(image = readPNG(paste0(dir_img, spp_file, ".png")),
                            x = .78, y = .44, # top right
                            # x = 0.07, y = -.42, # lower left
                            hjust = 0, vjust = 0,
                            width = .18)
    }
    
  } else {
    header <- ""
    figure_print <- ggplot(data = data.frame(x = 1, y = 1, label = "There are no data for this year and species"), mapping = aes(y=y, x=x)) +
      geom_text(mapping = aes(label = label))
  }
  
  return(list("figure_print" = figure_print, 
              "header" = header, 
              "height" = height, 
              "width" = width, 
              "nickname" = nickname))
  # res <- knitr::knit_child(text = knitr::knit_expand( file = paste0(dir_code, "_child_save_figtab.Rmd")), quiet = TRUE)
}
```

## fig-sizecomp-[spp]-data

```{r fig-sizecomp-[spp]-data, eval = spp_plot_sizecomp}
yrs <- nbsyr
height <- full_page_portrait_height 
print_n <- FALSE
srvy <- SRVY1
nickname <- paste0("fig-sizecomp-", spp_file, "-data")
legend_font_size <- 10
report_title0 <- "data"

temp <- size_plot(srvy, yrs, lengths, sizecomp, print_n, height, width, nickname, legend_font_size, report_title0) 
for (jjj in 1:length(temp)) { assign(names(temp)[jjj], temp[[jjj]]) }
res <- knitr::knit_child(text = knitr::knit_expand( file = paste0(dir_code, "_child_save_figtab.Rmd")), quiet = TRUE)
```

## fig-sizecomp-[spp]-comm

```{r fig-sizecomp-[spp]-comm, eval = spp_plot_sizecomp}
yrs <- nbsyr
height <- full_page_portrait_height 
print_n <- FALSE
srvy <- SRVY1
nickname <- paste0("fig-sizecomp-", spp_file, "-comm")
legend_font_size <- 10
report_title0 <- "community"
srvy <-"NBS"

temp <- size_plot(srvy, yrs, lengths, sizecomp, print_n, height, width, nickname, legend_font_size, report_title0) 
for (jjj in 1:length(temp)) { assign(names(temp)[jjj], temp[[jjj]]) }
res <- knitr::knit_child(text = knitr::knit_expand( file = paste0(dir_code, "_child_save_figtab.Rmd")), quiet = TRUE)
```

## fig-sizecomp-[spp]-pres

```{r fig-sizecomp-[spp]-pres, eval = spp_plot_sizecomp}
srvy <- SRVY1
nickname <- paste0("fig-sizecomp-", spp_file, "-pres")
yrs <- c(maxyr, compareyr)
print_n <- FALSE
height <- 4.5
width <- 5
legend_font_size <- 12
report_title0 <- "pres"

temp <- size_plot(srvy, yrs, lengths, sizecomp, print_n, height, width, nickname, legend_font_size, report_title0) 
pres_size <- temp$figure_print
for (jjj in 1:length(temp)) { assign(names(temp)[jjj], temp[[jjj]]) }
res <- knitr::knit_child(text = knitr::knit_expand( file = paste0(dir_code, "_child_save_figtab.Rmd")), quiet = TRUE)
```

## fig-agecomp-[spp]-prep

```{r fig-agecomp-[spp]-prep, eval = spp_plot_agecomp}
width <- full_page_portrait_width # 6.5  
header <- ""
legend_font_size <- 12

age_plot <- function(srvy, yrs, agecomp, height, width, nickname, legend_font_size, report_title0) {
  
  if (length(spp_code) > 1) {
    table_raw <- agecomp %>%
      dplyr::filter(group %in% spp_print)
  } else {
    table_raw <- agecomp %>%
      dplyr::filter(species_code %in% spp_code)
  }
  
  
  # find appropriate units
  a <- find_units(unit = "", unt = " years", dat = max(table_raw$population_count, na.rm = TRUE))
  for (jjj in 1:length(a)) { assign(names(a)[jjj], a[[jjj]]) }
  pop_unit <- divby
  pop_unit_word <- unit_word
  
  # len_unit_axis <- ifelse(max(table_raw$length_mm)-min(table_raw$length_mm)>150, 50, 
  #                         ifelse(max(table_raw$length_mm)-min(table_raw$length_mm)>45, 10, 5))
  
  table_raw <- table_raw  %>%
    dplyr::filter(SRVY %in% srvy &
                    year %in% yrs) %>% 
    dplyr::mutate(sex = str_to_sentence(sex), 
                  sex = factor(sex, 
                               levels = c("Unsexed", "Males", "Females"), 
                               labels = c("Unsexed", "Males", "Females"),
                               ordered = TRUE), 
                  SRVY_long = dplyr::case_when(
                    SRVY == "EBS" ~ "eastern Bering Sea", 
                    SRVY == "NBS" ~ "northern Bering Sea"), 
                  population_count = population_count/pop_unit
    ) %>% 
    dplyr::arrange(sex) 
        
        if (SRVY == "NEBS" & length(unique(table_raw$SRVY))>1) {
          table_raw <- dplyr::bind_rows(
            table_raw, 
            table_raw %>%
              dplyr::filter(species_code %in% spp_code &
                              SRVY %in% SRVY &
                              year %in% yrs) %>% 
              dplyr::group_by(year, species_code, sex, population_count) %>% 
              dplyr::summarise(age) %>% 
              dplyr::mutate(
                SRVY = factor(x = SRVY, levels = c("EBS", "NBS", "EBS and NBS"), ordered = TRUE), 
                SRVY = "EBS and NBS", 
                SRVY_long = paste0("combined ", SURVEY)))
        }
        
        header <- paste0("Total abundance-at-age estimates of ",
                         spp_print, ifelse(is.na(spp_sci), "", 
                                           paste0(" (",spp_sci,")")), 
                         " by sex (",text_list(tolower(unique(table_raw$sex))),
                         ") encountered during the ",
                         range_text(yrs)," ",
                         text_list(paste0(unique(table_raw$SRVY_long))), 
                         " shelf bottom trawl survey", 
                         ifelse(length(unique(table_raw$SRVY))==1 & length(unique(table_raw$year))==1, "", "s"),
                         ". ",
                         ifelse(length(setdiff(SRVY1, unique(table_raw$SRVY)))>0,
                                paste0("There were no ages collected for this species in the ", 
                                       range_text(yrs), " ",
                                       haul_cruises_maxyr$SRVY_long[haul_cruises_maxyr$SRVY != unique(table_raw$SRVY)],
                                       " shelf trawl survey",ifelse(length(yrs)>1, "s", ""),". "), 
                                ""),
                         
                         "Age distributions are scaled up to the total estimated population size. Note that otoliths are not collected for each species each year and require, occasionally, years to process after collection. ")
      
      figure_print <- ggplot2::ggplot(
        data = table_raw %>% 
          # dplyr::filter(sex %in% c(1,2)) %>%
          dplyr::mutate(
            population_count = # change male population to negative
              ifelse(sex=="Males", population_count*(-1), population_count*1)) , # /1e9
        mapping = 
          aes(x = age,
              y = population_count, 
              fill = sex)) +
        ggplot2::geom_bar(stat = "identity") +
        ggplot2::coord_flip() +
        # ggplot2::ggtitle(label = "2023 EBS (Standard Area + NW) walleye pollock Age Composition")  + 
        ggplot2::guides(fill = guide_legend(title = ""))  +
        scale_fill_viridis_d(option = "G", begin = .3, end = .7) +
        scale_x_continuous(name = "Age bin", 
                           breaks = function(age) unique(floor(pretty(seq(0, (max(age) + 1) * 1.1))))) +
        scale_y_continuous(name = paste0(spp_print, " population across years", unit_word),
                           labels = abs) + 
        ggplot2::facet_grid(rows = vars(year), cols = vars(SRVY_long)) +
        ggplot2::theme(
        legend.position = "bottom",
        legend.box = "horizontal",
        legend.box.spacing = unit(0, "pt"),
          # legend.position = c(.95, .95),
          # legend.justification = c("right", "top"),
          # legend.box.just = "right",
          # legend.margin = margin(6, 6, 6, 6), 
          #legend.position = "none", 
          panel.grid.major.x = element_line(colour = "grey80"),
          panel.background = element_rect(fill = "white"),
          panel.grid.major.y = element_line(colour = "grey80"),
          panel.grid.minor.y = element_blank(),
          panel.grid.minor.x = element_blank(),
          panel.border = element_rect(fill = NA,
                                    colour = "grey20"),
          strip.background = element_blank(),
          strip.text = element_text(size = legend_font_size, face = "bold"),
          legend.text = element_text(size = 9),
          legend.key = element_rect(colour = "transparent",
                                    fill = "transparent"),
          axis.title = element_text(size = legend_font_size, face = "bold"),
          axis.text = element_text(size = legend_font_size))
      
      if (report_title0 %in% c("community")) { 
        figure_print <-
          cowplot::ggdraw(figure_print + 
                            ggplot2::theme( plot.margin = margin(1.2, 0, 0, 0, "cm") ) ) +
          cowplot::draw_image(image = readPNG(paste0(dir_img, spp_file, ".png")),
                              x = .78, y = .44, # top right
                              # x = 0.07, y = -.42, # lower left
                              hjust = 0, vjust = 0,
                              width = .18)
      }
      
    # } else {
    #   header <- ""
    #   figure_print <- ggplot(data = data.frame(x = 1, y = 1, label = "There are no data for this year and species"), mapping = aes(y=y, x=x)) +
    #     geom_text(mapping = aes(label = label))
    # }
    
      if (plural_surveys == "") {
         figure_print <- figure_print + 
                                  # ggplot2::ggtitle("") + 
                                  # ggplot2::guides(fill=guide_legend(title=""))  +
                                  ggplot2::theme(legend.title=element_blank(), 
                                                 strip.text.x = element_blank(),
                                                 strip.background = element_blank())
      }
      
      
    return(list("figure_print" = figure_print, 
                "header" = header, 
                "height" = height, 
                "width" = width, 
                "nickname" = nickname))
    # res <- knitr::knit_child(text = knitr::knit_expand( file = paste0(dir_code, "_child_save_figtab.Rmd")), quiet = TRUE)
  }
```
  
## fig-agecomp-[spp]-data
  
```{r fig-agecomp-[spp]-data, eval = spp_plot_agecomp}
  yrs <- nbsyr
  height <- full_page_portrait_height 
  print_n <- FALSE
  srvy <- SRVY1
  nickname <- paste0("fig-agecomp-", spp_file, "-data")
  legend_font_size <- 10
  report_title0 <- "data"
  
  temp <- age_plot(srvy, yrs, agecomp, height, width, nickname, legend_font_size, report_title0) 
  for (jjj in 1:length(temp)) { assign(names(temp)[jjj], temp[[jjj]]) }
  res <- knitr::knit_child(text = knitr::knit_expand( file = paste0(dir_code, "_child_save_figtab.Rmd")), quiet = TRUE)
```
  
## fig-agecomp-[spp]-comm
  
```{r fig-agecomp-[spp]-comm, eval = spp_plot_agecomp}
  # yrs <- nbsyr
  # height <- full_page_portrait_height 
  # print_n <- FALSE
  # srvy <- SRVY1
  # nickname <- paste0("fig-agecomp-", spp_file, "-comm")
  # legend_font_size <- 10
  # report_title0 <- "community"
  # srvy <-"NBS"
  # 
  # temp <- age_plot(srvy, yrs, agecomp, height, width, nickname, legend_font_size, report_title0) 
  # for (jjj in 1:length(temp)) { assign(names(temp)[jjj], temp[[jjj]]) }
  # res <- knitr::knit_child(text = knitr::knit_expand( file = paste0(dir_code, "_child_save_figtab.Rmd")), quiet = TRUE)
```
  
## fig-agecomp-[spp]-pres
  
```{r fig-agecomp-[spp]-pres, eval = spp_plot_agecomp}
  # srvy <- SRVY1
  # nickname <- paste0("fig-agecomp-", spp_file, "-pres")
  # yrs <- c(maxyr, compareyr)
  # print_n <- FALSE
  # height <- 4.5
  # width <- 5
  # legend_font_size <- 12
  # report_title0 <- "pres"
  # 
  # temp <- age_plot(srvy, yrs, agecomp, height, width, nickname, legend_font_size, report_title0) 
  # pres_size <- temp$figure_print
  # for (jjj in 1:length(temp)) { assign(names(temp)[jjj], temp[[jjj]]) }
  # res <- knitr::knit_child(text = knitr::knit_expand( file = paste0(dir_code, "_child_save_figtab.Rmd")), quiet = TRUE)
```
  
  ## tab-stats-[spp]
  
```{r tab-stats-[spp], eval = c(report_title %in% c("community", "data"))}
  nickname <- paste0("tab-stats-", spp_file)
  ### Stats table ----------------------------------------------------------------
  haul0 <- catch_haul_cruises %>% 
    dplyr::select("station", "stratum", "latitude_dd_start", "longitude_dd_start", 
                  "depth_m", "bottom_temperature_c" ,"surface_temperature_c", 
                  "survey_name", "SRVY", "year", "species_code", 
                  "weight_kg", "count", "hauljoin")
  
  temp_stat <- dplyr::left_join(
    x = haul0 %>% 
      dplyr::filter(year == maxyr) %>% 
      dplyr::select(station, SRVY) %>% 
      dplyr::distinct() %>% 
      dplyr::select(SRVY) %>% 
      table() %>% 
      data.frame() %>% 
      dplyr::rename(tot = Freq), 
    y = haul0 %>% 
      dplyr::filter(species_code %in% spp_code & year == maxyr) %>% 
      dplyr::select(station, SRVY) %>% 
      dplyr::distinct() %>% 
      dplyr::select(SRVY) %>% 
      table() %>% 
      data.frame() %>% 
      dplyr::rename(spp = Freq), 
    by = "SRVY") %>% 
    dplyr::mutate(str = paste0(spp, " of ", tot, 
                               "\n(", formatC(spp/tot*100, digits = 1, format = "f", big.mark = ","), "%)")) %>% 
    dplyr::filter(!is.na(spp))
  
### Env table ------------------------------------------------------------------
  
  temp_env <- haul0 %>% 
    dplyr::filter(SRVY %in% SRVY1 & 
                    year == maxyr & 
                    species_code %in% spp_code) %>% 
    dplyr::select(SRVY, 
                  # "Latitude (°N)" = latitude_dd_start, 
                  # "Longitude (°W)" = longitude_dd_start, 
                  "Bottom\nDepth (m)" = depth_m, 
                  "Bottom Temperature (°C)" = bottom_temperature_c, 
                  "Surface Temperature (°C)" = surface_temperature_c) %>% 
    dplyr::group_by(SRVY) %>% 
    dplyr::summarise(across(where(is.numeric), .fns = 
                              list(Min = min,
                                   Max = max))) %>%
    tidyr::pivot_longer(is.numeric,
                        names_sep='_',
                        names_to=c('variable', '.value')) %>%
    dplyr::mutate(across(dplyr::ends_with("C)"), 
                         formatC, big.mark = ",", digits = 1, format = "f"), 
                  val = ifelse(Min == Max, Min, paste0(Min, " — ", Max))) %>%
    dplyr::mutate(across(dplyr::ends_with("m)"), 
                         formatC, big.mark = ",", digits = 0, format = "f"), 
                  val = ifelse(Min == Max, Min, paste0(Min, " — ", Max))) %>%
    dplyr::relocate(variable, dplyr::ends_with(SRVY1[1])) %>% 
    dplyr::select(-Min, -Max) %>% 
    tidyr::pivot_wider(id_cols = "SRVY",
                       names_from = "variable",
                       values_from = "val")
  # tidyr::pivot_wider(id_cols = "variable",
  #                    names_from = "SRVY",
  #                    values_from = c("val"))
  
  ### Biomass table --------------------------------------------------------------
  
  yrs <- c(maxyr, compareyr)
  
  if (length(spp_code) == 1) {
    temp_bio <- biomass %>% dplyr::filter(species_code %in% spp_code)
  } else {
    temp_bio <- biomass %>% dplyr::filter(group %in% spp_print)
  }
  temp_bio <- dplyr::left_join(
    x = total_biomass %>% 
      dplyr::group_by(SRVY, year) %>% 
      dplyr::summarise(total = sum(total, na.rm = TRUE)), 
    y = temp_bio %>% 
      dplyr::filter(year %in% yrs & 
                      # species_code %in% spp_code &
                      stratum %in% 999) %>%
      dplyr::select(SRVY, year, biomass_mt, population_count, 
                    cpue_kgkm2_mean, cpue_nokm2_mean) %>% 
      dplyr::filter((biomass_mt !=0)), 
    by = c("year", "SRVY")) %>% 
    dplyr::filter(year %in% yrs) %>% 
    dplyr::group_by(SRVY, year, total) %>% 
    dplyr::summarise(biomass_mt = sum(biomass_mt, na.rm = TRUE),  
                     population_count = sum(population_count, na.rm = TRUE),  
                     cpue_kgkm2_mean = sum(cpue_kgkm2_mean, na.rm = TRUE),  
                     cpue_nokm2_mean = sum(cpue_nokm2_mean, na.rm = TRUE)) %>% 
    dplyr::ungroup() %>% 
    dplyr::mutate(print_name = spp_print)
  
  if (sum(is.na(temp_bio$print_name[temp_bio$SRVY == "NBS"])) == 
      nrow(temp_bio[temp_bio$SRVY == "NBS",])) {
    temp_bio <- temp_bio %>% 
      dplyr::filter(SRVY != "NBS")
  }
  
  if (sum(is.na(temp_bio$print_name[temp_bio$SRVY == "EBS"])) == 
      nrow(temp_bio[temp_bio$SRVY == "EBS",])) {
    temp_bio <- temp_bio %>% 
      dplyr::filter(SRVY != "EBS")
  }
  
  temp_bio1 <- data.frame()
  for (i in 1:nrow(temp_bio)) {
    
    compareyr0 <- ifelse(temp_bio$year[i] == min(yrs), min(yrs), max(yrs[yrs < temp_bio$year[i]]))
    srvy0 <- temp_bio$SRVY[i]
    temp_bio0 <- ifelse(temp_bio$year[i] == min(yrs), NA, 
                        temp_bio$biomass_mt[temp_bio$SRVY == srvy0 & temp_bio$year == compareyr0])
    
    temp_bio1  <- dplyr::bind_rows(
      temp_bio1, 
      c(
        SRVY = temp_bio$SRVY[i], 
        year = temp_bio$year[i], 
        "Population" = ifelse(is.na(temp_bio$population_count[i]), 
                              "-", 
                              xunits(temp_bio$population_count[i])), 
        "Biomass\n(t)" = ifelse(is.na(temp_bio$biomass_mt[i]), 
                                "-", 
                                paste0(xunits(temp_bio$biomass_mt[i], 
                                              val_under_x_words = NULL))), 
        "Biomass\n% Total" = dplyr::case_when(
          is.na(temp_bio$biomass_mt[i]) ~ "-", 
          paste0(formatC(x = (temp_bio$biomass_mt[i]/temp_bio$total[i])*100, 
                         digits = 1, format = "f", big.mark = ","), "%") == "0.0%" ~ "<0.01%", 
          TRUE ~ paste0(formatC(x = (temp_bio$biomass_mt[i]/temp_bio$total[i])*100, 
                                digits = 1, format = "f", big.mark = ","), "%") ), 
        "Biomass\n% Change" = dplyr::case_when(
          temp_bio$year[i] == min(yrs) ~ "-",
          is.na(temp_bio$biomass_mt[i]) ~ "-", #paste0("none caught in ", temp_bio$year[i]), 
          is.na(temp_bio0) ~ "-", #paste0("none caught in ", compareyr0), 
          temp_bio0 == 0 ~ paste0("Not caught in ", compareyr),
          abs(pchange(start = temp_bio$biomass_mt[i], end = temp_bio0, value_only = TRUE)) < 1 ~ "no change",
          TRUE ~ sub(replacement = "", pattern = "an ", 
                     x = gsub(pattern = "a ", replacement = "", 
                              x = paste0(pchange(end = temp_bio$biomass_mt[i], 
                                                 start = temp_bio0), "\nfrom ", compareyr0)) ) ))
    )
  }
  
  ### Combine temp tables --------------------------------------------------------
  
  table_raw <- temp_stat %>% 
    dplyr::select(SRVY, "Stations\nPresent" = str) %>% 
    dplyr::left_join(temp_env) %>% 
    dplyr::left_join(temp_bio1 %>% 
                       dplyr::filter(year == maxyr) %>% 
                       dplyr::select(-year)) %>% 
    dplyr::left_join(data.frame(SRVY = SRVY1, 
                                SRVY_long = stringr::str_to_title(SRVY11), 
                                Survey = gsub(" .*$", "", stringr::str_to_title(SRVY11)))) %>% 
    dplyr::select(-SRVY) %>% 
    dplyr::relocate(Survey) %>% 
    dplyr::arrange(Survey) %>% 
    dplyr::rename("Bering Sea\nSurvey" = Survey)
  
  if (sum(table_raw$`Biomass\n% of Total` == "0.0%") == nrow(table_raw)) {
    table_raw <- table_raw %>% 
      dplyr::select(-`Biomass\n% of Total`)
  }
  
  ### print table ----------------------------------------------------------------
  
  header <- paste0("Summary of catch location environmental variables and biomass and population estimates for ", 
                   spp_print, " (", spp_sci, ") in the ", 
                   ifelse(length(table_raw$`Bering Sea\nSurvey`) == 1, paste0(tolower(table_raw$`Bering Sea\nSurvey`), " Bering Sea"), SURVEY), 
                   " survey area", 
                   ifelse(length(table_raw$`Bering Sea\nSurvey`) == 1, "s", plural_surveys),". ")
  
  table_raw0 <- table_raw %>% 
    dplyr::select(-SRVY_long)
  table_print0 <- data.frame("var" = rownames(t(table_raw0))[-1], 
                             data.frame(t(table_raw0)[-1,]))  
  names(table_print0) <- c("var", stringr::str_to_title(table_raw$SRVY_long))
  rownames(table_print0) <- NULL
  table_print0[,1] <- gsub(x = table_print0[,1], pattern = "\n", replacement = " ")
  table_print0[,2] <- gsub(x = table_print0[,2], pattern = "\n", replacement = " ")
  if (ncol(table_print0) > 2) {
    table_print0[,3] <- gsub(x = table_print0[,3], pattern = "\n", replacement = " ")
  }
  table_print <- table_print0 %>% 
    flextable::flextable()  %>% 
    theme_flextable_nmfstm(row_lines = FALSE, 
                           pgwidth = full_page_portrait_width)  %>%
    flextable::bold(j = 1, part = "body") %>% 
    flextable::theme_zebra() %>% 
    flextable::vline(border = fp_border(color="grey70")) %>% 
    flextable::set_header_labels("var" = "")   %>%
    # theme_flextable_nmfstm(row_lines = FALSE,
    #                        pgwidth = full_page_portrait_width) %>%
    flextable::width(width = 2.25) %>%
    flextable::width(j = 1, width = 2) %>%
    flextable::bg(
      i = ~ (grepl(x = table_print0[,names(table_print0)[2]], pattern = "increase")), 
      bg = positive, 
      j = names(table_print0)[2]) %>% 
    flextable::bg(
      i = ~ (grepl(x = table_print0[,names(table_print0)[2]], pattern = "decrease")), 
      bg = negative, 
      j = names(table_print0)[2]) %>% 
    flextable::bg(
      i = ~ (grepl(x = table_print0[,names(table_print0)[2]], pattern = "no change")), 
      bg = neutral, 
      j = names(table_print0)[2]) 
  
  if (ncol(table_print0) > 2) {
    table_print <- table_print %>% 
      flextable::bg(
        i = ~ (grepl(x = table_print0[,names(table_print0)[3]], pattern = "increase")), 
        bg = positive, 
        j = names(table_print0)[3]) %>% 
      flextable::bg(
        i = ~ (grepl(x = table_print0[,names(table_print0)[3]], pattern = "decrease")), 
        bg = negative, 
        j = names(table_print0)[3]) %>% 
      flextable::bg(
        i = ~ (grepl(x = table_print0[,names(table_print0)[3]], pattern = "no change")), 
        bg = neutral, 
        j = names(table_print0)[3]) 
  }
  pres_stats <- table_raw
  res <- knitr::knit_child(text = knitr::knit_expand( file = paste0(dir_code, "_child_save_figtab.Rmd")), quiet = TRUE)
```
  
## tab-est-[spp]-[wt or num]
  
```{r tab-est-[spp]-[wt or num], eval = ((report_title == "data") & spp_table_cpue)}
  nickname0 <- paste0("tab-est-", spp_file, "-") 
  
  if (length(spp_code) > 1) {
    table_raw <- biomass %>%
      dplyr::filter(group %in% spp_print)
  } else {
    table_raw <- biomass %>%
      dplyr::filter(species_code %in% spp_code)
  }
  
  temp <- table_raw %>% 
    dplyr::filter(year == maxyr &
                    stratum %in% strat0) %>% 
    dplyr::select(SRVY, stratum, cpue_kgkm2_mean, cpue_kgkm2_sd, 
                  biomass_mt, biomass_sd, biomass_dw, biomass_up, 
                  cpue_nokm2_mean, cpue_nokm2_sd, 
                  population_count, population_sd, population_dw, population_up, 
                  n_weight, n_count, n_length)  %>% 
    dplyr::right_join(y = biomass %>% 
                        dplyr::filter(year == maxyr &
                                        stratum %in% strat0) %>% 
                        dplyr::select(SRVY, stratum) %>%
                        dplyr::distinct()) %>% 
    dplyr::left_join(y = data.frame(SRVY = SRVY1, 
                                    SRVY_long = stringr::str_to_title(SRVY11))) %>%
    dplyr::mutate(stratum = as.character(stratum)) %>%
    dplyr::arrange(stratum) %>% 
    dplyr::arrange(SRVY) %>% 
    dplyr::mutate(stratum = ifelse(stratum == 999, "Total", stratum))
  
  if (sum(is.na(temp$cpue_kgkm2_mean[temp$SRVY == "NBS"])) == 
      nrow(temp[temp$SRVY == "NBS",])) {
    temp <- temp %>% 
      dplyr::filter(SRVY != "NBS")
  }
  
  if (sum(is.na(temp$cpue_kgkm2_mean[temp$SRVY == "EBS"])) == 
      nrow(temp[temp$SRVY == "EBS",])) {
    temp <- temp %>% 
      dplyr::filter(SRVY != "EBS")
  }
  
  # Were lengths taken for this taxon? If not, we wont include the n_length column in the table and optomize for space
  # include_n_length <- !(sum(temp$n_length[temp$stratum == "Total"] %in% 0) == 
  #                         length(temp$n_length[temp$stratum == "Total"]))
  include_n_length <- FALSE
  
  if (sum(temp$biomass_mt[temp$stratum == "Total"] != 0, na.rm = TRUE) > 0) {
    
    if (sum(temp$biomass_mt [temp$stratum == "Total"] %in% 0, na.rm = TRUE)>0) {
      
      temp <- temp %>% 
        dplyr::filter(SRVY == temp$SRVY[temp$stratum == "Total" & 
                                          temp$biomass_mt  != 0])
    }
    
    haul_cruises_maxyr0 <- haul_cruises_maxyr %>% 
      dplyr::filter(SRVY %in% unique(temp$SRVY))
    
    for (i in 1:2) {
      # table_raw <- data.frame()
      
      if (i == 1) { # CPUE (WT/km²) and BIOMASS
        nickname <- paste0(nickname0, "wt")
        
        table_raw <- temp %>% 
          dplyr::select(SRVY, SRVY_long, stratum, 
                        cpue_kgkm2_mean, cpue_kgkm2_sd, 
                        biomass_mt, biomass_sd, biomass_dw, biomass_up, 
                        n_weight) 
        
        # if (!include_n_length) {
        #   table_raw <- table_raw %>% 
        #     dplyr::select(-n_length)
        # }
        
        if (nrow(table_raw) != 0) { # if none were caught, don't do any of this
          
          cpue_kgkm2_mean0<-find_units(unit = "kg/km²", unt = "kg/km²", dat = table_raw$cpue_kgkm2_mean[table_raw$cpue_kgkm2_mean != 0])    
          cpue_kgkm2_sd0 <- find_units(unit = "kg/km²", unt = "kg/km²", table_raw$cpue_kgkm2_sd[table_raw$cpue_kgkm2_sd != 0])
          biomass_mt0 <- find_units(unit = "t", unt = "t", table_raw$biomass_mt [table_raw$biomass_mt  != 0])
          biomass_sd0 <- find_units(unit = "t", unt = "t", table_raw$biomass_sd[table_raw$biomass_sd != 0])
          
          header <- paste0("Mean weight CPUE",cpue_kgkm2_mean0$unit_word,
                           " with standard deviation (SD;", 
                           gsub("[()]", "", cpue_kgkm2_sd0$unit_word), ")",
                           ", estimated biomass", biomass_mt0$unit_word,
                           " with SD", biomass_sd0$unit_word, 
                           ", 95% lower (LCL;", gsub("[()]", "", biomass_mt0$unit_word),
                           ") and upper (UCL;", gsub("[()]", "", biomass_mt0$unit_word),
                           ") confidence limits, and number of hauls where species were weighed for ")      
          
          table_print0 <- table_raw %>% 
            dplyr::mutate(
              cpue_kgkm2_mean = formatC(x = cpue_kgkm2_mean/cpue_kgkm2_mean0$divby, 
                                        digits = 2, 
                                        format = "f", big.mark = ","),
              cpue_kgkm2_sd = formatC(x = cpue_kgkm2_sd/cpue_kgkm2_sd0$divby, 
                                      digits = 2, 
                                      format = "f", big.mark = ","), 
              biomass_mt = formatC(x = biomass_mt/biomass_mt0$divby, 
                                   digits = ifelse(biomass_mt0$divby>1, 2, 0), 
                                   format = "f", big.mark = ",") , 
              biomass_up = formatC(x = biomass_up/biomass_mt0$divby,
                                   digits = ifelse(biomass_mt0$divby>1, 2, 0),
                                   format = "f", big.mark = ",") ,
              biomass_dw = formatC(x = biomass_dw/biomass_mt0$divby,
                                   digits = ifelse(biomass_mt0$divby>1, 2, 0),
                                   format = "f", big.mark = ",") ,
              biomass_sd = formatC(x = biomass_sd/biomass_sd0$divby, 
                                   digits = ifelse(biomass_sd0$divby>1, 2, 0), 
                                   format = "f", big.mark = ","))
          table_print0[is.na(table_print0)] <- 0
          table_print0[table_print0 == " NA"] <- "-"
          table_print0[table_print0 == "NA"] <- "-"
          table_print0$n_weight[table_print0$n_weight == 0] <- "-"
          
          table_print <- table_print0 %>% 
            dplyr::select(-SRVY) %>% 
            flextable::as_grouped_data(groups = c("SRVY_long"), columns = NULL)  %>%
            flextable::as_flextable(hide_grouplabel = TRUE) %>%
            flextable::set_header_labels(
              cpue_kgkm2_mean = paste0("CPUE mean ", ifelse(cpue_kgkm2_mean0$unit_wrd=="", "", paste0(" (",cpue_kgkm2_mean0$unit_wrd, ")"))), 
              cpue_kgkm2_sd = paste0("CPUE SD ", ifelse(cpue_kgkm2_sd0$unit_wrd=="", "", paste0("\n(",cpue_kgkm2_sd0$unit_wrd, ")"))), 
              biomass_mt = paste0("Biomass", ifelse(biomass_mt0$unit_wrd=="", "", paste0("\n(",biomass_mt0$unit_wrd, ")"))), 
              biomass_sd = paste0("Biomass SD ", ifelse(biomass_sd0$unit_wrd=="", "", paste0(" (",biomass_sd0$unit_wrd, ")"))), 
              biomass_dw = paste0("95% LCL", ifelse(biomass_mt0$unit_wrd=="", "", paste0("\n(",biomass_mt0$unit_wrd, ")"))),
              biomass_up = paste0("95% UCL", ifelse(biomass_mt0$unit_wrd=="", "", paste0("\n(",biomass_mt0$unit_wrd, ")"))),
              n_weight = "Hauls w/weights"
            ) 
        }
      } else { # CPUE No/km² and population_count
        
        nickname <- paste0(nickname0, "num")
        
        table_raw <- temp %>% 
          dplyr::select(SRVY_long, SRVY, stratum, 
                        cpue_nokm2_mean, cpue_nokm2_sd, population_dw, population_up, 
                        population_count, population_sd, n_count, n_length)
        
        if (!include_n_length) {
          table_raw <- table_raw %>% 
            dplyr::select(-n_length)
        }
        
        if (nrow(table_raw) != 0) { # if none were caught, don't do any of this
          
          cpue_nokm2_mean0 <- find_units(unit = "no/km²", unt = "no/km²", dat = table_raw$cpue_nokm2_mean[table_raw$cpue_nokm2_mean != 0])
          cpue_nokm2_sd0 <- find_units(unit = "no/km²", unt = "no/km²", table_raw$cpue_nokm2_sd[table_raw$cpue_nokm2_sd != 0])
          population_count0 <- find_units(unit = "", unt = "", table_raw$population_count[table_raw$population_count != 0])
          population_sd0 <- find_units(unit = "", unt = "", table_raw$population_sd[table_raw$population_sd != 0])
          
          header <- paste0("Mean number CPUE", cpue_nokm2_mean0$unit_word,
                           " with standard deviation (SD;", 
                           gsub("[()]", "", cpue_nokm2_sd0$unit_word), ")",
                           ", estimated population", population_count0$unit_word,
                           " with SD", population_sd0$unit_word, 
                           ", 95% lower (LCL;", gsub("[()]", "", population_count0$unit_word),
                           ") and upper (UCL;", gsub("[()]", "", population_count0$unit_word),
                           ") confidence limits, and number of hauls where species were counted for ")
          
          table_print0 <- table_raw %>% 
            dplyr::mutate(
              cpue_nokm2_mean = formatC(x = cpue_nokm2_mean/cpue_nokm2_mean0$divby, 
                                        digits = 2, 
                                        format = "f", big.mark = ","),
              cpue_nokm2_sd = formatC(x = cpue_nokm2_sd/cpue_nokm2_sd0$divby, 
                                      digits = 2, 
                                      format = "f", big.mark = ","), 
              population_count = formatC(x = population_count/population_count0$divby, 
                                         digits = ifelse(population_count0$divby>1, 2, 0), 
                                         format = "f", big.mark = ",") , 
              population_up = formatC(x = population_up/population_count0$divby,
                                      digits = ifelse(population_count0$divby>1, 2, 0),
                                      format = "f", big.mark = ",") ,
              population_dw = formatC(x = population_dw/population_count0$divby,
                                      digits = ifelse(population_count0$divby>1, 2, 0),
                                      format = "f", big.mark = ",") ,
              population_sd = formatC(x = population_sd/population_sd0$divby, 
                                      digits = ifelse(population_sd0$divby>1, 2, 0), 
                                      format = "f", big.mark = ","))
          table_print0[is.na(table_print0)] <- 0
          table_print0[table_print0 == " NA"] <- "-"
          table_print0[table_print0 == "NA"] <- "-"
          table_print0$n_count[table_print0$n_count == 0] <- "-"
          
          table_print <- table_print0 %>% 
            dplyr::select(-SRVY) %>%
            flextable::as_grouped_data(groups = c("SRVY_long"), columns = NULL)  %>%
            flextable::as_flextable(hide_grouplabel = TRUE) %>%
            flextable::set_header_labels(
              cpue_nokm2_mean = paste0("CPUE mean", ifelse(cpue_nokm2_mean0$unit_wrd=="", "", paste0(" (", cpue_nokm2_mean0$unit_wrd, ")"))), 
              cpue_nokm2_sd = paste0("CPUE SD ", ifelse(cpue_nokm2_sd0$unit_wrd=="", "", paste0("\n(", cpue_nokm2_sd0$unit_wrd, ")"))), 
              population_count = paste0("Population", 
                                        ifelse(population_count0$unit_wrd=="", "", paste0("\n(", population_count0$unit_wrd, ")"))),
              population_sd = paste0("Population SD", ifelse(population_sd0$unit_wrd=="", "", paste0(" (", population_sd0$unit_wrd, ")"))), 
              population_dw = paste0("95% LCL", ifelse(population_count0$unit_wrd=="", "", paste0("\n(", population_count0$unit_wrd, ")"))),
              population_up = paste0("95% UCL", ifelse(population_count0$unit_wrd=="", "", paste0("\n(", population_count0$unit_wrd, ")"))),
              n_count = "Hauls w/counts"
            ) 
        }
      }
      
      header <- paste0(header,
                       spp_print, 
                       ifelse(is.na(spp_sci), "", paste0(" (", spp_sci, ")")), 
                       " by stratum encountered during the ",
                       maxyr," ", SURVEY, 
                       " shelf bottom trawl survey",plural_surveys,". ", 
                       ifelse(length(setdiff(SRVY1, unique(table_raw$SRVY)))>0, 
                              paste0("This species was not encountered in the ", 
                                     maxyr, " ",
                                     haul_cruises_maxyr$SRVY_long[haul_cruises_maxyr$SRVY != unique(table_raw$SRVY)],
                                     " shelf trawl survey. "), 
                              ""))# ifelse(!include_n_length, "No lengths were collected for this taxon. ", ""))
      
      table_print <- table_print %>% 
        flextable::bold(i = ~ (stratum == "Total") ) %>%
        flextable::valign(valign = "top") %>% 
        flextable::set_header_labels(stratum = "Stratum")  %>%
        theme_flextable_nmfstm(row_lines = FALSE, 
                               body_size = 10,
                               header_size = 10,
                               pgwidth = full_page_portrait_width)  %>%
        flextable::width(width = ((full_page_portrait_width-.6-.9)/6), unit = "in") %>% # need to not account for the SRVY_long column
        flextable::width(j = 1, width = .6, unit = "in") %>%
        flextable::width(j = 2, width = .9, unit = "in") %>%
        
        # flextable::width(j = (ncol(table_print0)-1), width = .9, unit = "in") %>%
        # flextable::width(width = ((full_page_portrait_width-.4)/(ncol(table_print0)-1)), unit = "in") %>%
        # flextable::width(width = .4, unit = "in", j = c("stratum")) %>%
        flextable::align(align = "right", part = "all") %>%
        flextable::align(align = "center", part = "body", j = "stratum") %>% 
        flextable::merge_v(j = 1:2, part = "header")
      
      if (include_n_length) { # if lengths were collected, include the column
        table_print <- table_print %>%
          flextable::set_header_labels(
            n_length = "Hauls w/lengths") %>% 
          flextable::width(width = .5, unit = "in", j = "n_length") 
      }
      
      # if (length(unique(table_raw$SRVY)) > 1) {
      table_print <- table_print %>% 
        flextable::align(j = 1, i = ~ !is.na(SRVY_long), align = "left") %>%
        flextable::bold(j = 1, i = ~ !is.na(SRVY_long) ) %>%
        flextable::padding(j = 1, i = ~ is.na(SRVY_long),
                           padding.left = 7) %>% 
        flextable::hline(x = .,i = ~ (stratum == "Total"), part = "body")
      # }
      
      res <- knitr::knit_child(text = knitr::knit_expand( file = paste0(dir_code, "_child_save_figtab.Rmd")), quiet = TRUE)
    }
  }
```
  
## fig-timeseries-[spp]-prep
  
```{r, fig-timeseries-[spp]-prep, eval = TRUE}
  pcol <- viridis::mako(n = 2, begin = .2, end = .6, direction = -1)
  
  if (length(spp_code) > 1) {
    table_raw <- biomass %>%
      dplyr::filter(group %in% spp_print)
  } else {
    table_raw <- biomass %>%
      dplyr::filter(species_code %in% spp_code)
  }
  
  table_raw <- table_raw %>%
    dplyr::filter(stratum == 999) %>% 
    dplyr::select(SRVY, year, 
                  biomass_mt, population_count, 
                  biomass_up, population_up, 
                  biomass_dw, population_dw) %>% 
    tidyr::pivot_longer(cols = c(biomass_mt, population_count, 
                                 biomass_up, population_up, 
                                 biomass_dw, population_dw), 
                        names_to = "var", 
                        values_to = "val") %>% 
    dplyr::mutate(coll = dplyr::case_when(
      var == "biomass_mt" ~ "val", 
      var == "population_count" ~ "val", 
      var == "biomass_up" ~ "ci_up", 
      var == "population_up" ~ "ci_up", 
      var == "biomass_dw" ~ "ci_dw", 
      var == "population_dw" ~ "ci_dw"
    ), 
    var = dplyr::case_when(
      grepl(x = var, pattern = "biomass") ~ "biomass_mt", 
      grepl(x = var, pattern = "population") ~ "population_count")) %>% 
    tidyr::pivot_wider(id_cols = c(SRVY, year, var), 
                       names_from = coll, 
                       values_from = val) %>%   
    dplyr::left_join(y = haul_cruises %>% 
                       dplyr::select(SRVY, SRVY_long) %>% 
                       dplyr::distinct(),
                     by = "SRVY") %>%
    dplyr::mutate(
      print_name = spp_print, 
      SRVY_long0 = SRVY_long, 
      SRVY_long = stringr::str_to_title(SRVY_long), 
      y_long = dplyr::case_when(
        grepl(x = var, pattern = "biomass") ~ "Biomass", 
        grepl(x = var, pattern = "population") ~ "Population"
      ) ) %>% 
    dplyr::ungroup() 
  
  # find missing years in timeseries and re-enter them so plot breaks for missing years
  yr_missing <- data.frame()
  for (i in 1:length(unique(table_raw$SRVY_long))){
    temp <- table_raw[table_raw$SRVY_long %in% unique(table_raw$SRVY_long)[i], ]
    
    yr_missing <- yr_missing %>% 
      dplyr::bind_rows(tidyr::crossing(year = setdiff((min(temp$year):max(temp$year)),
                                                      unique(temp$year)),
                                       y_long = unique(table_raw$y_long), 
                                       # var = unique(table_raw$var), 
                                       SRVY_long = unique(table_raw$SRVY_long)[i]) ) # %>% 
    # dplyr::mutate(var = dplyr::case_when(
    #   y_long == "Biomass" ~ "biomass_mt",
    #   y_long == "Population" ~ "population_count"
    # ))
    
  }
  
  yr_missing <- yr_missing %>%
    dplyr::left_join(y = haul_cruises %>% 
                       dplyr::select(SRVY, SRVY_long) %>% 
                       dplyr::distinct() %>% 
                       dplyr::mutate(SRVY_long0 = SRVY_long, 
                                     SRVY_long = stringr::str_to_title(SRVY_long)),
                     by = "SRVY_long")
  
  a_bio <- find_units(unit = "t", 
                      unt = "t", 
                      dat = table_raw$val[table_raw$y_long == "Biomass"]) 
  
  a_pop <- find_units(unit = "", 
                      unt = "", 
                      dat = table_raw$val[table_raw$y_long == "Population"]) 
  
  table_raw <- table_raw %>% 
    dplyr::bind_rows(yr_missing) %>% 
    # dplyr::bind_rows(yr_missing %>% dplyr::mutate(var = "population_count")) %>% 
    dplyr::mutate(
      species_name = spp_print, 
      common_name = spp_print, 
      print_name = spp_print, 
      taxon = spp_taxon, 
      col = dplyr::case_when(
        SRVY_long == "Eastern Bering Sea" ~ pcol[1],
        SRVY_long == "Northern Bering Sea" ~ pcol[2]), 
      var_ = dplyr::case_when(
        y_long == "Biomass" ~ 
          paste0("Biomass", 
                 # if no bio divby or pop divby (bc then would stay on same line)
                 ifelse(a_bio$unit_word == " (t)" & a_pop$unit_word == "", 
                        "", "\n"), a_bio$unit_word), 
        y_long == "Population" ~ 
          paste0("Population", ifelse(a_pop$unit_word == "", "", "\n"), a_pop$unit_word)        
      ), 
      divby = dplyr::case_when(
        y_long == "Biomass" ~ a_bio$divby, 
        y_long == "Population" ~ a_pop$divby        
      ),
      unit_wrd = dplyr::case_when(
        y_long == "Biomass" ~ a_bio$unit_wrd, 
        y_long == "Population" ~ a_pop$unit_wrd        
      ),
      unit_word = dplyr::case_when(
        y_long == "Biomass" ~ a_bio$unit_word, 
        y_long == "Population" ~ a_pop$unit_word        
      ),
      y = val/divby, 
      y_ci_dw = ci_dw/divby, 
      y_ci_up = ci_up/divby  ) %>% 
    dplyr::arrange(desc(year))  %>% 
    dplyr::mutate(group = paste0(SRVY, "_", y_long)) %>% 
    dplyr::ungroup() %>% 
    dplyr::mutate(var = dplyr::case_when(
      y_long == "Biomass" ~ "biomass_mt",
      y_long == "Population" ~ "population_count", 
    ))
  
  table_raw1 <- table_raw
  
  timeseries_plot <- function(table_raw, table_raw_mean, nickname, height, width, legend_font_size = 10, haul_cruises) {
    
    if (length(unique(table_raw$var_)) == 1) {
      table_raw$var_ <- gsub(x = table_raw$var_, replacement = "", pattern = "\n", fixed = TRUE)
      table_raw$var_ <- gsub(x = table_raw$var_, replacement = " ", pattern = "  ", fixed = TRUE)
    }
    
    # find mean for mean line
    table_raw_mean <- table_raw %>% 
      dplyr::group_by(SRVY_long, y_long, group, var_) %>% 
      dplyr::summarise(y_mean = mean(y, na.rm = TRUE)) %>% 
      dplyr::filter(!is.na(y_mean)) %>% 
      dplyr::left_join(
        biomass %>%
          dplyr::filter(stratum == 999 &
                          year >= min(table_raw$year, na.rm = TRUE) # 1987
          ) %>% 
          dplyr::group_by(survey_definition_id) %>% 
          dplyr::summarise(minyr = min(year, na.rm = TRUE), 
                           maxyr = max(year, na.rm = TRUE)) %>% 
          dplyr::left_join(y = haul_cruises %>% 
                             dplyr::select(survey_definition_id, SRVY_long) %>% 
                             dplyr::distinct()) %>% 
          dplyr::select(-survey_definition_id) %>% 
          dplyr::mutate(SRVY_long = stringr::str_to_title(SRVY_long))) %>% 
      dplyr::ungroup()
    
    # anno<-NA
    # temp<-setdiff(x = unique(table_raw$SRVY), 
    #               y = unique(table_raw_mean$SRVY))
    # if (length(temp) != 0) {
    #   anno <- paste0("Data for this species in the\n", 
    #                  temp, 
    #                  " is too limited to plot.")
    #   
    #   col_anno <- table_raw$col[which(unique(table_raw$SRVY)==temp)]
    #   col <- table_raw$col[which(unique(table_raw$SRVY)!=temp)]
    # }
    
    figure_print <-
      # general plotting aesthetics
      ggplot2::ggplot(data = table_raw,
                      mapping = aes(x = year, 
                                    y = y, 
                                    group = group,
                                    color = SRVY_long)) +
      # plot mean line 
      ggplot2::geom_segment(
        data = table_raw_mean,
        mapping = aes(x = minyr, 
                      xend = maxyr, 
                      y = y_mean, 
                      yend = y_mean),
        alpha = .5,
        linetype = "dashed", 
        linewidth = 1.5) +
      # plot points and lines
      ggplot2::geom_line(linewidth = .5) +
      ggplot2::geom_point(size = 1.5, mapping = aes(shape = SRVY_long)) + 
      # axis aesthetics 
      # ggplot2::ggtitle(spp_print) +  # No title
      ggplot2::scale_x_continuous(
        name = "", # "Year", 
        # limits = range(yrs_plotted, na.rm = TRUE), 
        labels = scales::label_number(accuracy = 1, big.mark = ""))  +
      ggplot2::scale_y_continuous(
        name = "", # spp_print, 
        labels = scales::label_number(accuracy = 1, big.mark = ","), 
        limits = c(0, NA)) +
      # survey area color aesthetics
      ggplot2::scale_color_manual(values = pcol) +
      # plot error bars
      ggplot2::geom_errorbar(mapping = aes(ymin = y_ci_dw, ymax = y_ci_up), 
                             width = .2,
                             alpha = 0.5) + 
      # Set y axis minimum to always be 0 & remove resulting "y" label
      # ylim(0, NA) +
      # ylab(" ") +
      
      # aesthetics
      # Create & position legend title
      ggplot2::labs(color = stringr::str_to_title(spp_print)) +  # force title case
      ggplot2::labs(shape = stringr::str_to_title(spp_print)) +
      ggplot2::guides(color = guide_legend(title.position = "top",
                                           title.hjust = 0.5,
                                           title.vjust = -0.5),
                      shape = guide_legend(title.position = "top",
                                           title.hjust = 0.5,
                                           title.vjust = -0.5)) +
      ggplot2::theme( 
        strip.placement = "outside",
        strip.background = element_blank(), 
        strip.text = element_text(size = 10, face = "bold"), 
        panel.background = element_rect(fill = "white"),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.x = element_line(colour = "grey95"),
        panel.border = element_rect(fill = NA, colour = "grey20"),
        legend.text = element_text(size = legend_font_size),
        legend.background = element_rect(colour = "transparent", 
                                         fill = "transparent"),
        legend.key = element_rect(colour = "transparent",
                                  fill = "transparent"),
        axis.title = element_text(size = legend_font_size, face = "bold"),
        axis.text = element_text(size = legend_font_size),
        legend.position = "bottom", 
        legend.box = "horizontal",
        legend.box.spacing = unit(0, "pt"),
        legend.margin=margin(0, 0, 0, 0)) + 
      ggplot2::facet_grid(rows = vars(var_), 
                          scales = "free", 
                          switch = "both") 
    # if (!is.na(anno[1])) {
    #   figure_print <- figure_print +
    #     ggplot2::geom_text(x = Inf, 
    #                        y = -Inf, 
    #                        hjust = 1.2, 
    #                        vjust = -.3, 
    #                        label = anno, 
    #                        show.legend = FALSE, 
    #                        size = 4, 
    #                        fontface = "italic",
    #                        color = col_anno)
    # }
    # If there's only one survey, remove legend with color guide.
    if (length(unique(table_raw$SRVY_long)) == 1) {
      figure_print <- figure_print + ggplot2::theme(legend.position = "none")
    }
    
    temp <- table_raw %>% 
      dplyr::select(y_long, unit_word, unit_wrd) %>% 
      unique() %>% 
      dplyr::mutate(str0 = paste0(
        tolower(y_long),
        paste0(ifelse(unit_wrd == "", "", unit_word))))
    
    header <- paste0("Time series of ", 
                     spp_print,
                     ifelse(is.na(spp_sci), "",
                            paste0(" (",spp_sci,")")), " ",
                     text_list(temp$str0), 
                     " from the ", 
                     min(table_raw$year, na.rm = TRUE),"-", 
                     max(table_raw$year, na.rm = TRUE), " ", 
                     # range_text(range(table_raw$year)), " ", 
                     ifelse(length(unique(table_raw$SRVY_long0)) > 1, 
                            SURVEY, 
                            unique(table_raw$SRVY_long0)), 
                     " shelf bottom trawl survey", 
                     ifelse(length(unique(table_raw$SRVY_long0)) > 1, plural_surveys, ""),". Dashed lines represent time series average and error bars represent estimated 95% confidence intervals. ")
    
    return(list("figure_print" = figure_print, 
                "table_raw" = table_raw, 
                "header" = header, 
                "height" = height, 
                "width" = width, 
                "nickname" = nickname, 
                "table_raw_mean" = table_raw_mean, 
                "unit_wrd" = unique(table_raw$unit_wrd[table_raw$var == "biomass_mt"])))
    # res <- knitr::knit_child(text = knitr::knit_expand( file = paste0(dir_code, "_child_save_figtab.Rmd")), quiet = TRUE)
  }
  
```
  
## fig-timeseries-[spp]-data
  
```{r, fig-timeseries-[spp]-data, eval = TRUE}
  nickname <- paste0("fig-timeseries-", spp_file, "-data")
  height <- 3
  width <- full_page_portrait_width
  legend_font_size <- 10
  
  temp <- timeseries_plot(table_raw = table_raw1, table_raw_mean, nickname, height, width, legend_font_size = 10, haul_cruises)
  for (jjj in 1:length(temp)) { assign(names(temp)[jjj], temp[[jjj]]) }
  res <- knitr::knit_child(text = knitr::knit_expand( file = paste0(dir_code, "_child_save_figtab.Rmd")), quiet = TRUE)
```
  
## fig-timeseries-[spp]-comm
  
```{r, fig-timeseries-[spp]-comm, eval = TRUE}
  nickname <- paste0("fig-timeseries-", spp_file, "-comm")
  height <- 3
  width <- full_page_portrait_width
  legend_font_size <- 10
  table_raw0 <- table_raw1 %>% dplyr::filter(var == "biomass_mt")
  
  temp <- timeseries_plot(table_raw = table_raw0, table_raw_mean, nickname, height, width, legend_font_size = 10, haul_cruises)
  for (jjj in 1:length(temp)) { assign(names(temp)[jjj], temp[[jjj]]) }
  res <- knitr::knit_child(text = knitr::knit_expand( file = paste0(dir_code, "_child_save_figtab.Rmd")), quiet = TRUE)
```
  
## fig-timeseries-[spp]-pres
  
```{r, fig-timeseries-[spp]-pres, eval = TRUE}
  nickname <- paste0("fig-timeseries-", spp_file, "-pres")
  height <- 3
  legend_font_size <- 12
  table_raw0 <- table_raw1 %>% dplyr::filter(var == "biomass_mt")
  
  temp <- timeseries_plot(table_raw = table_raw0, table_raw_mean, nickname, height, width, legend_font_size = 10, haul_cruises)
  pres_timeseries <- temp$figure_print
  pres_timeseries_mean <- temp$table_raw_mean
  pres_timeseries_unit_wrd <- temp$unit_wrd
  for (jjj in 1:length(temp)) { assign(names(temp)[jjj], temp[[jjj]]) }
  res <- knitr::knit_child(text = knitr::knit_expand( file = paste0(dir_code, "_child_save_figtab.Rmd")), quiet = TRUE)
```
  
## fig-combined-[spp]-pres
  
```{r, fig-combined-[spp]-pres, eval = TRUE}
  nickname <- paste0("fig-combined-", spp_file, "-pres")
  height <-8
  width <- 10
  pres_dist1 <- pres_dist + 
    ggplot2::ggtitle("") + 
    ggplot2::guides(fill=guide_legend(title="Weight CPUE (kg/km2)")) 
  if (exists("pres_size")) {
    temp1 <- cowplot::plot_grid(pres_dist1, 
                                pres_size + 
                                  ggplot2::ggtitle("") + 
                                  ggplot2::guides(fill=guide_legend(title="")) +
                                  ggplot2::theme(legend.title=element_blank(), 
                                                 strip.text.x = element_blank(),
                                                 strip.background = element_blank()), 
                                ncol = 2, 
                                rel_widths = c(1,.5))
  } else {
    temp1 <- cowplot::plot_grid(pres_dist1, 
                                NULL, 
                                ncol = 2, 
                                rel_widths = c(1,.5))
  }
  temp2 <- cowplot::plot_grid(pres_timeseries + 
                                ggplot2::ggtitle("") + 
                                ggplot2::guides(#fill = guide_legend(title=""), 
                                  fill = "none") +
                                ggplot2::labs(color = "") + 
                                ggplot2::labs(shape = "") +
                                ggplot2::theme(legend.position = "none"), 
                              NULL,
                              # cowplot::draw_image(readPNG(paste0(dir_img, spp_file, ".png")) ),
                              ncol = 2, 
                              rel_widths = c(.8, .2)) 
  # temp2 <- ggdraw() +
  #   draw_plot(temp2) +
  #   draw_image(
  #     paste0(dir_img, spp_file, ".png"), width = 1, x = 1,
  #     hjust = 1, halign = 1, valign = 0
  #   )
  
  # then combine with the top row for final plot
  figure_print <- cowplot::plot_grid(temp1, temp2, nrow = 2, rel_heights = c(1,.7))
  figure_print <- ggdraw(add_sub(plot = figure_print, 
                                 label = paste0(pres_stats$SRVY_long, " ", spp_print, " Biomass Mean: ", 
                                                round(x = pres_timeseries_mean$y_mean, digits = 1),
                                                " ", pres_timeseries_unit_wrd, " ", maxyr, ": ",
                                                pres_stats$`Biomass\n(t)`," (",
                                                gsub(pattern = "\n", replace = " ", x = pres_stats$`Biomass\n% Change`, fixed = TRUE), ")", collapse = "\n")#, 
                                 # vpadding = grid::unit(0, "lines"),
                                 # y = 3, x = 5, hjust = 0)
  ))
  
  header = ""
  
  res <- knitr::knit_child(text = knitr::knit_expand( file = paste0(dir_code, "_child_save_figtab.Rmd")), quiet = TRUE)
```
  
```{r, eval = TRUE}
  remove("pres_dist")
  remove("pres_size")
  remove("pres_timeseries_mean")
  remove("pres_timeseries")
  remove("pres_stats")
```
  
  