---
output:
  officedown::rdocx_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, error = FALSE, message = FALSE)
```

# Introduction

## fig-survey-points
(for community highlights)

```{r fig-survey-points}
nickname <- "fig-survey-points"

header <- paste0("Map of ",maxyr," ",SURVEY," survey",plural_surveys," sampling stations. The areas enclosed within the dark and light gray lines contain the eastern and northern Bering Sea shelf stations, respectively. The dots within each area indicate station locations. Filled dots are completed stations and unfilled dots represent planned but unsampled stations.") 

height <- ifelse(SRVY == "NEBS", full_page_portrait_height, 6)
width <- full_page_portrait_width

reg_dat0 <- reg_dat
if (length(cruises_race$data_in_final == "N")>0) {
  reg_dat0 <- report_types$NEBS$reg_dat
}
reg_dat0$survey.grid <- reg_dat0$survey.grid %>% 
  # dplyr::mutate(station = ifelse(!grepl(pattern = "-", x = station), "", station)) %>% 
  dplyr::left_join(station) %>% 
  dplyr::mutate(in_maxyr = ifelse(is.na(in_maxyr), FALSE, in_maxyr))
reg_dat0$place.labels <- reg_dat0$place.labels %>% 
  dplyr::filter(type %in% c("mainland", "peninsula"))

figure <- plot_survey_stations(reg_dat = reg_dat0, 
                               survey_outline = TRUE, 
                               stratum_grid = FALSE, 
                               stratum_no = FALSE, 
                               station_pts = "pts", 
                               place_labels = TRUE, 
                               bathymetry = TRUE)

res <- knitr::knit_child(text = knitr::knit_expand( file = paste0(dir_code, "_child_save_figtab.Rmd")), quiet = TRUE)
```

## fig-survey-sample-stations

```{r fig-survey-sample-stations}
nickname <- "fig-survey-sample-stations"
header <- paste0("Stratification scheme used for data analysis of the ", maxyr," ",
                 text_list(haul_cruises_maxyr$SRVY_long),
                 " shelf bottom trawl survey", ifelse(SRVY == "NEBS", "s", ""), 
                 ". The map also depicts the stations sampled by the ",
                 text_list(paste0(vessels$vessel_ital, " (",
                                  vessels$vess_shape, ")")), 
                 ifelse(crab_resample == TRUE, " and where Bristol Bay crab resampling was conducted", ""), ". ")

height <- ifelse(SRVY == "NEBS", full_page_portrait_height, 6) # height <- 
width <- full_page_portrait_width

reg_dat0 <- reg_dat
if (length(cruises_race$data_in_final == "N")>0) {
  reg_dat0 <- report_types$NEBS$reg_dat
}

reg_dat0$survey.grid <- reg_dat0$survey.grid %>% 
  dplyr::mutate(station = STATIONID) %>% 
  dplyr::left_join(y = haul_maxyr) %>% 
  dplyr::left_join(y = vessels) %>%
  dplyr::ungroup() 

if (crab_resample){
  reg_dat0$survey.grid <- dplyr::left_join(
    x = reg_dat0$survey.grid, 
    y = haul_maxyr_crabretow %>% 
      dplyr::mutate(study = "crab_resample", 
                    study_col = nmfspalette::nmfs_cols("medgray"),
                    study_long = "Red King Crab\nResample") %>% 
      dplyr::select(station, study, study_col, study_long) %>%
      dplyr::rename(station = station) %>% 
      unique(), 
    by = ("station")) 
}

figure <- plot_survey_stations(
  reg_dat = reg_dat0, 
  survey_outline = TRUE,
  stratum_grid = TRUE, 
  stratum_no = FALSE, 
  place_labels = TRUE, 
  bathymetry = FALSE, 
  station_pts = "vess", 
  study = crab_resample) # defined in data.r

res <- knitr::knit_child(text = knitr::knit_expand( file = paste0(dir_code, "_child_save_figtab.Rmd")), quiet = TRUE)
```

## fig-survey-sample-stations-1530

```{r fig-survey-sample-stations-1530, eval = FALSE}
# eval = tow1530
nickname <- "fig-survey-sample-stations-1530"
header <- ""

width <- full_page_portrait_width

reg_dat0 <- reg_dat
if (sum(cruises_race$data_in_final == "N")>0) {
  reg_dat0 <- report_types$NEBS$reg_dat
}
reg_dat0$survey.grid <-
  dplyr::left_join(x = reg_dat0$survey.grid,
                   y = dplyr::left_join(x = haul_maxyr,
                                        y = vessels) %>%
                     dplyr::select(station, vessel_name, vess_shape))
  
    reg_dat0$survey.grid <- dplyr::left_join(
    x = reg_dat0$survey.grid, 
    y = haul_maxyr_crabretow %>% 
      dplyr::mutate(study = "15_30_minute_tows", 
                    study_col = nmfspalette::nmfs_cols("medgray"),
                    study_long = "15/30 minute tows") %>% 
      dplyr::select(station, study, study_col, study_long) %>%
      dplyr::rename(station = station) %>% 
      unique(), 
    by = ("station")) 
    
figure <- plot_survey_stations(
  reg_dat = reg_dat0, 
  stratum_grid = FALSE, 
  stratum_no = TRUE, 
  bathymetry = FALSE, 
  station_pts = "vess", 
  place_labels = TRUE, 
  study = tow1530) # defined in data.r

res <- knitr::knit_child(text = knitr::knit_expand( file = paste0(dir_code, "_child_save_figtab.Rmd")), quiet = TRUE)
```

## fig-survey-grid

```{r fig-survey-grid}

nickname <- "fig-survey-grid"

header <- paste0("Sampling grid and station identifiers for the ",maxyr," ",
                 text_list(haul_cruises_maxyr$SRVY_long),
                 " continental shelf bottom trawl survey", 
                 ifelse(SRVY == "NEBS", "s", ""), 
                 ". ", ifelse(SRVY == "NBS", "", "Corner stations (denoted by circles) are not labeled for legibility. "))

height <- ifelse(SRVY == "NEBS", full_page_portrait_height, 6)
width <- full_page_portrait_width

reg_dat0 <- reg_dat
if (length(cruises_race$data_in_final == "N")>0) {
  reg_dat0 <- report_types$NEBS$reg_dat
}
reg_dat0$survey.grid <- reg_dat0$survey.grid %>% 
  dplyr::mutate(STATIONID = ifelse(!grepl(pattern = "-", x = STATIONID), "", STATIONID))
reg_dat0$place.labels <- reg_dat0$place.labels %>% 
  dplyr::filter(type %in% c("mainland", "peninsula"))

figure <- plot_survey_stations(reg_dat = reg_dat0, 
                               stratum_grid = FALSE, 
                               stratum_no = FALSE, 
                               station_pts = "names", 
                               bathymetry = FALSE,
                               place_labels = TRUE)

res <- knitr::knit_child(text = knitr::knit_expand( file = paste0(dir_code, "_child_save_figtab.Rmd")), quiet = TRUE)
```

# Methods

## fig-vessels

```{r fig-vessels}
header <- paste0("Fishing vessels ",
                 text_list(paste0(vessels$vessel_ital[vessels$vessel_ital != "Not Surveyed"], 
                                  " (", c("left", "right"), ")")),
                 " contracted to conduct the ",maxyr," ",
                 SURVEY,
                 " bottom trawl survey.")

nickname <- "fig-vessels"

height <- 2.5
width <- full_page_portrait_width

figure <- cowplot::plot_grid(
  cowplot::ggdraw() +
    cowplot::draw_image(readPNG(paste0(dir_img, vessels$img[1])), 
                        scale = 0.9 ), 
  cowplot::ggdraw() +
    cowplot::draw_image(readPNG(paste0(dir_img, vessels$img[2])), 
                        scale = 0.9 ),  
  ncol = 2, rel_heights = c(0.1, 1))

res <- knitr::knit_child(text = knitr::knit_expand( file = paste0(dir_code, "_child_save_figtab.Rmd")), quiet = TRUE)
```

## fig-trawl-gear

```{r fig-trawl-gear}
header <- paste0("Schematic diagram of the 83-112 eastern otter trawl gear used during the ", 
                 maxyr ," ", SURVEY ," bottom trawl survey", 
                 ifelse(length(SRVY1)>1, "s", ""), ".")
footnote<- NA
nickname <- "fig-trawl-gear"
alttext <- paste0(header)
height = 8
width <- full_page_portrait_width

# Select data and make plot
figure <- 
  cowplot::ggdraw() +
  cowplot::draw_image(readPNG(paste0(dir_img, "EASTERN83-112.png")) )

res <- knitr::knit_child(text = knitr::knit_expand( file = paste0(dir_code, "_child_save_figtab.Rmd")), quiet = TRUE)
```

## fig-trawl-gear-alt
(for community highlights)

```{r fig-trawl-gear-alt}
header <- paste0("Diagram of the 83/112 Eastern trawl net.")
nickname <- "fig-trawl-gear-alt"
height <- 4
width <- 6
bg <- 'transparent'

# Select data and make plot
figure <- 
  cowplot::ggdraw() +
  cowplot::draw_image(readPNG(paste0(dir_img, "bottom_trawl_net.png")), scale = 0.9 )

res <- knitr::knit_child(text = knitr::knit_expand( file = paste0(dir_code, "_child_save_figtab.Rmd")), quiet = TRUE)
```

## tab-stratum-areas

```{r tab-stratum-areas}
header <- paste0("Stratum areas and sampling densities used during the ",maxyr,
                 " ", SURVEY ," bottom trawl survey", 
                 ifelse(length(SRVY1)>1, "s", ""),". Stratum area calculations were updated in ", 
                 strat_yr , ". ")

nickname <- "tab-stratum-areas" 

temp <- stratum %>% 
  dplyr::select(area_km2, stations_avail, stations_completed, stratum, area_name, SRVY) %>% 
  dplyr::mutate(area_name = gsub(replacement = "Shelf", x = area_name, pattern = "Domain")) 

if (length(unique(station$SRVY))>1) {
  totals_sub <- temp %>%
    dplyr::group_by(SRVY) %>%
    dplyr::summarise(
      area_km2 = sum(area_km2, na.rm = TRUE),
      stations_completed = sum(stations_completed, na.rm = TRUE), 
      stations_avail = sum(stations_avail, na.rm = TRUE)) %>%
    dplyr::mutate(area_name = "Total") 
}

totals <- temp %>% 
  dplyr::summarise(
    area_km2 = sum(area_km2, na.rm = TRUE), 
    stations_completed = sum(stations_completed, na.rm = TRUE), 
    stations_avail = sum(stations_avail, na.rm = TRUE)) %>% 
  dplyr::mutate(area_name = "Total", 
                SRVY = paste0("Z", text_list(SRVY1))) 

table_raw <- dplyr::bind_rows(
  temp, 
  if(exists("totals_sub")){totals_sub}, 
  totals) %>% 
  dplyr::mutate(
    density = round(area_km2/stations_completed, 0), 
    area_km2 = round(area_km2, digits = 0)) %>%
  dplyr::arrange(SRVY, area_name, stratum) %>% 
  dplyr::relocate(SRVY, area_name, stratum, area_km2, 
                  stations_avail, stations_completed, density) %>% 
  dplyr::mutate(SRVY = gsub(replacement = "", x = SRVY, pattern = "Z"))

table_print <- table_raw %>%
  flextable::as_grouped_data(x = ., groups = c("SRVY"), columns = NULL)  %>%
  flextable::as_flextable(font = font0, x = ., hide_grouplabel = TRUE) %>%
  flextable::compose(x = ., i = 1, j = "area_km2", part = "header",
                     value = as_paragraph("Representative\narea (km", as_sup("2"), ")")) %>%
  flextable::compose(x = ., i = 1, j = "density", part = "header",
                     value = as_paragraph("Sampling density\n(km", as_sup("2"), "/Stations successfully sampled)")) %>%  
  flextable::set_header_labels(., 
                               area_name = "",
                               stratum = "Stratum",
                               stations_avail = "Stations\nin stratum",
                               stations_completed = "Stations\nsuccessfully sampled") %>% 
  flextable::merge_v(j = "area_name") %>%
  flextable::merge_h_range(x = ., 
                           i = ~ stratum == "", 
                           j1 = "area_name", 
                           j2 = "stratum", 
                           part = "body") %>%
  flextable::valign(valign = "top") %>%
  theme_flextable_nmfstm(x = ., 
                         row_lines = FALSE, 
                         pad = 0, 
                         font0 = font0, 
                         pgwidth = full_page_portrait_width)  %>%
  flextable::align(x = ., j = c("stratum", "area_km2", "stations_completed", "density"), 
                   align = "right", part = "all")  %>% 
  flextable::bold(x = ., j = 1, i = ~ !is.na(SRVY) ) %>%
  flextable::padding(x = .,
                     j = 1, i = ~ is.na(SRVY),
                     padding.left = 5)   %>%
  flextable::hline(x = ., i = ~ !is.na(area_name), #j = SRVY, #border = fp_border(width = 3), 
                   part = "body")  %>%
  flextable::hline(x = ., i = ~ (area_name == "Total"), #j = SRVY, #border = fp_border(width = 3), 
                   part = "body", border = fp_border(width = 2)) 

res <- knitr::knit_child(text = knitr::knit_expand( file = paste0(dir_code, "_child_save_figtab.Rmd")), quiet = TRUE)
```

## tab-oto-collection-scheme

```{r tab-oto-collection-scheme-[SRVY]}
nickname <- paste0("tab-oto-collection-scheme") 

table_raw <- readxl::read_excel(path = paste0(dir_out_rawdata, "/0_collection_scheme.xlsx"), 
                                sheet = "Sheet1", 
                                skip = 1) %>% 
  dplyr::filter(year == maxyr & 
                  !is.na(oto_target)) %>% 
  dplyr::mutate(oto_target = paste0(oto_target, ifelse(oto_rules != 1, paste0("; collect when \u2265", oto_rules, " individuals caught in each haul"), ""))) %>% 
  dplyr::left_join(
    y = report_spp1 %>% 
      dplyr::select(print_name, order) %>% 
      dplyr::distinct(), 
    by = "print_name") %>% 
  dplyr::distinct() %>%
  dplyr::arrange(SRVY, oto_samp_type, order) %>% 
  dplyr::select(SRVY, print_name, oto_target, oto_samp_type)

header <- paste0("Otolith collection types and counts during the ", 
                 maxyr, " ", 
                 text_list(haul_cruises_maxyr$SRVY_long),
                 " shelf bottom trawl survey", ifelse(length(SRVY1)>1, "s", ""),".")

table_print <- table_raw %>% 
  flextable::as_grouped_data(x = ., groups = c(
    "SRVY", "oto_samp_type"), 
    columns = NULL) %>% 
  flextable::as_flextable(x = ., hide_grouplabel = TRUE) %>% 
  flextable::bold(x = ., j = 1, i = ~ !is.na(oto_samp_type) ) %>% 
  flextable::bold(x = ., j = 1, i = ~ !is.na(SRVY) ) %>% 
  flextable::set_header_labels(.,
                               print_name = "Common name", 
                               oto_target = "Target collection number per haul") %>%
  theme_flextable_nmfstm(x = ., pad = 0, 
                         font0 = font0, 
                         row_lines = TRUE, 
                         pgwidth = full_page_portrait_width)  %>%
  flextable::padding(x = .,
                     j = 1, i = ~ !is.na(oto_samp_type),
                     padding.left = 5) %>%
  flextable::padding(x = .,
                     j = 1, i = ~ (is.na(oto_samp_type) &  is.na(SRVY)),
                     padding.left = 10) %>%
  flextable::width(x = ., j = "oto_target", width = 4.5, unit = "in") %>%
  flextable::width(x = ., j = c("print_name"), width = 2) %>% 
  flextable::hline(x = ., i = ~ !is.na(oto_samp_type), 
                   border = fp_border(color = "white"), 
                   part = "body") 

res <- knitr::knit_child(text = knitr::knit_expand( file = paste0(dir_code, "_child_save_figtab.Rmd")), quiet = TRUE)
```

## tab-stomach-collection-scheme

```{r tab-stomach-collection-scheme}
nickname <- paste0("tab-stomach-collection-scheme") 

header <- paste0("Stomach collection targets during the ", 
                 maxyr, " ", 
                 text_list(paste0( 
                   haul_cruises_maxyr$SRVY_long)),
                 " shelf bottom trawl survey.")

table_raw <- readxl::read_excel(path = paste0(dir_out_rawdata, "/0_collection_scheme.xlsx"), 
                                sheet = "Sheet1", 
                                skip = 1) %>% 
  dplyr::filter(year == maxyr & !is.na(stomach_target)) %>% 
  dplyr::left_join(
    y = report_spp1 %>% 
      dplyr::select(print_name, order) %>% 
      dplyr::distinct(), 
    by = "print_name") %>% 
  dplyr::distinct() %>%
  dplyr::arrange(SRVY, stomach_target, order) %>% 
  dplyr::select(SRVY, print_name, stomach_target) %>% 
    dplyr::mutate(stomach_target = as.character(round(as.numeric(stomach_target), digits = 0))) 

table_raw <- table_raw %>%
  tidyr::pivot_wider(data = ., id_cols = c("print_name"), 
                     names_from = "SRVY", values_from = "stomach_target")

table_raw[is.na(table_raw)] <- "-"

table_print <- table_raw %>% 
  flextable::flextable() %>% 
  flextable::set_header_labels(x = .,
                               print_name = "Common name", 
                               stomach_target = "Target collection number per survey") %>%
  theme_flextable_nmfstm(x = ., 
                         pad = 0, 
                         font0 = font0, 
                         row_lines = TRUE, 
                         pgwidth = full_page_portrait_width)  %>%
  # flextable::align(x = ., j = c(SRVY1), 
  #                  align = "right", part = "all")   %>%
  flextable::width(x = ., width = (2.5/length(SRVY1)))  %>%
  flextable::width(x = ., j = "print_name", width = 4)  

res <- knitr::knit_child(text = knitr::knit_expand( file = paste0(dir_code, "_child_save_figtab.Rmd")), quiet = TRUE)
```

## tab-special-projects

```{r tab-special-projects}
nickname <- "tab-special-projects" 
places <- readxl::read_excel(path = paste0(dir_out_rawdata, "/0_special_projects.xlsx"), 
                             sheet = "affiliations", 
                             skip = 1)

table_raw <- readxl::read_excel(path = paste0(dir_out_rawdata, "/0_special_projects.xlsx"), 
                                sheet = "projects", 
                                skip = 1)  %>% 
  dplyr::filter(!is.na(`Project title`) & 
                  year == maxyr) %>% 
  dplyr::select(SRVY, `Project title`, `Principal investigator`, Agency) %>% 
  dplyr::mutate(
    SRVY = gsub(pattern = "&", x = SRVY, replacement = "and"), 
    SRVY = factor(x = SRVY, 
                  levels = c("EBS and NBS", "EBS", "NBS"), 
                  labels = c("EBS and NBS", "EBS", "NBS"), 
                  ordered = TRUE))%>%
  dplyr::arrange(SRVY, Agency, `Principal investigator`, `Project title`)

header <- paste0("Special projects and collections undertaken during the ",
                 maxyr, " ", 
                 text_list(haul_cruises_maxyr$SRVY_long), 
                 " shelf bottom trawl survey, sorted by principal investigator and agency.")

# find places
temp0 <- unlist(strsplit(x = table_raw$Agency, split = " & ", fixed = TRUE))
temp0 <- unlist(strsplit(x = temp0, split = ", ", fixed = TRUE))
temp1 <- places[places$Agency %in% 
                  unique(temp0), ]

footnote0 <- paste(paste(temp1$Agency, " - ", temp1$agency_long, sep = ""), collapse = "; ")

table_print <- table_raw %>%
  flextable::as_grouped_data(groups = c("SRVY"), columns = NULL) %>% 
  flextable::as_flextable(., hide_grouplabel = TRUE)  %>% 
  flextable::bold(x = ., j = 1, i = ~ !is.na(SRVY) ) %>%
  flextable::width(x = ., j = "Agency", width = 2, unit = "in") %>%
  flextable::width(x = ., j = "Principal investigator", width = 3, unit = "in") %>%
  flextable::width(x = ., j = "Project title", width = 4, unit = "in") %>% 
  flextable::footnote(x = ., 
                      value = as_paragraph(footnote0), 
                      ref_symbols = "1",
                      part = "header", 
                      j = "Agency", i = 1)  %>%
  theme_flextable_nmfstm(x = ., 
                         font0 = font0, 
                         pad = 0, 
                         row_lines = TRUE, 
                         pgwidth = full_page_portrait_width) %>% 
  flextable::padding(x = .,
                     j = 1, i = ~ is.na(SRVY),
                     padding.left = 5) %>% 
  flextable::hline(x = ., i = ~ !is.na(SRVY), 
                   border = fp_border(color = "white"), 
                   part = "body")

res <- knitr::knit_child(text = knitr::knit_expand( file = paste0(dir_code, "_child_save_figtab.Rmd")), quiet = TRUE)
```

## tab-ptpres-special-projects

```{r tab-ptpres-special-projects}
nickname <- "tab-ptpres-special-projects" 

header <- paste0("Special projects and collections undertaken during the ",
                 maxyr, " ", 
                 text_list(haul_cruises_maxyr$SRVY_long), 
                 " shelf bottom trawl survey, sorted by principal investigator and agency.")

table_raw <- readxl::read_excel(path = paste0(dir_out_rawdata, "/0_special_projects.xlsx"), 
                                sheet = "projects", 
                                skip = 1)  %>% 
  dplyr::filter(!is.na(`Project title`) & 
                  year == maxyr) %>% 
  dplyr::select(SRVY, #`Project Title`, `Principal investigator`, Agency, 
                nickname, group) %>% 
  dplyr::mutate(nickname = 
                  if_else((tolower(SRVY) == "EBS & NBS" | is.na(SRVY)), 
                          paste0(nickname), 
                          paste0(SRVY, " ", nickname))) %>% 
  dplyr::select(group, nickname) %>%
  dplyr::arrange(nickname) %>%
  dplyr::ungroup() %>%
  dplyr::arrange(group, #SRVY, 
                 nickname) %>% 
  dplyr::rename("Special Projects" = nickname)

table_print <- table_raw %>% 
  flextable::as_grouped_data(x = ., groups = c("group"), columns = NULL) %>% 
  flextable::as_flextable(x = ., hide_grouplabel = TRUE) %>% 
  flextable::bold(x = ., j = 1, i = ~ !is.na(group) ) %>%
  theme_flextable_nmfstm(x = ., 
                         row_lines = FALSE, 
                         font = "Arial")  %>%
  flextable::padding(x = ., 
                     j = 1, i = ~ is.na(group), 
                     padding.left = 20)

res <- knitr::knit_child(text = knitr::knit_expand( file = paste0(dir_code, "_child_save_figtab.Rmd")), quiet = TRUE)
```

# Results

## tab-ptpres-length-samples

```{r tab-ptpres-length-samples}

nickname <- paste0("tab-ptpres-length-samples") 
header <- paste0("Lengths collected during the ", maxyr, " ",
                 SURVEY, 
                 " shelf bottom trawl survey.")

table_raw <- lengths %>% 
  dplyr::left_join(report_spp1 %>% 
                     dplyr::select(species_code, order) %>% 
                     dplyr::distinct(), 
                   relationship = "many-to-many")  %>%
  dplyr::left_join(
    y = spp_info %>% dplyr::select(species_code,  common_name), 
    by = "species_code") %>%
  dplyr::filter(year %in% c(maxyr, compareyr) &
                  !(species_code %in% c(68560, 68580, 68590, 69322, 
                                        69323, 69400, 69310, 68577, 68781) ))  %>%  # no crab!
  dplyr::group_by(SRVY, year, common_name, order) %>%
  dplyr::summarise(frequency = sum(frequency, na.rm = TRUE)) %>%
  tidyr::pivot_wider(data = ., 
                     id_cols = c("common_name", "order"), 
                     names_from = c("SRVY", "year"), 
                     values_from = "frequency") %>% 
  dplyr::ungroup() %>% 
  dplyr::arrange(order) %>%
  dplyr::select(-order) 

table_print0 <- 
  dplyr::bind_rows(
    table_raw[1:18,], # first 18
    table_raw[19:nrow(table_raw),] %>%    # summed others
      dplyr::mutate(common_name = paste0("other taxa (", nrow(table_raw[21:nrow(table_raw),]), ")")) %>%
      dplyr::group_by(common_name) %>% 
      dplyr::summarise(dplyr::across(dplyr::where(is.numeric), sum, na.rm = TRUE)) %>% 
      dplyr::ungroup(),
    table_raw %>%    # total
      dplyr::mutate(common_name = "TOTAL") %>%
      dplyr::group_by(common_name) %>% 
      dplyr::summarise(dplyr::across(dplyr::where(is.numeric), sum, na.rm = TRUE)) %>%
      dplyr::ungroup())  %>% 
  dplyr::mutate(dplyr::across(dplyr::where(is.numeric), xunits, val_under_x_words = -1))

table_print0[is.na(table_print0)]<- "-"

h_r1 <- c("Common name", sapply(strsplit(x = names(table_print0)[-1], split = "_"), "[[", 1))
h_r2 <- c("Common name", sapply(strsplit(x = names(table_print0)[-1], split = "_"), "[[", 2))
std_b <- officer::fp_border(width = 2, color = "grey10")

table_print <- table_print0 %>% 
  flextable::flextable() %>%
  flextable::add_header(
    x = .,
    values = eval(parse(text = paste0("list(",
                                      text_list(paste0(names(table_print0), " = '", h_r1, "'"),
                                                sep_last = ", ", sep_last2 = ", "), ") " ) ) ),
    top = TRUE) %>%
  flextable::set_header_labels(x = .,
                               values = eval(parse(text = paste0("list(",
                                                                 text_list(paste0(names(table_print0), " = '", h_r2, "'"),
                                                                           sep_last = ", ", sep_last2 = ", "), ") " ) ) )
  ) %>% 
  theme_flextable_nmfstm(x = ., 
                         font = "Arial")  %>%
  flextable::merge_h(i = 1, part = "header") %>% 
  flextable::merge_v(j = "common_name", part = "header") %>%
  flextable::valign(valign = "top") %>%
  flextable::bold(x = ., i = ~(common_name == "TOTAL") ) %>%
  flextable::align(i = 1, j = 2:ncol(table_print0), align = "center", part = "header") %>% 
  flextable::hline(x = ., border = std_b, part = "header")  

if (SRVY == "NEBS" & 
    paste0("EBS_", compareyr) %in% names(table_raw)) {
  table_print <- table_print %>% 
    flextable::vline(j = paste0("EBS_", compareyr))
}

res <- knitr::knit_child(text = knitr::knit_expand( file = paste0(dir_code, "_child_save_figtab.Rmd")), quiet = TRUE)
```

## tab-ptpres-age-samples

```{r tab-ptpres-age-samples}
nickname <- paste0("tab-ptpres-age-samples") 
header <- paste0("Otoliths collected during the ", maxyr, " ", 
                 text_list(haul_cruises_maxyr$SRVY_long), 
                 " shelf bottom trawl survey.")

a <- report_spp1 %>% 
  dplyr::select(print_name, species_code, species_name1, plot_sizecomp, order) %>% 
  dplyr::distinct() %>% 
  dplyr::mutate(include  = ifelse(is.na(plot_sizecomp ) | isFALSE(plot_sizecomp ), 
                                  FALSE, TRUE)) %>% 
  dplyr::filter(include == TRUE) 

table_raw <- specimen %>% 
  dplyr::filter(year %in% c(maxyr, compareyr) &
                  specimen_subsample_method %in% c(19, 6, 1) & 
                  specimen_sample_type == 1) %>%
  dplyr::select(SRVY, specimen_subsample_method, species_code, year) %>% 
  dplyr::mutate(specimen_subsample_method = dplyr::case_when(
    specimen_subsample_method %in% c(1, 19) ~ "random-by-haul",
    specimen_subsample_method == 6 ~ "length/region-stratified (cm/sex/southeast and northwest regions)" )) %>%
  dplyr::left_join(
    y = spp_info %>% 
      dplyr::select(species_code, common_name), 
    by = "species_code") %>% 
  dplyr::left_join(
    y = a %>%
      dplyr::select(order, species_code) %>%
      distinct(),
    by = "species_code") %>%
  dplyr::group_by(common_name, SRVY, order, year, specimen_subsample_method) %>% 
  dplyr::summarise(ages = n()) %>% 
  dplyr::ungroup() %>% 
  tidyr::pivot_wider(id_cols = c("common_name", "order", "specimen_subsample_method"), 
                     values_from = "ages", 
                     names_from = c("SRVY", "year")) %>%
  dplyr::arrange(order) %>%
  dplyr::select(-order) %>%
  dplyr::arrange(specimen_subsample_method) %>% 
  dplyr::relocate(specimen_subsample_method) %>% 
  dplyr::ungroup()


table_print0 <- dplyr::bind_rows(
  table_raw, 
  # summed total
  table_raw %>% 
    dplyr::mutate(common_name = "TOTAL") %>% 
    dplyr::group_by(specimen_subsample_method , common_name) %>% 
    dplyr::summarise(dplyr::across(dplyr::where(is.numeric), sum, na.rm = TRUE))) %>%
  dplyr::mutate(dplyr::across(dplyr::where(is.numeric), xunits, val_under_x_words = -1))
table_print0[is.na(table_print0)] <- "-"

h_r1 <- c("Common name", sapply(strsplit(x = names(table_print0)[-(1:2)], split = "_"), "[[", 1))
h_r2 <- c("Common name", sapply(strsplit(x = names(table_print0)[-(1:2)], split = "_"), "[[", 2))
std_b <- officer::fp_border(width = 2, color = "grey10")

table_print <- table_print0 %>% 
  flextable::as_grouped_data(x = ., groups = c("specimen_subsample_method")) %>% 
  flextable::as_flextable(x = ., hide_grouplabel = TRUE) %>% 
  flextable::bold(x = ., j = 1, i = ~ !is.na(specimen_subsample_method) ) %>%
  flextable::bold(x = ., i = ~(common_name == "TOTAL") ) %>%
  flextable::add_header(
    x = .,
    values = eval(parse(text = paste0("list(",
                                      text_list(paste0(names(table_print0)[-1], " = '", h_r1, "'"),
                                                sep_last = ", ", sep_last2 = ", "), ") " ) ) ),
    top = TRUE) %>%
  flextable::set_header_labels(x = .,
                               values = eval(parse(text = paste0("list(",
                                                                 text_list(paste0(names(table_print0)[-1], " = '", h_r2, "'"),
                                                                           sep_last = ", ", sep_last2 = ", "), ") " ) ) )
  ) %>% 
  theme_flextable_nmfstm(x = ., 
                         font = "Arial")  %>%
  flextable::merge_h(i = 1, part = "header") %>% 
  flextable::merge_v(j = "common_name", part = "header") %>%
  flextable::valign(valign = "top") %>%
  # flextable::bold(x = ., 
  #                 i = c((nrow(table_print0)-1), nrow(table_print0))) %>% 
  flextable::align(i = 1, j = 2:(ncol(table_print0)-1), align = "center", part = "header") %>% 
  flextable::padding(x = ., 
                     j = 1, i = ~ is.na(specimen_subsample_method), 
                     padding.left = 20) %>%   
  flextable::hline(x = ., border = std_b, part = "header") 

if (SRVY == "NEBS") {
  table_print <- table_print %>% 
    flextable::vline(j = paste0("EBS_", compareyr))
}

res <- knitr::knit_child(text = knitr::knit_expand( file = paste0(dir_code, "_child_save_figtab.Rmd")), quiet = TRUE)
```

## fig-mean-temperature

```{r fig-mean-temperature}
# code orig from sean rohan's coldpool package! Jan 23 2021 
nickname <- "fig-mean-temperature"
header <- paste0("Average summer surface and bottom and time-series average surface and bottom (dashed lines) temperatures (°C) on the eastern Bering Sea shelf, based on data collected during standardized summer bottom trawl surveys from 1982–",maxyr,
                 ifelse(SRVY == "NEBS", 
                        paste0(" (left), and northern Bering Sea shelf based on data collected during standardized summer bottom trawl surveys (right)"), ""), 
                 ". ")

height <- 3.25
width <- full_page_portrait_width # 6.5

a <- plot_mean_temperatures(maxyr, SRVY)
for (jjj in 1:length(a)) { assign(names(a)[jjj], a[[jjj]]) }

res <- knitr::knit_child(text = knitr::knit_expand( file = paste0(dir_code, "_child_save_figtab.Rmd")), quiet = TRUE)
```

## fig-cold-pool-area

```{r fig-cold-pool-area}
header <- paste0("Annual summer cold pool extent on the eastern Bering Sea shelf, based on observations from the eastern Bering Sea bottom trawl survey. The extent of the cold pool is shown as a percentage of the total eastern Bering Sea shelf survey area. Shading denotes near-bottom temperatures \u2264 2°C, \u2264 1°C, \u2264 0°C, and \u2264 -1°C.")

footnote <- "Areas were summarized from areas in inverse distance weighted rasters."
nickname <- "fig-cold-pool-area"

height <- 3
width <- full_page_portrait_width

figure <- plot_coldpool_area(coldpool_ebs_bin_area = coldpool_ebs_bin_area, maxyr = maxyr)

res <- knitr::knit_child(text = knitr::knit_expand( file = paste0(dir_code, "_child_save_figtab.Rmd")), quiet = TRUE)
```

## fig-temperature-[st/bt]-prep

```{r fig-temperature-[st/bt]-prep}
temp <- function(yrs, 
                 row0, 
                 case, 
                 title0 = NULL) {
  
  if (case == "surface") {
    raster_nebs <- terra::rast(coldpool::nbs_ebs_surface_temperature)
    raster_ebs <- terra::rast(coldpool::ebs_surface_temperature)
    colorbar_breaks <- c(-Inf, seq(2, 14, 1), Inf)
  } else if (case == "bottom") {
    raster_nebs <- terra::rast(coldpool::nbs_ebs_bottom_temperature)
    raster_ebs <- terra::rast(coldpool::ebs_bottom_temperature)
    # colorbar_breaks <- c(-Inf, -1, 0, 1, seq(2, 8, 2), Inf)
    colorbar_breaks <- c(-Inf, seq(-1, 8, 1), Inf)
  }
  
  header <- paste0(stringr::str_to_title(case)," temperatures (°C) during the ", 
                   range_text(yrs), " ", 
                   SURVEY, " shelf bottom trawl survey",
                   ifelse(SRVY=="NEBS", "s", ""),
                   ". Years in which the mean ", case, 
                   " temperature is 1 or more standard deviations above or below the time-series mean ", case, 
                   " temperature are denoted with '+' and '-' in the upper right-hand corner of each subplot, respectively. ")
  
  # Create figure
  key.title = ifelse(case == "bottom", 
                     expression(bold("Bottom temperature (°C)")), 
                     expression(bold("Surface temperature (°C)")))
  reg_dat = reg_dat0
  if(is.null(title0)) {
  title0 = paste0("Eastern", ifelse(SRVY == "NEBS", " and northern", ""), 
                  " Bering Sea\n", 
                  case, " temperature (", range_text(yrs), ")") 
  }
  figure <- plot_temperature_facet(
    raster_nebs = raster_nebs, 
    raster_ebs = raster_ebs, 
    colorbar_breaks = colorbar_breaks, 
    yrs = yrs, 
    yrs_nbs = nbsyr[nbsyr %in% names(raster_nebs)], # in case data isn't ready yet at time of run 
    key.title = key.title, 
    reg_dat = reg_dat0, 
    row0 = row0, 
    title0 = title0, 
    temperature_zscore = TRUE) 
  
  return(list("figure" = figure, 
              "header" = header))
}
```

## fig-temperature-[st/bt]

```{r fig-temperature-[st/bt]}
height <- full_page_portrait_height
width <- full_page_portrait_width
yrs0 <- (maxyr-17):maxyr
row0 <- 3
case_yr0 <- 1:2

for (case in c("bottom", "surface")) {
  for (case_yr in case_yr0) {
    
    if (case_yr == 1) {
      yrs <- yrs0[1:(length(yrs0)/2)]
    } else if (case_yr == 2) {
      yrs <- yrs0[((length(yrs0)/2)+1):length(yrs0)]
    }
    nickname <- paste0("fig-temperature-", ifelse(case=="bottom", "bt", "st"), paste0("-", case_yr))
    a <- temp(yrs, row0, case)
    figure <- a$figure
    header <- a$header
    
    res <- knitr::knit_child(text = knitr::knit_expand( file = paste0(dir_code, "_child_save_figtab.Rmd")), quiet = TRUE)
  }
}
```

## fig-ptpres-temperature-[st/bt]

```{r fig-ptpres-temperature-[st/bt]}
height <- 8
width <- 8
yrs <- sort(unique(haul$year), decreasing = TRUE)
yrs <- yrs[yrs != 2020][1:8]
row0 <- 2
reg_dat0 <- report_types$NEBS$reg_dat

for (case in c("bottom", "surface")) {
  nickname <- paste0("fig-ptpres-temperature-", ifelse(case=="bottom", "bt", "st"))
  a <- temp(yrs, row0, case, 
            title0 = paste0("Eastern", ifelse(SRVY == "NEBS", " and northern", ""), " ",  
                   case, " temperature (", range_text(yrs), ")"))
  figure <- a$figure
  header <- a$header
  
  res <- knitr::knit_child(text = knitr::knit_expand( file = paste0(dir_code, "_child_save_figtab.Rmd")), quiet = TRUE)
}
```

## fig-nbspres-temperature-[st/bt]

```{r fig-nbspres-temperature-[st/bt]}
height <- 8
width <- 8
yrs <- sort(nbsyr, decreasing = TRUE)
row0 <- 2
reg_dat0 <- report_types$NEBS$reg_dat

for (case in c("bottom", "surface")) {
  nickname <- paste0("fig-nbspres-temperature-", ifelse(case=="bottom", "bt", "st"))
  a <- temp(yrs, row0, case)
  figure <- a$figure
  header <- a$header
  
  res <- knitr::knit_child(text = knitr::knit_expand( file = paste0(dir_code, "_child_save_figtab.Rmd")), quiet = TRUE)
}
```

## tab-specimen-samples

```{r tab-specimen-samples-}
nickname0 <- paste0("tab-specimen-samples-") 

# length data - from oracle
l <- lengths_maxyr %>% 
  dplyr::filter(!(species_code %in% c(68580, 68590, 68560))) %>%
  dplyr::select(SRVY, species_code, frequency) %>% 
  dplyr::group_by(SRVY, species_code) %>% 
  dplyr::summarise(length = sum(frequency, na.rm = TRUE)) %>% 
  dplyr::ungroup() 

# age oto data - from oracle
a <- specimen_maxyr %>% 
  dplyr::filter(!is.na(species_code) & specimen_sample_type == 1) %>%
  dplyr::select("SRVY", species_code) %>% 
  dplyr::group_by("SRVY" = SRVY, species_code) %>% 
  dplyr::summarise(age = as.numeric(n())) %>% 
  dplyr::ungroup()

# other collections not in oracle
temp <- readxl::read_excel(path = paste0(dir_out_rawdata, "/0_other_field_collections.xlsx"), 
                           sheet = "Sheet1", 
                           skip = 1) %>%
  dplyr::filter(year == maxyr) %>% 
  dplyr::select(SRVY, print_name, dplyr::starts_with("count_")) %>% 
  dplyr::select(where(~sum(!is.na(.x)) > 0)) 
names(temp) <- gsub(pattern = "count_", replacement = "", x = names(temp))

# Combine
table_raw0 <- 
  dplyr::full_join(x = l, y = a, 
                   by = c("SRVY", "species_code")) %>% 
  dplyr::left_join(x = ., 
                   y = spp_info %>% 
                     dplyr::mutate(
                       common_name = gsub(pattern = " (juvenile)", 
                                          replacement = "", x = common_name, fixed = TRUE), 
                       common_name = dplyr::case_when(
                         is.na(common_name) ~ species_name, 
                         common_name == "shorthorn (=warty) sculpin" ~ "shorthorn sculpin", 
                         TRUE ~ common_name)) %>% 
                     dplyr::select(species_code, common_name), 
                   by = "species_code") %>% 
  dplyr::group_by(SRVY, common_name) %>% 
  dplyr::summarise_if(is.numeric, sum, na.rm = TRUE) %>% 
  dplyr::ungroup() %>% 
  dplyr::full_join(x = ., 
                   y = temp, 
                   by = c("SRVY", "common_name" = "print_name")) %>% 
  dplyr::mutate(dplyr::across(where(is.numeric), ~replace(., is.na(.), 0))) %>%
  dplyr::select(-species_code) %>% 
  dplyr::arrange(SRVY, common_name) %>% 
  dplyr::filter(!grepl(pattern = " crab", x = common_name, ignore.case = TRUE))

table_raw0$common_name[is.na(table_raw0$common_name)] <- "other" # TOLEDO

table_raw0 <- 
  dplyr::bind_rows(table_raw0, 
                   table_raw0 %>% 
                     dplyr::group_by(SRVY) %>% 
                     dplyr::summarise_if(is.numeric, sum, na.rm = TRUE) %>% 
                     dplyr::mutate(common_name = "Total") ) %>% 
  dplyr::relocate(SRVY, common_name, length, age) %>% 
  dplyr::rename("length_measurements" = length,
                "otolith_age_structure_samples" = age) #%>%
# data.frame()

for (i in 1:nrow(haul_cruises_maxyr)) {
  nickname <- paste0(nickname0, haul_cruises_maxyr$SRVY[i]) 
  header <- paste0("Biological data collected during the ", maxyr, " ", 
                   haul_cruises_maxyr$SRVY_long[i],
                   " shelf bottom trawl survey. The annual crab Technical Memorandum produced by the shellfish assessment program summarizes crab samples collected during the survey. ")
  
  table_raw <- table_raw0 %>% 
    dplyr::filter(SRVY == haul_cruises_maxyr$SRVY[i]) %>% 
    dplyr::select(where(~ any(. != 0)))
  
  names(table_raw)[!(names(table_raw) %in% c("SRVY", "common_name"))] <- 
    stringr::str_to_sentence(names(table_raw)[!(names(table_raw) %in% c("SRVY", "common_name"))])
  
  names(table_raw)[!(names(table_raw) %in% c("SRVY", "common_name"))] <- 
    (gsub(pattern = "_",
          replacement = "\n", 
          x = names(table_raw)[!(names(table_raw) %in% 
                                   c("SRVY", "common_name"))], 
          fixed = TRUE))
  names(table_raw)[names(table_raw) == "Otolith\nage\nstructure\nsamples"] <- 
    "Otolith age\nstructure samples"
  names(table_raw)[names(table_raw) == "Pathobiology\nblood\nsamples"] <- 
    "Pathobiology\nblood samples"
  
  table_print <- table_raw %>% 
    dplyr::mutate(across(where(is.numeric), 
                         formatC, big.mark=",", digits = 0, format = "f")) %>% 
    dplyr::ungroup() %>% 
    dplyr::filter(SRVY == haul_cruises_maxyr$SRVY[i]) %>% 
    dplyr::select(-"SRVY") 
  
  table_print[is.na(table_print) | table_print == "0"] <- "-"
  
  table_print <- table_print %>% 
    flextable::flextable(data = .) %>%
    flextable::set_header_labels(x = .,
                                 common_name = haul_cruises_maxyr$SRVY[i]) %>% 
    flextable::bold(x = ., i = which(table_print$common_name == "Total")) %>%
    flextable::valign(valign = "top") %>%
    theme_flextable_nmfstm(x = ., 
                           pad = 0, 
                           spacing = 0.4,
                           font0 = font0, 
                           pgwidth = full_page_portrait_width) %>%
    flextable::align(x = ., j = 2:ncol(table_print), 
                     align = "right", part = "all")  %>%
    flextable::width(x = ., width = (5/(ncol(table_raw)-2)), unit = "in") %>%
    flextable::width(x = ., j = "common_name", width = 1.5, unit = "in")
  
  res <- knitr::knit_child(text = knitr::knit_expand( file = paste0(dir_code, "_child_save_figtab.Rmd")), quiet = TRUE)
}
```


## tab-species-composition

```{r tab-species-composition, eval = (SRVY == "NEBS")}
nickname <- "tab-species-composition" 
header <- paste0("Composition of fish taxa encountered in the ",
                 text_list(paste0(haul_cruises_maxyr$SRVY_long, " shelf (", 
                                  haul_cruises_maxyr$SRVY, ")"))," survey catches. ")

height <- full_page_portrait_height # 7
width <- full_page_portrait_width # 6.5

if (!("NBS" %in% catch_haul_cruises_maxyr$SRVY)) {
  table_raw <- data.frame(val = "There are no data for this table yet. ")
  table_print <- table_raw %>% flextable::flextable()
} else {
  # Select data and make plot
  table_raw <- catch_haul_cruises_maxyr %>% 
    dplyr::select(species_code, SRVY, latitude_dd_start) %>% 
    dplyr::group_by(species_code, SRVY) %>% 
    dplyr::summarise(lat_max = max(latitude_dd_start, na.rm = TRUE),
                     lat_min = min(latitude_dd_start, na.rm = TRUE)) %>%
    dplyr::mutate(above_60 = (lat_max >= 60 & lat_min >= 60)) %>%
    tidyr::pivot_wider(data = ., 
                       id_cols = species_code, 
                       names_from = SRVY, 
                       values_from = c(above_60),#, lat_min, lat_max), 
                       values_fill = NA) %>% 
    dplyr::mutate(where = dplyr::case_when(
      !is.na(EBS) & !is.na(NBS) ~ "both", 
      is.na(NBS) & !is.na(EBS)~ "ebs", 
      is.na(EBS) & !is.na(NBS) ~ "nbs")) %>% 
    dplyr::left_join(y = spp_info, 
                     by = "species_code") %>% 
    dplyr::filter(taxon == "fish") %>% 
    dplyr::ungroup() %>% 
    dplyr::select(species_code, common_name, all_of(SRVY1), where) %>% 
    dplyr::filter(!grepl(x = common_name, pattern = " unid.", fixed = TRUE) &
                    !grepl(x = common_name, pattern = " egg", fixed = TRUE) & 
                    !is.na(common_name)) %>%
    dplyr::arrange(common_name)
  
  
  temp <- table_raw %>% 
    dplyr::select(-species_code)
  
  temp1 <- temp %>% 
    dplyr::filter(where == "ebs" & 
                    !is.na(common_name)) %>% 
    dplyr::select(-where, -NBS) %>% 
    dplyr::rename(above_60 = EBS)
  
  temp2 <- temp %>% 
    dplyr::filter(where == "nbs" & 
                    !is.na(common_name)) %>% 
    dplyr::select(-where, -EBS) %>% 
    dplyr::rename(above_60 = NBS)
  
  # make the same length so they can be bound together
  if (nrow(temp1)>nrow(temp2)) {
    temp2 <- temp2 %>% 
      dplyr::bind_rows(., 
                       data.frame(common_name = rep_len(NA, (nrow(temp1)-nrow(temp2))), 
                                  report_name_scientific = NA, 
                                  above_60 = FALSE))
  } else {
    temp1 <- temp1 %>% 
      dplyr::bind_rows(., 
                       data.frame(common_name = rep_len(NA, (nrow(temp2)-nrow(temp1))), 
                                  report_name_scientific = NA, 
                                  above_60 = FALSE))
  }
  
  names(temp1) <- paste0(names(temp1), "_")
  
  temp0 <- dplyr::bind_cols(temp1, temp2)
  
  for (iii in 1:nrow(temp0)) {
    if (grepl(pattern = " unid.", x = temp0$report_name_scientific[iii])) {
      temp0$common_name[iii] <- paste0(temp0$common_name[iii], 
                                       " (", temp0$report_name_scientific[iii], ")")
      temp0$report_name_scientific[iii] <- NA
    }
    if (grepl(pattern = " unid.", x = temp0$report_name_scientific[iii])) {
      temp0$common_name_[iii] <- paste0(temp0$common_name_[iii], 
                                        " (", temp0$report_name_scientific_[iii], ")")
      temp0$report_name_scientific_[iii] <- NA
    }
  }
  
  table_print <- flextable::flextable(
    data = temp0,
    col_keys = c("dummy_ebs","dummy_nbs"))  %>%
    flextable::compose(j = "dummy_ebs", part = "body",
                       value = as_paragraph(
                         as_chunk(ifelse(!is.na(common_name_), 
                                         paste0(common_name_), ""),
                                  props = fp_text_default(bold = FALSE, font.size = 10, font.family = font0)), 
                         as_chunk(ifelse(!is.na(common_name_), 
                                         paste0(" (", common_name_, ")"), ""),
                                  props = fp_text_default(italic = TRUE, font.size = 10, font.family = font0)))) %>%  
    flextable::compose(j = "dummy_nbs", part = "body",
                       value = as_paragraph(
                         as_chunk(ifelse(!is.na(common_name), 
                                         paste0(common_name), ""),
                                  props = fp_text_default(bold = FALSE, font.size = 10, font.family = font0)), 
                         as_chunk(ifelse(!is.na(common_name), 
                                         paste0(" (", common_name, ")"), ""),
                                  props = fp_text_default(italic = TRUE, font.size = 10, font.family = font0)))) %>%  
    flextable::compose(x = ., i = 1, j = "dummy_ebs", part = "header",
                       as_paragraph("Encountered in EBS but not in NBS\nCommon Name ", 
                                    as_chunk(paste0("(Scientific Name)"),
                                             props = fp_text_default(italic = TRUE, bold = TRUE, 
                                                                     font.size = 10, font.family = font0)))) %>%  
    flextable::compose(x = ., i = 1, j = "dummy_nbs", part = "header",
                       as_paragraph("Encountered in northern Bering Sea but not in eastern Bering Sea\nCommon Name ", 
                                    as_chunk(paste0("(Scientific Name)"),
                                             props = fp_text_default(italic = TRUE, bold = TRUE, 
                                                                     font.size = 10, font.family = font0)))) %>%  
    theme_flextable_nmfstm(x = ., 
                           font0 = font0, 
                           pad = 0, 
                           row_lines = FALSE, 
                           pgwidth = full_page_portrait_width) %>%
    flextable::vline(x = ., j = "dummy_ebs", part = "all") %>%
    flextable::padding(x = ., j = "dummy_nbs", padding.left = 5, part = "all")
  
  res <- knitr::knit_child(text = knitr::knit_expand( file = paste0(dir_code, "_child_save_figtab.Rmd")), quiet = TRUE)
}
```

## tab-biomass-est-[SRVY]-[taxon]

```{r tab-biomass-est-[SRVY]-[taxon]}

temp <- function(exp0, 
                 maxyr, 
                 biomass_by_stratum0,
                 catch_haul_cruises_maxyr0,
                 total_biomass0,
                 spp_code_rnge) {
  
  confint <- function(n_haul, biomass_var) {
    out <- qt(p = 0.025, df = n_haul - 1, lower.tail = F) * sqrt(biomass_var)
    return(out)
  }
  
  biomass_by_stratum0 <- biomass_by_stratum0 %>% 
    dplyr::filter(year == maxyr)
  
  # species level --------------------------------------------------------------
  
  dat <- eval(parse( # select spp 
    text=gsub(pattern = "DATAFRAME", 
              replacement = "biomass_by_stratum0", 
              x = exp0) )) %>% 
    dplyr::ungroup() %>% 
    tidyr::separate(
      col = group0, 
      into = c("group", "taxon"), 
      sep = "_", 
      remove = FALSE) %>% 
    dplyr::select(SRVY, stratum, group, group0, taxon, biomass_mt, n_haul, biomass_var) %>% 
    dplyr::group_by(SRVY, stratum, group, group0, taxon) %>% 
    dplyr::summarise(biomass_mt = sum(biomass_mt, na.rm = TRUE), 
                     biomass_var = sum(biomass_var, na.rm = TRUE), 
                     n_haul = sum(n_haul, na.rm = TRUE), 
                     ci = confint(n_haul, biomass_var)) %>% 
    dplyr::ungroup()
  
  biomass_spp_bystrata <- dat %>%
    dplyr::group_by(SRVY, stratum, group, taxon) %>% # , n_haul
    dplyr::summarise(biomass_mt = sum(biomass_mt, na.rm = TRUE),
                     biomass_var = sum(biomass_var, na.rm = TRUE),
                     n_haul = mean(n_haul, na.rm = TRUE)) %>% 
    dplyr::mutate(ci = confint(n_haul, biomass_var))
  
  # group level --------------------------------------------------------------
  
  dat0 <- eval(parse(
    text = gsub(pattern = "DATAFRAME",
                replacement = "catch_haul_cruises_maxyr0",
                x = exp0) )) %>%
    ungroup() %>%
    tidyr::separate(
      col = group0,
      into = c("group", "taxon"),
      sep = "_",
      remove = FALSE) %>%
    dplyr::filter(year == maxyr) %>%
    dplyr::distinct(SRVY, stratum, station, group, # not strictly necessary, but helpful
                    hauljoin, species_code) %>%
    dplyr::group_by(SRVY, group) %>%
    dplyr::summarise(num = n()) # the number of hauls the group was caught in for all stratum
  
  ## find estimated total biomass by stratum for group complexes (e.g., groups with more than one line)
  biomass_group_bystrata <- dat %>%
    dplyr::filter(grepl(pattern = "_", x = group0)) %>% 
    dplyr:: group_by(SRVY, stratum, group) %>%
    dplyr::summarise(biomass_mt = sum(biomass_mt, na.rm = TRUE), 
                     biomass_var = sum(biomass_var, na.rm = TRUE), 
                     n_haul = sum(n_haul, na.rm = TRUE)) %>% # do I need to sum n_haul from all spp or sum of tows where any of those species ever occured
    dplyr::mutate(ci = confint(n_haul, biomass_var), 
                  taxon = paste0("total ", gsub("\\s*\\([^\\)]+\\)","",as.character(group)))) %>% 
    dplyr::ungroup()
  
  # total level -----------------------------------------------------------------
  
  biomass_total_bystrata <- # find estimated total biomass for all stratum for all taxon
    biomass_by_stratum0 %>% 
    dplyr::filter(eval(parse( text = spp_code_rnge))) %>% # species codes greater than 35000 are invertebrates
    dplyr::mutate(group0 = "Total") %>% 
    dplyr::ungroup() %>% 
    dplyr::select(SRVY, group0, stratum, biomass_mt, n_haul, biomass_var) %>% 
    dplyr::group_by(SRVY, group0, stratum) %>% 
    dplyr::summarise(biomass_mt = sum(biomass_mt, na.rm = TRUE), 
                     biomass_var = sum(biomass_var, na.rm = TRUE)) %>% 
    dplyr::ungroup() %>% 
    dplyr::left_join(
      y = catch_haul_cruises_maxyr0 %>% 
        dplyr::mutate(stratum = dplyr::case_when(
          (stratum == 31 | stratum == 32) ~ 30,
          (stratum == 41 | stratum == 42) | stratum == 43 ~ 40,
          (stratum == 61 | stratum == 62) ~ 60, 
          TRUE ~ as.numeric(stratum))) %>%
        dplyr::filter(eval(parse( text = spp_code_rnge))) %>% # species_code < 35000
        dplyr::group_by(year, SRVY, stratum) %>%
        dplyr::distinct(hauljoin) %>%
        dplyr::summarize(num = n()),  # number of hauls the group was caught in for all stratum,
      by = c("SRVY", "stratum")) %>% 
    dplyr::mutate(
      n_haul = ifelse(num == 1, 1, (num-1)), # ifelse require bc lumpsuckers only caught in 1 hauls (can't divide by 0)
      ci = NA, 
      taxon = NA, 
      group = "Total")
  
  out <- dplyr::bind_rows(biomass_group_bystrata, 
                          biomass_spp_bystrata,
                          biomass_total_bystrata ) %>% 
    dplyr::select(-num, -n_haul, -biomass_var) %>%
    dplyr::mutate(
      order = dplyr::case_when(
        grepl(pattern = "other ", x = taxon) ~ 2,
        grepl(pattern = "total ", x = taxon) ~ 3,
        TRUE ~ 1)) %>%
    tidyr::pivot_wider(id_cols = c("group", "taxon", "order", "SRVY"), 
                       names_from = c("stratum"), 
                       values_from = c("biomass_mt", "ci")) %>% 
    dplyr::arrange(SRVY, group, order, taxon) %>% 
    dplyr::ungroup() %>% 
    dplyr::left_join(
      y = total_biomass0, 
      by = "SRVY")
  
  out$order <- 1:nrow(out)
  out$order[grepl(pattern = "other", x = out$group, ignore.case = TRUE)] <- nrow(out)+1
  out$order[grepl(pattern = "total", x = out$group, ignore.case = TRUE)] <- nrow(out)+2
  names(out) <- gsub(pattern = "biomass_mt_", replacement = "", x = names(out))
  
  out <- out %>% 
    dplyr::mutate(CI95 = ci_999, 
                  a = "±",
                  prop = `999`/total) %>% 
    dplyr::arrange(order) %>%
    dplyr::relocate(SRVY, group, taxon, `999`, a, CI95, prop) %>% 
    dplyr::filter(`999` != 0) %>% # TOLEDO 
    dplyr::select(-order, -total, -dplyr::starts_with("ci_"))
  
  return(out)
}

FitFlextableToPage <- function(x, pgwidth = 6) {
  ft_out <- x %>% flextable::autofit()
  ft_out <- flextable::width(ft_out, width = dim(ft_out)$widths * 
                               pgwidth/(flextable::flextable_dim(ft_out)$widths))
  return(ft_out)
}

temp1 <- function(table_raw, strat, total) {
  
  footnote0 <- paste0("Total estimated biomass is ", 
                      formatC(x = total, digits = 0, format = "f", big.mark = ","), 
                      " t for fish and invertebrates in the ",  
                      unique(table_raw$SRVY), " bottom trawl survey.")
  
  table_raw0 <- table_raw %>% 
    dplyr::select(group, taxon, `999`, a, CI95, 
                  prop, 
                  all_of(strat)) %>% 
    mutate_if(is.numeric , replace_na, replace = 0) %>% 
    dplyr::mutate(
      
      # biomass_mt = ifelse(is.na(biomass_mt), "-", round(biomass_mt, digits = 0)),
      # ci = ifelse(is.na(ci), "-", round(ci, digits = 0)),
      prop = ifelse(prop < 0.0001, "<0.0001", 
                    formatC(x = prop, digits = 4, 
                            format = "f", big.mark = ",")), 
      across(where(is.numeric), 
             formatC, big.mark=",", digits = 0, format = "f"))#, 
  # across(everything(), ~replace_na(.x, "-")),
  # across(everything(), ~replace_na(.x, "-")),
  # `999` = paste0(`999`, " ", a)) %>% 
  # dplyr::select(-a)
  
  table_print <- table_raw0 %>%
    flextable::flextable(data = .)  %>%
    flextable::merge_v(x = ., j = ~ group) %>%
    flextable::merge_h_range(x = ., i = ~ is.na(taxon), 
                             j1 = "group", j2 = "taxon", part = "body") %>%
    flextable::add_header_row(x = .,
                              top = TRUE,
                              values = c("Taxon",
                                         "Estimated total biomass (t)\n± 95% confidence interval",
                                         "Proportion of total animal biomass",
                                         "Estimated biomass by stratum (t)"),
                              colwidths = c(2,3,1,length(strat)-1)) %>%
    flextable::width(x = .,  
                     width = ifelse(length(strat)>3, 0.7, 1.25),
                     unit = "in") %>%
    flextable::width(x = ., j = "prop", 
                     width = 0.8, unit = "in") %>%
    flextable::width(x = ., j = c("a"), 
                     width = 0.25, unit = "in") %>%   
    flextable::width(x = ., j = c("group"), 
                     width = 1, unit = "in") %>%    
    flextable::width(x = ., j = c("taxon"), 
                     ifelse(length(strat)>3, 1.5, 1), 
                     unit = "in") %>% 
    flextable::footnote(x = ., part = "header", i = 1, j = 5, ref_symbols = "1",
                        value = as_paragraph(footnote0)) %>%
    flextable::bold(x = ., i = ~ (grepl(pattern = "Total", x = group) )) %>%
    flextable::set_header_labels(.,
                                 "group" = "", 
                                 "taxon" = "",
                                 "999" = "", 
                                 "CI95" = "",
                                 "prop" = "") %>%
    flextable::merge_at(x = ., j = c("group", "taxon"), part = "header") %>% 
    flextable::merge_at(x = ., j = c("999", "a", "CI95"), part = "header") %>% 
    flextable::merge_at(x = ., j = c("prop"), part = "header") 
  
  row_lines <- TRUE
  pad = 0
  body_size = 10
  header_size = 10
  spacing = 0.6
  pgwidth = full_page_landscape_width
  std_b <- officer::fp_border(width = 2, color = "grey10")
  thin_b <- officer::fp_border(width = 0.5, color = "grey10") 
  
  x <- flextable::border_remove(x = table_print)
  if (row_lines == TRUE) {
    table_print <- flextable::hline(x = table_print, border = thin_b, part = "body")
  }
  
  table_print <- table_print %>% 
    flextable::hline(x = ., border = std_b, part = "header") %>% 
    flextable::hline_bottom(x = ., border = std_b, part = "body") %>% 
    flextable::bold(x = ., bold = TRUE, part = "header") %>% 
    flextable::align_text_col(x = ., align = "left", header = TRUE) %>% 
    flextable::align_nottext_col(x = ., align = "right", header = TRUE) %>% 
    flextable::padding(x = ., padding = pad, part = "all") %>% 
    flextable::font(x = ., fontname = font0, part = "all") %>% 
    flextable::fontsize(x = ., size = body_size - 2, part = "footer") %>% 
    flextable::fontsize(x = ., size = body_size, part = "body") %>% 
    flextable::fontsize(x = ., size = header_size, part = "header") %>% 
    flextable::fix_border_issues(x = .) %>% 
    flextable::align(x = ., j = c("999", "CI95", "prop",  strat), 
                     align = "right", part = "all") %>%
    flextable::align(x = ., 
                     j = c(strat), 
                     align = "center", i = 1, part = "header") %>%
    flextable::padding(padding.left = 3, x = ., j = "a", part = "body")
  
  return(list("table_raw" = table_raw, 
              "table_print" = table_print))
}


nickname0 <- "tab-biomass-est-"

for (taxon0 in c("fish", "invert")) {
  
  # # Select data and make plot
  # place species codes into groups and major species
  if (taxon0 == "fish") {
    exp0 <- ('DATAFRAME %>% dplyr::filter(species_code < 35000) %>% # species codes greater than 35000 are invertebrates
  dplyr::mutate(group0 = case_when(
    species_code == 471 ~ "Rajidae (skates)_Alaska skate",
    species_code >= 401 & 
      species_code <= 495 & 
      species_code != 471 ~ "Rajidae (skates)_other skates",
    species_code == 10210 ~ "Pleuronectidae (flatfishes)_yellowfin sole",
    species_code == 10261 ~ "Pleuronectidae (flatfishes)_northern rock sole",
    species_code == 10130 ~ "Pleuronectidae (flatfishes)_flathead sole",
    species_code == 10140 ~ "Pleuronectidae (flatfishes)_Bering flounder",
    species_code == 10285 ~ "Pleuronectidae (flatfishes)_Alaska plaice",
    species_code == 10110 ~ "Pleuronectidae (flatfishes)_arrowtooth flounder",
    species_code == 10112 ~ "Pleuronectidae (flatfishes)_Kamchatka flounder",
    species_code == 10120 ~ "Pleuronectidae (flatfishes)_Pacific halibut",
    species_code >= 10041 & 
      species_code <= 10295 & 
      species_code != 10210 &
      species_code != 10261 &
      species_code != 10130 &
      species_code != 10140 &
      species_code != 10285 &
      species_code != 10110 &
      species_code != 10112 &
      species_code != 10115 &
      species_code != 10120 ~ "Pleuronectidae (flatfishes)_other flatfish",
    species_code >= 21740 & species_code <= 21741 ~ "Gadidae (cods)_walleye pollock",
    species_code >= 21720 & species_code <= 21721 ~ "Gadidae (cods)_Pacific cod",
    species_code >= 21710 & 
      species_code <= 21737 &
      species_code != 21740 &
      species_code != 21741 &
      species_code != 21720 &
      species_code != 21721 ~ "Gadidae (cods)_other cods",
    species_code >= 20000 & species_code <= 20075 ~ "Agonidae (poachers)",
    species_code >= 21300 & species_code <= 21447 ~ "Cottidae (sculpins)",
    species_code >= 21900 & species_code <= 21935 ~ "Hexagrammidae (greenlings)",
    species_code >= 22170 & species_code <= 22199 ~ "Cyclopteridae (lumpsuckers)",
    species_code >= 22200 & species_code <= 22286 ~ "Liparidae (snailfishes)",
    species_code >= 23000 & species_code <= 23099 ~ "Osmeridae (smelts)",
    species_code >= 23800 & species_code <= 23870 ~ "Stichaeidae (blennies)", 
    species_code >= 24100 & species_code <= 24395 ~ "Zoarcidae (eelpouts)",
    species_code == 30060 ~ "Scorpaenidae (rockfishes)_Pacific ocean perch",
    species_code >= 30000 & 
      species_code <= 31550 & 
      species_code != 30060 ~ "Scorpaenidae (rockfishes)_other rockfish",
    TRUE ~ "Other"))')
    
    spp_code_rnge = "species_code < 35000"
    
  } else {
    exp0 <- ('DATAFRAME %>% dplyr::filter(species_code >= 40000 & 
                  species_code < 99991) %>% # groups greater than 99991 are empty shells, empty barnacles
  dplyr::mutate(group0 = dplyr::case_when(
    species_code >= 66000 & species_code <= 67499 ~ "Crustacea_shrimps",
    species_code >= 60000 & species_code <= 65999 ~ "Crustacea_other crustaceans",
    species_code >= 67500 & species_code <=	67999 ~ "Crustacea_other crustaceans", 
    species_code >= 69550	& species_code <= 68999 ~ "Crustacea_other crustaceans",
    species_code >= 71000 & species_code <= 73999 ~ "Mollusca_Gastropoda (snails)",
    species_code >= 74000 & species_code <= 75799 ~ "Mollusca_Pelecypoda (bivalves)",
    species_code >= 78500 & species_code <= 79600 ~ "Mollusca_squids",
    species_code >= 78010 & species_code <= 78499 ~ "Mollusca_octopuses",
    species_code >= 70000	& species_code <= 70999	~ "Mollusca_other mollusks",
    species_code >= 78000 & species_code <=	78009 ~ "Mollusca_other mollusks",
    species_code >= 80000	& species_code <= 82499 ~ "Echinodermata_Asteroidea (sea stars)",
    species_code >= 83000	& species_code <= 83701 ~ "Echinodermata_Ophiuroidea (brittle stars)",
    species_code >= 83800 & species_code <= 83701 ~ "Echinodermata_Ophiuroidea (brittle stars)",
    species_code >= 82500	& species_code <= 82749 ~ "Echinodermata_Echinoidea (sea urchins)",
    species_code >= 85000 & species_code <= 85999 ~ "Echinodermata_Holothuroidea (sea cucumbers)",
    species_code >= 98000	& species_code <= 99909 ~ "Ascidiacea",
    species_code >= 91000 & species_code <=	91999 ~ "Porifera (sponges)",
    species_code >= 40000	& species_code <= 44999 ~ "Coelenterata",
    species_code >= 45000	& species_code <= 59999 ~ "Other",
    species_code >= 92000	& species_code <= 97999 ~ "Other",
    species_code >= 99990 & species_code <=	99992 ~ "Other",
    species_code >= 77011 & species_code <= 77012 ~ "Other",
    species_code == 99987 ~ "Porifera (sponges)",
    TRUE ~ "Other"))')
    spp_code_rnge = "species_code >= 40000 & species_code < 99991"
  }
  
  table_raw1 <- temp(exp0 = exp0, 
                     maxyr = maxyr, 
                     biomass_by_stratum0 = biomass %>% 
                       dplyr::mutate(stratum = dplyr::case_when(
                         (stratum == 31 | stratum == 32) ~ 30,
                         (stratum == 41 | stratum == 42) | stratum == 43 ~ 40,
                         (stratum == 61 | stratum == 62) ~ 60, 
                         TRUE ~ as.numeric(stratum))) %>%
                       dplyr::group_by(year, SRVY, stratum, common_name, taxon, species_code) %>%
                       dplyr::summarize(biomass_mt = sum(biomass_mt, na.rm = TRUE),  
                                        biomass_var = sum(biomass_var, na.rm = TRUE), 
                                        population_count = sum(population_count, na.rm = TRUE), 
                                        population_var = sum(population_var, na.rm = TRUE), 
                                        n_haul = sum(n_haul, na.rm = TRUE)) %>% 
                       dplyr::ungroup(),
                     catch_haul_cruises_maxyr0 = catch_haul_cruises_maxyr,
                     total_biomass0 = total_biomass %>% 
                       dplyr::filter(year == maxyr &
                                       taxon == taxon0) %>% 
                       dplyr::select(total, SRVY), 
                     spp_code_rnge = spp_code_rnge)
  
  for (i in 1:nrow(haul_cruises_maxyr)) {
    
    header <- paste0("Biomass estimates (t) for major ", 
                     ifelse(taxon0 =="invert", "invertebrate", "fish") ,
                     " taxa collected during the ", 
                     maxyr, " ", 
                     haul_cruises_maxyr$SRVY_long[i],
                     " shelf bottom trawl survey.")
    
    nickname <- paste0(nickname0, haul_cruises_maxyr$SRVY[i], "-", taxon0) 
    
    table_raw0 <- table_raw1 %>% 
      janitor::remove_empty(which = "cols")
    
    strat <- strat0[strat0 %in% names(table_raw0)]
    strat = strat[strat %in% report_types[[haul_cruises_maxyr$SRVY[i]]]$strat0]
    
    a <- temp1(table_raw = table_raw0 %>% 
                 dplyr::filter(SRVY == haul_cruises_maxyr$SRVY[i]), 
               strat = strat, 
               total = total_biomass %>% 
                 dplyr::filter(year == maxyr &
                                 SRVY == haul_cruises_maxyr$SRVY[i]) %>% 
                 dplyr::select(total) %>% 
                 unlist() %>% 
                 sum())
    
    table_raw <- a$table_raw
    table_print <- a$table_print
    
    res <- knitr::knit_child(text = knitr::knit_expand( file = paste0(dir_code, "_child_save_figtab.Rmd")), quiet = TRUE)
  } 
}
```

## tab-majortaxa-pchange-[SRVY]

```{r tab-majortaxa-pchange-[SRVY]}

nickname0 <- "tab-majortaxa-pchange-" 
yrs <- nbsyr

table_raw0 <- 
  dplyr::left_join(
    y = biomass %>% 
      dplyr::filter(stratum == 999 & 
                      SRVY %in% SRVY1 &
                      year %in% yrs) %>% 
      dplyr::select(species_code, year, SRVY, biomass_mt), 
    x = report_spp1 %>% 
      dplyr::select(print_name, species_name = species_name1, species_code, taxon, table_bio_spp), 
    relationship = "many-to-many",
    by = c("species_code")) %>%
  dplyr::filter(table_bio_spp & 
                  !is.na(print_name) & 
                  !is.na(year)) %>%
  dplyr::group_by(print_name, SRVY, year, taxon) %>% 
  dplyr::summarise(biomass_mt = sum(biomass_mt, na.rm = TRUE)) %>% 
  dplyr::ungroup() %>%
  tidyr::pivot_wider(id_cols = c(SRVY, print_name, taxon), 
                     names_from = year, 
                     values_from = biomass_mt) %>% 
  dplyr::mutate(
    print_name = gsub(pattern = "smelts (*Osmeridae*) include eulachon, capelin, and rainbow smelt",
                      replacement = "smelts",
                      x = print_name, fixed = TRUE))

table_raw0$maxyr <- unlist(table_raw0[names(table_raw0) %in% maxyr])
table_raw0$compareyr <- unlist(table_raw0[names(table_raw0) %in% compareyr])

table_raw0 <- table_raw0 %>% 
  dplyr::mutate(
    change = pchange(start = compareyr, end = maxyr, value_only = TRUE), 
    # change = pchange(start = maxyr, end = compareyr, value_only = TRUE), 
    dplyr::across(where(is.character), gsub, pattern = "NA", replacement = ""), 
    change0 = change,
    change = paste0(formatC(x = change, big.mark=",", digits = 1, format = "f"), "%") ) %>% 
  dplyr::ungroup()  %>%
  dplyr::arrange(desc(change0)) 

table_raw  <- table_raw0

table_print0 <- table_raw %>% 
  dplyr::mutate(
    dplyr::across(dplyr::starts_with("20"), formatC, big.mark=",", digits = 0, format = "f"), 
    dplyr::across(dplyr::starts_with("20"), gsub, pattern = "NA%", replacement = ""), 
    dplyr::across(dplyr::ends_with("yr"), formatC, big.mark=",", digits = 0, format = "f"), 
    dplyr::across(dplyr::ends_with("yr"), gsub, pattern = "NA%", replacement = "") , 
    dplyr::across(dplyr::everything(), gsub, pattern = "NA", replacement = "-") )  %>%
  dplyr::filter(!is.na(change0)) %>% 
  dplyr::relocate(print_name, as.character(yrs))

for (i in 1:c(nrow(haul_cruises_maxyr))) {
  nickname <- paste0(nickname0, haul_cruises_maxyr$SRVY[i]) 
  table_raw <- table_raw0
  header <- paste0(
    "Total estimated biomass in metric tons (t) and the percent change between the ",
    compareyr," and ",maxyr," ", 
    haul_cruises_maxyr$SRVY_long[i], 
    ' shelf bottom trawl surveys for predominant fish and invertebrate taxa. ') 
  # Crab data are summarized under other crabs and discussed in detail in the annual crab Technical Memorandum produced by the Shellfish Assessment Program. 
  
  table_print <- table_print0  %>% 
    dplyr::filter(SRVY == haul_cruises_maxyr$SRVY[i]) %>% 
    dplyr::select(-SRVY, -change0) %>%
    flextable::flextable(data = ., 
                         col_keys = c("print_name",
                                      # "dummy", 
                                      nbsyr, 
                                      "change")) %>%
    # flextable::compose(j = "dummy",
    #                    value = as_paragraph(as_i(species_name_ital), species_name_noital, " ", spp)) %>%
    flextable::color(color = "red", # https://stackoverflow.com/questions/57474647/italic-and-color-in-an-r-flextable
                     i = ~ grepl(pattern = "-", x = change), 
                     j = "change") %>% 
    flextable::width(x = ., j = "change", width = 1) %>% 
    flextable::set_header_labels(.,
                                 print_name = "Common name", 
                                 dummy = "Scientific name", 
                                 change = paste0("Change (", maxyr, ", ", compareyr, ")" )) %>% 
    theme_flextable_nmfstm(x = ., 
                           font0 = font0, 
                           pad = 0, 
                           row_lines = FALSE, 
                           pgwidth = full_page_portrait_width) %>% 
    flextable::align(x = ., part = "all", align = "right") %>%
    flextable::align(x = ., part = "all", align = "left", j = c("print_name"))
  
  res <- knitr::knit_child(text = knitr::knit_expand( file = paste0(dir_code, "_child_save_figtab.Rmd")), quiet = TRUE)
}
```

## tab-est-spp-[SRVY]

```{r tab-est-spp-[SRVY]}
nickname0 <- paste0("tab-est-spp-") 

temp <- biomass %>% 
  dplyr::filter(year == maxyr &
                  stratum == 999) %>% 
  dplyr::select(species_code, SRVY, 
                cpue_kgkm2_mean, cpue_kgkm2_sd, 
                biomass_mt, biomass_sd, #upperb, lowerb, 
                cpue_nokm2_mean, cpue_nokm2_sd, 
                population_count, population_sd, # upperp, lowerp, 
                n_weight) %>%# n_haul, n_count, n_length
  dplyr::left_join(
    x = ., 
    y = report_spp1 %>% 
      dplyr::select(species_code, print_name, order, taxon), 
    by = "species_code") %>% 
  dplyr::filter(taxon == "fish" &
                  (n_weight != 0# & n_count != 0 & n_length != 0
                  ) & # if there were none in that survey, don't include
                  order > 0) %>% 
  dplyr::arrange(order) %>% 
  dplyr::select(-species_code, -order, -taxon) %>% 
  dplyr::relocate(print_name)

type <- c("wt", "num")
for (i in 1:2) {
  
  nickname <- paste0(nickname0, type[i]) 
  
  if (i == 1){ # CPUE (WT/HA) and BIOMASS
    
    header <- paste0("Mean CPUE by weight (kg/ha) with standard deviation, and estimated biomass (t) with standard deviation and 95% lower (LCL) and upper (UCL) confidence limits for common groundfish species for the ",
                     maxyr," ", text_list(paste0(SRVY1), 
                                          # text_list(paste0( 
                                          #   haul_cruises_maxyr$SRVY, " (",
                                          #   haul_cruises_maxyr$stations_completed,
                                          #   " stations completed)")),
                                          " shelf bottom trawl survey."))
    
    table_raw <- temp %>% 
      dplyr::select(print_name, SRVY, 
                    cpue_kgkm2_mean, cpue_kgkm2_sd, 
                    biomass_mt, biomass_sd, #lowerb, upperb, 
                    # n_haul, 
                    n_weight#, n_count, n_length
      ) 
    
    table_print <- table_raw %>% 
      dplyr::mutate(cpue_kgkm2_mean = formatC(x = cpue_kgkm2_mean, 
                                              digits = 2, 
                                              format = "f", big.mark = ","), 
                    cpue_kgkm2_sd = formatC(x = cpue_kgkm2_sd, 
                                            digits = 2, 
                                            format = "f", big.mark = ","), 
                    biomass_mt = formatC(x = biomass_mt, 
                                         digits = 0, 
                                         format = "f", big.mark = ",") , 
                    # upperb = formatC(x = upperb, 
                    #                  digits = 0, 
                    #                  format = "f", big.mark = ",") , 
                    # lowerb = formatC(x = lowerb, 
                    #                  digits = 0, 
                    #                  format = "f", big.mark = ",") , 
                    biomass_sd = formatC(x = biomass_sd, 
                                         digits = 0, 
                                         format = "f", big.mark = ","))
    
    if (SRVY == "NEBS"){
      table_print <- table_print %>% 
        flextable::flextable(data = .) %>% 
        flextable::set_header_labels(
          x = ., 
          print_name = "Species", 
          SRVY = "Shelf area", 
          cpue_kgkm2_mean = paste0("Mean CPUE (kg/ha)"), 
          cpue_kgkm2_sd = paste0("SD CPUE"), 
          biomass_mt = paste0("Estimated\nBiomass"), 
          biomass_sd = paste0("SD Biomass"), 
          # lowerb = paste0("95% LCL"), 
          # upperb = paste0("95% UCL"), 
          # n_haul = "Total hauls", 
          n_weight = "Hauls with\nweights"#, 
          # n_count = "Hauls with\ncounts", 
          # n_length = "Hauls with\nlengths"
        ) 
    } else {
      table_print <- table_print %>% 
        dplyr::select(-SRVY) %>%
        flextable::flextable(data = .) %>% 
        flextable::set_header_labels(
          x = ., 
          print_name = "Species", 
          # SRVY = "Shelf area", 
          cpue_kgkm2_mean = paste0("Mean CPUE (kg/ha)"), 
          cpue_kgkm2_sd = paste0("SD CPUE"), 
          biomass_mt = paste0("Estimated\nBiomass"), 
          biomass_sd = paste0("SD Biomass"), 
          # lowerb = paste0("95% LCL"), 
          # upperb = paste0("95% UCL"), 
          # n_haul = "Total hauls", 
          n_weight = "Hauls with\nweights"#, 
          # n_count = "Hauls with\ncounts", 
          # n_length = "Hauls with\nlengths"
        ) 
    } 
    
  } else { # CPUE No/HA and population_count
    
    header <- paste0("Mean CPUE by number (no./ha) with standard deviation, and estimated population with standard deviation ", 
                     # "and 95% lower (LCL) and upper (UCL) confidence limits ",
                     "for other common groundfish species for the ", 
                     maxyr," ",
                     text_list(paste0(haul_cruises_maxyr$SRVY_long, 
                                      " shelf (", 
                                      haul_cruises_maxyr$SRVY, "; ",
                                      haul_cruises_maxyr$stations_completed,
                                      " stations completed)")),
                     " trawl surveys.")
    
    table_raw <- temp %>% 
      dplyr::select(print_name, SRVY, 
                    cpue_nokm2_mean, cpue_nokm2_sd, 
                    population_count, population_sd, #lowerp, upperp, 
                    # n_haul, 
                    n_weight#, n_count, n_length
      )
    
    # population_count0 <- find_units(unit = "", unt = "", dat = table_raw$population_count)
    # population_sd0 <- find_units(unit = "", unt = "", dat = table_raw$population_sd)
    
    table_print <- table_raw %>% 
      dplyr::mutate(cpue_nokm2_mean = formatC(x = cpue_nokm2_mean, 
                                              digits = 2, 
                                              format = "f", big.mark = ","),
                    cpue_nokm2_sd = formatC(x = cpue_nokm2_sd, 
                                            digits = 2, 
                                            format = "f", big.mark = ","), 
                    population_count = formatC(x = population_count, 
                                               digits = 0, 
                                               format = "f", big.mark = ",") , 
                    # upperp = formatC(x = upperp, 
                    #                  digits = 0, 
                    #                  format = "f", big.mark = ",") , 
                    # lowerp = formatC(x = lowerp, 
                    #                  digits = 0, 
                    #                  format = "f", big.mark = ",") , 
                    population_sd = formatC(x = population_sd, 
                                            digits = 0, 
                                            format = "f", big.mark = ","))
    
    if (SRVY == "EBS") {
      table_print <- table_print %>% 
        dplyr::select(-SRVY) %>%
        flextable::flextable(data = .) %>% 
        flextable::set_header_labels(
          x = ., 
          print_name = "Species", 
          # SRVY = "Shelf area", 
          cpue_nokm2_mean = paste0("Mean CPUE (no/ha)"), 
          cpue_nokm2_sd = paste0("SD CPUE"), 
          population_count = paste0("Estimated\npopulation"), 
          population_sd = paste0("SD population"), 
          # lowerp = paste0("95% LCL"), 
          # upperp = paste0("95% UCL"), 
          # n_haul = "Total hauls", 
          n_weight = "Hauls with\nweights"#, 
          # n_count = "Hauls with\ncounts", 
          # n_length = "Hauls with\nlengths"
        ) 
    } else {
      table_print <- table_print %>% 
        flextable::flextable(data = .) %>% 
        flextable::set_header_labels(
          x = ., 
          print_name = "Species", 
          SRVY = "Shelf area", 
          cpue_nokm2_mean = paste0("Mean CPUE (no/ha)"), 
          cpue_nokm2_sd = paste0("SD CPUE"), 
          population_count = paste0("Estimated\npopulation"), 
          population_sd = paste0("SD population"), 
          # lowerp = paste0("95% LCL"), 
          # upperp = paste0("95% UCL"), 
          # n_haul = "Total hauls", 
          n_weight = "Hauls with\nweights"#, 
          # n_count = "Hauls with\ncounts", 
          # n_length = "Hauls with\nlengths"
        ) 
    }
  }
  
  
  table_print <- table_print %>% 
    flextable::width(x = ., j = "print_name", width = 3) %>%
    # flextable::width(x = ., j = "SRVY", width = 0.5) %>%
    flextable::merge_v(x = ., target = "print_name", 
                       j = "print_name", part = "body") %>% 
    flextable::valign(valign = "top") %>%  
    theme_flextable_nmfstm(x = ., 
                           font0 = font0, 
                           pad = 0, 
                           row_lines = TRUE, 
                           pgwidth = full_page_portrait_width) %>%
    flextable::align(x = ., align = "right", part = "all") %>%
    flextable::align(x = ., j = c("print_name"), #, "SRVY"
                     align = "left", part = "all") #%>%
  # flextable::hline(x = ., i = 1, part = "header")
  
  res <- knitr::knit_child(text = knitr::knit_expand( file = paste0(dir_code, "_child_save_figtab.Rmd")), quiet = TRUE)
}
```


## tab-biomass-pchange-ptpres

```{r tab-biomass-pchange-ptpres}

nickname <- "tab-biomass-pchange-ptpres"
header <- paste0("Biomass and abundance change for major species in ", 
                 maxyr, " and ", compareyr," ", SURVEY, 
                 " shelf bottom trawl survey.")

table_raw <- biomass %>%
  dplyr::left_join(
  #   x = biomass, 
    y = report_spp1 %>%
      dplyr::filter(!is.na(order) & table_bio_portion ) %>%
      dplyr::select(species_code, order) %>%
      dplyr::distinct(),
    by = "species_code") %>%
  dplyr::filter(year %in% c(maxyr, compareyr) &
                  stratum == 999 & 
                  !is.na(order) &
                  !is.na(common_name)
                  ) %>% 
  dplyr::group_by(common_name, year, SRVY, order) %>% 
  dplyr::summarise(biomass = sum(biomass_mt, na.rm = TRUE), 
                   population = sum(population_count, na.rm = TRUE)) %>% 
  # calculate pchange
  dplyr::mutate(year0 = ifelse(year == maxyr, "maxyr", "compareyr")) %>% 
  tidyr::pivot_wider(id_cols = c("order", "common_name", "SRVY"), 
                     names_from = "year0", 
                     values_from = c("biomass", "population")) %>% 
  dplyr::mutate(
    biomass_pchange = pchange(end = biomass_maxyr, 
                              start = biomass_compareyr, 
                              value_only = TRUE), 
    population_pchange = pchange(end = population_maxyr, 
                                 start = population_compareyr, 
                                 value_only = TRUE), 
    population_maxyr = population_maxyr/1000, 
    population_compareyr = population_compareyr/1000, 
    dplyr::across(dplyr::where(is.numeric), formatC, format = "f", big.mark = ",", digits = 0), 
    dplyr::across(dplyr::ends_with("_pchange"), gsub, pattern = "-0", replacement = "0"), 
    dplyr::across(dplyr::ends_with("yr"), gsub, pattern = "NA", replacement = ""), 
    biomass_maxyr = paste0(biomass_maxyr, "", ifelse(biomass_pchange %in% c("NA"), "", paste0(" (", biomass_pchange, "%)"))), 
    population_maxyr = paste0(population_maxyr, ifelse(population_pchange %in% c("NA"), "", paste0(" (", population_pchange, "%)"))), 
    order = as.numeric(order), 
    biomass = paste0(biomass_compareyr, "\n", biomass_maxyr), 
    population = paste0(population_compareyr, "\n", population_maxyr), 
    year = paste0(compareyr, "\n", maxyr)) %>% 
  dplyr::select(order, common_name, SRVY, year, biomass, population) %>%
  # tidyr::pivot_longer(names_to = "var", 
  #                     values_to = "val", 
  #                     cols = c("biomass_compareyr", "population_compareyr", "biomass_maxyr", "population_maxyr")) %>% 
  # dplyr::mutate(year = dplyr::case_when(
  #   grepl(x = var, pattern = "pchange") ~ 1, 
  #   grepl(x = var, pattern = "maxyr") ~ maxyr, 
  #   grepl(x = var, pattern = "compareyr") ~ compareyr), 
  #   var = sapply((strsplit(x = var, split = "_")),"[[",1)) %>% 
  # # final format
  tidyr::pivot_wider(id_cols = c("order", "common_name", "year"),
                     names_from = c("SRVY"),
                     values_from = c("biomass", "population")) %>%
  dplyr::arrange((order)) %>%
  dplyr::select(-order) %>%
  dplyr::ungroup() %>% 
  dplyr::relocate(common_name, year, dplyr::ends_with("_EBS"), dplyr::ends_with("_NBS"))

h_r1 <- rep_len(x = " ", length.out = ncol(table_raw))
h_r1[grepl(pattern = "EBS", x = names(table_raw))] <- "EBS"
h_r1[grepl(pattern = "NBS", x = names(table_raw))] <- "NBS"

h_r2 <- stringr::str_to_sentence(names(table_raw))
h_r2 <- gsub(pattern = "_", replacement = " ", x = h_r2)
h_r2[grepl(pattern = "Biomass", x = h_r2)] <- "Biomass (mt)"
h_r2[grepl(pattern = "Population", x = h_r2)] <- "Population (x1,000)"

table_print <- table_raw %>% 
  flextable::flextable()  %>%  
  theme_flextable_nmfstm(x = ., 
                         font0 = font0, 
                         pad = 0, 
                         row_lines = TRUE, 
                         pgwidth = full_page_landscape_width) %>% 
  flextable::merge_v(j = "common_name", part = "body") %>%
  flextable::bold(x = ., j = 1, i = ~ !is.na(common_name) ) %>% 
  flextable::add_header(
    x = .,
    values = eval(parse(text = paste0("list(", 
                                      text_list(paste0(names(table_raw), " = '", h_r1, "'"), 
                                                sep_last = ", ", sep_last2 = ", "), ") " ) ) ), 
    top = TRUE) %>%
  flextable::set_header_labels(
    x = .,
    values = eval(parse(text = paste0("list(", 
                                      text_list(paste0(names(table_raw), " = '", h_r2, "'"), 
                                                sep_last = ", ", sep_last2 = ", "), ") " ) ) ), 
    # year = "Year",
    # common_name = "Common name", 
    # biomass_EBS = "Biomass (mt)", 
    # population_EBS = "Population (x1,000)", 
    # biomass_NBS = "Biomass (mt)", 
    # population_NBS = "Population (x1,000)"
  )  %>%
  flextable::merge_h(i = c(1), part = "header") %>%
  flextable::align(i = 1, align = "center", part = "header") %>% 
  flextable::vline(j = "population_EBS", part = "all") %>% 
  # make all biomass and population columns green
  flextable::bg(x = ., bg = positive, 
                j = c(which(grepl(x = names(table_raw), pattern = "biomass")),
                      which(grepl(x = names(table_raw), pattern = "population")))) %>%
  # EBS biomass
  flextable::bg(x = ., bg = negative,
                i = ~ grepl(pattern = "-", x = biomass_EBS),
                j = c("biomass_EBS")) %>%
  flextable::bg(x = ., bg = "white",
                i = ~ (is.na(biomass_EBS) | 
                         grepl(pattern = "\\(0%)", x = biomass_EBS) | 
                         !grepl(pattern = "%)", x = biomass_EBS)) ,
                j = c("biomass_EBS")) %>% 
  # EBS population
  flextable::bg(x = ., bg = negative,
                i = ~ grepl(pattern = "-", x = population_EBS),
                j = c("population_EBS")) %>%
  flextable::bg(x = ., bg = "white",
                i = ~ (is.na(population_EBS) | 
                         grepl(pattern = "\\(0%)", x = population_EBS) | 
                         !grepl(pattern = "%)", x = population_EBS)) ,
                j = c("population_EBS")) %>% 
  flextable::padding(padding = 5) %>% 
  flextable::valign(x = ., valign = "top", part = "body", 
                    j = c(which(grepl(x = names(table_raw), pattern = "biomass")),
                          which(grepl(x = names(table_raw), pattern = "population"))) ) %>%
  flextable::fontsize(x = .,  size = 14, part = "header") %>%
  flextable::fontsize(x = .,  size = 12, part = "body") %>%
  flextable::fontsize(x = .,  size = 14, part = "body", j = 1) %>%
  flextable::hline_bottom(x = ., part = "body",
                          border = fp_border(color = "transparent", style = "solid", width = 1))

if (SRVY == "NEBS") {
  table_print <- table_print  %>% 
    # NBS biomass
    flextable::bg(x = ., bg = negative,
                  i = ~ grepl(pattern = "-", x = biomass_NBS),
                  j = c("biomass_NBS")) %>%
    flextable::bg(x = ., bg = "white",
                  i = ~ (is.na(biomass_NBS) | 
                           grepl(pattern = "\\(0%)", x = biomass_NBS) | 
                           !grepl(pattern = "%)", x = biomass_NBS)) ,
                  j = c("biomass_NBS")) %>% 
    # NBS biomass
    flextable::bg(x = ., bg = negative,
                  i = ~ grepl(pattern = "-", x = population_NBS),
                  j = c("population_NBS")) %>%
    flextable::bg(x = ., bg = "white",
                  i = ~ (is.na(population_NBS) | 
                           grepl(pattern = "\\(0%)", x = population_NBS) | 
                           !grepl(pattern = "%)", x = population_NBS)) ,
                  j = c("population_NBS"))
}
res <- knitr::knit_child(text = knitr::knit_expand( file = paste0(dir_code, "_child_save_figtab.Rmd")), quiet = TRUE)
```

# Appendix A and B

## tab_taxa_found_*_prep

```{r tab_app_taxa_found_*_prep}

tab_taxa_found_ <- function(temp, 
                            nickname0, 
                            maxyr, 
                            catch_haul_cruises_maxyr, 
                            spp_info) {
  
  list_tables0 <- list()
  
  cnt_tables <- 0
  nickname0 <- "tab-app-taxa-found-" 
  
  for (i in 1:nrow(temp)) {
    cnt_tables <- cnt_tables + 1
    newobj <- TRUE
    nickname <- paste0(nickname0, 
                       temp$SRVY[i], 
                       "-",  
                       temp$taxon[i])
    
    header <- paste0(stringr::str_to_sentence(temp$taxon[i]), 
                     " taxa encountered during the ", 
                     maxyr, " ", temp$SRVY_long[i], 
                     " bottom trawl survey listed alphabetically by ", 
                     ifelse(temp$taxon[i] == "fish", "family", "phylum"), ".")
    
    table_raw <- 
      dplyr::left_join(
        x = catch_haul_cruises_maxyr %>% 
          dplyr::filter(year == maxyr &
                          SRVY == temp$SRVY[i]) %>% 
          dplyr::select(station, latitude_dd_start, longitude_dd_start, depth_gear_m, species_code), 
        y = spp_info %>% 
          dplyr::rename(taxon0 = ifelse(temp$taxon[i] == "fish", "family", "phylum")) %>%
          dplyr::select(species_name, common_name, taxon, species_code, taxon0), 
        by = "species_code") %>% 
      dplyr::filter(taxon == temp$taxon0[i]) %>% 
      dplyr::mutate(taxon = taxon0) %>% 
      dplyr::group_by(taxon, species_name, common_name ) %>% 
      dplyr::summarise(stations_n = n(), 
                       depth_min = min(depth_gear_m, na.rm = TRUE), 
                       depth_max = max(depth_gear_m, na.rm = TRUE), 
                       depth_mean = mean(depth_gear_m, na.rm = TRUE), 
                       lat_min = min(latitude_dd_start, na.rm = TRUE), 
                       lat_max = max(latitude_dd_start, na.rm = TRUE)) %>% 
      dplyr::ungroup() %>% 
      dplyr::arrange(species_name)  %>%
      dplyr::arrange(taxon)  %>%
      dplyr::mutate(stations_n = formatC(stations_n, big.mark=",", digits = 0, format = "f"))  %>%
      dplyr::mutate(across(c("lat_min", "lat_max", "depth_mean"), 
                           formatC, big.mark=",", digits = 1, format = "f"), 
                    taxon = ifelse(is.na(taxon), "Other", taxon), 
                    across(c("depth_min", "depth_max"), 
                           formatC, big.mark=",", digits = 0, format = "f"))
    
    table_print <- table_raw %>% 
      dplyr::mutate(species_name1 = species_name) %>%
      dplyr::mutate(spp = dplyr::case_when(
        grepl(pattern = "sp.", x = species_name1, fixed = TRUE) ~ "sp.", 
        grepl(pattern = "spp.", x = species_name1, fixed = TRUE) ~ "spp.", 
        grepl(pattern = "egg case", x = species_name1, fixed = TRUE) ~ "egg case", 
        grepl(pattern = "Naticidae egg", x = species_name1, fixed = TRUE) ~ "gastropod egg", 
        grepl(pattern = "gastropod egg", x = species_name1, fixed = TRUE) ~ "gastropod egg", 
        grepl(pattern = "hybrid", x = species_name1, fixed = TRUE) ~ "hybrid", 
        grepl(pattern = "Polychaete tubes", x = species_name1, fixed = TRUE) ~ "Polychaete tubes", 
        TRUE ~ "")) %>%
      dplyr::mutate(
        spacer = "",
        species_name = species_name1, 
        species_name1 = 
          gsub(pattern = " sp.", replacement = "", 
               x = species_name1, fixed = TRUE), 
        species_name1 =
          gsub(pattern = " spp.", replacement = "",
               x = species_name1, fixed = TRUE),
        species_name1 =
          gsub(pattern = " egg case", replacement = "",
               x = species_name1, fixed = TRUE),          
        species_name1 =
          gsub(pattern = "Naticidae egg", replacement = "",
               x = species_name1, fixed = TRUE),  
        species_name1 =
          gsub(pattern = "gastropod egg", replacement = "",
               x = species_name1, fixed = TRUE),          
        species_name1 =
          gsub(pattern = " hybrid", replacement = "",
               x = species_name1, fixed = TRUE),    
        species_name1 =
          gsub(pattern = "Polychaete tubes", replacement = "",
               x = species_name1, fixed = TRUE),      
        species_name2 = dplyr::case_when(
          !grepl(pattern = " ", x = species_name, fixed = TRUE) ~ species_name1), 
        species_name1 = dplyr::case_when(
          grepl(pattern = " ", x = species_name, fixed = TRUE) ~ species_name1))
    
    table_print <- table_print %>%
      flextable::flextable(data = ., 
                           col_keys = c("taxon" ,
                                        "species_name",
                                        "common_name", "stations_n", 
                                        "depth_min", "depth_max", "depth_mean", 
                                        "spacer", "lat_min", "lat_max"))  %>%
      flextable::merge_v(x = ., j = ~ taxon) %>%
      flextable::merge_h_range(x = ., i = ~ is.na(taxon), j1 = "species_name", j2 = "taxon", part = "body") %>%
      flextable::compose(j = "species_name",
                         value = as_paragraph(as_i(species_name1), species_name2, " ", spp)) %>% # https://stackoverflow.com/questions/57474647/italic-and-color-in-an-r-flextable
      # flextable::width(x = ., j = "taxon", width = 0.5, unit = "in") %>%
      flextable::set_header_labels(., 
                                   values = list(
                                     taxon = "", #ifelse(temp$taxon[i] == "fish", "Family", "Phylum"),
                                     species_name = "", #"Scientific name",
                                     common_name = "", #"Common name",
                                     stations_n = "", #"Number stations present", 
                                     depth_min = "Min.", 
                                     depth_max = "Max.", 
                                     depth_mean = "Avg.", 
                                     spacer = " ", 
                                     lat_max = "S", 
                                     lat_min = "N")) %>%
      flextable::add_header_row(x = .,
                                top = TRUE,
                                values = c(ifelse(temp$taxon[i] == "fish", "Family", "Phylum"),
                                           "Scientific name", "Common name", "Number stations present",
                                           "Bottom depth (m)", "", "Latitude range"),
                                colwidths = c(1,1,1,1,3,1,2)) %>%
      flextable::align(i = 1, align = "center", part = "header")  %>%  
      flextable::merge_at(x = ., j = c("taxon"), part = "header") %>%
      flextable::merge_at(x = ., j = c("species_name"), part = "header") %>%
      flextable::merge_at(x = ., j = c("common_name"), part = "header") %>%
      flextable::merge_at(x = ., j = c("spacer"), part = "header") %>%
      flextable::merge_at(x = ., j = c("stations_n"), part = "header") %>%
      theme_flextable_nmfstm(x = ., 
                             font0 = font0, 
                             row_lines = TRUE, 
                             # body_size = 8, 
                             # header_size = 9, 
                             pad = 0, 
                             pgwidth = full_page_portrait_width) %>%
      # flextable::hline(x = ., part = "header") %>%
      flextable::width(x = ., width = .5, unit = "in") %>%
      # flextable::width(x = ., width = .75, j = "stations_n", unit = "in") %>%
      flextable::width(x = ., width = .1, j = c("spacer"), unit = "in") %>%
      flextable::width(x = ., width = 1, j = c("taxon", "common_name"), unit = "in") %>%
      flextable::width(x = ., width = 1.25, j = c("species_name"), unit = "in") %>%
      flextable::align(x = ., 
                       j = c("stations_n", "depth_min", "depth_max", "depth_mean", "lat_max", "lat_min"), 
                       align = "right", part = "all") %>%
      flextable::align(x = ., 
                       j = c("depth_max", "depth_min", "depth_mean", "lat_max", "lat_min"), 
                       align = "center", i = 1, part = "header") 
    
    # output from function
    list_tables0$temp <- list("table_print" = table_print, 
                              "table_raw" = table_raw, 
                              "header" = header, 
                              "nickname" = nickname)
    names(list_tables0)[names(list_tables0) == "temp"] <- nickname
  }
  
  return(list_tables0)
}

```


## Appendix A (EBS)

```{r tab-app-taxa-found-EBS}
temp <- tidyr::crossing(data.frame(taxon = c("invertebrate", "fish"), 
                                   taxon0 = c("invert", "fish")), 
                        haul_cruises_maxyr %>% 
                          dplyr::select(SRVY_long, SRVY) %>% 
                          dplyr::filter(SRVY == "EBS"))

# cnt_pre0 <- cnt_pre0 + 1; cnt_pre1 <- LETTERS[cnt_pre0]
list_tables0 <- tab_taxa_found_(temp = temp, 
                                # cnt_pre = cnt_pre, #paste0("Appendix ", cnt_pre), 
                                maxyr = maxyr, 
                                catch_haul_cruises_maxyr = catch_haul_cruises_maxyr, 
                                spp_info = spp_info) 
cnt_tables <- 0
for (i in 1:length(list_tables0)) {
  # cnt_pre <- cnt_pre1 # paste0("Appendix ", cnt_pre1)
  a <- list_tables0[[i]]
  for (jjj in 1:length(a)) { assign(names(a)[jjj], a[[jjj]]) }
  
  # Save table
  res <- knitr::knit_child(
    text = knitr::knit_expand(
      file = paste0(dir_code, "_child_save_figtab.Rmd")), 
    quiet = TRUE
  )
}

```

## Appendix B (NBS)

```{r tab-app-taxa-found-NBS}
if (SRVY == "NEBS") {
  temp <- tidyr::crossing(data.frame(taxon = c("invertebrate", "fish"), 
                                     taxon0 = c("invert", "fish")), 
                          haul_cruises_maxyr %>% 
                            dplyr::select(SRVY_long, SRVY) %>% 
                            dplyr::filter(SRVY == "NBS"))
  if (nrow(temp) != 0) {   
    list_tables0 <- tab_taxa_found_(temp = temp, 
                                    # cnt_pre = cnt_pre, #paste0("Appendix ", cnt_pre), 
                                    maxyr = maxyr, 
                                    catch_haul_cruises_maxyr = catch_haul_cruises_maxyr, 
                                    spp_info = spp_info) 
    
    cnt_tables <- 0
    for (i in 1:length(list_tables0)) {
      # cnt_pre <- cnt_pre1 # paste0("Appendix ", cnt_pre1)
      a <- list_tables0[[i]]
      for (jjj in 1:length(a)) { assign(names(a)[jjj], a[[jjj]]) }
      
      # Save table
      res <- knitr::knit_child(
        text = knitr::knit_expand(
          file = paste0(dir_code, "_child_save_figtab.Rmd")), 
        quiet = TRUE
      )
    }
  }
}
```

# Appendix C and D

## tab_fish_*_prep

```{r tab_app_fish_*_prep}

tab_app_fish_ <- function(temp, 
                          maxyr, 
                          haul_cruises_maxyr, 
                          report_spp1,
                          spp_info) {
  list_tables0 <- list()
  
  nickname0 <- "tab-app-fish-" 
  cnt_tables <- 0
  
  temp0 <- report_spp1 %>% 
    dplyr::filter(taxon == "fish" & 
                    text_spp == TRUE &
                    file_name != "pacific_halibut") %>% 
    dplyr::select(file_name, species_code) %>% 
    dplyr::distinct() 
  
  for (i in 1:nrow(temp)) {
    cnt_tables <- cnt_tables + 1
    print(temp$file_name[i])
    
    nickname <- paste0(nickname0, 
                       temp$SRVY[i], 
                       "-",  
                       temp$file_name[i])
    
    spp_code <- temp0$species_code[temp0$file_name == temp$file_name[i]]
    
    header <- paste0("Population estimates by sex and size for ",
                     temp$print_name[i], " (", temp$species_name[i], ")", 
                     " from the ", 
                     maxyr, " ", temp$SRVY_long[i], 
                     " bottom trawl survey.")
    
    table_raw <- sizecomp_maxyr %>% 
      dplyr::filter(species_code %in% spp_code &
                      SRVY == temp$SRVY[i]) %>% 
      dplyr::distinct() %>%
      dplyr::ungroup()
    
    if (nrow(table_raw) != 0) { 
      
      table_raw <- table_raw %>% 
        dplyr::select(length_mm, population_count, sex) %>%
        tidyr::pivot_wider(data = ., 
                           id_cols = length_mm, 
                           names_from = sex, 
                           values_from = population_count, 
                           values_fill = 0) 
      
      if (!("males" %in% names(table_raw))) {
        table_raw$males <- 0
      }
      if (!("females" %in% names(table_raw))) {
        table_raw$females <- 0
      }
      if (!("unsexed" %in% names(table_raw))) {
        table_raw$unsexed <- 0
      }
      
      table_raw <- table_raw %>%
        dplyr::mutate(
          total = males + females + unsexed) %>%
        dplyr::arrange(length_mm) %>% 
        dplyr::ungroup() %>% 
        dplyr::mutate(
          prop = total/sum(total, na.rm = TRUE), 
          cumprop = cumsum(prop))

      table_raw <- 
        dplyr::bind_rows(table_raw %>% 
                           dplyr::mutate(length_mm = as.character(length_mm)), 
                         table_raw %>%
                           dplyr::summarise(across(everything(), ~ sum(., is.na(.), 0))) %>% 
                           dplyr::mutate(length_mm = "Total", 
                                         cumprop = 1))  %>%
        dplyr::mutate(across((ends_with("prop")), 
                             formatC, big.mark=",", digits = 4, format = "f")) %>%
        dplyr::mutate(across(where(is.numeric), 
                             formatC, big.mark=",", digits = 0, format = "f"))
      
      table_print <- table_raw %>%
        flextable::flextable(data = .) %>% 
        flextable::set_header_labels(.,
                                     length_mm = "Length (cm)",
                                     males = "Males",
                                     females = "Females",
                                     unsexed = "Unsexed", 
                                     total = "Total", 
                                     prop = "Proportion", 
                                     cumprop = "Cumulative proportion") %>%
        flextable::align(i = 1, align = "center", part = "header")  %>%  
        flextable::bold(x = ., i = nrow(table_raw), part = "body") %>%
        theme_flextable_nmfstm(x = ., 
                               font0 = font0, 
                               row_lines = FALSE, 
                               pad = 0, 
                               pgwidth = full_page_portrait_width) %>%
        flextable::width(x = ., width = .9, unit = "in") %>% 
        flextable::hline_bottom(x = ., border = fp_border(width = 2), part = "header")
      
      list_tables0$temp <- list("table_print" = table_print, 
                                "table_raw" = table_raw, 
                                "header" = header, 
                                "nickname" = nickname)
      names(list_tables0)[names(list_tables0) == "temp"] <- nickname
    }
  }
  return(list_tables0)
}
```


## Appendix C (or B if EBS only) (EBS)

```{r tab-app-fish-EBS}
temp <- tidyr::crossing(haul_cruises_maxyr %>% 
                          dplyr::select(SRVY_long, SRVY) %>% 
                          dplyr::filter(SRVY == "EBS"), 
                        report_spp1 %>% 
                          dplyr::filter(taxon == "fish" & text_spp == TRUE) %>% 
                          dplyr::select(file_name, print_name, common_name1, species_name)  %>% 
                          dplyr::mutate(species_name = gsub(species_name, pattern = " larva", replacement = "")) %>% 
                          dplyr::distinct())

list_tables0 <- tab_app_fish_(
  temp = temp, 
  maxyr = maxyr, 
  haul_cruises_maxyr = haul_cruises_maxyr, 
  report_spp1 = report_spp1,
  spp_info = spp_info)

cnt_tables <- 0
for (i in 1:length(list_tables0)) {
  a <- list_tables0[[i]]
  for (jjj in 1:length(a)) { assign(names(a)[jjj], a[[jjj]]) }
  
  # Save table
  res <- knitr::knit_child(
    text = knitr::knit_expand(
      file = paste0(dir_code, "_child_save_figtab.Rmd")), 
    quiet = TRUE
  )
}
```

## Appendix D (NBS)

```{r tab-app-fish-NBS}
if (SRVY == "NEBS") {
  temp <- tidyr::crossing(haul_cruises_maxyr %>% 
                            dplyr::select(SRVY_long, SRVY) %>% 
                            dplyr::filter(SRVY == "NBS"), 
                          report_spp1 %>% 
                            dplyr::filter(taxon == "fish" & text_spp == TRUE) %>% 
                            dplyr::select(file_name, print_name, common_name1, species_name) %>% 
                          dplyr::mutate(species_name = gsub(species_name, pattern = " larva", replacement = "")) %>% 
                            dplyr::distinct())
  if (nrow(temp) != 0) {   
    list_tables0 <- tab_app_fish_(
      temp = temp, 
      maxyr = maxyr, 
      haul_cruises_maxyr = haul_cruises_maxyr, 
      report_spp1 = report_spp1,
      spp_info = spp_info)
    
    cnt_tables <- 0
    for (i in 1:length(list_tables0)) {
      a <- list_tables0[[i]]
      for (jjj in 1:length(a)) { assign(names(a)[jjj], a[[jjj]]) }
      
      # Save table
      res <- knitr::knit_child(
        text = knitr::knit_expand(
          file = paste0(dir_code, "_child_save_figtab.Rmd")), 
        quiet = TRUE
      )
    }
  }
}
```


