---
output:
  word_document:
    pandoc_args: ["--metadata-file=header.yaml"]
    reference_docx: styles_reference.docx
    df_print: kable
csl: "../cite/citestyle.csl"
bibliography: "../cite/bibliography.bib"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, error = FALSE, message = FALSE)
```

### `r spp.common` (*`r spp.sci`*)

Walleye pollock were captured at 98% of the stations sampled in the EBS and NBS. Catch rates were lowest in the inner shelf, and highest north of 56°N and west of 173°W where bottom depths were greater than 70 m and bottom water temperatures were above -1°C (Figure 7). The total estimated biomass of walleye pollock in the EBS was 4.81 million t (Table 7a), which was a 2% decrease from the 2016 estimate of 4.91 million t. The lower biomass corresponded to a 1% decrease in population size from 8.53 billion to 8.48 billion fish (Table 7b). The biomass and population size in the NBS were smaller than that of the EBS with 1.32 t and 1.83 billion fish.

One-year-old pollock, represented by lengths ranging from 10 to 20 cm, had a modal peak of 127 million in the EBS and 47 million in the NBS (Figure 8). These 10-20 cm juveniles were mostly found at stations where catch rates were less than 75 kg/ha (Figure 9) and they were generally segregated from larger adults (> 40 cm) in the middle and outer shelf. The abundance-at-size plot of pollock in both the NBS and EBS inner shelf shows a large mode of age-1 pollock followed by a large gap and then a small mode of much larger pollock having lengths greater than 60 cm (Figure 10). Age-2 and age-3 pollock (length range of 20-40 cm) are generally underrepresented in survey trawl catches; however, relatively small modes for both year classes are present in the plot of abundance-at-size (Figure 10). 


```{r fig.width=8, fig.height = 6, fig.cap=paste0("Figure 1. -- Sampling grid and station identifiers for the ", maxyr, " eastern and northern Bering Sea continental shelf bottom trawl surveys.")}

SEBS <- get_base_layers(select.region = "bs.south", set.crs = "auto")
# class(SEBS)
# names(SEBS)

temp<-dat[dat$YEAR %in% maxyr, ]
temp<-unique(temp[,c("VESSEL", "STATION", "LATITUDE", "LONGITUDE", "STRATUM")])


(SEBS_plot <- ggplot() +
  geom_sf(data = SEBS$akland) +
  geom_sf(data = SEBS$bathymetry) +
  geom_sf(data = SEBS$survey.area, fill = NA) +
  geom_sf(data = SEBS$graticule, color = "grey70", alpha = 0.5) +
  coord_sf(xlim = SEBS$plot.boundary$x, 
           ylim = SEBS$plot.boundary$y) +
  scale_x_continuous(name = "Longitude", 
                     breaks = SEBS$lon.breaks) + 
  scale_y_continuous(name = "Latitude", 
                     breaks = SEBS$lat.breaks) + 
  geom_point(data = temp, mapping = aes(x = temp$LONGITUDE, y = temp$LATITUDE, 
                                        colour = factor(temp$VESSEL), shape = factor(temp$VESSEL))) +
  theme_bw())

# my_label <- data.frame(x = -165, y = 58, label = "Thar be\ndragons")
# SEBS_plot + geom_text(data = my_label, 
#                       mapping = aes(x = x, 
#                                     y = y, 
#                                     label = label), 
#                       color = "red")
# 
# my_label <- data.frame(x = -165, y = 58, label = "Thar be\ndragons") %>% 
#   akgfmaps::transform_data_frame_crs(in.crs = "+proj=longlat", out.crs = SEBS$crs)
# SEBS_plot + geom_text(data = my_label, 
#                       mapping = aes(x = x, 
#                                     y = y, 
#                                     label = label), 
#                       color = "red")


akgfmaps::YFS2017 %>% 
  make_idw_map(region = "bs.all",
               set.breaks = "jenks",
               grid.cell = c(0.02, 0.02)) %>%
  add_map_labels() %>% 
  change_fill_color(new.scheme = "purple2", show.plot = TRUE) %>%
  create_map_file(file.prefix = NA, 
                            file.path = NA, 
                            try.change_text_size = TRUE, # 12x9 is a pre-defined size
                            width = 12, 
                            height = 9, 
                            units = "in", 
                            res = 300, 
                            bg = "transparent")

yfs2017 <- akgfmaps::YFS2017

opt1 <- make_idw_map(x = yfs2017, # Pass data as a data frame
             region = "bs.all", # Predefined bs.all area
             set.breaks = "jenks", # Gets Jenks breaks from classint::classIntervals()
             grid.cell = c(0.02, 0.02), # 0.2x0.2 degree grid cells
             key.title = "yellowfin sole") # Include yellowfin sole in the legend title




eval_plot_breaks(CPUE = yfs2017$CPUE_KGHA, n.breaks = 5)

yfs.opt1 <- make_idw_map(x = yfs2017,
             region = "bs.all",
             set.breaks = "jenks",
             grid.cell = c(0.05, 0.05), # Coarse grid
             key.title = "yellowfin sole")

yfs.opt2 <- make_idw_map(x = yfs2017,
             region = "bs.all",
             set.breaks = "kmeans", 
             grid.cell = c(0.05, 0.05), # Coarse grid
             key.title = "yellowfin sole")

yfs.opt3 <- make_idw_map(x = yfs2017,
             region = "bs.all",
             set.breaks = c(0, 25, 100, 250, 500, 1000),
             grid.cell = c(0.05, 0.05), # Coarse grid
             key.title = "yellowfin sole")
yfs.opt3$plot

```


 
Pacific Cod (Gadus macrocephalus)
Pacific cod were broadly distributed across the EBS and NBS shelf and were present at 99% of the sampled stations compared to the slightly more concentrated distribution in the NBS, where they were present at 78% of the stations (Figure 9). The biomass of Pacific cod in the EBS was 0.64 million t (Table 8a), which 35% less than the 2016 estimate, and population numbers decreased 45% to 364 million (Table 8b). The biomass and population size in the NBS were larger than in 2010 with 283,479 t and 133.5 million fish (Table 8a, b), although only 37% of the Pacific cod in the NBS were over 60 cm in length (Figure 10). 
 
Yellowfin Sole (Limanda aspera)
Yellowfin sole were distributed across the shelf to a bottom depth of 100 m with highest catch rates occurring in Bristol Bay and along the inner shelf from the Alaska Peninsula north to St. Lawrence Island (Table 9a, b; Figure 11). The biomass on the EBS shelf, where the world’s largest flatfish commercial fishery operates (Wilderbeur et al. 2010), decreased from 2.9 to about 2.8 million t (Table 9a) and the population number increased from 8.8 billion to 
9.7 billion (Table 9b). In the NBS, there was an additional 0.43 million t of yellowfin sole (Table 9a), but this area is not opened to large-scale commercial fishing. 
Yellowfin sole are segregated by depth based on size and sexual maturity (Nichol 1997, 1998). The size composition of yellowfin sole during the 2017 survey differed between the EBS and NBS, between the EBS middle and inner shelf, and between males and females on the EBS middle shelf (Figure 12). Sexually mature yellowfin sole undergo an annual spring-summer spawning migration across the shelf into the shallow waters of Bristol Bay and off Nunivak Island (Bakkala 1981) with most spawning activity occurring at bottom depths < 30 m (Nichol 1995). Sexually immature individuals, which can be up to 6-8 years old, undergo an ontogenetic migration rather than a spawning migration by moving deeper as they get older (Nichol 1997). Length or age at sexual maturity differs for males and females causing further size segregation among spawning and non-spawning portions of the population (Nichol 1998).
 
Northern Rock Sole (Lepidopsetta polyxystra)
Rock sole were broadly distributed across the shelf with highest concentrations in Bristol Bay and around the Pribilof Islands (Table 10a, b; Figure 13). From 2016, estimated biomass in the EBS decreased 9% to 1.33 million t (Table 10a) and the estimated population number increased by 10% to 5.3 billion (Table 10b). Less than 4% of the total shelf-wide biomass was in the NBS. Mean length of rock sole increased slightly moving deeper across the EBS shelf in contrast to the NBS where the mean size was very similar to EBS outer shelf (Figure 14). Spawning and feeding migrations for rock soles are poorly understood, but in general it is believed that rock sole use active tidal stream transport during nighttime hours (Nichol and Somerton 2009) to migrate from shallow summer feeding grounds to deep winter and spring spawning grounds (Fadeev 1965, Shubnikov and Lisovenko 1964). 

Flathead Sole (Hippoglossoides elassodon)
Flathead sole and Bering flounder are members of the same genus, and they are difficult to distinguish based on appearance. Consequently, the accuracy of identifications in the commercial fishery data is unknown and the two species are combined into a single stock assessment by the NPFMC (Stockhausen et al. 2010). In contrast, BT survey scientists are trained to make reliable field identifications for flathead sole and Bering flounder; hence, results here are presented by species. Despite belonging to the same genus and having a similar appearance, the two species have entirely different geographic distributions (Figure 15; compare with Bering flounder below Figure 17). Flathead sole were present at 76% of the EBS stations and 1% of the NBS stations (Figure 15). The highest catch rates of flathead sole were at depths below 70 m and the estimated biomass in the EBS of 0.54 million t (Table 11a) and population number of 2.1 billion (Table 11b) were both increases from 2016 levels. A similar size range of flathead sole (10-50 cm) was observed at all depths and the mean length for the entire EBS shelf was 
26.5 cm (Figure 16). 

Bering Flounder (Hippoglossoides robustus)
Bering flounder is an arctic species with a distribution extending north into the Chukchi Sea (Mecklenburg et al. 2007). Bering Flounder were present at 21% of the EBS stations, and 66% of the NBS stations. The spatial distribution of Bering flounder in the EBS and NBS BT survey was mostly contained within an area where bottom water temperatures were between -2 and 4°C (Figure 17). The highest catch rates were in the middle shelf close to the U.S.-Russian Convention Line where bottom water temperatures were below 0°C (Figure 17). The total estimated biomass for the EBS and NBS was 48,186 t (Table 12a) and the total population number was 363 million fish (Table 12b). Seventy-five percent of the total population consisted of juveniles measuring ≤ 20 cm (Figure 18). Within the last warm stanza, we have seen increasing Bering flounder biomass in the EBS in 2014 (19,749 t), 2015 (26,453 t), and 2016 (37,624 t), with a slight decrease in 2017 (27,404 t).

Alaska Plaice (Pleuronectes quadrituberculatus)
Alaska plaice were distributed throughout the inner and middle shelf from Bristol Bay to the Bering Strait with the highest densities found along the 50 m contour and south of 
St. Lawrence Island (Figure 19). The summer distribution of Alaska plaice appeared to be unaffected by bottom temperatures as Alaska plaice were distributed in areas of bottom temperatures ranging from -1 to > 6°C (Figure 19). Alaska plaice are well-adapted to sea water temperatures near the freezing point (-1.9°C) because they are capable of synthesizing an antifreeze glycoprotein to prevent ice crystal formation in their blood (Knight et al. 1991). 
Results from this year and previous AFSC trawl surveys show that females attain a maximum length about 10 cm greater than males, and that the proportion of males in the population increases with decreasing bottom depth (Figure 20, Zhang et al. 1998). Males were only made up 3% of the population on the EBS outer shelf but increased to 46% of the population on the middle shelf and 59% of the population on the inner shelf (Figure 20).
 In 2017, the estimated biomass of Alaska plaice in the EBS was 491,050 t (666 million fish) with an additional 324,264 t (496 million fish) in the NBS (Table 13a, b). Biomass estimates on the EBS shelf alone have fluctuated between 423,000 t and 642,000 t over the past 20 years. Alaska plaice biomass increased 15% and the population size increased 18% from 2016 (425,217 t, 565 million) to 2017 (491,050 t, 666 million). It is evident from the expanded coverage during the NBS surveys in 2010 and 2017 survey that a large proportion of Alaska plaice can occupy the area north of the standard annual EBS survey. Interpreting a meaningful relative trend in Alaska plaice abundance in the EBS time series is difficult without more knowledge about the variability in seasonal migratory patterns of Alaska plaice between the EBS and NBS. 

Greenland Turbot (Reinhardtius hippoglossoides)
Greenland turbot has a circumpolar distribution and, on the Pacific side, is most abundant in the Bering Sea continental shelf and upper slope (Allen and Smith 1988). Greenland turbot were caught at 18% of the EBS stations and 2% of the NBS stations. The total estimated biomass on the Eastern Bering Sea continental shelf was 21,519 t (Table 14a) with the highest catch rates of Greenland turbot in the northernmost section of the EBS outer and middle shelf (Figure 21). 52.4 percent of the total shelf biomass was on the EBS outer shelf, 47.3% on the middle shelf, and the remaining 0.3% on the combined EBS inner shelf and the NBS (Table 14a, Figure 21). The estimated number of Greenland turbot on the EBS shelf was 10.5 million (Table 14b) which was 25% less than the population estimate in 2016 (14.1 m). Generally, the majority of the Greenland turbot caught on the EBS shelf BT survey are smaller than 50 cm, and a majority of Greenland turbot caught on the EBS continental slope BT survey are > 60 cm (Figure 67 in Hoff and Britt 2011). However, in 2017, 24% of the Greenland turbot caught in the EBS survey were 50 cm or less, and 76% were 51 cm or greater (Figure 22). In general, the maximum size of Greenland turbot differs by sex being about 80 cm for males and 110 cm for females.
Sizes-at-age extrapolated from lengths of Greenland turbot observed in BT surveys (Gregg et al. 2006, Ianelli et al. 2010) are consistent with a hypothesized framework for spawning, recruitment, and ontogenetic migration (Alton et al. 1988, Sohn et al. 2010). Greenland turbot spawn on the continental slope between Unimak Pass and the Pribilof Islands (Alton et al. 1988). Once hatched from eggs, the larvae and juveniles undergo a prolonged pelagic phase drifting northward in the Bering Slope Current to the vicinity of St. Matthew Island, where they settle on nursery grounds (Sohn et al. 2010). After spending 4 to 5 years on the shelf, Greenland turbot undergo an ontogenetic migration down the slope and back toward the spawning area in the south (Alton et al. 1988). 

Arrowtooth Flounder (Atheresthes stomias)
Arrowtooth flounder were not present within the NBS but were distributed in the EBS along the outer shelf and at the deeper end of the middle shelf with a small portion of the population in southern Bristol Bay (Figure 23). The cross-shelf spatial distribution of arrowtooth flounder may be affected by the extent of the cold bottom water ≤ 1°C on the EBS middle shelf. In 2017, a warm year, the highest catch rates were seaward of the 1°C isotherm and arrowtooth flounder were caught at 63% of the stations sampled in the middle shelf (Figure 25). In contrast, in colder years, arrowtooth flounder were caught at less than half of the stations sampled in the middle shelf. In 2005, another warm year on record, arrowtooth flounder were more broadly distributed across the middle shelf south of the 1°C isotherm near St. Matthew Island (Lauth and Acuna 2007). 
The 2017 estimates of total survey biomass decreased 11% from 0.48 million t in 2016 to 
0.42 million t (Table 15a), as did the estimated survey population number from 0.84 billion in 2016 to about 0.74 billion in 2017 (Table 15b). The lengths of arrowtooth flounder ranged from 7 to 82 cm and the mean size for the population was 36.1 cm (Figure 24). In addition to being found on the shelf, arrowtooth flounder are broadly distributed along the EBS continental slope where lengths exceed 30 cm and the mean length is much higher (46.8 cm; Figure 69 in Hoff and Britt 2011). Similar to Greenland turbot, the maximum size of females (80 cm) is about 30 cm greater than males (50 cm; Figure 26 and Hoff and Britt 2011). Another consistent pattern evident in all Alaska BT surveys is that there is a higher ratio of females to males in BT catches, which may be due to males having a higher mortality rate than females (Wilderbuer et al. 2010).

Kamchatka Flounder (Atheresthes evermanni)
Kamchatka flounder are similar in appearance to the congeneric arrowtooth flounder (Yang 1988), and it wasn’t until 1994 that field characters were established to reliably distinguish between the two species during AFSC BT surveys. The spatial distribution of the two species overlap but Kamchatka flounder generally has higher catch rates on the northwest relative to the southeast shelf (Figure 25). Trends in relative abundance are similar but the biomass and population size of Kamchatka flounder are about one-tenth that of arrowtooth flounder. From 2016 to 2017, the total survey biomass of Kamchatka flounder decreased 13% from 55,324 to 48,084 t (Table 16a) and the population decreased 11% from 124 million to 111 million fish (Table 16b). The measured lengths of Kamchatka flounder on the EBS shelf ranged from 10 to 63 cm and had a mean of 32.2 cm (Figure 26). Similar to arrowtooth flounder, the portion of the Kamchatka flounder population inhabiting the EBS slope has a greater mean length (55.2 cm; Hoff and Britt 2011) than on the shelf and females attain a greater maximum size (Figure 26). A characteristic that distinguishes Kamchatka from arrowtooth flounder is that the proportion of females to males in the Kamchatka flounder population is roughly equal (Figure 26).

Pacific Halibut (Hippoglossus stenolepis)
Pacific	halibut were present at 69% of the stations sampled in the EBS with the highest density catches near the Pribilof Islands, Nunivak, and along the inner southeastern half of the shelf (Figure 27). Other than some relatively high catch rates north of Nunivak Island close to shore (Figure 27), where bottom water temperatures were > 6°C (Figure 6), Pacific halibut were scarce in the NBS being present at only 27% of the stations sampled. The 2017 estimated biomass of 126,684 t (Table 17a) was 18% less than the estimated biomass in 2016 (153,704 t). The 2017 population of 53 million halibut (Table 17b) was 20% less than the population estimate in 2016 (66 million). Pacific halibut biomass has shown a decreasing trend since 2010 and abundance since 2006. Additionally, Pacific halibut size-at-age has been decreasing since the 1990s.
Research and management of Pacific halibut stocks is the responsibility of the IPHC and their stock assessments include all available fisheries and scientific survey data from the U.S. and Canada (Hare 2010). The AFSC BT survey provides an important estimate of Pacific halibut abundance-at-length on the EBS shelf, especially for tracking strong incoming year classes. However, the BT survey gear is size-selective for Pacific halibut (< 100 cm; Figure 28) and an adjustment for size-selectivity must be made before BT data from the EBS shelf can be incorporated into the Pacific halibut stock assessment model (Hare 2010). In 2006, the IPHC standardized setline survey added 100 EBS shelf stations for a comparison to the area swept estimates from our BT survey (Clark and Hare 2007). The comparison study was used to derive a size selectivity schedule that was applied to the EBS BT survey data to create an index of shelf abundance for the Pacific halibut stock assessment model (Hare 2010).
